### 2021-02-23 ofv_fife_2021.Rmd
Add files via upload
Draft of article for submission to the Journal of Integrated Pest Management, Category: 'Issues'

---
title: "For submission to the Journal of Integrated Pest Management"
subtitle: "Category: 'Issues'"
output: 
  word_document:
    reference_docx: ../r-templates/word-template-jis.docx
# - html_document
bibliography: 'thesis.bib'
csl: 'j_med_entomol.csl'
#always_allow_html: true
---
```{r setup, include=FALSE}
#setup options
knitr::opts_chunk$set(fig.width=12, fig.height=8, echo=FALSE)

#a list of packages used for scripts
pkgs <- c('captioner', 'pryr', 'tiff')

#loading required packages
lapply(pkgs, library, character.only = TRUE)
rm(pkgs)

#setting up captions for use in the document
fig_nums <- captioner::captioner(prefix = 'Fig.')
tab_nums <- captioner::captioner(prefix = 'Table')

#allows me to use a custom function instead of the citation function of captioner, which is wordy to use
citef <- pryr::partial(fig_nums, display = "cite")
citet <- pryr::partial(tab_nums, display = "cite")
```

### First report of the *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) virus, *Orchid fleck dichorhavirus* (Mononegavirales: Rhabdoviridae) infecting various Nolinoideae in the Florida panhandle

Austin **Fife**^1^, Daniel **Carrillo**^2^, Gary **Knox**^3^, Fanny **Iriarte**^4^, Kishore **Dey**^5^, Avijit **Roy**^6^, Ronald **Ochoa**^6^, Gary **Bauchan**^7^ $\dagger$, Mathews **Paret**^4^, Xavier **Martini**^1^\*

^1^ University of Florida, Department of Entomology and Nematology, North Florida Research and Education Center, Quincy FL 32351

^2^ University of Florida, Department of Entomology and Nematology,Tropical Research and Education Center, Homestead FL 33031

^3^ University of Florida, Department of Environmental Horticulture, North Florida Research and Education Center, Quincy FL 32351

^4^ University of Florida, Department of Plant Pathology, North Florida Research and Education Center, Quincy FL 32351

^5^ The Florida Department of Agriculture and Consumer Services, Division of Plant Industry, Section of Plant Pathology, Doyle Conner Building, 1911 SW 34th street, Gainesville, FL 32608

^6^	United States Department of Agriculture - Animal and Plant Health Inspection Service, Systematic Entomology Laboratory 10300 Baltimore Ave, Bldg. 5 BARC-West, Beltsville, MD 20705

^7^	United States Department of Agriculture - Animal and Plant Health Inspection Service, Electron and Confocal Microscopy Unit, Bldg. 12  BARC-West, 10300 Baltimore Ave, Beltsville, MD 20705

*Corresponding author; E-mail: xmartini\@ufl.edu Phone: 850-875-7160 Fax: 352-846-6617

\pagebreak

### Abstract
Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the only known vectors of dichorhaviruses and transmit *Orchid fleck dichorhavirus* (OFV) in a persistent propagative manner. OFV is the type species for the genus *Dichorhavirus* and infects 50+ spp. of Orchidaceae, Nolinoideae, and *Citrus*.
During June 2020, we observed chlorotic ringspot symptoms on Giant Lilyturf (*Liriope* spp., cv. ‘Gigantea’) in the landscape of Leon County, Florida. We tested plant samples for a wide range of pathogens and ultimately identified the pathogen as *Orchid fleck dichorhavirus*. We took further samples from other *Liriope* spp., *Ophiopogon* spp., and *Aspidistra elatior* Blume (Asparagales: Nolinoideae) in Leon and Alachua county. All symptomatic plants tested positive for OFV. We recovered *Brevipalpus* mites from OFV-infected plants, which belong to the *Brevipalpus californicus* group, but may be a new subspecies associated with Nolinoideae.
Florida has various pest species of *Brevipalpus* and a diverse array of susceptible plant species in the landscape, both native and introduced. We suggest that OFV has a wide distribution in Florida which will continue to spread if unchecked, representing a potential threat for many plants of economic importance for Florida.

### Keywords:
false spider mite, flat mite, Brevipalpus-transmitted viruses, Liriope, Ruscaceae, Asparagaceae, orchid, Orchidaceae, pests, ornamental plants

### Body Text
*Orchid fleck dichorhavirus* (OFV) is the type species for the genus *Dichorhavirus*, a group of plant-infecting, bacilliform, nuclear rhabdoviruses composed of two segments of single-stranded, negative-sense RNA [@Amarasinghe2019; @Dietzgen2014; @Walker2018]. Other members of this genus are: *Citrus chlorotic spot dichorhavirus*, *Citrus leprosis N dichorhavirus*, *Clerodendrum chlorotic spot dichorhavirus* and *Coffee ringspot dichorhavirus* [@Dietzgen2018a]. Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the only known vector for dichorhaviruses [@Maeda1998]. These mites transmit OFV in a persistent propagative manner [@Kondo2003].

OFV-infected plants exhibit various symptoms dependent on the variety of plant infected as well as the strain of the virus [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns (see *`r citef("fig_1")`*).
<!-- These lesions are thought to be associated with the feeding sites of the mite vector [@cite]. Also, is it probably a sign of RNAi plant defenses: see Hull Plant Virology -->

OFV was first described infecting *Cymbidium* orchids in Japan [@Doi1977]. Many countries have reported OFV and OFV-like rhabdoviruses infecting orchids worldwide [@Kondo2003], including Australia [@Lesemann1971; @Lesemann1975; @Gibbs2000], Brazil [@Kitajima1974; @Kitajima2001], China [@Peng2017], Colombia [@Kubo2009b], Costa Rica [@FreitasAstua2002], Denmark [@Begtrup1972], Fiji [@Pearson1993], France [@Sauvetre2018], Germany [@Lesemann1975; @Petzold1971], Korea [@Chang1991, @Zheng2013], Paraguay [@RamosGonzalez2015], South Africa [@Blanchfield2001], the United States [@Blanchfield2001; @Bratsch2015] and Vanuatu [@Pearson1993]. The prevalence of OFV and its mite vector is thought to be associated with the movement of infected orchids [@Dietzgen2018a].

OFV naturally infects 50+ spp of Orchidaceae [@Kitajima2010; @Peng2013], some Nolinoideae [@Mei2016, @Dietzgen2018b], and *Citrus* [@BeltranBeltran2020; @GarciaEscamilla2018 @Roy2020]. Mechanical transmission of OFV is possible under lab conditions to various *Chenopodiaceae*, *Aizoaceae*, *Fabaceae*, and *Solanaceae* [@Chang1976; @Kondo2003; @Peng2013].

On June 2020, chlorotic ringspot symptoms were observed on the liriopogon Giant Lilyturf *Liriope* spp., cv. 'Gigantea' in the landscape of Leon County, Florida (see *`r citef("fig_1")`*). Liropogons belong to the plant family Asparagaceae, subfamily Nolinoideae, which includes various monocotyledonous lilliod plants [@Chase2009]. Liriopogons are native to southeastern Asia, encompassing the closely-related genera *Liriope* and *Ophiopogon*, which are characterized by evergreen, long grass-like leaves, and erect flowers which produce black, purple or blue, berry-like fruits, depending on the cultivar [@Lattier2014; @Fantz2015]. These characteristics have given rise to various common names, including: monkey grass, Aztec grass, lilyturf, mondo grass, etc. (see *`r citet("tab_1")`*). The genus *Liriope* contains eight species, four of which are commonly cultivated, while the genus *Ophiopogon* consists of about 65 species, with only a handful which are commonly cultivated [@Lattier2014; @Nesom2010]. Liripogons are considered the most important ground cover sold by the nursery industry in southeastern US [@Mcharo2003].

Plant samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL. The plant samples were tested for a wide range of pathogens, including **[Ask Dr. Iriarte]** but the results were inconclusive. The infected materials were subsequently sent to the Florida Department of Agriculture and Consumer Services (FDACS). The pathogen was identified as *Orchid fleck dichorhavirus* via RT-qPCR with a partial sequence match, following the procedures described by @Kubo2009b. **[Which primers were used?]** Further samples were taken from other *Liriope* spp., *Ophiopogon* spp., as well as *Aspidistra elatior* Blume (Asparagales: Nolinoideae) in Leon county. All symptomatic plants were tested positive for OFV. **[Mention the different strains?]**

More cases of OFV-infected Nolinoideae were observed in subsequent visits to the initial site of collection. After a brief search, it appears that the disease is widely distributed in Florida, with symptomatic plants found in Leon, Alachua and Duval counties.

In addition to the discovery of the OFV-infected plants, our lab collected mites from symptomatic plants in Leon county and observed with phase contrast microscopy at the NFREC. We encountered both eriophyoid mites and flat mites which were initially identified as *Brevipalpus californicus* (Banks) *sensu lato*. *Brevipalpus* mites have been previously associated with OFV [@BeltranBeltran2020; @GarciaEscamilla2018; @Dietzgen2018b] and similar diseases [@Kitajima2010] and are known to feed on a large variety of economically-important plants [@Childers2003a; @Akyazi2017]. To verify our identification, we sent the flat mite samples to the FDACS. FDACS used the more advanced techniques of Differential Interference Contrast (DIC) microscopy to verify that our mites belonged to the *B. californicus* group. Unfortunately, even this verification needed further validation, because the *Brevipalpus* mite species complex is known to contain cryptic species [@Childers2011] whose identification can be improved with molecular methods as well as more advanced microscopy techniques, such as low-temperature scanning electron microscopy (LT-SEM) [@Skoracka2015; @Leon2010]. With that in mind, we sent additional samples of the mites to the USDA-ARS in Beltsville, where LT-SEM techniques revealed these mites as a possibly new subspecies of the *B. californicus* group (see *`r citef("fig_2")`*).

The earliest mention of a virus which may have been OFV is @Ko1985, who detected nuclear inclusions caused by an undescribed bacilliform rhabdovirus. @Ko1985 described the spoke-wheel configurations typically associated with OFV (see [@Chang1976]), in *Brassia* orchids, but unfortunately made no mention of mites or further investigations of this virus.

The first certain report of OFV in the US was made by @Bratsch2015, who confirmed the presence of OFV in *Phalaenopsis* hybrids in the US, using TEM of ultrathin sections of plant tissue as well as molecular sequence analysis. In addition, @Bratsch2015 detected *Brevipalpus* mites and their exoskeletons associated with OFV-infected plants. It appears that @Bratsch2015 did not make a conclusive species identification, but did cite @Kondo2003, suggesting that they suspected *B. californicus* as their vector.

OFV has been reported in other Nolinoideae in Australia [@Dietzgen2018b; @Mei2016], including *Liriope spicata* (Thunb.) Lour. [@Mei2016]. We are not aware of any record which reports OFV infection in *Ophiopogon* plants. Unfortunately, liriopogons species are very similar in appearance and growth habit, with few useful characters used for their classification [@Fantz2008a]. Furthermore, the horticultural industry has created a diverse array of cultivars of these plants, which are often mislabeled [@Fantz2008a]. Aside from the horticultural confusion created by humans, natural hybrids between *Ophiopogon* and *Liriope* have created another source of confusion for phylogeny [@Zhou2009]. Together, these factors make it difficult to differentiate and identify species in the landscape. This taxonomic confusion may be accounted for in the future via sequence comparisons of the OFV-infected plants, but these comparisons are beyond the scope of our current report. Nonetheless, we are confident that ours is the first report of OFV infecting *Aspidistra elatior*; although [@Zheng2013] mentions the association of *B. californicus* with *A. elatior* they make no mention of OFV symptoms in this plant.

Detecting OFV in Florida represents a concern for horticulturalist which grow susceptible plants of economic importance such as *Liriope*, *Ophiopogon*, and other susceptible Asparagales spp. which are commonly used in landscaping. Florida is also home to a plethora of native and naturalized orchid species, many of which are threatened, including the famous Ghost Orchid, *Dendrophylax lindenii* (Lindl.) Benth. ex Rolfe. Furthermore, OFV represents an obstacle to overcome for the burgeoning interest in cultivating Vanilla in southern Florida [@Chambers2019]. Lastly, some OFV isolates are known to be involved with nuclear types of Citrus Leprosis [@Roy2015a], which may be a cause for concern for the citrus industry. In fact, @Kitajima2011a found that the Citrus Leprosis virus (CiLV) which previously affected Florida citrus was a nuclear type of citrus leprosis, which are closely related to OFV strains [@Roy2013a]. *B. californicus* and *B. yothersi* are both known vectors of Dichorhaviruses (OFV) and Cileviruses (Citrus Leprosis) [@BeltranBeltran2020; @Kondo2003; @Knorr1968] and *B. obovatus* is a suspected vector as well [@Childers2003a]. All three mite species/complexes are present in Florida [@Childers2003a; @Akyazi2017] (see *`r citef("fig_3")`*), therefore it is critical to monitor the spread of Orchid Fleck Virus and its mite vector(s) to determine what risk this virus represents for plants in Florida and the surrounding regions.

### Control Options

*Galendromus helveolus* (Acari: Phytoseiidae) have been reported to feed on eggs, larvae and nymphs of *B. californicus* [@Chen2006].

*Metarhizium anisopliae* var. *acridum* has been shown to be pathogenic to *B. phoenicis* [@Magalhaes2005], we have encountered similar fungal infections

### Figures and Tables

```{r, fig_1, warning=FALSE}
grid::grid.raster(tiff::readTIFF( "images/fig_1.tif"))
```
`r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by plants infected with Orchid fleck dichorhavirus: (a) ringspot symptoms on *Liriope gigantea* (b) chlorosis on *Aspidistra elatior*.")`

```{r, fig_2, warning=FALSE}
grid::grid.raster(tiff::readTIFF( "images/b_cali.tif"))
```
`r fig_nums(name = "fig_2", caption = "LT-SEM images of *Brevipalpus californicus* sensu lato used for identification (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with paired solenidia (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum LT-SEM images provided by Dr. Gary Bauchan, USDA-ARS 2021")`

```{r, fig_3, warning=FALSE}
grid::grid.raster(tiff::readTIFF( "images/other_mites.tif"))
```
`r fig_nums(name = "fig_3", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B. yothersi*, dorsal (b) *B. yothersi*, lateral (c) *B. obovatus*, dorsal")`

|Scientific Name|Common Names|Symptoms Observed|
|:-----------|:--------------|:----------------|
|*Liriope muscari* Bailey| Lilyturf, Orchardgrass, Monkeygrass| Ringspots, Chlorotic Flecking, Necrotic Lesions|
|*Liriope gigantea*\* Hume| Giant Lilyturf| Ringspots, Chlorotic Flecking, Necrotic Lesions|
|*Ophiopogon japonicus* Ker Gawl.| Dwarf Lilyturf, Mondo Grass, Snake's beard| Ringspots, Chlorotic Flecking, Necrotic Lesions|
|*Ophiopogon intermedius*\*\* Don| Aztec Grass, 'Argenteomarginatus' | Ringspots, Chlorotic Flecking, Necrotic Lesions|
|*Aspidistra elatior* Blume| Cast Iron Plant, Bar-room Plant | Chlorosis, Necrotic Lesions|
`r tab_nums(name = "tab_1", caption = "List of plants with symptoms of Orchid fleck dichorhavirus found in northern Florida. * *L. gigantea* have been traditionally classified as seperate from *L. muscari* by @Broussard2007 and @Fantz2015, although this distinction has been challenged by @Wang2014 and @Masiero2020. * * *O. intermedius* is sometimes misclassified as *Liriope muscari* ‘Variegated Evergreen Giant’ [@Fantz2008b, @Fantz2009] or ‘Grandiflora White’ [@Fantz2009].")`

### Acknowledgements
We thank Dr. Sam Bolton for confirmation of the mite group.
We are especially indebted to the late Dr. Gary Bauchan for permitting us to use these beautiful LT-SEM images, he will be greatly missed. This research was partly funded by the USDA National Institute of Food and Agriculture, Hatch project FLA-NFC-005607.

### References

### 2021-02-23 test.Rmd
Add files via upload
Draft of article for submission to the Journal of Integrated Pest Management, Category: 'Issues'

---
title: "test"
author: "Austin N. Fife"
date: "2/22/2021"
output: 
  word_document:
    reference_docx: ../r-templates/word-template-jis-01.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-02-24 ofv_fife_2021.Rmd
Work done on work PC

@@
 All symptomatic plants tested positive for OFV.
-We recovered *Brevipalpus* mites from OFV-infected plants, which belong to the *Brevipalpus californicus* group, but may be a new subspecies associated with Nolinoideae.
+We recovered *Brevipalpus* mites from OFV-infected plants, which belong to *Brevipalpus californicus* sensu lato, associated with Nolinoideae.
 Florida has various pest species of *Brevipalpus* and a diverse array of susceptible plant species in the landscape, both native and introduced.
@@
 (see *`r citet("tab_1")`*).
-The genus *Liriope* contains eight species, four of which are commonly cultivated, while the genus *Ophiopogon* consists of about 65 species, with only a handful which are commonly cultivated [@Lattier2014; @Nesom2010].
+The genus *Liriope* contains eight species, four of which are commonly cultivated, while the genus *Ophiopogon* consists of about 65 species, with only a handful are available for horticulture [@Lattier2014; @Nesom2010].
 Liripogons are considered the most important ground cover sold by the nursery industry in southeastern US [@Mcharo2003].
 
-Plant samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL.
+Plant leaf samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL.
 The plant samples were tested for a wide range of pathogens, including **[Ask Dr.
@@
 The infected materials were subsequently sent to the Florida Department of Agriculture and Consumer Services (FDACS).
-The pathogen was identified as *Orchid fleck dichorhavirus* via RT-qPCR with a partial sequence match, following the procedures described by @Kubo2009b.
-**[Which primers were used?]** Further samples were taken from other *Liriope* spp., *Ophiopogon* spp., as well as *Aspidistra elatior* Blume (Asparagales: Nolinoideae) in Leon county.
-All symptomatic plants were tested positive for OFV.
-**[Mention the different strains?]**
+The presence of *Orchid fleck dichorhavirus* was confirmed via generic one step conventional RT-PCR with R2-Dicho-GF and R2-Dicho-GR primers, amplifying ~800 nt of L-gene (RNA2) amplicon from a leaf sample of infected *Liriope* [@Kubo2009b].
+RT-qPCR confirmed OFV and the RT-PCR product was sequenced using Sanger sequencing and High Throughput Sequencing [@Kondo2006].
+Sanger sequencing of RT-PCR amplicons shared 98 \% nucleotide identity with OFV strains which infect orchids (GenBank Accession numbers: AB244418 and MK522807) [@Kondo2006; @Kondo2014; @Cook2019].
+Further samples were taken from various symptomatic cultivars of *Liriope* spp., *Ophiopogon* spp., as well as *Aspidistra elatior* Blume (Asparagales: Nolinoideae) during subsequent visits to the initial site of collection as well as other locations in Leon county.
+Samples were tested via RT-PCR at the NFREC (see *`r citet("tab_1")`*) to confirm the presence of OFV.
 
-More cases of OFV-infected Nolinoideae were observed in subsequent visits to the initial site of collection.
-After a brief search, it appears that the disease is widely distributed in Florida, with symptomatic plants found in Leon, Alachua and Duval counties.
-
-In addition to the discovery of the OFV-infected plants, our lab collected mites from symptomatic plants in Leon county and observed with phase contrast microscopy at the NFREC.
-We encountered both eriophyoid mites and flat mites which were initially identified as *Brevipalpus californicus* (Banks) *sensu lato*.
+Further surveys of Nolinoideae in Florida have revealed more sites with symptomatic plants in both Leon and Alachua counties.
+In addition to the discovery of the OFV-infected plants, our lab at the NFREC collected mites from symptomatic plants in Leon county which were observed with phase contrast microscopy.
+We encountered both eriophyoid mites and flat mites which were identified as *Brevipalpus californicus* (Banks) sensu lato, an identity which was confirmed by the FDACS via Differential Interference Contrast (DIC) microscopy.
 *Brevipalpus* mites have been previously associated with OFV [@BeltranBeltran2020; @GarciaEscamilla2018; @Dietzgen2018b] and similar diseases [@Kitajima2010] and are known to feed on a large variety of economically-important plants [@Childers2003a; @Akyazi2017].
-To verify our identification, we sent the flat mite samples to the FDACS.
-FDACS used the more advanced techniques of Differential Interference Contrast (DIC) microscopy to verify that our mites belonged to the *B.
-californicus* group.
-Unfortunately, even this verification needed further validation, because the *Brevipalpus* mite species complex is known to contain cryptic species [@Childers2011] whose identification can be improved with molecular methods as well as more advanced microscopy techniques, such as low-temperature scanning electron microscopy (LT-SEM) [@Skoracka2015; @Leon2010].
-With that in mind, we sent additional samples of the mites to the USDA-ARS in Beltsville, where LT-SEM techniques revealed these mites as a possibly new subspecies of the *B.
-californicus* group (see *`r citef("fig_2")`*).
+Unfortunately, the *Brevipalpus* mite species complex is known to contain cryptic species [@Childers2011] whose identification can be improved with molecular methods as well as more advanced microscopy techniques, such as low-temperature scanning electron microscopy (LT-SEM) [@Skoracka2015; @Leon2010].
+With that in mind, we sent additional samples of the mites to the USDA-ARS in Beltsville to observe the mites with LT-SEM techniques, which agreed with both prior identifications of *B.
+californicus* s.l.
+(see *`r citef("fig_2")`*).
 
@@
 @Ko1985 described the spoke-wheel configurations typically associated with OFV (see [@Chang1976]), in *Brassia* orchids, but unfortunately made no mention of mites or further investigations of this virus.
-
 The first certain report of OFV in the US was made by @Bratsch2015, who confirmed the presence of OFV in *Phalaenopsis* hybrids in the US, using TEM of ultrathin sections of plant tissue as well as molecular sequence analysis.
@@
 [@Mei2016].
-We are not aware of any record which reports OFV infection in *Ophiopogon* plants.
+Our plants are thought to belong to different species of *Liriope* which are not *L.
+spicata* and we are not aware of any record which reports OFV infection in *Ophiopogon* plants.
 Unfortunately, liriopogons species are very similar in appearance and growth habit, with few useful characters used for their classification [@Fantz2008a].
 Furthermore, the horticultural industry has created a diverse array of cultivars of these plants, which are often mislabeled [@Fantz2008a].
-Aside from the horticultural confusion created by humans, natural hybrids between *Ophiopogon* and *Liriope* have created another source of confusion for phylogeny [@Zhou2009].
-Together, these factors make it difficult to differentiate and identify species in the landscape.
-This taxonomic confusion may be accounted for in the future via sequence comparisons of the OFV-infected plants, but these comparisons are beyond the scope of our current report.
+Aside from the taxonomic confusion created by humans, natural hybrids between *Ophiopogon* and *Liriope* have created a natural source of error for reconstructing phylogenies [@Zhou2009].
+Together, these factors make it difficult to differentiate and identify plants in the landscape by visual inspection alone.
+These obfuscations of species identity may be accounted for in the future via sequence comparisons of the OFV-infected plants, but these comparisons are beyond the scope of our current report.
 Nonetheless, we are confident that ours is the first report of OFV infecting *Aspidistra elatior*; although [@Zheng2013] mentions the association of *B.
@@
 
-Detecting OFV in Florida represents a concern for horticulturalist which grow susceptible plants of economic importance such as *Liriope*, *Ophiopogon*, and other susceptible Asparagales spp.
+Detecting OFV in Florida represents a concern for horticulturalists who grow susceptible plants of economic importance, including orchids, *Liriope*, *Ophiopogon*, or other susceptible Asparagales spp.
 which are commonly used in landscaping.
@@
 ex Rolfe.
-Furthermore, OFV represents an obstacle to overcome for the burgeoning interest in cultivating Vanilla in southern Florida [@Chambers2019].
+Furthermore, OFV represents an obstacle to overcome for the burgeoning interest in cultivating *Vanilla* in southern Florida [@Chambers2019].
 Lastly, some OFV isolates are known to be involved with nuclear types of Citrus Leprosis [@Roy2015a], which may be a cause for concern for the citrus industry.
@@
 ```
-`r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by plants infected with Orchid fleck dichorhavirus: (a) ringspot symptoms on *Liriope gigantea* (b) chlorosis on *Aspidistra elatior*.")`
+`r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by plants infected with Orchid fleck dichorhavirus: (a) ringspot symptoms on *Liriope gigantea* (b) chlorotic flecking on *Aspidistra elatior*.")`
 
@@
 ```
-`r fig_nums(name = "fig_2", caption = "LT-SEM images of *Brevipalpus californicus* sensu lato used for identification (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with paired solenidia (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum LT-SEM images provided by Dr.
+`r fig_nums(name = "fig_2", caption = "LT-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.
+LT-SEM images provided by Dr.
 Gary Bauchan, USDA-ARS 2021")`
@@
 yothersi*, lateral (c) *B.
-obovatus*, dorsal")`
+obovatus*, dorsal.
+SEM images provided by Dr.
+Ron Ochoa, USDA-ARS 2021")`
 
@@
 ### Acknowledgements
-We thank Dr. Sam Bolton for confirmation of the mite group.
+We would like to give a special thanks to the Tallahassee Museum for their patience, cooperation and support with collecting plant samples.
+We also want to thank Dr.
+Sam Bolton for checking the mites we have sent to FDACS for species validation.
 We are especially indebted to the late Dr.

### 2021-03-02 ofv_fife_2021.Rmd
Made minor change, waiting on Dr. Iriarte to send info on her methods
Accepted Dr. Martini's suggestions to the paper

@@
 
-### First report of the *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) virus, *Orchid fleck dichorhavirus* (Mononegavirales: Rhabdoviridae) infecting various Nolinoideae in the Florida panhandle
+### First report of the *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) virus, *Orchid fleck dichorhavirus* (Mononegavirales: Rhabdoviridae) infecting ornamental Nolinoideae in the Florida panhandle
 
@@
 
-^2^ University of Florida, Department of Entomology and Nematology,Tropical Research and Education Center, Homestead FL 33031
+^2^ University of Florida, Department of Entomology and Nematology, Tropical Research and Education Center, Homestead FL 33031
 
@@
 All symptomatic plants tested positive for OFV.
-We recovered *Brevipalpus* mites from OFV-infected plants, which belong to *Brevipalpus californicus* sensu lato, associated with Nolinoideae.
-Florida has various pest species of *Brevipalpus* and a diverse array of susceptible plant species in the landscape, both native and introduced.
-We suggest that OFV has a wide distribution in Florida which will continue to spread if unchecked, representing a potential threat for many plants of economic importance for Florida.
+We recovered mites from OFV-infected plants, which belonged to *Brevipalpus californicus* sensu lato.
+Florida has various mite species of *Brevipalpus* and a diverse array of susceptible plant species in the landscape, both native and introduced.
+We suggest that OFV already has a wide distribution in Florida which will continue to spread if unchecked, representing a potential threat for many plants of economic importance for Florida.
 
 ### Keywords:
-false spider mite, flat mite, Brevipalpus-transmitted viruses, Liriope, Ruscaceae, Asparagaceae, orchid, Orchidaceae, pests, ornamental plants
+false spider mite, flat mite, *Brevipalpus*-transmitted viruses, *Liriope*, Ruscaceae, Asparagaceae, orchid, Orchidaceae, pests, ornamental plants
 
@@
 
-OFV-infected plants exhibit various symptoms dependent on the variety of plant infected as well as the strain of the virus [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns (see *`r citef("fig_1")`*).
+OFV-infected plants exhibit various symptoms dependent on the variety of plant infected as well as the strain of the virus [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns (*`r citef("fig_1")`*).
 <!-- These lesions are thought to be associated with the feeding sites of the mite vector [@cite]. Also, is it probably a sign of RNAi plant defenses: see Hull Plant Virology -->
@@
 
-OFV naturally infects 50+ spp of Orchidaceae [@Kitajima2010; @Peng2013], some Nolinoideae [@Mei2016, @Dietzgen2018b], and *Citrus* [@BeltranBeltran2020; @GarciaEscamilla2018 @Roy2020].
+OFV naturally infects 50+ spp of Orchidaceae [@Kitajima2010; @Peng2013], some Nolinoideae [@Mei2016, @Dietzgen2018b], and *Citrus* where it causes citrus leprosis-like symptoms [@BeltranBeltran2020; @GarciaEscamilla2018 @Roy2020].
 Mechanical transmission of OFV is possible under lab conditions to various *Chenopodiaceae*, *Aizoaceae*, *Fabaceae*, and *Solanaceae* [@Chang1976; @Kondo2003; @Peng2013].
@@
 On June 2020, chlorotic ringspot symptoms were observed on the liriopogon Giant Lilyturf *Liriope* spp., cv.
-'Gigantea' in the landscape of Leon County, Florida (see *`r citef("fig_1")`*).
+'Gigantea' in the landscape of Leon County, Florida (*`r citef("fig_1")`*).
 Liropogons belong to the plant family Asparagaceae, subfamily Nolinoideae, which includes various monocotyledonous lilliod plants [@Chase2009].
@@
 These characteristics have given rise to various common names, including: monkey grass, Aztec grass, lilyturf, mondo grass, etc.
-(see *`r citet("tab_1")`*).
+(*`r citet("tab_1")`*).
 The genus *Liriope* contains eight species, four of which are commonly cultivated, while the genus *Ophiopogon* consists of about 65 species, with only a handful are available for horticulture [@Lattier2014; @Nesom2010].
@@
 Plant leaf samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL.
-The plant samples were tested for a wide range of pathogens, including **[Ask Dr.
-Iriarte]** but the results were inconclusive.
+The plant samples were tested for a wide range of pathogens, including **[Waiting on Dr.
+Iriarte's response]** but the results were inconclusive.
 The infected materials were subsequently sent to the Florida Department of Agriculture and Consumer Services (FDACS).
@@
 Further samples were taken from various symptomatic cultivars of *Liriope* spp., *Ophiopogon* spp., as well as *Aspidistra elatior* Blume (Asparagales: Nolinoideae) during subsequent visits to the initial site of collection as well as other locations in Leon county.
-Samples were tested via RT-PCR at the NFREC (see *`r citet("tab_1")`*) to confirm the presence of OFV.
+Samples were tested via RT-PCR at the NFREC (*`r citet("tab_1")`*) to confirm the presence of OFV.
 
 Further surveys of Nolinoideae in Florida have revealed more sites with symptomatic plants in both Leon and Alachua counties.
-In addition to the discovery of the OFV-infected plants, our lab at the NFREC collected mites from symptomatic plants in Leon county which were observed with phase contrast microscopy.
+In addition to the discovery of the OFV-infected plants, we collected mites from symptomatic plants in Leon county which were observed with phase contrast microscopy.
 We encountered both eriophyoid mites and flat mites which were identified as *Brevipalpus californicus* (Banks) sensu lato, an identity which was confirmed by the FDACS via Differential Interference Contrast (DIC) microscopy.
@@
 californicus* s.l.
-(see *`r citef("fig_2")`*).
+(*`r citef("fig_2")`*).
 
 The earliest mention of a virus which may have been OFV is @Ko1985, who detected nuclear inclusions caused by an undescribed bacilliform rhabdovirus.
-@Ko1985 described the spoke-wheel configurations typically associated with OFV (see [@Chang1976]), in *Brassia* orchids, but unfortunately made no mention of mites or further investigations of this virus.
+@Ko1985 described the spoke-wheel configurations typically associated with OFV [@Chang1976], in *Brassia* orchids, but unfortunately made no mention of mites or further investigations of this virus.
 The first certain report of OFV in the US was made by @Bratsch2015, who confirmed the presence of OFV in *Phalaenopsis* hybrids in the US, using TEM of ultrathin sections of plant tissue as well as molecular sequence analysis.
@@
 Furthermore, OFV represents an obstacle to overcome for the burgeoning interest in cultivating *Vanilla* in southern Florida [@Chambers2019].
-Lastly, some OFV isolates are known to be involved with nuclear types of Citrus Leprosis [@Roy2015a], which may be a cause for concern for the citrus industry.
+Lastly, some OFV isolates are known to be involved with nuclear types of citrus leprosis [@Roy2015a], which may be a cause for concern for the citrus industry.
 In fact, @Kitajima2011a found that the Citrus Leprosis virus (CiLV) which previously affected Florida citrus was a nuclear type of citrus leprosis, which are closely related to OFV strains [@Roy2013a].
@@
 obovatus* is a suspected vector as well [@Childers2003a].
-All three mite species/complexes are present in Florida [@Childers2003a; @Akyazi2017] (see *`r citef("fig_3")`*), therefore it is critical to monitor the spread of Orchid Fleck Virus and its mite vector(s) to determine what risk this virus represents for plants in Florida and the surrounding regions.
+All three mite species/complexes are present in Florida [@Childers2003a; @Akyazi2017] (*`r citef("fig_3")`*); therefore, it is critical to monitor the spread of Orchid Fleck Virus and its mite vector(s) to determine what risk this virus represents for plants in Florida and the surrounding regions.
 
-### Control Options
+### Brief Section on Control Options
 
-*Galendromus helveolus* (Acari: Phytoseiidae) have been reported to feed on eggs, larvae and nymphs of *B. californicus* [@Chen2006].
+The predatory mite *Galendromus helveolus* (Acari: Phytoseiidae) have been reported to feed on eggs, larvae and nymphs of *B. californicus* [@Chen2006].
 
-*Metarhizium anisopliae* var. *acridum* has been shown to be pathogenic to *B. phoenicis* [@Magalhaes2005], we have encountered similar fungal infections
+The entomopathogenic fungus *Metarhizium anisopliae* var. *acridum* has been shown to be pathogenic to *B. phoenicis* [@Magalhaes2005], we have encountered similar fungal infections
+
+### References
+
+<div id="refs"></div>
 
@@
 This research was partly funded by the USDA National Institute of Food and Agriculture, Hatch project FLA-NFC-005607.
-
-### References

### 2021-03-02 ofv_fife_2021.Rmd
Finished control methods section, added bibliography entries, added Figure 4, swapped figure positions, moved bibliography up and images to end.

@@
 Plant leaf samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL.
-The plant samples were tested for a wide range of pathogens, including **[Waiting on Dr.
-Iriarte's response]** but the results were inconclusive.
+The plant samples were tested for a wide range of common plant pathogens, but the results were inconclusive.
 The infected materials were subsequently sent to the Florida Department of Agriculture and Consumer Services (FDACS).
@@
 
+### Control methods for *Brevipalpus* mites
+
+Reducing the populations of the *Brevipalpus* mite vector may be able to reduce the spread of OFV by infective mites, but infected plants are not able to recover from the virus and must be rouged, or removed.
+Rouging plants is a direct and efficient option to remove mite and virus populations quickly, but increases in difficultly with the number of plants involved.
+Once infected plants have been removed, it may be possible to prevent re-infestation with conventional pest management methods to prevent the *Brevipalpus* vector from reestablishing and further spreading OFV.
+
+Most research on the integrated management of mites has been catered towards controlling various species of spider mites (Acari: Tetranychidae) [@Leeuwen2015], but many of those methods can be applied to *Brevipalpus* spp.
+as well:
+
+Chemical control via synthetic acaricides is commonly used to control *Brevipalpus* spp.
+[@Leeuwen2015], but acaricides have some drawbacks.
+Many products are able to control a broad class of arthropods, but often they do so indiscriminately, killing beneficial insects as well as pests [@Suckling2013].
+The need for chemical control has become increasingly relied on for citrus crops which are combating citrus greening (huanglongbing) [@Tansey2015].
+Control strategies which rely heavily on chemical control have the potential to encourage pesticide resistance in mite populations; pesticide resistance has been reported in various *Brevipalpus* populations [@Alves2000; @Campos2002; @Omoto2000].
+In addition, it is important to consider the interactions which may occur between different chemical applications or tank mixes [@Vechia2018].
+Lastly, application costs of chemical controls can be large and greatly contribute to the cost of production [@Rodrigues2000a], nevertheless chemical applications are an important tool used to control pests.
+
+Various biological control methods have also been studied, but their use has not been widely adopted for various reasons [@Messing2017].
+Even so, some studies have found biological control methods which could be used specifically for *Brevipalpus* mites: The predatory mite *Galendromus helveolus* (Chant) (Acari: Phytoseiidae) have been reported to feed on eggs, larvae and nymphs of *B.
+californicus* [@Chen2006] and studies of *Amblyseius largoensis* (Muma) (Acari: Phytoseiidae) demonstrated its ability to suppress populations of *B.
+yothersi* on citrus plants [@Argolo2020].
+In addition, the entomopathogenic fungus *Metarhizium anisopliae* var.
+*acridum* was found to be pathogenic to *B.
+phoenicis* [@Magalhaes2005].
+Our own surveys have found mites which succumbed to fungal infections (*`r citef("fig_3")`*), so there may be other fungi which could be developed for biological control.
+
+### Conclusion
+
 Detecting OFV in Florida represents a concern for horticulturalists who grow susceptible plants of economic importance, including orchids, *Liriope*, *Ophiopogon*, or other susceptible Asparagales spp.
@@
 obovatus* is a suspected vector as well [@Childers2003a].
-All three mite species/complexes are present in Florida [@Childers2003a; @Akyazi2017] (*`r citef("fig_3")`*); therefore, it is critical to monitor the spread of Orchid Fleck Virus and its mite vector(s) to determine what risk this virus represents for plants in Florida and the surrounding regions.
-
-### Brief Section on Control Options
-
-The predatory mite *Galendromus helveolus* (Acari: Phytoseiidae) have been reported to feed on eggs, larvae and nymphs of *B. californicus* [@Chen2006].
-
-The entomopathogenic fungus *Metarhizium anisopliae* var. *acridum* has been shown to be pathogenic to *B. phoenicis* [@Magalhaes2005], we have encountered similar fungal infections
+All three mite species/complexes are present in Florida [@Childers2003a; @Akyazi2017] (*`r citef("fig_4")`*); therefore, it is critical to monitor the spread of Orchid Fleck Virus and its mite vector(s) to determine what risk this virus represents for plants in Florida and the surrounding regions.
 
@@
 ```{r, fig_3, warning=FALSE}
+grid::grid.raster(tiff::readTIFF( "images/fungus_mite.tif"))
+```
+`r fig_nums(name = "fig_3", caption = "LT-SEM images of unidentified fungus infecting *Brevipalpus californicus* sensu lato: (a) Infested *B.
+californicus* adult, dorsal (b) Detail of fungal sporangia.
+LT-SEM images provided by Dr.
+Gary Bauchan, USDA-ARS 2021")`
+
+```{r, fig_4, warning=FALSE}
 grid::grid.raster(tiff::readTIFF( "images/other_mites.tif"))
 ```
-`r fig_nums(name = "fig_3", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
+`r fig_nums(name = "fig_4", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
 yothersi*, dorsal (b) *B.

### 2021-03-09 ofv_fife_2021.Rmd
Revised according to Dr. Martini's suggestions

--- 2021-03-02 ofv_fife_2021.Rmd
@@
 
-### Body Text
+\pagebreak
 *Orchid fleck dichorhavirus* (OFV) is the type species for the genus *Dichorhavirus*, a group of plant-infecting, bacilliform, nuclear rhabdoviruses composed of two segments of single-stranded, negative-sense RNA [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
@@
 
-OFV-infected plants exhibit various symptoms dependent on the variety of plant infected as well as the strain of the virus [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns (*`r citef("fig_1")`*).
+OFV-infected plants exhibit various symptoms dependent on the variety of plant infected as well as the strain of the virus [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns (`r citef("fig_1")`).
 <!-- These lesions are thought to be associated with the feeding sites of the mite vector [@cite]. Also, is it probably a sign of RNAi plant defenses: see Hull Plant Virology -->
@@
 
-On June 2020, chlorotic ringspot symptoms were observed on the liriopogon Giant Lilyturf *Liriope* spp., cv.
-'Gigantea' in the landscape of Leon County, Florida (*`r citef("fig_1")`*).
+During June 2020, chlorotic ringspot symptoms were observed on the liriopogon Giant Lilyturf *Liriope* spp., cv.
+'Gigantea' in the landscape of Leon County, Florida (`r citef("fig_1")`).
 Liropogons belong to the plant family Asparagaceae, subfamily Nolinoideae, which includes various monocotyledonous lilliod plants [@Chase2009].
@@
 californicus* s.l.
-(*`r citef("fig_2")`*).
+(`r citef("fig_2")`).
 
@@
 
+### Control methods for *Brevipalpus* mites
+
+Reducing the populations of the *Brevipalpus* mite vector may be able to reduce the spread of OFV by infective mites, but infected plants are not able to recover from the virus and must be rouged or removed.
+Rouging plants is a direct and efficient option to remove mite and virus populations quickly but increases in difficultly with the number of plants involved.
+Once infected plants have been removed, the objective will be to prevent re-infestation of the *Brevipalpus* vector via conventional pest management methods.
+
+Most research on the integrated management of mites has been catered towards controlling various species of spider mites (Acari: Tetranychidae) [@Leeuwen2015], but many of those methods can be applied to *Brevipalpus* spp.
+as well:
+
+Chemical control via synthetic acaricides is commonly used to control *Brevipalpus* spp.
+[@Leeuwen2015], but acaricides have some drawbacks.
+Many products control a broad class of arthropods, but often they do so indiscriminately, killing beneficial insects as well as pests [@Suckling2013].
+Control strategies which rely heavily on chemical control have the potential to encourage pesticide resistance in mite populations and pesticide resistance has been reported in various *Brevipalpus* populations [@Alves2000; @Campos2002; @Omoto2000].
+In addition, it is important to consider the interactions which may occur between different chemical applications or tank mixes [@Vechia2018].
+Lastly, application costs of chemical controls can be large and increase the cost of production [@Rodrigues2000a], nevertheless chemical applications are valuable tools used to consider against *Brevipalpus*.
+
+Various biological control methods have also been studied, but their use has not been widely adopted [@Messing2017].
+Even so, some studies have found biological control methods which could be used specifically for *Brevipalpus* mites: The predatory mite *Galendromus helveolus* (Chant) (Acari: Phytoseiidae) has been reported to feed on eggs, larvae and nymphs of *B.
+californicus* [@Chen2006] and studies of *Amblyseius largoensis* (Muma) (Acari: Phytoseiidae) demonstrated its ability to suppress populations of *B.
+yothersi* on citrus plants [@Argolo2020].
+In addition, the entomopathogenic fungus *Metarhizium anisopliae* var.
+*acridum* was found to be pathogenic to *B.
+phoenicis* [@Magalhaes2005].
+In our own surveys, we have found mites which succumbed to fungal infections (`r citef("fig_3")`); however the fungal species was not determined.
+
+### Conclusion
+
 Detecting OFV in Florida represents a concern for horticulturalists who grow susceptible plants of economic importance, including orchids, *Liriope*, *Ophiopogon*, or other susceptible Asparagales spp.
@@
 obovatus* is a suspected vector as well [@Childers2003a].
-All three mite species/complexes are present in Florida [@Childers2003a; @Akyazi2017] (*`r citef("fig_3")`*); therefore, it is critical to monitor the spread of Orchid Fleck Virus and its mite vector(s) to determine what risk this virus represents for plants in Florida and the surrounding regions.
+All three mite species/complexes are present in Florida [@Childers2003a; @Akyazi2017] (`r citef("fig_4")`); therefore, it is critical to monitor the spread of Orchid Fleck Virus and its mite vector(s) to determine what risk this virus represents for plants in Florida and the surrounding regions.
 
-### Brief Section on Control Options
-
-The predatory mite *Galendromus helveolus* (Acari: Phytoseiidae) have been reported to feed on eggs, larvae and nymphs of *B. californicus* [@Chen2006].
-
-The entomopathogenic fungus *Metarhizium anisopliae* var. *acridum* has been shown to be pathogenic to *B. phoenicis* [@Magalhaes2005], we have encountered similar fungal infections
+### Acknowledgements
+We would like to give a special thanks to the Tallahassee Museum for their patience, cooperation and support with collecting plant samples.
+We also want to thank Dr.
+Sam Bolton for checking the mites we have sent to FDACS for species validation.
+We are especially indebted to the late Dr.
+Gary Bauchan for permitting us to use these beautiful LT-SEM images, he will be greatly missed.
+This research was partly funded by the USDA National Institute of Food and Agriculture, Hatch project FLA-NFC-005607.
 
@@
 
-### Figures and Tables
-
-```{r, fig_1, warning=FALSE}
-grid::grid.raster(tiff::readTIFF( "images/fig_1.tif"))
-```
-`r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by plants infected with Orchid fleck dichorhavirus: (a) ringspot symptoms on *Liriope gigantea* (b) chlorotic flecking on *Aspidistra elatior*.")`
-
-```{r, fig_2, warning=FALSE}
-grid::grid.raster(tiff::readTIFF( "images/b_cali.tif"))
-```
-`r fig_nums(name = "fig_2", caption = "LT-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.
-LT-SEM images provided by Dr.
-Gary Bauchan, USDA-ARS 2021")`
-
-```{r, fig_3, warning=FALSE}
-grid::grid.raster(tiff::readTIFF( "images/other_mites.tif"))
-```
-`r fig_nums(name = "fig_3", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
-yothersi*, dorsal (b) *B.
-yothersi*, lateral (c) *B.
-obovatus*, dorsal.
-SEM images provided by Dr.
-Ron Ochoa, USDA-ARS 2021")`
+### Table
 
@@
 
-### Acknowledgements
-We would like to give a special thanks to the Tallahassee Museum for their patience, cooperation and support with collecting plant samples.
-We also want to thank Dr.
-Sam Bolton for checking the mites we have sent to FDACS for species validation.
-We are especially indebted to the late Dr.
-Gary Bauchan for permitting us to use these beautiful LT-SEM images, he will be greatly missed.
-This research was partly funded by the USDA National Institute of Food and Agriculture, Hatch project FLA-NFC-005607.
+### Figure captions
+`r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by plants infected with Orchid fleck dichorhavirus: (a) ringspot symptoms on *Liriope gigantea* (b) chlorotic flecking on *Aspidistra elatior*.")`
+
+`r fig_nums(name = "fig_2", caption = "LT-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.
+LT-SEM images provided by Dr.
+Gary Bauchan, USDA-ARS 2021")`
+
+`r fig_nums(name = "fig_3", caption = "LT-SEM images of unidentified fungus infecting *Brevipalpus californicus* sensu lato: (a) Infested *B.
+californicus* adult, dorsal (b) Detail of fungal sporangia.
+LT-SEM images provided by Dr.
+Gary Bauchan, USDA-ARS 2021")`
+
+`r fig_nums(name = "fig_4", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
+yothersi*, dorsal (b) *B.
+yothersi*, lateral (c) *B.
+obovatus*, dorsal.
+SEM images provided by Dr.
+Ron Ochoa, USDA-ARS 2021")`
+
+### Figures
+```{r, fig_1, warning=FALSE}
+grid::grid.raster(tiff::readTIFF( "images/fig_1.tif"))
+```
+```{r, fig_2, warning=FALSE}
+grid::grid.raster(tiff::readTIFF( "images/b_cali.tif"))
+```
+```{r, fig_3, warning=FALSE}
+grid::grid.raster(tiff::readTIFF( "images/fungus_mite.tif"))
+```
+```{r, fig_4, warning=FALSE}
+grid::grid.raster(tiff::readTIFF( "images/other_mites.tif"))
+```

### 2021-03-16 ofv_fife_2021.Rmd
Accepted almost all of the changes the authors suggested: clarified plant taxonomy, made it clear that there were more than one mite species recovered from plants. Removed first part of section on control, which will require a rewrite. Other minor edits to formatting, added a new reference Dr. Carillo suggested

@@
 
-### First report of the *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) virus, *Orchid fleck dichorhavirus* (Mononegavirales: Rhabdoviridae) infecting ornamental Nolinoideae in the Florida panhandle
+### First report of the *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) virus, *Orchid fleck dichorhavirus* (Mononegavirales: Rhabdoviridae) infecting ornamental Nolinoidaea in the Florida panhandle
 
@@
 OFV is the type species for the genus *Dichorhavirus* and infects 50+ spp.
-of Orchidaceae, Nolinoideae, and *Citrus*.
-During June 2020, we observed chlorotic ringspot symptoms on Giant Lilyturf (*Liriope* spp., cv.
-‘Gigantea’) in the landscape of Leon County, Florida.
-We tested plant samples for a wide range of pathogens and ultimately identified the pathogen as *Orchid fleck dichorhavirus*.
-We took further samples from other *Liriope* spp., *Ophiopogon* spp., and *Aspidistra elatior* Blume (Asparagales: Nolinoideae) in Leon and Alachua county.
-All symptomatic plants tested positive for OFV.
-We recovered mites from OFV-infected plants, which belonged to *Brevipalpus californicus* sensu lato.
+of Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (*Citrus*).
+During June 2020, chlorotic ringspot symptoms on Giant Lilyturf (*Liriope* spp., cv.
+‘Gigantea’) were observed in a landscape in Leon County, Florida.
+Later in the year, the presence of *Orchid fleck dichorhavirus* was confirmed via generic one step conventional RT-PCR and Sanger sequencing.
+Amplicons had a 98\% identity with OFV strains which infect orchids.
+The identification was also confirmed with RT-qPCR and High Throughput Sequencing (HTS).
+Additional samples were taken from other *Liriope* spp., *Ophiopogon* spp., and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua county.
+All symptomatic plants tested positive for OFVs.
+Three mite species were recovered from OFV-infected plants: *Brevipalpus californicus* sensu lato, *B.
+obovatus* Donnadieu and *B.
+confusus* Banks.
+One of these species is presumably responsible for OFV transmission.
 Florida has various mite species of *Brevipalpus* and a diverse array of susceptible plant species in the landscape, both native and introduced.
-We suggest that OFV already has a wide distribution in Florida which will continue to spread if unchecked, representing a potential threat for many plants of economic importance for Florida.
+We suggest that OFV already has a wide distribution in Florida which will continue to spread if unchecked, representing a potential threat for *Liriope* spp., *Ophiopogon* spp.
+and *Aspidistra elatior*, which are commonly used in landscaping in Florida.
 
 ### Keywords:
-false spider mite, flat mite, *Brevipalpus*-transmitted viruses, *Liriope*, Ruscaceae, Asparagaceae, orchid, Orchidaceae, pests, ornamental plants
+False spider mite, flat mite, *Brevipalpus*-transmitted viruses, *Liriope*, Ruscaceae, Asparagaceae, orchid, Orchidaceae, pests, ornamental plants, orchid fleck virus
 
@@
 
-OFV naturally infects 50+ spp of Orchidaceae [@Kitajima2010; @Peng2013], some Nolinoideae [@Mei2016, @Dietzgen2018b], and *Citrus* where it causes citrus leprosis-like symptoms [@BeltranBeltran2020; @GarciaEscamilla2018 @Roy2020].
-Mechanical transmission of OFV is possible under lab conditions to various *Chenopodiaceae*, *Aizoaceae*, *Fabaceae*, and *Solanaceae* [@Chang1976; @Kondo2003; @Peng2013].
+OFV naturally infects 50+ spp of Orchidaceae [@Kitajima2010; @Peng2013], some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], as well as Rutaceae: *Citrus* where it causes citrus leprosis-like symptoms [@BeltranBeltran2020; @GarciaEscamilla2018; @Roy2020].
+Mechanical transmission of OFV is possible under lab conditions to various Chenopodiaceae, Aizoaceae, Fabaceae, and Solanaceae [@Chang1976; @Kondo2003; @Peng2013].
 
 During June 2020, chlorotic ringspot symptoms were observed on the liriopogon Giant Lilyturf *Liriope* spp., cv.
-'Gigantea' in the landscape of Leon County, Florida (`r citef("fig_1")`).
-Liropogons belong to the plant family Asparagaceae, subfamily Nolinoideae, which includes various monocotyledonous lilliod plants [@Chase2009].
+'Gigantea' in a landscape of Leon County, Florida (`r citef("fig_1")`).
+Liropogons belong to the plant family Asparagaceae, subfamily Nolinoidaea, which includes various monocotyledonous lilliod plants [@Chase2009].
 Liriopogons are native to southeastern Asia, encompassing the closely-related genera *Liriope* and *Ophiopogon*, which are characterized by evergreen, long grass-like leaves, and erect flowers which produce black, purple or blue, berry-like fruits, depending on the cultivar [@Lattier2014; @Fantz2015].
@@
 Plant leaf samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL.
-The plant samples were tested for a wide range of common plant pathogens, but the results were inconclusive.
+The plant samples tested negative for begomovirus, potyvirus, tospovirus, as well as INSV, TMV and TSWV.
 The infected materials were subsequently sent to the Florida Department of Agriculture and Consumer Services (FDACS).
@@
 RT-qPCR confirmed OFV and the RT-PCR product was sequenced using Sanger sequencing and High Throughput Sequencing [@Kondo2006].
-Sanger sequencing of RT-PCR amplicons shared 98 \% nucleotide identity with OFV strains which infect orchids (GenBank Accession numbers: AB244418 and MK522807) [@Kondo2006; @Kondo2014; @Cook2019].
-Further samples were taken from various symptomatic cultivars of *Liriope* spp., *Ophiopogon* spp., as well as *Aspidistra elatior* Blume (Asparagales: Nolinoideae) during subsequent visits to the initial site of collection as well as other locations in Leon county.
-Samples were tested via RT-PCR at the NFREC (*`r citet("tab_1")`*) to confirm the presence of OFV.
+Sanger sequencing of RT-PCR amplicons shared 98\% nucleotide identity with OFV strains which infect orchids (GenBank Accession numbers: AB244418 and MK522807) [@Kondo2006; @Kondo2014; @Cook2019].
+Further samples were taken from various symptomatic cultivars of *Liriope* spp., *Ophiopogon* spp., as well as *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) during subsequent visits to the initial site of collection as well as other locations in Leon county.
+Samples were tested via RT-PCR at the NFREC (`r citet("tab_1")`) to confirm the presence of OFV.
 
-Further surveys of Nolinoideae in Florida have revealed more sites with symptomatic plants in both Leon and Alachua counties.
+Further surveys of Nolinoidaea in Florida have revealed more sites with symptomatic plants in both Leon and Alachua counties.
 In addition to the discovery of the OFV-infected plants, we collected mites from symptomatic plants in Leon county which were observed with phase contrast microscopy.
-We encountered both eriophyoid mites and flat mites which were identified as *Brevipalpus californicus* (Banks) sensu lato, an identity which was confirmed by the FDACS via Differential Interference Contrast (DIC) microscopy.
+We encountered both eriophyoid mites and flat mites which were originally identified as *Brevipalpus californicus* (Banks) sensu lato, an identity which was confirmed by the FDACS via Differential Interference Contrast (DIC) microscopy.
 *Brevipalpus* mites have been previously associated with OFV [@BeltranBeltran2020; @GarciaEscamilla2018; @Dietzgen2018b] and similar diseases [@Kitajima2010] and are known to feed on a large variety of economically-important plants [@Childers2003a; @Akyazi2017].
 Unfortunately, the *Brevipalpus* mite species complex is known to contain cryptic species [@Childers2011] whose identification can be improved with molecular methods as well as more advanced microscopy techniques, such as low-temperature scanning electron microscopy (LT-SEM) [@Skoracka2015; @Leon2010].
-With that in mind, we sent additional samples of the mites to the USDA-ARS in Beltsville to observe the mites with LT-SEM techniques, which agreed with both prior identifications of *B.
+With that in mind, we sent additional samples of the mites to the USDA-ARS in Beltsville to observe the mites with Cryo LT-SEM techniques, which agreed with both prior identifications of *B.
 californicus* s.l.
-(`r citef("fig_2")`).
+(`r citef("fig_2")`) but also revealed the presence of two other species: *B.
+obovatus* and *B.
+confusus*.
 
@@
 In addition, @Bratsch2015 detected *Brevipalpus* mites and their exoskeletons associated with OFV-infected plants.
-It appears that @Bratsch2015 did not make a conclusive species identification, but did cite @Kondo2003, suggesting that they suspected *B.
-californicus* as their vector.
+It appears that @Bratsch2015 did not make a conclusive species identification, but did cite @Kondo2003, suggesting a mite in the *B.
+californicus* group as the vector.
 
-OFV has been reported in other Nolinoideae in Australia [@Dietzgen2018b; @Mei2016], including *Liriope spicata* (Thunb.) Lour.
+OFV has been reported in other Nolinoidaea in Australia [@Dietzgen2018b; @Mei2016], including *Liriope spicata* (Thunb.) Lour.
 [@Mei2016].
 Our plants are thought to belong to different species of *Liriope* which are not *L.
-spicata* and we are not aware of any record which reports OFV infection in *Ophiopogon* plants.
+spicata* and we are not aware of any record other than this manuscript which reports OFV infection in *Ophiopogon* plants.
 Unfortunately, liriopogons species are very similar in appearance and growth habit, with few useful characters used for their classification [@Fantz2008a].
@@
 
-Reducing the populations of the *Brevipalpus* mite vector may be able to reduce the spread of OFV by infective mites, but infected plants are not able to recover from the virus and must be rouged or removed.
+<!-- Reducing the populations of the *Brevipalpus* mite vector may be able to reduce the spread of OFV by infective mites, but infected plants are not able to recover from the virus and must be rouged or removed.
 Rouging plants is a direct and efficient option to remove mite and virus populations quickly but increases in difficultly with the number of plants involved.
 Once infected plants have been removed, the objective will be to prevent re-infestation of the *Brevipalpus* vector via conventional pest management methods.
+-->
 
-Most research on the integrated management of mites has been catered towards controlling various species of spider mites (Acari: Tetranychidae) [@Leeuwen2015], but many of those methods can be applied to *Brevipalpus* spp.
-as well:
-
-Chemical control via synthetic acaricides is commonly used to control *Brevipalpus* spp.
+<!-- Most research on the integrated management of mites has been catered towards controlling various species of spider mites (Acari: Tetranychidae) [@Leeuwen2015], but many of those methods can be applied to *Brevipalpus* spp.
+as well: -->
+Chemical control via synthetic acaricides is commonly used to manage *Brevipalpus* spp.
 [@Leeuwen2015], but acaricides have some drawbacks.
 Many products control a broad class of arthropods, but often they do so indiscriminately, killing beneficial insects as well as pests [@Suckling2013].
-Control strategies which rely heavily on chemical control have the potential to encourage pesticide resistance in mite populations and pesticide resistance has been reported in various *Brevipalpus* populations [@Alves2000; @Campos2002; @Omoto2000].
+Control strategies which rely heavily on chemical control have the potential to encourage pesticide resistance in mite populations and pesticide resistance has been reported in various *Brevipalpus* populations [@Alves2000; @Campos2002; @Omoto2000; @Rocha2021].
 In addition, it is important to consider the interactions which may occur between different chemical applications or tank mixes [@Vechia2018].
@@
 
-Detecting OFV in Florida represents a concern for horticulturalists who grow susceptible plants of economic importance, including orchids, *Liriope*, *Ophiopogon*, or other susceptible Asparagales spp.
+Detecting OFV in Florida represents a concern for horticulturists who grow susceptible plants of economic importance, including orchids, *Liriope*, *Ophiopogon*, or other susceptible Asparagaceae spp.
 which are commonly used in landscaping.
@@
 obovatus* is a suspected vector as well [@Childers2003a].
-All three mite species/complexes are present in Florida [@Childers2003a; @Akyazi2017] (`r citef("fig_4")`); therefore, it is critical to monitor the spread of Orchid Fleck Virus and its mite vector(s) to determine what risk this virus represents for plants in Florida and the surrounding regions.
+All three mite species/complexes are present in Florida [@Childers2003a; @Akyazi2017] (`r citef("fig_4")`); therefore, it is critical to identify the vector of OFVs in Florida and monitor its spread to determine what risk this virus represents for plants in Florida and the surrounding regions.
 

### 2021-03-23 ofv_fife_2021.Rmd
Fixed broken path to template. Integrated most of Dr. Ochoa and Dr. Roy's comments. Did a hatchet job of the table, figures, and my bad attempt at a management section. Need to write about symptoms on A. elatior. Maybe better photos?

@@
   word_document:
-    reference_docx: ../r-templates/word-template-jis.docx
+    reference_docx: ../r-word-templates/word-template-jis.docx
 # - html_document
@@
 
-### First report of the *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) virus, *Orchid fleck dichorhavirus* (Mononegavirales: Rhabdoviridae) infecting ornamental Nolinoidaea in the Florida panhandle
+### First report of the *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) virus, *Orchid fleck virus* (Mononegavirales: Rhabdoviridae) infecting three ornamentals in Florida
 
-Austin **Fife**^1^, Daniel **Carrillo**^2^, Gary **Knox**^3^, Fanny **Iriarte**^4^, Kishore **Dey**^5^, Avijit **Roy**^6^, Ronald **Ochoa**^6^, Gary **Bauchan**^7^ $\dagger$, Mathews **Paret**^4^, Xavier **Martini**^1^\*
+Austin **Fife**^1^, Daniel **Carrillo**^2^, Gary **Knox**^3^, Fanny **Iriarte**^4^, Kishore **Dey**^5^, Avijit **Roy**^6^, Ronald **Ochoa**^7^, Gary **Bauchan**^8^ $\dagger$, Mathews **Paret**^4^, Xavier **Martini**^1^\*
 
@@
 
-^6^	United States Department of Agriculture - Animal and Plant Health Inspection Service, Systematic Entomology Laboratory 10300 Baltimore Ave, Bldg. 5 BARC-West, Beltsville, MD 20705
+^6^	United States Department of Agriculture – Agriculture Research Service, Molecular Plant Pathology Laboratory, 10300 Baltimore Ave, Bldg. 4 BARC-West, Beltsville, MD 20705
 
-^7^	United States Department of Agriculture - Animal and Plant Health Inspection Service, Electron and Confocal Microscopy Unit, Bldg. 12  BARC-West, 10300 Baltimore Ave, Beltsville, MD 20705
+^7^ United States Department of Agriculture - Agriculture Research Service, Systematic Entomology Laboratory 10300 Baltimore Ave, Bldg. 5 BARC-West, Beltsville, MD 20705
+
+^8^	United States Department of Agriculture - Animal and Plant Health Inspection Service, Electron and Confocal Microscopy Unit, Bldg. 12  BARC-West, 10300 Baltimore Ave, Beltsville, MD 20705
 
@@
 ### Abstract
-Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the only known vectors of dichorhaviruses and transmit *Orchid fleck dichorhavirus* (OFV) in a persistent propagative manner.
-OFV is the type species for the genus *Dichorhavirus* and infects 50+ spp.
-of Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (*Citrus*).
+Several flat mite species, all from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae), are the only known vectors of dichorhaviruses.
+The *B.
+californicus* species group exclusively can transmit Orchid fleck dichorhavirus (OFV) in a persistent propagative manner.
+OFV is the type species for the genus *Dichorhavirus* and infects more than fifty plant species belongs to the family Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (*Citrus*).
 During June 2020, chlorotic ringspot symptoms on Giant Lilyturf (*Liriope* spp., cv.
 ‘Gigantea’) were observed in a landscape in Leon County, Florida.
-Later in the year, the presence of *Orchid fleck dichorhavirus* was confirmed via generic one step conventional RT-PCR and Sanger sequencing.
-Amplicons had a 98\% identity with OFV strains which infect orchids.
-The identification was also confirmed with RT-qPCR and High Throughput Sequencing (HTS).
-Additional samples were taken from other *Liriope* spp., *Ophiopogon* spp., and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua county.
-All symptomatic plants tested positive for OFVs.
+Later in the year, the presence of OFV was confirmed using OFV specific conventional reverse transcription polymerase chain assay (RT-PCR) assay and Sanger sequencing.
+RT-PCR amplicons had a 98\% identity with the known OFV sequences available in the Genbank.
+The identification was also confirmed with the quantitative RT-PCR (RT-qPCR).
+Additional samples were taken from other Nolinoidaea, including *Liriope muscari*, *Ophiopogon japonicus*, *O.
+intermedius* and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua counties.
+Identification of partial genome sequence confirmed the presence of both the orchid strains (OFV-Orc1 and OFV-Orc2) in Florida.
 Three mite species were recovered from OFV-infected plants: *Brevipalpus californicus* sensu lato, *B.
@@
 One of these species is presumably responsible for OFV transmission.
-Florida has various mite species of *Brevipalpus* and a diverse array of susceptible plant species in the landscape, both native and introduced.
+Florida has various mite species of *Brevipalpus* and a diverse array of susceptible native and introduced plant species in the landscape.
 We suggest that OFV already has a wide distribution in Florida which will continue to spread if unchecked, representing a potential threat for *Liriope* spp., *Ophiopogon* spp.
-and *Aspidistra elatior*, which are commonly used in landscaping in Florida.
+and *Aspidistra elatior* which are commonly used in landscaping in Florida .
+In this study we are reporting three new hosts from the family Asperagaceae.
+To know the extended host range of OFVs, a survey in the citrus growing regions in Florida is essential with special emphasis to the plants belongs to the family Rutaceae and Asparagaceae.
 
 ### Keywords:
-False spider mite, flat mite, *Brevipalpus*-transmitted viruses, *Liriope*, Ruscaceae, Asparagaceae, orchid, Orchidaceae, pests, ornamental plants, orchid fleck virus
+False spider mite, flat mite, *Brevipalpus*-transmitted viruses, *Liriope*, Nolinoideae, *Ophiopogon*, Ruscaceae, Rutaceae, Asparagaceae, orchid, Orchidaceae, pests, ornamental plants, orchid fleck virus.
 
 \pagebreak
-*Orchid fleck dichorhavirus* (OFV) is the type species for the genus *Dichorhavirus*, a group of plant-infecting, bacilliform, nuclear rhabdoviruses composed of two segments of single-stranded, negative-sense RNA [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
-Other members of this genus are: *Citrus chlorotic spot dichorhavirus*, *Citrus leprosis N dichorhavirus*, *Clerodendrum chlorotic spot dichorhavirus* and *Coffee ringspot dichorhavirus* [@Dietzgen2018a].
-Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the only known vector for dichorhaviruses [@Maeda1998].
-These mites transmit OFV in a persistent propagative manner [@Kondo2003].
+*Orchid fleck virus* (OFV) is the type member for the genus *Dichorhavirus*, family Rhabdoviridae; a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
+Other members of this genus are: *Citrus chlorotic spot virus*, *Citrus leprosis virus* N, *Clerodendrum chlorotic spot virus* and *Coffee ringspot virus* [@Dietzgen2018a].
+Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the only known vector for dichorhaviruses [@Maeda1998], and *Brevipalpus californicus* (Banks) mites are the only mite known to transmit OFV in a persistent propagative manner [@Kondo2003].
 
-OFV-infected plants exhibit various symptoms dependent on the variety of plant infected as well as the strain of the virus [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns (`r citef("fig_1")`).
-<!-- These lesions are thought to be associated with the feeding sites of the mite vector [@cite]. Also, is it probably a sign of RNAi plant defenses: see Hull Plant Virology -->
+OFV-infected plants exhibit various symptoms dependent on the infected plant species as well as the strain of the OFV [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns (`r citef("fig_1")`).
+<!-- These lesions are thought to be associated with the feeding sites of the mite vector [@cite?]. Also, is it possibly a sign of RNAi plant defenses? See Hull Plant Virology -->
 
 OFV was first described infecting *Cymbidium* orchids in Japan [@Doi1977].
-Many countries have reported OFV and OFV-like rhabdoviruses infecting orchids worldwide [@Kondo2003], including Australia [@Lesemann1971; @Lesemann1975; @Gibbs2000], Brazil [@Kitajima1974; @Kitajima2001], China [@Peng2017], Colombia [@Kubo2009b], Costa Rica [@FreitasAstua2002], Denmark [@Begtrup1972], Fiji [@Pearson1993], France [@Sauvetre2018], Germany [@Lesemann1975; @Petzold1971], Korea [@Chang1991, @Zheng2013], Paraguay [@RamosGonzalez2015], South Africa [@Blanchfield2001], the United States [@Blanchfield2001; @Bratsch2015] and Vanuatu [@Pearson1993].
+Many countries have reported OFV and OFV-like rhabdoviruses infecting orchids worldwide [@Kondo2003], including Asia: [China [@Peng2017], Korea [@Chang1991, @Zheng2013]], Africa: [South Africa [@Blanchfield2001]], North America: [The United States [@Blanchfield2001; @Bratsch2015]], South America: [Brazil [@Kitajima1974; @Kitajima2001], Colombia [@Kubo2009b], Costa Rica [@FreitasAstua2002], Paraguay [@RamosGonzalez2015]], Europe: [Denmark [@Begtrup1972], France [@Sauvetre2018], Germany [@Lesemann1975; @Petzold1971]] and Oceania: [Australia [@Lesemann1971; @Lesemann1975; @Gibbs2000], Fiji [@Pearson1993], Vanuatu [@Pearson1993]].
 The prevalence of OFV and its mite vector is thought to be associated with the movement of infected orchids [@Dietzgen2018a].
 
-OFV naturally infects 50+ spp of Orchidaceae [@Kitajima2010; @Peng2013], some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], as well as Rutaceae: *Citrus* where it causes citrus leprosis-like symptoms [@BeltranBeltran2020; @GarciaEscamilla2018; @Roy2020].
+OFV naturally infects more than fifty species of Orchidaceae [@Kitajima2010; @Peng2013], some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], as well as Rutaceae: *Citrus* where it causes citrus leprosis-like symptoms [@Beltran-Beltran2020; @GarciaEscamilla2018; @Roy2020].
 Mechanical transmission of OFV is possible under lab conditions to various Chenopodiaceae, Aizoaceae, Fabaceae, and Solanaceae [@Chang1976; @Kondo2003; @Peng2013].
 
-During June 2020, chlorotic ringspot symptoms were observed on the liriopogon Giant Lilyturf *Liriope* spp., cv.
+During June 2020, chlorotic ringspot symptoms were observed on Giant Lilyturf *Liriope* spp., cv.
 'Gigantea' in a landscape of Leon County, Florida (`r citef("fig_1")`).
-Liropogons belong to the plant family Asparagaceae, subfamily Nolinoidaea, which includes various monocotyledonous lilliod plants [@Chase2009].
-Liriopogons are native to southeastern Asia, encompassing the closely-related genera *Liriope* and *Ophiopogon*, which are characterized by evergreen, long grass-like leaves, and erect flowers which produce black, purple or blue, berry-like fruits, depending on the cultivar [@Lattier2014; @Fantz2015].
-These characteristics have given rise to various common names, including: monkey grass, Aztec grass, lilyturf, mondo grass, etc.
-(*`r citet("tab_1")`*).
-The genus *Liriope* contains eight species, four of which are commonly cultivated, while the genus *Ophiopogon* consists of about 65 species, with only a handful are available for horticulture [@Lattier2014; @Nesom2010].
-Liripogons are considered the most important ground cover sold by the nursery industry in southeastern US [@Mcharo2003].
+*Liriope* belong to a group of plants in the family Asparagaceae, subfamily Nolinoidaea, which includes a diverse array of various monocotyledonous lilliod plants which are native to southeastern Asia [@Chase2009; @Meng2021].
+*Liriope* and the closely related *Ophiopogon* Ker Gawler (Asparagaceae: Nolinoidaea) are considered the most important ground cover sold by the nursery industry in southeastern US [@Mcharo2003].
 
-Plant leaf samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL.
-The plant samples tested negative for begomovirus, potyvirus, tospovirus, as well as INSV, TMV and TSWV.
+Viral infections of suspected plant leaf samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL.
+All the samples tested negative for begomovirus, potyvirus, tospovirus as well as for Impatiens necrotic spot virus, Tobacco mosaic virus and Tomato spotted wilt virus.
 The infected materials were subsequently sent to the Florida Department of Agriculture and Consumer Services (FDACS).
-The presence of *Orchid fleck dichorhavirus* was confirmed via generic one step conventional RT-PCR with R2-Dicho-GF and R2-Dicho-GR primers, amplifying ~800 nt of L-gene (RNA2) amplicon from a leaf sample of infected *Liriope* [@Kubo2009b].
-RT-qPCR confirmed OFV and the RT-PCR product was sequenced using Sanger sequencing and High Throughput Sequencing [@Kondo2006].
-Sanger sequencing of RT-PCR amplicons shared 98\% nucleotide identity with OFV strains which infect orchids (GenBank Accession numbers: AB244418 and MK522807) [@Kondo2006; @Kondo2014; @Cook2019].
-Further samples were taken from various symptomatic cultivars of *Liriope* spp., *Ophiopogon* spp., as well as *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) during subsequent visits to the initial site of collection as well as other locations in Leon county.
-Samples were tested via RT-PCR at the NFREC (`r citet("tab_1")`) to confirm the presence of OFV.
+The presence of OFV was confirmed using OFV generic R2-Dicho-GF and R2-Dicho-GR primers [@Roy2020] by one step conventional RT-PCR, amplifying ~800 nt of L-gene (RNA2) amplicon from an infected *Liriope* leaf sample.
+The RT-PCR amplicon was sequenced using Sanger sequencing and confirmed the presence of OFV in the tested samples.
+Sanger sequencing of RT-PCR amplicons shared 98\% nucleotide identity with orchid strains of OFV (GenBank Accession numbers: AB244418 and LC222630) [@Kondo2006; @Kondo2017].
+Further surveys of putatively OFV-infected plants were taken during subsequent visits to the initial site of collection.
+Plant samples included various cultivars of Nolinoid plants, including *Liriope* spp., *Ophiopogon* spp., and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) which were located at the same site as the original infected *Liriope* spp., cv 'Gigantea'.
+Samples were tested via RT-PCR at the NFREC<!-- (`r citet("tab_1")`) --> to confirm the presence of OFV.
 
-Further surveys of Nolinoidaea in Florida have revealed more sites with symptomatic plants in both Leon and Alachua counties.
+Further surveys of plants belonging to the subfamily Nolinoidaea in Florida have revealed more sites with symptomatic plants in both Leon and Alachua counties.
+In addition to the discovery of the OFV-infected plants, we collected mites from symptomatic plants in both Leon and Alachua counties.
 In addition to the discovery of the OFV-infected plants, we collected mites from symptomatic plants in Leon county which were observed with phase contrast microscopy.
-We encountered both eriophyoid mites and flat mites which were originally identified as *Brevipalpus californicus* (Banks) sensu lato, an identity which was confirmed by the FDACS via Differential Interference Contrast (DIC) microscopy.
-*Brevipalpus* mites have been previously associated with OFV [@BeltranBeltran2020; @GarciaEscamilla2018; @Dietzgen2018b] and similar diseases [@Kitajima2010] and are known to feed on a large variety of economically-important plants [@Childers2003a; @Akyazi2017].
-Unfortunately, the *Brevipalpus* mite species complex is known to contain cryptic species [@Childers2011] whose identification can be improved with molecular methods as well as more advanced microscopy techniques, such as low-temperature scanning electron microscopy (LT-SEM) [@Skoracka2015; @Leon2010].
-With that in mind, we sent additional samples of the mites to the USDA-ARS in Beltsville to observe the mites with Cryo LT-SEM techniques, which agreed with both prior identifications of *B.
+We encountered both an unidentified eriophyoid mite species on the *Liriope* spp., along with flat mites on all species tested (*Liriope* spp., *Ophiopogon* spp., and *A.
+elatior*).
+The flat mites were originally identified as *Brevipalpus californicus* (Banks) sensu lato, an identity which was confirmed by the FDACS via Differential Interference Contrast (DIC) microscopy.
+*Brevipalpus* mites have been previously associated with OFV [@Beltran-Beltran2020; @GarciaEscamilla2018; @Dietzgen2018b] as well as similar diseases [@Kitajima2010] and are known to feed on a large variety of economically important plants [@Childers2003a; @Akyazi2017].
+Unfortunately, the *Brevipalpus* mite species complex is known to contain cryptic species [@Childers2011] whose identification can be improved with molecular methods as well as more advanced microscopy techniques, such as cryo scanning electron microscopy (currently known as Cryo-SEM) [@Skoracka2015; @Leon2010; @Beard2015].
+With that in mind, we collected additional samples   of the mites from the same site as the original OFV detection and sent them to the USDA-ARS in Beltsville to observe the mites with Cryo-SEM  techniques, which agreed with both prior identifications of *B.
 californicus* s.l.
-(`r citef("fig_2")`) but also revealed the presence of two other species: *B.
+<!-- (`r citef("fig_2")`) -->but revealed the presence of two other species: *B.
 obovatus* and *B.
@@
 
-The earliest mention of a virus which may have been OFV is @Ko1985, who detected nuclear inclusions caused by an undescribed bacilliform rhabdovirus.
-@Ko1985 described the spoke-wheel configurations typically associated with OFV [@Chang1976], in *Brassia* orchids, but unfortunately made no mention of mites or further investigations of this virus.
-The first certain report of OFV in the US was made by @Bratsch2015, who confirmed the presence of OFV in *Phalaenopsis* hybrids in the US, using TEM of ultrathin sections of plant tissue as well as molecular sequence analysis.
-In addition, @Bratsch2015 detected *Brevipalpus* mites and their exoskeletons associated with OFV-infected plants.
-It appears that @Bratsch2015 did not make a conclusive species identification, but did cite @Kondo2003, suggesting a mite in the *B.
-californicus* group as the vector.
+The first report of OFV in the United State is thought to be @Ko1985, who describes nuclear inclusions caused by an undescribed bacilliform rhabdovirus in *Brassia* orchids.
+The significance of this report is their reference to spoke-wheel configurations of the viral particles [@Ko1985], a sign typically associated with OFV infection [@Chang1976].
+Unfortunately, @Ko1985 made no mention of mites or further investigations of this virus.
+The first certain report of OFV in the US was made by @Bratsch2015, who confirmed the presence of OFV in *Phalaenopsis* hybrids in the US, using TEM of ultrathin sections of plant tissue as well as molecular sequence analysis and its association with *Brevipalpus* mites.
+The authors did not make a conclusive species identification but suggested the mite species was *B.
+californicus* group as the vector as referred by @Kondo2003.
 
@@
 [@Mei2016].
-Our plants are thought to belong to different species of *Liriope* which are not *L.
-spicata* and we are not aware of any record other than this manuscript which reports OFV infection in *Ophiopogon* plants.
-Unfortunately, liriopogons species are very similar in appearance and growth habit, with few useful characters used for their classification [@Fantz2008a].
+The Florida collected plants of *Liriope* spp., cv 'Gigantea' are thought to belong to either *Liriope muscari* or *Liriope gigantea*.
+In addition, we are not aware of any record other than this manuscript which reports OFV infection in *Ophiopogon* plants.
+Unfortunately, the Ophiopogonae group includes species of *Liriope* and *Ophiopogon* which are very similar in appearance and growth habit, with few useful morphological characters used for their classification [@Fantz2008a].
 Furthermore, the horticultural industry has created a diverse array of cultivars of these plants, which are often mislabeled [@Fantz2008a].
@@
 Together, these factors make it difficult to differentiate and identify plants in the landscape by visual inspection alone.
-These obfuscations of species identity may be accounted for in the future via sequence comparisons of the OFV-infected plants, but these comparisons are beyond the scope of our current report.
+These obfuscations of species identity may be accounted for in the future via sequence comparisons of the OFV-infected plants [@Rudall2000; @Wang2014], but these comparisons are beyond the scope of our current report.
 Nonetheless, we are confident that ours is the first report of OFV infecting *Aspidistra elatior*; although [@Zheng2013] mentions the association of *B.
@@
 
-### Control methods for *Brevipalpus* mites
+<!-- ### Control methods for *Brevipalpus* mites -->
 
-<!-- Reducing the populations of the *Brevipalpus* mite vector may be able to reduce the spread of OFV by infective mites, but infected plants are not able to recover from the virus and must be rouged or removed.
+<!-- <!-- Reducing the populations of the *Brevipalpus* mite vector may be able to reduce the spread of OFV by infective mites, but infected plants are not able to recover from the virus and must be rouged or removed.
 Rouging plants is a direct and efficient option to remove mite and virus populations quickly but increases in difficultly with the number of plants involved.
@@
 
-<!-- Most research on the integrated management of mites has been catered towards controlling various species of spider mites (Acari: Tetranychidae) [@Leeuwen2015], but many of those methods can be applied to *Brevipalpus* spp.
+<!-- <!-- Most research on the integrated management of mites has been catered towards controlling various species of spider mites (Acari: Tetranychidae) [@Leeuwen2015], but many of those methods can be applied to *Brevipalpus* spp.
 as well: -->
-Chemical control via synthetic acaricides is commonly used to manage *Brevipalpus* spp.
+<!-- Chemical control via synthetic acaricides is commonly used to manage *Brevipalpus* spp.
 [@Leeuwen2015], but acaricides have some drawbacks.
@@
 Lastly, application costs of chemical controls can be large and increase the cost of production [@Rodrigues2000a], nevertheless chemical applications are valuable tools used to consider against *Brevipalpus*.
+-->
 
-Various biological control methods have also been studied, but their use has not been widely adopted [@Messing2017].
+<!-- Various biological control methods have also been studied, but their use has not been widely adopted [@Messing2017].
 Even so, some studies have found biological control methods which could be used specifically for *Brevipalpus* mites: The predatory mite *Galendromus helveolus* (Chant) (Acari: Phytoseiidae) has been reported to feed on eggs, larvae and nymphs of *B.
@@
 In our own surveys, we have found mites which succumbed to fungal infections (`r citef("fig_3")`); however the fungal species was not determined.
+-->
 
 ### Conclusion
-
-Detecting OFV in Florida represents a concern for horticulturists who grow susceptible plants of economic importance, including orchids, *Liriope*, *Ophiopogon*, or other susceptible Asparagaceae spp.
-which are commonly used in landscaping.
-Florida is also home to a plethora of native and naturalized orchid species, many of which are threatened, including the famous Ghost Orchid, *Dendrophylax lindenii* (Lindl.) Benth.
-ex Rolfe.
-Furthermore, OFV represents an obstacle to overcome for the burgeoning interest in cultivating *Vanilla* in southern Florida [@Chambers2019].
-Lastly, some OFV isolates are known to be involved with nuclear types of citrus leprosis [@Roy2015a], which may be a cause for concern for the citrus industry.
-In fact, @Kitajima2011a found that the Citrus Leprosis virus (CiLV) which previously affected Florida citrus was a nuclear type of citrus leprosis, which are closely related to OFV strains [@Roy2013a].
+OFV is the type member of the genus *Dichorhavirus* (family *Rhabdoviridae*, order *Mononegavirales*) contain a bipartite, single-stranded and negative sense RNA genome.
+The dichorhavirus that infects citrus in Hawaii, Mexico, Colombia, and South Africa are identical to the OFV in gene order, content, and the genome sequence.
+According to the International committee on Taxonomy of Viruses (ICTV) classification, OFV consist of two orchid strains (OFV-Orc1 and OFV-Orc2) and two citrus strains (OFV-Cit1 and OFV-Cit2).
+Both the orchid strains of OFV infects citrus but none of the citrus strain have been reported from any orchid species.
+Detecting OFV in Florida represents a concern for horticulturists who grow orchids, *Liriope*, *Ophiopogon*, or other susceptible Asparagaceae species which are commonly used in landscaping.
+Florida is also home to a plethora of native and naturalized orchid species, many of which are threatened, including cultivating *Vanilla* in southern Florida [@Chambers2019] and the famous Ghost Orchid, [*Dendrophylax lindenii* (Lindl.) Benth.
+ex Rolfe].
+The first time leprosis has been observed in the Florida in 1860’s and eradicated in the mid-1960s.
+In fact, @Kitajima2011 found that the Citrus Leprosis virus (CiLV) which previously affected Florida citrus was a nuclear type of citrus leprosis, which are closely related to OFV strains [@Roy2013].
+Association of a distant relative of OFV which was named as Citrus leprosis dichorhavirus-N0 (CiLV-N0) was confirmed in relation to the leprosis disease outbreak in Florida [@Hartung2015].
+The recent detection of OFV-Orc1 in South Africa [@Cook2019] in *C.
+sinensis* (Navel and Valencia orange) and OFV-Orc2 in Hawaii [@Velarde2021] in *C.
+reticulata* (mandarin) and *C.
+jambhiri* (rough lemon) highlights the threat of different strains of OFV; which will be a definite concern to the multi-billion dollar citrus industry.
+Lastly, some OFV isolates are known to be involved with citrus leprosis disease in Mexico [@Roy2015], which may be a cause for concern for the citrus industry.
 *B.
 californicus* and *B.
-yothersi* are both known vectors of Dichorhaviruses (OFV) and Cileviruses (Citrus Leprosis) [@BeltranBeltran2020; @Kondo2003; @Knorr1968] and *B.
-obovatus* is a suspected vector as well [@Childers2003a].
-All three mite species/complexes are present in Florida [@Childers2003a; @Akyazi2017] (`r citef("fig_4")`); therefore, it is critical to identify the vector of OFVs in Florida and monitor its spread to determine what risk this virus represents for plants in Florida and the surrounding regions.
+yothersi* are both known vectors of Dichorhaviruses (OFV) and Cileviruses (Citrus Leprosis) [@Knorr1968; @Kondo2003; @Beltran-Beltran2020] and *B.
+obovatus* is a suspected vector as well [@Childers2003].
+All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017]<!-- (`r citef("fig_4")`) -->.
+Therefore, it is critical to identify the vector of OFVs in Florida and monitor its spread to determine the risk this virus represents for the native plants, agriculture and the ornamental/landscaping industries of Florida and the surrounding regions.
 
 ### Acknowledgements
-We would like to give a special thanks to the Tallahassee Museum for their patience, cooperation and support with collecting plant samples.
-We also want to thank Dr.
-Sam Bolton for checking the mites we have sent to FDACS for species validation.
+We would like to give a special thanks to the Tallahassee Museum for their patience, cooperation, and support with collecting plant samples.
+We also want to thank Drs.
+Sam Bolton, FDACS and Aline Tassi, Univ.
+of Sao Paulo, Brazil for checking the mites we have sent for species validation.
 We are especially indebted to the late Dr.
@@
 This research was partly funded by the USDA National Institute of Food and Agriculture, Hatch project FLA-NFC-005607.
+Mention of trade names or commercial products in this publication is solely for the purpose of providing specific information and does not imply recommendation or endorsement by the USDA; USDA is an equal opportunity provider and employer.
 
 ### References
-
 <div id="refs"></div>
 
-### Table
+<!-- ### Table -->
 
-|Scientific Name|Common Names|Symptoms Observed|
-|:-----------|:--------------|:----------------|
-|*Liriope muscari* Bailey| Lilyturf, Orchardgrass, Monkeygrass| Ringspots, Chlorotic Flecking, Necrotic Lesions|
-|*Liriope gigantea*\* Hume| Giant Lilyturf| Ringspots, Chlorotic Flecking, Necrotic Lesions|
-|*Ophiopogon japonicus* Ker Gawl.| Dwarf Lilyturf, Mondo Grass, Snake's beard| Ringspots, Chlorotic Flecking, Necrotic Lesions|
-|*Ophiopogon intermedius*\*\* Don| Aztec Grass, 'Argenteomarginatus' | Ringspots, Chlorotic Flecking, Necrotic Lesions|
-|*Aspidistra elatior* Blume| Cast Iron Plant, Bar-room Plant | Chlorosis, Necrotic Lesions|
-`r tab_nums(name = "tab_1", caption = "List of plants with symptoms of Orchid fleck dichorhavirus found in northern Florida.
+<!-- |Scientific Name|Common Names|Symptoms Observed| -->
+<!-- |:-----------|:--------------|:----------------| -->
+<!-- |*Liriope muscari* Bailey| Lilyturf, Orchardgrass, Monkeygrass| Ringspots, Chlorotic Flecking, Necrotic Lesions| -->
+<!-- |*Liriope gigantea*\* Hume| Giant Lilyturf| Ringspots, Chlorotic Flecking, Necrotic Lesions| -->
+<!-- |*Ophiopogon japonicus* Ker Gawl.| Dwarf Lilyturf, Mondo Grass, Snake's beard| Ringspots, Chlorotic Flecking, Necrotic Lesions| -->
+<!-- |*Ophiopogon intermedius*\*\* Don| Aztec Grass, 'Argenteomarginatus' | Ringspots, Chlorotic Flecking, Necrotic Lesions| -->
+<!-- |*Aspidistra elatior* Blume| Cast Iron Plant, Bar-room Plant | Chlorosis, Necrotic Lesions| -->
+<!-- `r tab_nums(name = "tab_1", caption = "List of plants with symptoms of Orchid fleck dichorhavirus found in northern Florida.
 * *L.
@@
 * * *O.
-intermedius* is sometimes misclassified as *Liriope muscari* ‘Variegated Evergreen Giant’ [@Fantz2008b, @Fantz2009] or ‘Grandiflora White’ [@Fantz2009].")`
+intermedius* is sometimes misclassified as *Liriope muscari* ‘Variegated Evergreen Giant’ [@Fantz2008b, @Fantz2009] or ‘Grandiflora White’ [@Fantz2009].")` -->
 
@@
 
-`r fig_nums(name = "fig_2", caption = "LT-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.
+<!-- `r fig_nums(name = "fig_2", caption = "LT-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.
 LT-SEM images provided by Dr.
-Gary Bauchan, USDA-ARS 2021")`
+Gary Bauchan, USDA-ARS 2021")` -->
 
-`r fig_nums(name = "fig_3", caption = "LT-SEM images of unidentified fungus infecting *Brevipalpus californicus* sensu lato: (a) Infested *B.
+<!-- `r fig_nums(name = "fig_3", caption = "LT-SEM images of unidentified fungus infecting *Brevipalpus californicus* sensu lato: (a) Infested *B.
 californicus* adult, dorsal (b) Detail of fungal sporangia.
 LT-SEM images provided by Dr.
-Gary Bauchan, USDA-ARS 2021")`
+Gary Bauchan, USDA-ARS 2021")` -->
 
-`r fig_nums(name = "fig_4", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
+<!-- `r fig_nums(name = "fig_4", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
 yothersi*, dorsal (b) *B.
@@
 SEM images provided by Dr.
-Ron Ochoa, USDA-ARS 2021")`
+Ron Ochoa, USDA-ARS 2021")` -->
 
@@
 ```
-```{r, fig_2, warning=FALSE}
-grid::grid.raster(tiff::readTIFF( "images/b_cali.tif"))
-```
-```{r, fig_3, warning=FALSE}
-grid::grid.raster(tiff::readTIFF( "images/fungus_mite.tif"))
-```
-```{r, fig_4, warning=FALSE}
-grid::grid.raster(tiff::readTIFF( "images/other_mites.tif"))
-```
+
+<!-- ```{r, fig_2, warning=FALSE} -->
+<!-- grid::grid.raster(tiff::readTIFF( "images/b_cali.tif")) -->
+<!-- ``` -->
+
+<!-- ```{r, fig_3, warning=FALSE} -->
+<!-- grid::grid.raster(tiff::readTIFF("images/fungus_mite.tif")) -->
+<!-- ``` -->
+
+<!-- ```{r, fig_4, warning=FALSE} -->
+<!-- grid::grid.raster(tiff::readTIFF( "images/other_mites.tif")) -->
+<!-- ``` -->

### 2021-03-24 ofv_fife_2021.Rmd
Added a brief description of symptoms on A. elatior

@@
 Plant samples included various cultivars of Nolinoid plants, including *Liriope* spp., *Ophiopogon* spp., and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) which were located at the same site as the original infected *Liriope* spp., cv 'Gigantea'.
-Samples were tested via RT-PCR at the NFREC<!-- (`r citet("tab_1")`) --> to confirm the presence of OFV.
+*A.
+elatior* infected with OFV have chlorotic leaves or chlorotic flecks (`r citef("fig_1")`).
+No ringspots have been observed on *A.
+elatior* to date.
+All plant samples were tested via RT-PCR at the NFREC<!-- (`r citet("tab_1")`) --> to confirm the presence of OFV.
 
@@
 These obfuscations of species identity may be accounted for in the future via sequence comparisons of the OFV-infected plants [@Rudall2000; @Wang2014], but these comparisons are beyond the scope of our current report.
-Nonetheless, we are confident that ours is the first report of OFV infecting *Aspidistra elatior*; although [@Zheng2013] mentions the association of *B.
+Nonetheless, we are confident that ours is the first report of OFV infecting *A.
+elatior*; although [@Zheng2013] mentions the association of *B.
 californicus* with *A.

### 2021-03-26 ofv_presentation_2021.Rmd
New Rmd for creating ESA SEB 2021 presentation

--- 2021-03-24 ofv_fife_2021.Rmd
@@
 output: 
-  word_document:
-    reference_docx: ../r-word-templates/word-template-jis.docx
-# - html_document
+  beamer_presentation: 
+    latex_engine: xelatex
 bibliography: 'thesis.bib'
@@
 
-### Keywords:
-False spider mite, flat mite, *Brevipalpus*-transmitted viruses, *Liriope*, Nolinoideae, *Ophiopogon*, Ruscaceae, Rutaceae, Asparagaceae, orchid, Orchidaceae, pests, ornamental plants, orchid fleck virus.
-
-\pagebreak
+### Background
 *Orchid fleck virus* (OFV) is the type member for the genus *Dichorhavirus*, family Rhabdoviridae; a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
@@
 
+### Symptoms
 OFV-infected plants exhibit various symptoms dependent on the infected plant species as well as the strain of the OFV [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns (`r citef("fig_1")`).
@@
 
+### Distribution
 OFV was first described infecting *Cymbidium* orchids in Japan [@Doi1977].
@@
 
+### Infectivity
 OFV naturally infects more than fifty species of Orchidaceae [@Kitajima2010; @Peng2013], some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], as well as Rutaceae: *Citrus* where it causes citrus leprosis-like symptoms [@Beltran-Beltran2020; @GarciaEscamilla2018; @Roy2020].
@@
 
+### Detection
 During June 2020, chlorotic ringspot symptoms were observed on Giant Lilyturf *Liriope* spp., cv.
@@
 
+### Testing
 Viral infections of suspected plant leaf samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL.
@@
 
+### Map
 Further surveys of plants belonging to the subfamily Nolinoidaea in Florida have revealed more sites with symptomatic plants in both Leon and Alachua counties.
@@
 
+### Previous Reports
 The first report of OFV in the United State is thought to be @Ko1985, who describes nuclear inclusions caused by an undescribed bacilliform rhabdovirus in *Brassia* orchids.
@@
 We are especially indebted to the late Dr.
-Gary Bauchan for permitting us to use these beautiful LT-SEM images, he will be greatly missed.
+Gary Bauchan for permitting us to use these beautiful Cryo-SEM images, he will be greatly missed.
 This research was partly funded by the USDA National Institute of Food and Agriculture, Hatch project FLA-NFC-005607.
@@
 
-### References
-<div id="refs"></div>
+<!-- ### References -->
+<!-- <div id="refs"></div> -->
 

### 2021-03-26 ofv_fife_2021.Rmd
Made corrections and edits from collaborators

@@
 
-Austin **Fife**^1^, Daniel **Carrillo**^2^, Gary **Knox**^3^, Fanny **Iriarte**^4^, Kishore **Dey**^5^, Avijit **Roy**^6^, Ronald **Ochoa**^7^, Gary **Bauchan**^8^ $\dagger$, Mathews **Paret**^4^, Xavier **Martini**^1^\*
+Austin **Fife**^1^, Daniel **Carrillo**^2^, Gary **Knox**^3^, Fanny **Iriarte**^4^, Kishore **Dey**^5^, Avijit **Roy**^6^, Ronald **Ochoa**^7^, Gary **Bauchan**^8^ $\dagger$, Mathews **Paret**^4,9^, Xavier **Martini**^1^\*
 
@@
 
+^9^ Plant Pathology Department, University of Florida, Gainesville, FL 32611
+
 *Corresponding author; E-mail: xmartini\@ufl.edu Phone: 850-875-7160 Fax: 352-846-6617
@@
 californicus* species group exclusively can transmit Orchid fleck dichorhavirus (OFV) in a persistent propagative manner.
-OFV is the type species for the genus *Dichorhavirus* and infects more than fifty plant species belongs to the family Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (*Citrus*).
+OFV is the type species for the genus *Dichorhavirus* and infects more than fifty plant species belonging to the family Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (*Citrus*).
 During June 2020, chlorotic ringspot symptoms on Giant Lilyturf (*Liriope* spp., cv.
@@
 In this study we are reporting three new hosts from the family Asperagaceae.
-To know the extended host range of OFVs, a survey in the citrus growing regions in Florida is essential with special emphasis to the plants belongs to the family Rutaceae and Asparagaceae.
+To know the extended host range of OFVs, a survey in Florida's citrus growing regions is essential, emphasizing plants within the families Rutaceae and Asparagaceae.
 
@@
 Other members of this genus are: *Citrus chlorotic spot virus*, *Citrus leprosis virus* N, *Clerodendrum chlorotic spot virus* and *Coffee ringspot virus* [@Dietzgen2018a].
-Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the only known vector for dichorhaviruses [@Maeda1998], and *Brevipalpus californicus* (Banks) mites are the only mite known to transmit OFV in a persistent propagative manner [@Kondo2003].
+Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the only known vector for dichorhaviruses [@Maeda1998], and mites in the *Brevipalpus californicus* (Banks) group are the only known to transmit OFV in a persistent propagative manner [@Kondo2003].
 
-OFV-infected plants exhibit various symptoms dependent on the infected plant species as well as the strain of the OFV [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns (`r citef("fig_1")`).
+OFV-infected plants exhibit various symptoms depending on the infected plant species as well as the strain of the OFV [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns (`r citef("fig_1")`).
 <!-- These lesions are thought to be associated with the feeding sites of the mite vector [@cite?]. Also, is it possibly a sign of RNAi plant defenses? See Hull Plant Virology -->
@@
 OFV was first described infecting *Cymbidium* orchids in Japan [@Doi1977].
-Many countries have reported OFV and OFV-like rhabdoviruses infecting orchids worldwide [@Kondo2003], including Asia: [China [@Peng2017], Korea [@Chang1991, @Zheng2013]], Africa: [South Africa [@Blanchfield2001]], North America: [The United States [@Blanchfield2001; @Bratsch2015]], South America: [Brazil [@Kitajima1974; @Kitajima2001], Colombia [@Kubo2009b], Costa Rica [@FreitasAstua2002], Paraguay [@RamosGonzalez2015]], Europe: [Denmark [@Begtrup1972], France [@Sauvetre2018], Germany [@Lesemann1975; @Petzold1971]] and Oceania: [Australia [@Lesemann1971; @Lesemann1975; @Gibbs2000], Fiji [@Pearson1993], Vanuatu [@Pearson1993]].
+OFV and OFV-like rhabdoviruses have been reported infecting orchids in Asia: [China [@Peng2017], Korea [@Chang1991, @Zheng2013]], Africa: [South Africa [@Cook2019]], North America: [The United States [@Blanchfield2001; @Bratsch2015], Mexico [@OteroColina2021]], South America: [Brazil [@Kitajima1974; @Kitajima2001], Colombia [@Kubo2009b], Costa Rica [@FreitasAstua2002], Paraguay [@RamosGonzalez2015]], Europe: [Denmark [@Begtrup1972], France [@Sauvetre2018], Germany [@Lesemann1975; @Petzold1971]] and Oceania: [Australia [@Lesemann1971; @Lesemann1975; @Gibbs2000], Fiji [@Pearson1993], Vanuatu [@Pearson1993]].
 The prevalence of OFV and its mite vector is thought to be associated with the movement of infected orchids [@Dietzgen2018a].
 
-OFV naturally infects more than fifty species of Orchidaceae [@Kitajima2010; @Peng2013], some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], as well as Rutaceae: *Citrus* where it causes citrus leprosis-like symptoms [@Beltran-Beltran2020; @GarciaEscamilla2018; @Roy2020].
+OFV naturally infects more than fifty species of Orchidaceae [@Kitajima2010; @Peng2013], some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], as well as Rutaceae: (*Citrus*), where it causes citrus leprosis-like symptoms [@Cook2019; @OlmedoVelarde2019; @Roy2015; @Roy2020].
 Mechanical transmission of OFV is possible under lab conditions to various Chenopodiaceae, Aizoaceae, Fabaceae, and Solanaceae [@Chang1976; @Kondo2003; @Peng2013].
@@
 The presence of OFV was confirmed using OFV generic R2-Dicho-GF and R2-Dicho-GR primers [@Roy2020] by one step conventional RT-PCR, amplifying ~800 nt of L-gene (RNA2) amplicon from an infected *Liriope* leaf sample.
-The RT-PCR amplicon was sequenced using Sanger sequencing and confirmed the presence of OFV in the tested samples.
-Sanger sequencing of RT-PCR amplicons shared 98\% nucleotide identity with orchid strains of OFV (GenBank Accession numbers: AB244418 and LC222630) [@Kondo2006; @Kondo2017].
+Sanger sequencing of RT-PCR amplicons shared 98\% nucleotide identity with orchid strains of OFV: OFV-Orc1 and OFV-Orc2 (GenBank Accession numbers: AB244418 and LC222630) [@Kondo2006; @Kondo2017].
 Further surveys of putatively OFV-infected plants were taken during subsequent visits to the initial site of collection.
-Plant samples included various cultivars of Nolinoid plants, including *Liriope* spp., *Ophiopogon* spp., and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) which were located at the same site as the original infected *Liriope* spp., cv 'Gigantea'.
+Plant samples included various cultivars of Nolinoid plants, including *Liriope* spp., *Ophiopogon* spp., and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea).
 *A.
@@
 
-Further surveys of plants belonging to the subfamily Nolinoidaea in Florida have revealed more sites with symptomatic plants in both Leon and Alachua counties.
-In addition to the discovery of the OFV-infected plants, we collected mites from symptomatic plants in both Leon and Alachua counties.
-In addition to the discovery of the OFV-infected plants, we collected mites from symptomatic plants in Leon county which were observed with phase contrast microscopy.
-We encountered both an unidentified eriophyoid mite species on the *Liriope* spp., along with flat mites on all species tested (*Liriope* spp., *Ophiopogon* spp., and *A.
+Further surveys of plants belonging to the subfamily Nolinoidaea in Florida have revealed more sites with symptomatic plants in Leon and Alachua counties.
+Mites were collected from symptomatic plants in Leon county and observed with phase contrast microscopy.
+We encountered both an unidentified eriophyoid mite species on the *Liriope* spp., along with flat mites on all the plant species tested (*Liriope* spp., *Ophiopogon* spp., and *A.
 elatior*).
-The flat mites were originally identified as *Brevipalpus californicus* (Banks) sensu lato, an identity which was confirmed by the FDACS via Differential Interference Contrast (DIC) microscopy.
-*Brevipalpus* mites have been previously associated with OFV [@Beltran-Beltran2020; @GarciaEscamilla2018; @Dietzgen2018b] as well as similar diseases [@Kitajima2010] and are known to feed on a large variety of economically important plants [@Childers2003a; @Akyazi2017].
-Unfortunately, the *Brevipalpus* mite species complex is known to contain cryptic species [@Childers2011] whose identification can be improved with molecular methods as well as more advanced microscopy techniques, such as cryo scanning electron microscopy (currently known as Cryo-SEM) [@Skoracka2015; @Leon2010; @Beard2015].
-With that in mind, we collected additional samples   of the mites from the same site as the original OFV detection and sent them to the USDA-ARS in Beltsville to observe the mites with Cryo-SEM  techniques, which agreed with both prior identifications of *B.
+The flat mites were originally identified as *Brevipalpus californicus* (Banks) sensu lato by the FDACS via Differential Interference Contrast (DIC) microscopy.
+The *Brevipalpus* mite species complex is known to contain cryptic species [@Childers2011] that require advanced microscopy techniques, such as cryo scanning electron microscopy (Cryo-SEM) for species identification [@Skoracka2015; @Leon2010; @Beard2015].
+Additional mite samples from the original OFV detection site were observed with Cryo-SEM (`r citef("fig_2")`).
+The determinations agreed with both prior identifications of *B.
 californicus* s.l.
-<!-- (`r citef("fig_2")`) -->but revealed the presence of two other species: *B.
+but revealed the presence of two other species *B.
 obovatus* and *B.
-confusus*.
+confusus* (`r citef("fig_3")`).
 
-The first report of OFV in the United State is thought to be @Ko1985, who describes nuclear inclusions caused by an undescribed bacilliform rhabdovirus in *Brassia* orchids.
+The first report of OFV in the United States is thought to be @Ko1985, who describes nuclear inclusions caused by an undescribed bacilliform rhabdovirus in *Brassia* orchids.
 The significance of this report is their reference to spoke-wheel configurations of the viral particles [@Ko1985], a sign typically associated with OFV infection [@Chang1976].
 Unfortunately, @Ko1985 made no mention of mites or further investigations of this virus.
-The first certain report of OFV in the US was made by @Bratsch2015, who confirmed the presence of OFV in *Phalaenopsis* hybrids in the US, using TEM of ultrathin sections of plant tissue as well as molecular sequence analysis and its association with *Brevipalpus* mites.
-The authors did not make a conclusive species identification but suggested the mite species was *B.
-californicus* group as the vector as referred by @Kondo2003.
+The first certain report of OFV in the US was made by @Bratsch2015, confirming the presence of OFV in *Phalaenopsis* hybrids in the US, using TEM of ultrathin sections of plant tissue as well as molecular sequence analysis and its association with *Brevipalpus* mites.
+The authors did not make a conclusive species identification but suggested the mite vector was within the *B.
+californicus* group, as referred by @Kondo2003.
 
@@
 The Florida collected plants of *Liriope* spp., cv 'Gigantea' are thought to belong to either *Liriope muscari* or *Liriope gigantea*.
-In addition, we are not aware of any record other than this manuscript which reports OFV infection in *Ophiopogon* plants.
-Unfortunately, the Ophiopogonae group includes species of *Liriope* and *Ophiopogon* which are very similar in appearance and growth habit, with few useful morphological characters used for their classification [@Fantz2008a].
+We are not aware of any previous report of OFV infection in *Ophiopogon* plants.
+Unfortunately, the Ophiopogonae group includes species of *Liriope* and *Ophiopogon* which are very similar in appearance and growth habit, with few useful morphological characters availabe for their classification [@Fantz2008a].
 Furthermore, the horticultural industry has created a diverse array of cultivars of these plants, which are often mislabeled [@Fantz2008a].
@@
 ### Conclusion
-OFV is the type member of the genus *Dichorhavirus* (family *Rhabdoviridae*, order *Mononegavirales*) contain a bipartite, single-stranded and negative sense RNA genome.
 The dichorhavirus that infects citrus in Hawaii, Mexico, Colombia, and South Africa are identical to the OFV in gene order, content, and the genome sequence.
 According to the International committee on Taxonomy of Viruses (ICTV) classification, OFV consist of two orchid strains (OFV-Orc1 and OFV-Orc2) and two citrus strains (OFV-Cit1 and OFV-Cit2).
-Both the orchid strains of OFV infects citrus but none of the citrus strain have been reported from any orchid species.
+Both the orchid strains of OFV infects citrus [@Roy2020], but none of the citrus strains have been reported from any orchid species.
 Detecting OFV in Florida represents a concern for horticulturists who grow orchids, *Liriope*, *Ophiopogon*, or other susceptible Asparagaceae species which are commonly used in landscaping.
@@
 ex Rolfe].
-The first time leprosis has been observed in the Florida in 1860’s and eradicated in the mid-1960s.
-In fact, @Kitajima2011 found that the Citrus Leprosis virus (CiLV) which previously affected Florida citrus was a nuclear type of citrus leprosis, which are closely related to OFV strains [@Roy2013].
-Association of a distant relative of OFV which was named as Citrus leprosis dichorhavirus-N0 (CiLV-N0) was confirmed in relation to the leprosis disease outbreak in Florida [@Hartung2015].
+Citrus leprosis was present in Florida during the 1860’s and eradicated in the mid-1960s.
+In fact, @Kitajima2011 found that the Citrus Leprosis virus (CiLV) which previously affected Florida citrus was a nuclear type of citrus leprosis closely related to OFV strains [@Roy2013].
+Association of a distant relative of OFV named Citrus leprosis dichorhavirus-N0 (CiLV-N0) was confirmed in relation to the leprosis disease outbreak in Florida [@Hartung2015].
 The recent detection of OFV-Orc1 in South Africa [@Cook2019] in *C.
@@
 jambhiri* (rough lemon) highlights the threat of different strains of OFV; which will be a definite concern to the multi-billion dollar citrus industry.
-Lastly, some OFV isolates are known to be involved with citrus leprosis disease in Mexico [@Roy2015], which may be a cause for concern for the citrus industry.
+Lastly, some OFV isolates are known to be involved with citrus leprosis disease in Mexico [@Roy2015], which is a cause for concern for the citrus industry.
 *B.
@@
 obovatus* is a suspected vector as well [@Childers2003].
-All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017]<!-- (`r citef("fig_4")`) -->.
+All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017] (`r citef("fig_3")`).
 Therefore, it is critical to identify the vector of OFVs in Florida and monitor its spread to determine the risk this virus represents for the native plants, agriculture and the ornamental/landscaping industries of Florida and the surrounding regions.
@@
 We are especially indebted to the late Dr.
-Gary Bauchan for permitting us to use these beautiful LT-SEM images, he will be greatly missed.
+Gary Bauchan for his contributions to this study and the field of acarology, he will be greatly missed.
 This research was partly funded by the USDA National Institute of Food and Agriculture, Hatch project FLA-NFC-005607.
@@
 
-<!-- `r fig_nums(name = "fig_2", caption = "LT-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.
-LT-SEM images provided by Dr.
-Gary Bauchan, USDA-ARS 2021")` -->
+`r fig_nums(name = "fig_2", caption = "LT-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.")`
 
-<!-- `r fig_nums(name = "fig_3", caption = "LT-SEM images of unidentified fungus infecting *Brevipalpus californicus* sensu lato: (a) Infested *B.
+`r fig_nums(name = "fig_3", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
+yothersi*, dorsal (b) *B.
+yothersi*, lateral (c) *B.
+obovatus*, dorsal.")`
+
+<!-- `r fig_nums(name = "fig_4", caption = "LT-SEM images of unidentified fungus infecting *Brevipalpus californicus* sensu lato: (a) Infested *B.
 californicus* adult, dorsal (b) Detail of fungal sporangia.
@@
 Gary Bauchan, USDA-ARS 2021")` -->
-
-<!-- `r fig_nums(name = "fig_4", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
-yothersi*, dorsal (b) *B.
-yothersi*, lateral (c) *B.
-obovatus*, dorsal.
-SEM images provided by Dr.
-Ron Ochoa, USDA-ARS 2021")` -->
 
@@
 
-<!-- ```{r, fig_2, warning=FALSE} -->
-<!-- grid::grid.raster(tiff::readTIFF( "images/b_cali.tif")) -->
-<!-- ``` -->
+```{r, fig_2, warning=FALSE}
+grid::grid.raster(tiff::readTIFF( "images/b_cali.tif"))
+```
 
-<!-- ```{r, fig_3, warning=FALSE} -->
+```{r, fig_3, warning=FALSE}
+grid::grid.raster(tiff::readTIFF( "images/other_mites.tif"))
+```
+
+<!-- ```{r, fig_4, warning=FALSE} -->
 <!-- grid::grid.raster(tiff::readTIFF("images/fungus_mite.tif")) -->
 <!-- ``` -->
-
-<!-- ```{r, fig_4, warning=FALSE} -->
-<!-- grid::grid.raster(tiff::readTIFF( "images/other_mites.tif")) -->
-<!-- ``` -->

### 2021-03-26 ofv_fife_2021.Rmd
Fixed misspelling

@@
 We are not aware of any previous report of OFV infection in *Ophiopogon* plants.
-Unfortunately, the Ophiopogonae group includes species of *Liriope* and *Ophiopogon* which are very similar in appearance and growth habit, with few useful morphological characters availabe for their classification [@Fantz2008a].
+Unfortunately, the Ophiopogonae group includes species of *Liriope* and *Ophiopogon* which are very similar in appearance and growth habit, with few useful morphological characters available for their classification [@Fantz2008a].
 Furthermore, the horticultural industry has created a diverse array of cultivars of these plants, which are often mislabeled [@Fantz2008a].

### 2021-03-26 ofv_presentation_2021.Rmd
Working on presentation. I will need to produce the text & etc here, then apply the template after rendering

--- 2021-03-23 ofv_fife_2021.Rmd
@@
 ---
-title: "For submission to the Journal of Integrated Pest Management"
-subtitle: "Category: 'Issues'"
+title: "*Orchid fleck dichorhavirus*: a new *Brevipalpus* transmitted virus fresh from Florida"
+subtitle: "A. **Fife**^1^, D. **Carrillo**^2^, G. **Knox**^3^, F. **Iriarte**^4^, K. **Dey**^5^, A. **Roy**^6^, R. **Ochoa**^7^, G. **Bauchan**^8^, M. **Paret**^4,9^, X. **Martini**^1^*"
+author: "^1^ University of Florida, Department of Entomology and Nematology, North Florida Research and Education Center, Quincy FL 32351 ^2^ University of Florida, Department of Entomology and Nematology, Tropical Research and Education Center, Homestead FL 33031 ^3^ University of Florida, Department of Environmental Horticulture, North Florida Research and Education Center, Quincy FL 32351 ^4^ University of Florida, Department of Plant Pathology, North Florida Research and Education Center, Quincy FL 32351 ^5^ The Florida Department of Agriculture and Consumer Services, Division of Plant Industry, Section of Plant Pathology, Doyle Conner Building, 1911 SW 34th street, Gainesville, FL 32608 ^6^	United States Department of Agriculture – Agriculture Research Service, Molecular Plant Pathology Laboratory, 10300 Baltimore Ave, Bldg.
+4 BARC-West, Beltsville, MD 20705 ^7^ United States Department of Agriculture - Agriculture Research Service, Systematic Entomology Laboratory 10300 Baltimore Ave, Bldg.
+5 BARC-West, Beltsville, MD 20705 ^8^	United States Department of Agriculture - Animal and Plant Health Inspection Service, Electron and Confocal Microscopy Unit, Bldg.
+12  BARC-West, 10300 Baltimore Ave, Beltsville, MD 20705 ^9^ Plant Pathology Department, University of Florida, Gainesville, FL 32611"
+date: March 29, 2021
 output: 
-  word_document:
-    reference_docx: ../r-word-templates/word-template-jis.docx
-# - html_document
+  powerpoint_presentation
 bibliography: 'thesis.bib'
@@
 
-### First report of the *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) virus, *Orchid fleck virus* (Mononegavirales: Rhabdoviridae) infecting three ornamentals in Florida
+# A visit to the Zoo
+```{r, warning=FALSE}
+knitr::include_graphics('images/symp-ofv-lir.jpg')
+```
 
-Austin **Fife**^1^, Daniel **Carrillo**^2^, Gary **Knox**^3^, Fanny **Iriarte**^4^, Kishore **Dey**^5^, Avijit **Roy**^6^, Ronald **Ochoa**^7^, Gary **Bauchan**^8^ $\dagger$, Mathews **Paret**^4^, Xavier **Martini**^1^\*
+# a
+```{r, warning=FALSE}
+knitr::include_graphics('images/symp-ofv-lir.jpg')
+```
 
-^1^ University of Florida, Department of Entomology and Nematology, North Florida Research and Education Center, Quincy FL 32351
+# a
+```{r, warning=FALSE}
+grid::grid.raster(tiff::readTIFF("images/symp-ofv-asp-1.tif"))
+```
 
-^2^ University of Florida, Department of Entomology and Nematology, Tropical Research and Education Center, Homestead FL 33031
+# a
+```{r, warning=FALSE}
+grid::grid.raster(tiff::readTIFF("images/symp-ofv-asp-2.tif"))
+```
 
-^3^ University of Florida, Department of Environmental Horticulture, North Florida Research and Education Center, Quincy FL 32351
+# Intro 
+During June 2020, chlorotic ringspot symptoms on Giant Lilyturf (*Liriope* spp., cv. ‘Gigantea’) were observed in a landscape in Leon County, Florida.
+ - Initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL
+ - Tested negative for begomovirus, potyvirus, tospovirus as well as for Impatiens necrotic spot virus, Tobacco mosaic virus and Tomato spotted wilt virus
+ - Sent to the Florida Department of Agriculture and Consumer Services (FDACS)
 
-^4^ University of Florida, Department of Plant Pathology, North Florida Research and Education Center, Quincy FL 32351
+# OFV Confirmation
+ - Identified using OFV specific conventional reverse transcription polymerase chain assay (RT-PCR) assay + Sanger sequencing + quantitative RT-PCR (RT-qPCR)
+ - Presence of Orchid fleck dichorhavirus confirmed using OFV generic R2-Dicho-GF and R2-Dicho-GR primers [@Roy2020] 
+ - Sanger sequencing of RT-PCR amplicons shared 98\% nucleotide identity with orchid strains of OFV: OFV-Orc1 and OFV-Orc2 (GenBank Accession numbers: AB244418 and LC222630) [@Kondo2006; @Kondo2017].
 
-^5^ The Florida Department of Agriculture and Consumer Services, Division of Plant Industry, Section of Plant Pathology, Doyle Conner Building, 1911 SW 34th street, Gainesville, FL 32608
+# *Orchid fleck virus* (OFV)
+ - Type member for the genus *Dichorhavirus*, family Rhabdoviridae
+ - *Citrus chlorotic spot virus*, *Citrus leprosis virus* N, *Clerodendrum chlorotic spot virus* and *Coffee ringspot virus*
+ - Infects 50+ plant species, including Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (*Citrus*)
+ - Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) only known vectors of dichorhaviruses
 
-^6^	United States Department of Agriculture – Agriculture Research Service, Molecular Plant Pathology Laboratory, 10300 Baltimore Ave, Bldg. 4 BARC-West, Beltsville, MD 20705
+# Distribution of OFV
+ - first described infecting *Cymbidium* orchids in Japan [@Doi1977]
+ - OFV and OFV-like rhabdoviruses have been reported from
+  - Asia: [China [@Peng2017], Korea [@Chang1991, @Zheng2013]]
+  - Africa: [South Africa [@Cook2019]]
+  - North America: [The United States [@Blanchfield2001; @Bratsch2015], Mexico [@OteroColina2021]]
+  - South America: [Brazil [@Kitajima1974; @Kitajima2001], Colombia [@Kubo2009b], Costa Rica [@FreitasAstua2002], Paraguay [@RamosGonzalez2015]]
+  - Europe: [Denmark [@Begtrup1972], France [@Sauvetre2018], Germany [@Lesemann1975; @Petzold1971]]
+  - Oceania: [Australia [@Lesemann1971; @Lesemann1975; @Gibbs2000], Fiji [@Pearson1993], Vanuatu [@Pearson1993]]
+- Prevalence of OFV and its mite vector is thought to be associated with the movement of infected orchids [@Dietzgen2018a]
 
-^7^ United States Department of Agriculture - Agriculture Research Service, Systematic Entomology Laboratory 10300 Baltimore Ave, Bldg. 5 BARC-West, Beltsville, MD 20705
+# Further Surveys
+- Additional samples were taken from other Nolinoidaea, including *Liriope muscari*, *Ophiopogon japonicus*, *O.
+intermedius* and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua counties.
 
-^8^	United States Department of Agriculture - Animal and Plant Health Inspection Service, Electron and Confocal Microscopy Unit, Bldg. 12  BARC-West, 10300 Baltimore Ave, Beltsville, MD 20705
+# Mites Recovered
+ - Three *Brevipalpus* mite species were recovered from OFV-infected plants: 
+  - *Brevipalpus californicus* sensu lato
+  - *B. obovatus* Donnadieu 
+  - *B. confusus* Banks
+- One of these species is presumably responsible for OFV transmission
+  - *Brevipalpus californicus* (Banks) group are the only known to transmit OFV in a persistent propagative manner
+  - *Brevipalpus* mite species complex contains cryptic species [@Childers2011]
 
-*Corresponding author; E-mail: xmartini\@ufl.edu Phone: 850-875-7160 Fax: 352-846-6617
-
-\pagebreak
-
-### Abstract
-Several flat mite species, all from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae), are the only known vectors of dichorhaviruses.
-The *B.
-californicus* species group exclusively can transmit Orchid fleck dichorhavirus (OFV) in a persistent propagative manner.
-OFV is the type species for the genus *Dichorhavirus* and infects more than fifty plant species belongs to the family Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (*Citrus*).
-During June 2020, chlorotic ringspot symptoms on Giant Lilyturf (*Liriope* spp., cv.
-‘Gigantea’) were observed in a landscape in Leon County, Florida.
-Later in the year, the presence of OFV was confirmed using OFV specific conventional reverse transcription polymerase chain assay (RT-PCR) assay and Sanger sequencing.
-RT-PCR amplicons had a 98\% identity with the known OFV sequences available in the Genbank.
-The identification was also confirmed with the quantitative RT-PCR (RT-qPCR).
-Additional samples were taken from other Nolinoidaea, including *Liriope muscari*, *Ophiopogon japonicus*, *O.
-intermedius* and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua counties.
-Identification of partial genome sequence confirmed the presence of both the orchid strains (OFV-Orc1 and OFV-Orc2) in Florida.
-Three mite species were recovered from OFV-infected plants: *Brevipalpus californicus* sensu lato, *B.
-obovatus* Donnadieu and *B.
-confusus* Banks.
-One of these species is presumably responsible for OFV transmission.
-Florida has various mite species of *Brevipalpus* and a diverse array of susceptible native and introduced plant species in the landscape.
-We suggest that OFV already has a wide distribution in Florida which will continue to spread if unchecked, representing a potential threat for *Liriope* spp., *Ophiopogon* spp.
-and *Aspidistra elatior* which are commonly used in landscaping in Florida .
-In this study we are reporting three new hosts from the family Asperagaceae.
-To know the extended host range of OFVs, a survey in the citrus growing regions in Florida is essential with special emphasis to the plants belongs to the family Rutaceae and Asparagaceae.
-
-### Keywords:
-False spider mite, flat mite, *Brevipalpus*-transmitted viruses, *Liriope*, Nolinoideae, *Ophiopogon*, Ruscaceae, Rutaceae, Asparagaceae, orchid, Orchidaceae, pests, ornamental plants, orchid fleck virus.
-
-\pagebreak
-*Orchid fleck virus* (OFV) is the type member for the genus *Dichorhavirus*, family Rhabdoviridae; a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
-Other members of this genus are: *Citrus chlorotic spot virus*, *Citrus leprosis virus* N, *Clerodendrum chlorotic spot virus* and *Coffee ringspot virus* [@Dietzgen2018a].
-Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the only known vector for dichorhaviruses [@Maeda1998], and *Brevipalpus californicus* (Banks) mites are the only mite known to transmit OFV in a persistent propagative manner [@Kondo2003].
-
-OFV-infected plants exhibit various symptoms dependent on the infected plant species as well as the strain of the OFV [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns (`r citef("fig_1")`).
-<!-- These lesions are thought to be associated with the feeding sites of the mite vector [@cite?]. Also, is it possibly a sign of RNAi plant defenses? See Hull Plant Virology -->
-
-OFV was first described infecting *Cymbidium* orchids in Japan [@Doi1977].
-Many countries have reported OFV and OFV-like rhabdoviruses infecting orchids worldwide [@Kondo2003], including Asia: [China [@Peng2017], Korea [@Chang1991, @Zheng2013]], Africa: [South Africa [@Blanchfield2001]], North America: [The United States [@Blanchfield2001; @Bratsch2015]], South America: [Brazil [@Kitajima1974; @Kitajima2001], Colombia [@Kubo2009b], Costa Rica [@FreitasAstua2002], Paraguay [@RamosGonzalez2015]], Europe: [Denmark [@Begtrup1972], France [@Sauvetre2018], Germany [@Lesemann1975; @Petzold1971]] and Oceania: [Australia [@Lesemann1971; @Lesemann1975; @Gibbs2000], Fiji [@Pearson1993], Vanuatu [@Pearson1993]].
-The prevalence of OFV and its mite vector is thought to be associated with the movement of infected orchids [@Dietzgen2018a].
-
-OFV naturally infects more than fifty species of Orchidaceae [@Kitajima2010; @Peng2013], some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], as well as Rutaceae: *Citrus* where it causes citrus leprosis-like symptoms [@Beltran-Beltran2020; @GarciaEscamilla2018; @Roy2020].
-Mechanical transmission of OFV is possible under lab conditions to various Chenopodiaceae, Aizoaceae, Fabaceae, and Solanaceae [@Chang1976; @Kondo2003; @Peng2013].
-
-During June 2020, chlorotic ringspot symptoms were observed on Giant Lilyturf *Liriope* spp., cv.
-'Gigantea' in a landscape of Leon County, Florida (`r citef("fig_1")`).
-*Liriope* belong to a group of plants in the family Asparagaceae, subfamily Nolinoidaea, which includes a diverse array of various monocotyledonous lilliod plants which are native to southeastern Asia [@Chase2009; @Meng2021].
-*Liriope* and the closely related *Ophiopogon* Ker Gawler (Asparagaceae: Nolinoidaea) are considered the most important ground cover sold by the nursery industry in southeastern US [@Mcharo2003].
-
-Viral infections of suspected plant leaf samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL.
-All the samples tested negative for begomovirus, potyvirus, tospovirus as well as for Impatiens necrotic spot virus, Tobacco mosaic virus and Tomato spotted wilt virus.
-The infected materials were subsequently sent to the Florida Department of Agriculture and Consumer Services (FDACS).
-The presence of OFV was confirmed using OFV generic R2-Dicho-GF and R2-Dicho-GR primers [@Roy2020] by one step conventional RT-PCR, amplifying ~800 nt of L-gene (RNA2) amplicon from an infected *Liriope* leaf sample.
-The RT-PCR amplicon was sequenced using Sanger sequencing and confirmed the presence of OFV in the tested samples.
-Sanger sequencing of RT-PCR amplicons shared 98\% nucleotide identity with orchid strains of OFV (GenBank Accession numbers: AB244418 and LC222630) [@Kondo2006; @Kondo2017].
-Further surveys of putatively OFV-infected plants were taken during subsequent visits to the initial site of collection.
-Plant samples included various cultivars of Nolinoid plants, including *Liriope* spp., *Ophiopogon* spp., and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) which were located at the same site as the original infected *Liriope* spp., cv 'Gigantea'.
-Samples were tested via RT-PCR at the NFREC<!-- (`r citet("tab_1")`) --> to confirm the presence of OFV.
-
-Further surveys of plants belonging to the subfamily Nolinoidaea in Florida have revealed more sites with symptomatic plants in both Leon and Alachua counties.
-In addition to the discovery of the OFV-infected plants, we collected mites from symptomatic plants in both Leon and Alachua counties.
-In addition to the discovery of the OFV-infected plants, we collected mites from symptomatic plants in Leon county which were observed with phase contrast microscopy.
-We encountered both an unidentified eriophyoid mite species on the *Liriope* spp., along with flat mites on all species tested (*Liriope* spp., *Ophiopogon* spp., and *A.
-elatior*).
-The flat mites were originally identified as *Brevipalpus californicus* (Banks) sensu lato, an identity which was confirmed by the FDACS via Differential Interference Contrast (DIC) microscopy.
-*Brevipalpus* mites have been previously associated with OFV [@Beltran-Beltran2020; @GarciaEscamilla2018; @Dietzgen2018b] as well as similar diseases [@Kitajima2010] and are known to feed on a large variety of economically important plants [@Childers2003a; @Akyazi2017].
-Unfortunately, the *Brevipalpus* mite species complex is known to contain cryptic species [@Childers2011] whose identification can be improved with molecular methods as well as more advanced microscopy techniques, such as cryo scanning electron microscopy (currently known as Cryo-SEM) [@Skoracka2015; @Leon2010; @Beard2015].
-With that in mind, we collected additional samples   of the mites from the same site as the original OFV detection and sent them to the USDA-ARS in Beltsville to observe the mites with Cryo-SEM  techniques, which agreed with both prior identifications of *B.
-californicus* s.l.
-<!-- (`r citef("fig_2")`) -->but revealed the presence of two other species: *B.
-obovatus* and *B.
-confusus*.
-
-The first report of OFV in the United State is thought to be @Ko1985, who describes nuclear inclusions caused by an undescribed bacilliform rhabdovirus in *Brassia* orchids.
-The significance of this report is their reference to spoke-wheel configurations of the viral particles [@Ko1985], a sign typically associated with OFV infection [@Chang1976].
-Unfortunately, @Ko1985 made no mention of mites or further investigations of this virus.
-The first certain report of OFV in the US was made by @Bratsch2015, who confirmed the presence of OFV in *Phalaenopsis* hybrids in the US, using TEM of ultrathin sections of plant tissue as well as molecular sequence analysis and its association with *Brevipalpus* mites.
-The authors did not make a conclusive species identification but suggested the mite species was *B.
-californicus* group as the vector as referred by @Kondo2003.
-
-OFV has been reported in other Nolinoidaea in Australia [@Dietzgen2018b; @Mei2016], including *Liriope spicata* (Thunb.) Lour.
-[@Mei2016].
-The Florida collected plants of *Liriope* spp., cv 'Gigantea' are thought to belong to either *Liriope muscari* or *Liriope gigantea*.
-In addition, we are not aware of any record other than this manuscript which reports OFV infection in *Ophiopogon* plants.
-Unfortunately, the Ophiopogonae group includes species of *Liriope* and *Ophiopogon* which are very similar in appearance and growth habit, with few useful morphological characters used for their classification [@Fantz2008a].
-Furthermore, the horticultural industry has created a diverse array of cultivars of these plants, which are often mislabeled [@Fantz2008a].
-Aside from the taxonomic confusion created by humans, natural hybrids between *Ophiopogon* and *Liriope* have created a natural source of error for reconstructing phylogenies [@Zhou2009].
-Together, these factors make it difficult to differentiate and identify plants in the landscape by visual inspection alone.
-These obfuscations of species identity may be accounted for in the future via sequence comparisons of the OFV-infected plants [@Rudall2000; @Wang2014], but these comparisons are beyond the scope of our current report.
-Nonetheless, we are confident that ours is the first report of OFV infecting *Aspidistra elatior*; although [@Zheng2013] mentions the association of *B.
-californicus* with *A.
-elatior* they make no mention of OFV symptoms in this plant.
-
-<!-- ### Control methods for *Brevipalpus* mites -->
-
-<!-- <!-- Reducing the populations of the *Brevipalpus* mite vector may be able to reduce the spread of OFV by infective mites, but infected plants are not able to recover from the virus and must be rouged or removed.
-Rouging plants is a direct and efficient option to remove mite and virus populations quickly but increases in difficultly with the number of plants involved.
-Once infected plants have been removed, the objective will be to prevent re-infestation of the *Brevipalpus* vector via conventional pest management methods.
--->
-
-<!-- <!-- Most research on the integrated management of mites has been catered towards controlling various species of spider mites (Acari: Tetranychidae) [@Leeuwen2015], but many of those methods can be applied to *Brevipalpus* spp.
-as well: -->
-<!-- Chemical control via synthetic acaricides is commonly used to manage *Brevipalpus* spp.
-[@Leeuwen2015], but acaricides have some drawbacks.
-Many products control a broad class of arthropods, but often they do so indiscriminately, killing beneficial insects as well as pests [@Suckling2013].
-Control strategies which rely heavily on chemical control have the potential to encourage pesticide resistance in mite populations and pesticide resistance has been reported in various *Brevipalpus* populations [@Alves2000; @Campos2002; @Omoto2000; @Rocha2021].
-In addition, it is important to consider the interactions which may occur between different chemical applications or tank mixes [@Vechia2018].
-Lastly, application costs of chemical controls can be large and increase the cost of production [@Rodrigues2000a], nevertheless chemical applications are valuable tools used to consider against *Brevipalpus*.
--->
-
-<!-- Various biological control methods have also been studied, but their use has not been widely adopted [@Messing2017].
-Even so, some studies have found biological control methods which could be used specifically for *Brevipalpus* mites: The predatory mite *Galendromus helveolus* (Chant) (Acari: Phytoseiidae) has been reported to feed on eggs, larvae and nymphs of *B.
-californicus* [@Chen2006] and studies of *Amblyseius largoensis* (Muma) (Acari: Phytoseiidae) demonstrated its ability to suppress populations of *B.
-yothersi* on citrus plants [@Argolo2020].
-In addition, the entomopathogenic fungus *Metarhizium anisopliae* var.
-*acridum* was found to be pathogenic to *B.
-phoenicis* [@Magalhaes2005].
-In our own surveys, we have found mites which succumbed to fungal infections (`r citef("fig_3")`); however the fungal species was not determined.
--->
-
-### Conclusion
-OFV is the type member of the genus *Dichorhavirus* (family *Rhabdoviridae*, order *Mononegavirales*) contain a bipartite, single-stranded and negative sense RNA genome.
+# Conclusions
 The dichorhavirus that infects citrus in Hawaii, Mexico, Colombia, and South Africa are identical to the OFV in gene order, content, and the genome sequence.
 According to the International committee on Taxonomy of Viruses (ICTV) classification, OFV consist of two orchid strains (OFV-Orc1 and OFV-Orc2) and two citrus strains (OFV-Cit1 and OFV-Cit2).
-Both the orchid strains of OFV infects citrus but none of the citrus strain have been reported from any orchid species.
+Both the orchid strains of OFV infects citrus [@Roy2020], but none of the citrus strains have been reported from any orchid species.
 Detecting OFV in Florida represents a concern for horticulturists who grow orchids, *Liriope*, *Ophiopogon*, or other susceptible Asparagaceae species which are commonly used in landscaping.
@@
 obovatus* is a suspected vector as well [@Childers2003].
-All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017]<!-- (`r citef("fig_4")`) -->.
+All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017] (`r citef("fig_3")`).
 Therefore, it is critical to identify the vector of OFVs in Florida and monitor its spread to determine the risk this virus represents for the native plants, agriculture and the ornamental/landscaping industries of Florida and the surrounding regions.
 
-### Acknowledgements
+# Risk to Florida
+ - Florida has various mite species of *Brevipalpus*
+ - Diverse array of susceptible native and introduced plant species in the landscape
+ - OFV already has a wide distribution in Florida which will continue to spread if unchecked
+ - Represents a threat for *Liriope* spp., *Ophiopogon* spp. and *Aspidistra elatior* $\rightarrow$ most important ground covers in southeastern US [@Mcharo2003]
+
+# Take home and future need for study
+ - Three new hosts from the family Asperagaceae
+ - Need to know the extended host range of OFVs
+  - Survey of Florida's citrus growing regions, esp. plants within the families Rutaceae and Asparagaceae
+ - Mite species determination: PCR methods?
+ - Mite transmission assays
+
+# Acknowledgements
 We would like to give a special thanks to the Tallahassee Museum for their patience, cooperation, and support with collecting plant samples.
@@
 
-### References
+# References
 <div id="refs"></div>
 
-<!-- ### Table -->
+<!-- # The Citrus Leprosis Disease Complex -->
+<!-- - Disease caused by Seven similar viruses, *Citrus leprosis virus* (CiLV) -->
+<!-- - Two main groups: -->
+<!--      - Cytoplasmic (CiLV-C, Cilevirus) -->
+<!--      - Nuclear (CiLV-N, Dichorhavirus), **rarer?** -->
+<!-- - Other Cileviruses: Hibiscus-infecting cilevirus -->
+<!-- - Other Dichorhaviruses: Citrus chlorotic spot dicorhavirus, Clerodendrum chlorotic spot dichorhavirus, Coffee ringspot dichorhavirus, Orchid fleck dichorhavirus -->
 
-<!-- |Scientific Name|Common Names|Symptoms Observed| -->
-<!-- |:-----------|:--------------|:----------------| -->
-<!-- |*Liriope muscari* Bailey| Lilyturf, Orchardgrass, Monkeygrass| Ringspots, Chlorotic Flecking, Necrotic Lesions| -->
-<!-- |*Liriope gigantea*\* Hume| Giant Lilyturf| Ringspots, Chlorotic Flecking, Necrotic Lesions| -->
-<!-- |*Ophiopogon japonicus* Ker Gawl.| Dwarf Lilyturf, Mondo Grass, Snake's beard| Ringspots, Chlorotic Flecking, Necrotic Lesions| -->
-<!-- |*Ophiopogon intermedius*\*\* Don| Aztec Grass, 'Argenteomarginatus' | Ringspots, Chlorotic Flecking, Necrotic Lesions| -->
-<!-- |*Aspidistra elatior* Blume| Cast Iron Plant, Bar-room Plant | Chlorosis, Necrotic Lesions| -->
-<!-- `r tab_nums(name = "tab_1", caption = "List of plants with symptoms of Orchid fleck dichorhavirus found in northern Florida.
-* *L.
-gigantea* have been traditionally classified as seperate from *L.
-muscari* by @Broussard2007 and @Fantz2015, although this distinction has been challenged by @Wang2014 and @Masiero2020.
-* * *O.
-intermedius* is sometimes misclassified as *Liriope muscari* ‘Variegated Evergreen Giant’ [@Fantz2008b, @Fantz2009] or ‘Grandiflora White’ [@Fantz2009].")` -->
+<!-- ```{r cilv_virion, echo=FALSE} -->
+<!-- knitr::include_graphics('../images/cilv_virion.jpg') -->
+<!-- ``` -->
 
-### Figure captions
-`r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by plants infected with Orchid fleck dichorhavirus: (a) ringspot symptoms on *Liriope gigantea* (b) chlorotic flecking on *Aspidistra elatior*.")`
+<!-- # Growing concerns for citrus producers -->
+<!-- - Primarily issue for sweet orange: *Citrus sinensis* (L.), some other citrus cultivars -->
+<!-- - Non-systemic infections develop, lesions, scaly bark, fruit drop -->
+<!-- - Hypersensitive-like response, lesion progresses to become necrotic at center -->
+<!-- - High yield loss, ruins fresh market value -->
+<!-- - No host plant resistance, Bastianel et al. 2007: CiLV controlled by only a few genes -->
 
-<!-- `r fig_nums(name = "fig_2", caption = "LT-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.
-LT-SEM images provided by Dr.
-Gary Bauchan, USDA-ARS 2021")` -->
+<!-- ```{r citrus_fruits, echo=FALSE} -->
+<!-- knitr::include_graphics('../images/citrus_fruits.jpg') -->
+<!-- ``` -->
 
-<!-- `r fig_nums(name = "fig_3", caption = "LT-SEM images of unidentified fungus infecting *Brevipalpus californicus* sensu lato: (a) Infested *B.
-californicus* adult, dorsal (b) Detail of fungal sporangia.
-LT-SEM images provided by Dr.
-Gary Bauchan, USDA-ARS 2021")` -->
+<!-- # Citrus Leprosis Symptoms -->
 
-<!-- `r fig_nums(name = "fig_4", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
-yothersi*, dorsal (b) *B.
-yothersi*, lateral (c) *B.
-obovatus*, dorsal.
-SEM images provided by Dr.
-Ron Ochoa, USDA-ARS 2021")` -->
+<!-- ```{r cilv_symp, fig.height=9, fig.width=10.5, echo=FALSE} -->
+<!-- knitr::include_graphics('../images/cilv_symptoms.png') -->
+<!-- ``` -->
 
-### Figures
-```{r, fig_1, warning=FALSE}
-grid::grid.raster(tiff::readTIFF( "images/fig_1.tif"))
-```
+<!-- # Small Cause for Alarm: Tenuipalpid Mites and CiLV -->
+<!-- - FL natives: *Brevipalpus phoenicis*, *B. californicus*, *B. obovatus* and *B. yothersi* -->
+<!-- - Wide range of host plants, Cryptic species, mite/virus specificity? -->
+<!-- - Virus improves mite colonization, inhibits plant defensive pathways -->
+<!-- - Thelytokous parthenogenic mites, unfertilized eggs produce females -->
+<!-- - Fast population growth: ~14-40 days egg $\rightarrow$ adult, ~0.128 females/female/day -->
+<!-- - Short viral acquisition time (4-7 hours), 2 hours of feeding to transmit -->
+<!-- - Lesions appear slowly, continue developing 1-2 months after inoculation -->
 
-<!-- ```{r, fig_2, warning=FALSE} -->
+<!-- ```{r brevi_mite, fig.height=9, fig.width=10.5, echo=FALSE} -->
+<!-- knitr::include_graphics('../images/brevi_cali.png') -->
+<!-- ``` -->
+
+<!-- # Fresh from Florida: Historical Eradication, Future Reintroduction? -->
+<!-- - Main threat for Florida citrus industry between 1900-1925 -->
+
+<!-- - Reports of resurgence of leprosis symptoms 1950s -->
+
+<!-- - Disappeared in early 1960s, eradicated on accident? -->
+
+<!-- - Speculated causes: severe winter freeze in 1966 & new/better pesticides: wettable sulfur &etc. -->
+
+<!-- - Now considered an exotic disease to US -->
+
+<!-- - Review of historical herbarium samples revealed Nuclear type Leprosis, **CiLV-N** -->
+
+<!-- ```{r citrus_label, fig.height=9, fig.width=10.5, echo=FALSE} -->
+<!-- knitr::include_graphics('../images/orange_label.png') -->
+<!-- ``` -->
+
+<!-- # Map of Citrus Leprosis in World -->
+<!-- - CiLV serious problem for Americas: Moving northward: Mexico, Central America, Panama, Paraguay, Peru, Uruguay, Venezuela, Argentina and Brazil -->
+
+<!-- ```{r cilv_map, fig.height=9, fig.width=10.5, echo=FALSE} -->
+<!-- knitr::include_graphics('../images/leprosis-Fig1.jpg') -->
+<!-- ``` -->
+
+<!-- # Overview of What is Known About Citrus Leprosis Disease -->
+<!-- - Citrus Leprosis is a complex of similar diseases transmitted by mites in the genus *Brevipalpus* -->
+<!-- - Multiple mite species are involved, and are present in Florida -->
+<!-- - *Brevipalpus* mites are known to have cryptic species complexes and unresolved questions about host specificity -->
+<!-- - There is some variability in susceptibility of CiLV for different orange cultivars -->
+<!-- - Citrus leprosis has been reported from non-citrus plants in citrus groves (both Cytoplasmic and Nuclear types) -->
+<!-- - The unusual Nuclear-type Dichorhavirus species of Citrus Leprosis (CiLV-N) was likely the virus devastating Florida oranges in the past, and yet we know very little about CiLV-N and the related Dichorhavirus-disease complexes -->
+<!-- - **Some reports of Citrus Leprosis have been found to be caused by another Dichorhavirus closely related to CiLV-N: Orchid Fleck Virus** -->
+
+<!-- # Statement of Research Frontiers -->
+<!-- - The dispersal of mites and virus through the landscape still needs more work -->
+<!-- - It is not clear how mite populations are correlated with disease symptoms severity over time -->
+<!-- - The percentage of viruliferous mites in a population is either unknown or is not being reported -->
+<!-- - Very little research has been done on the nuclear CiLV or related Dichorhaviruses -->
+
+<!-- ```{r front_img, fig.height=9, fig.width=10.5, echo=FALSE} -->
+<!-- knitr::include_graphics('../images/brevi_scope.jpg') -->
+<!-- ``` -->
+
+<!-- # Overview of What is Known About Citrus Leprosis Disease -->
+<!-- - Citrus Leprosis is a complex of similar diseases transmitted by mites in the genus *Brevipalpus* -->
+<!-- - Multiple mite species are involved, and are present in Florida -->
+<!-- - *Brevipalpus* mites are known to have cryptic species complexes and unresolved questions about host specificity -->
+<!-- - There is some variability in susceptibility of CiLV for different orange cultivars -->
+<!-- - Citrus leprosis has been reported from non-citrus plants in citrus groves (both Cytoplasmic and Nuclear types) -->
+<!-- - The unusual Nuclear-type Dichorhavirus species of Citrus Leprosis (CiLV-N) was likely the virus devastating Florida oranges in the past, and yet we know very little about CiLV-N and the related Dichorhavirus-disease complexes -->
+<!-- - **Some reports of Citrus Leprosis have been found to be caused by another Dichorhavirus closely related to CiLV-N: Orchid Fleck Virus** -->
+
+<!-- # Symptoms of Orchid Fleck Virus (OFV) on *Liriope gigantea* -->
+
+<!-- ```{r ofv_1, fig.height=9, fig.width=10.5, echo=FALSE} -->
+<!-- knitr::include_graphics('../images/ofv.jpg') -->
+<!-- ``` -->
+
+<!-- # OFV Symptoms on *Ophiopogon intermedius* -->
+
+<!-- ```{r ofv_2, fig.height=9, fig.width=10.5, echo=FALSE} -->
+<!-- knitr::include_graphics('../images/ofv_2.jpg') -->
+<!-- ``` -->
+
+<!-- # OFV causes chlorosis on *Aspidistra elatior* -->
+
+<!-- ```{r ofv_asp, fig.height=9, fig.width=10.5, echo=FALSE} -->
+<!-- knitr::include_graphics('../images/ofv_asp.jpg') -->
+<!-- ``` -->
+
+<!-- # Suspected Vector: *Brevipalpus californicus*, *sensu lato* -->
+
+<!-- ```{r brevi_cali, fig.height=9, fig.width=10.5, echo=FALSE} -->
+<!-- knitr::include_graphics('../images/brevi_mite.jpg') -->
+<!-- ``` -->
+
+<!-- # Distribution of Orchid Fleck Virus in Florida -->
+
+<!-- ```{r ofv_city_map, echo=FALSE, fig.height=8, fig.width=10.5} -->
+<!-- ##LOADING REQUIRED FILES# -->
+<!-- knitr::include_graphics('../images/map_combo_city_ofv.png') -->
+<!-- ``` -->
+
+<!-- # Distribution of OFV-Infected Plants -->
+
+<!-- ```{r ofv_muse_map, echo=FALSE, fig.height=8, fig.width=10.5} -->
+<!-- knitr::include_graphics('../images/horseycorn_1.png') -->
+<!-- ``` -->
+
+<!-- # Results & Discussion -->
+<!-- - Citrus currently uninfected, in spite of close proximity and high levels of OFV present in the landscape -->
+<!-- - Monitoring these trees may give us further insight into -->
+
+<!-- # Figures -->
+<!-- ```{r, fig_3, warning=FALSE} -->
 <!-- grid::grid.raster(tiff::readTIFF( "images/b_cali.tif")) -->
 <!-- ``` -->
-
-<!-- ```{r, fig_3, warning=FALSE} -->
-<!-- grid::grid.raster(tiff::readTIFF("images/fungus_mite.tif")) -->
-<!-- ``` -->
+<!-- `r fig_nums(name = "fig_3", caption = "LT-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.")` -->
 
@@
 <!-- ``` -->
+<!-- `r fig_nums(name = "fig_4", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
+yothersi*, dorsal (b) *B.
+yothersi*, lateral (c) *B.
+obovatus*, dorsal.")` -->
+
+<!-- ```{r, fig_5, warning=FALSE} -->
+<!-- grid::grid.raster(tiff::readTIFF("images/fungus_mite.tif")) -->
+<!-- ``` -->
+<!-- `r fig_nums(name = "fig_5", caption = "LT-SEM images of unidentified fungus infecting *Brevipalpus californicus* sensu lato: (a) Infested *B.
+californicus* adult, dorsal (b) Detail of fungal sporangia.
+LT-SEM images provided by Dr.
+Gary Bauchan, USDA-ARS 2021")` -->

### 2021-03-26 ofv_presentation_2021.Rmd
More edits

@@
 
-# A visit to the Zoo
+# A visit to the Zoo in June 2020
 ```{r, warning=FALSE}
@@
 
-# a
+# Chlorotic ringspot symptoms on Giant Lilyturf (*Liriope* spp., cv. ‘Gigantea’)
 ```{r, warning=FALSE}
@@
 
-# Intro 
-During June 2020, chlorotic ringspot symptoms on Giant Lilyturf (*Liriope* spp., cv. ‘Gigantea’) were observed in a landscape in Leon County, Florida.
+# What was causing these symptoms?
  - Initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL
@@
 
-# OFV Confirmation
+# Confirmation: *Orchid fleck dichorhavirus* (OFV)
  - Identified using OFV specific conventional reverse transcription polymerase chain assay (RT-PCR) assay + Sanger sequencing + quantitative RT-PCR (RT-qPCR)
@@
 
-# *Orchid fleck virus* (OFV)
- - Type member for the genus *Dichorhavirus*, family Rhabdoviridae
- - *Citrus chlorotic spot virus*, *Citrus leprosis virus* N, *Clerodendrum chlorotic spot virus* and *Coffee ringspot virus*
- - Infects 50+ plant species, including Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (*Citrus*)
+# What is OFV?
+ - Type member for *Dichorhavirus*, family Rhabdoviridae
+ - Other dichorhaviruses: *Citrus chlorotic spot virus*, *Citrus leprosis virus* N, *Clerodendrum chlorotic spot virus* and *Coffee ringspot virus*
+ - OFV infects 50+ plant species, including Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (*Citrus*)
  - Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) only known vectors of dichorhaviruses
@@
 # Distribution of OFV
- - first described infecting *Cymbidium* orchids in Japan [@Doi1977]
- - OFV and OFV-like rhabdoviruses have been reported from
-  - Asia: [China [@Peng2017], Korea [@Chang1991, @Zheng2013]]
-  - Africa: [South Africa [@Cook2019]]
-  - North America: [The United States [@Blanchfield2001; @Bratsch2015], Mexico [@OteroColina2021]]
-  - South America: [Brazil [@Kitajima1974; @Kitajima2001], Colombia [@Kubo2009b], Costa Rica [@FreitasAstua2002], Paraguay [@RamosGonzalez2015]]
-  - Europe: [Denmark [@Begtrup1972], France [@Sauvetre2018], Germany [@Lesemann1975; @Petzold1971]]
-  - Oceania: [Australia [@Lesemann1971; @Lesemann1975; @Gibbs2000], Fiji [@Pearson1993], Vanuatu [@Pearson1993]]
+ - First described infecting *Cymbidium* orchids in Japan [@Doi1977]
+ - OFV and OFV-like rhabdoviruses have been reported worldwide
+ - Asia, Africa, North America, South America, Europe and Oceania
  - Prevalence of OFV and its mite vector is thought to be associated with the movement of infected orchids [@Dietzgen2018a]
 
-# Further Surveys
+# Maps
  - Additional samples were taken from other Nolinoidaea, including *Liriope muscari*, *Ophiopogon japonicus*, *O.
@@
 
-# Conclusions
-The dichorhavirus that infects citrus in Hawaii, Mexico, Colombia, and South Africa are identical to the OFV in gene order, content, and the genome sequence.
-According to the International committee on Taxonomy of Viruses (ICTV) classification, OFV consist of two orchid strains (OFV-Orc1 and OFV-Orc2) and two citrus strains (OFV-Cit1 and OFV-Cit2).
-Both the orchid strains of OFV infects citrus [@Roy2020], but none of the citrus strains have been reported from any orchid species.
-Detecting OFV in Florida represents a concern for horticulturists who grow orchids, *Liriope*, *Ophiopogon*, or other susceptible Asparagaceae species which are commonly used in landscaping.
-Florida is also home to a plethora of native and naturalized orchid species, many of which are threatened, including cultivating *Vanilla* in southern Florida [@Chambers2019] and the famous Ghost Orchid, [*Dendrophylax lindenii* (Lindl.) Benth.
-ex Rolfe].
-Citrus leprosis was present in Florida during the 1860’s and eradicated in the mid-1960s.
-In fact, @Kitajima2011 found that the Citrus Leprosis virus (CiLV) which previously affected Florida citrus was a nuclear type of citrus leprosis closely related to OFV strains [@Roy2013].
-Association of a distant relative of OFV named Citrus leprosis dichorhavirus-N0 (CiLV-N0) was confirmed in relation to the leprosis disease outbreak in Florida [@Hartung2015].
-The recent detection of OFV-Orc1 in South Africa [@Cook2019] in *C.
+# OFV is an issue for Florida agriculture
+ - The dichorhavirus that infects citrus in Hawaii, Mexico, Colombia, and South Africa are identical to the OFV in gene order, content, and the genome sequence.
+ - ICTV: Officially, OFV consists of two orchid strains (OFV-Orc1 and OFV-Orc2) and two citrus strains (OFV-Cit1 and OFV-Cit2)
+ - Orchid strains of OFV infects citrus [@Roy2020], but none of the citrus strains have been reported from any orchid species
+ - OFV in Florida represents a concern for horticulturists who grow orchids, *Liriope*, *Ophiopogon*, or other susceptible Asparagaceae species which are commonly used in landscaping
+
+# Further considerations
+ - Florida is also home to a plethora of native and naturalized orchid species
+  - Cultivating *Vanilla* in southern Florida [@Chambers2019] 
+  - Famous Ghost Orchid, [*Dendrophylax lindenii* (Lindl.) Benth. ex Rolfe].
+ - Citrus leprosis was present in Florida during the 1860’s and eradicated in the mid-1960s
+ - @Kitajima2011 found that the Citrus Leprosis virus (CiLV) which previously affected Florida citrus was a nuclear type of citrus leprosis closely related to OFV strains [@Roy2013]
+  - Association of a distant relative of OFV named Citrus leprosis dichorhavirus-N0 (CiLV-N0) was confirmed in relation to the leprosis disease outbreak in Florida [@Hartung2015].
+
+# Threat for the multi-billion dollar citrus industry
+  - Detection of OFV-Orc1 in South Africa [@Cook2019] in *C.
 sinensis* (Navel and Valencia orange) and OFV-Orc2 in Hawaii [@Velarde2021] in *C.
 reticulata* (mandarin) and *C.
-jambhiri* (rough lemon) highlights the threat of different strains of OFV; which will be a definite concern to the multi-billion dollar citrus industry.
-Lastly, some OFV isolates are known to be involved with citrus leprosis disease in Mexico [@Roy2015], which is a cause for concern for the citrus industry.
-*B.
-californicus* and *B.
-yothersi* are both known vectors of Dichorhaviruses (OFV) and Cileviruses (Citrus Leprosis) [@Knorr1968; @Kondo2003; @Beltran-Beltran2020] and *B.
-obovatus* is a suspected vector as well [@Childers2003].
-All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017] (`r citef("fig_3")`).
-Therefore, it is critical to identify the vector of OFVs in Florida and monitor its spread to determine the risk this virus represents for the native plants, agriculture and the ornamental/landscaping industries of Florida and the surrounding regions.
+jambhiri* (rough lemon) highlights the threat of different strains of OFV
+  - Lastly, some OFV isolates are known to be involved with citrus leprosis disease in Mexico [@Roy2015]
+
+# Mites: a large part of the problem
+- *B. californicus* and *B. yothersi* are both known vectors of Dichorhaviruses (OFV) and Cileviruses (Citrus Leprosis) [@Knorr1968; @Kondo2003; @Beltran-Beltran2020]
+- *B. obovatus* is a suspected vector as well [@Childers2003]
+- All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017]
+- Critical to identify the vector of OFVs in Florida and monitor its spread to determine the risk this virus represents for the native plants, agriculture and the ornamental/landscaping industries of Florida and the surrounding regions.
 

### 2021-03-28 ofv_presentation_2021.Rmd
Deleted the silenced text, modified some slide structures, added a few images

@@
 
-# A visit to the Zoo in June 2020
+# Chlorotic ringspot symptoms on Giant Lilyturf (*Liriope* spp., cv. ‘Gigantea’)
 ```{r, warning=FALSE}
-knitr::include_graphics('images/symp-ofv-lir.jpg')
+knitr::include_graphics('images/symp-ofv-lir-1.jpg')
 ```
 
-# Chlorotic ringspot symptoms on Giant Lilyturf (*Liriope* spp., cv. ‘Gigantea’)
-```{r, warning=FALSE}
-knitr::include_graphics('images/symp-ofv-lir.jpg')
-```
-
-# a
+# Chlorotic leaves on Cast Iron Plant (*Aspidistra elatior*)
 ```{r, warning=FALSE}
@@
 
-# a
+# Chlorotic spots on *A. elatior* - Early infection?
 ```{r, warning=FALSE}
@@
 # What was causing these symptoms?
- - Initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL
+:::::::::::::: {.columns}
+::: {.column}
  - Tested negative for begomovirus, potyvirus, tospovirus as well as for Impatiens necrotic spot virus, Tobacco mosaic virus and Tomato spotted wilt virus
- - Sent to the Florida Department of Agriculture and Consumer Services (FDACS)
+ - Sent to the Florida Department of Agriculture and Consumer Services (FDACS) $\rightarrow$ sent to USDA
+:::
+::: {.column}
+![Symptoms on varigated Ophiopogonae](images/symp-ofv-lir-2.jpg)
+:::
+::::::::::::::
 
@@
 # What is OFV?
+:::::::::::::: {.columns}
+::: {.column}
  - Type member for *Dichorhavirus*, family Rhabdoviridae
@@
  - Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) only known vectors of dichorhaviruses
+:::
+::: {.column}
+![Symptoms of OFV on *Oncidium*](images/oncidium_ofv.tif)
+:::
+::::::::::::::
 
 # Distribution of OFV
+:::::::::::::: {.columns}
+::: {.column}
+content
+:::
+::: {.column}
  - First described infecting *Cymbidium* orchids in Japan [@Doi1977]
@@
  - Prevalence of OFV and its mite vector is thought to be associated with the movement of infected orchids [@Dietzgen2018a]
+:::
+::::::::::::::
 
 # Maps
+:::::::::::::: {.columns}
+::: {.column}
  - Additional samples were taken from other Nolinoidaea, including *Liriope muscari*, *Ophiopogon japonicus*, *O.
 intermedius* and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua counties.
+:::
+::: {.column}
+content
+:::
+::::::::::::::
 
 # Mites Recovered
+:::::::::::::: {.columns}
+::: {.column}
  - Three *Brevipalpus* mite species were recovered from OFV-infected plants: 
@@
   - *Brevipalpus* mite species complex contains cryptic species [@Childers2011]
+:::
+::: {.column}
+content
+:::
+::::::::::::::
 
 # OFV is an issue for Florida agriculture
+:::::::::::::: {.columns}
+::: {.column}
  - The dichorhavirus that infects citrus in Hawaii, Mexico, Colombia, and South Africa are identical to the OFV in gene order, content, and the genome sequence.
@@
  - OFV in Florida represents a concern for horticulturists who grow orchids, *Liriope*, *Ophiopogon*, or other susceptible Asparagaceae species which are commonly used in landscaping
+:::
+::: {.column}
+content
+:::
+::::::::::::::
 
@@
 # Mites: a large part of the problem
+:::::::::::::: {.columns}
+::: {.column}
+- Florida has various mite species of *Brevipalpus*:
 - *B. californicus* and *B. yothersi* are both known vectors of Dichorhaviruses (OFV) and Cileviruses (Citrus Leprosis) [@Knorr1968; @Kondo2003; @Beltran-Beltran2020]
 - *B. obovatus* is a suspected vector as well [@Childers2003]
-- All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017]
+- *Brevipalpus* mites are known to have cryptic species complexes and unresolved questions about host specificity
 - Critical to identify the vector of OFVs in Florida and monitor its spread to determine the risk this virus represents for the native plants, agriculture and the ornamental/landscaping industries of Florida and the surrounding regions.
+:::
+::: {.column}
+content
+:::
+::::::::::::::
 
-# Risk to Florida
- - Florida has various mite species of *Brevipalpus*
- - Diverse array of susceptible native and introduced plant species in the landscape
- - OFV already has a wide distribution in Florida which will continue to spread if unchecked
- - Represents a threat for *Liriope* spp., *Ophiopogon* spp. and *Aspidistra elatior* $\rightarrow$ most important ground covers in southeastern US [@Mcharo2003]
-
-# Take home and future need for study
+# Conclusions
  - Three new hosts from the family Asperagaceae
@@
 <div id="refs"></div>
-
-<!-- # The Citrus Leprosis Disease Complex -->
-<!-- - Disease caused by Seven similar viruses, *Citrus leprosis virus* (CiLV) -->
-<!-- - Two main groups: -->
-<!--      - Cytoplasmic (CiLV-C, Cilevirus) -->
-<!--      - Nuclear (CiLV-N, Dichorhavirus), **rarer?** -->
-<!-- - Other Cileviruses: Hibiscus-infecting cilevirus -->
-<!-- - Other Dichorhaviruses: Citrus chlorotic spot dicorhavirus, Clerodendrum chlorotic spot dichorhavirus, Coffee ringspot dichorhavirus, Orchid fleck dichorhavirus -->
-
-<!-- ```{r cilv_virion, echo=FALSE} -->
-<!-- knitr::include_graphics('../images/cilv_virion.jpg') -->
-<!-- ``` -->
-
-<!-- # Growing concerns for citrus producers -->
-<!-- - Primarily issue for sweet orange: *Citrus sinensis* (L.), some other citrus cultivars -->
-<!-- - Non-systemic infections develop, lesions, scaly bark, fruit drop -->
-<!-- - Hypersensitive-like response, lesion progresses to become necrotic at center -->
-<!-- - High yield loss, ruins fresh market value -->
-<!-- - No host plant resistance, Bastianel et al. 2007: CiLV controlled by only a few genes -->
-
-<!-- ```{r citrus_fruits, echo=FALSE} -->
-<!-- knitr::include_graphics('../images/citrus_fruits.jpg') -->
-<!-- ``` -->
-
-<!-- # Citrus Leprosis Symptoms -->
-
-<!-- ```{r cilv_symp, fig.height=9, fig.width=10.5, echo=FALSE} -->
-<!-- knitr::include_graphics('../images/cilv_symptoms.png') -->
-<!-- ``` -->
-
-<!-- # Small Cause for Alarm: Tenuipalpid Mites and CiLV -->
-<!-- - FL natives: *Brevipalpus phoenicis*, *B. californicus*, *B. obovatus* and *B. yothersi* -->
-<!-- - Wide range of host plants, Cryptic species, mite/virus specificity? -->
-<!-- - Virus improves mite colonization, inhibits plant defensive pathways -->
-<!-- - Thelytokous parthenogenic mites, unfertilized eggs produce females -->
-<!-- - Fast population growth: ~14-40 days egg $\rightarrow$ adult, ~0.128 females/female/day -->
-<!-- - Short viral acquisition time (4-7 hours), 2 hours of feeding to transmit -->
-<!-- - Lesions appear slowly, continue developing 1-2 months after inoculation -->
-
-<!-- ```{r brevi_mite, fig.height=9, fig.width=10.5, echo=FALSE} -->
-<!-- knitr::include_graphics('../images/brevi_cali.png') -->
-<!-- ``` -->
-
-<!-- # Fresh from Florida: Historical Eradication, Future Reintroduction? -->
-<!-- - Main threat for Florida citrus industry between 1900-1925 -->
-
-<!-- - Reports of resurgence of leprosis symptoms 1950s -->
-
-<!-- - Disappeared in early 1960s, eradicated on accident? -->
-
-<!-- - Speculated causes: severe winter freeze in 1966 & new/better pesticides: wettable sulfur &etc. -->
-
-<!-- - Now considered an exotic disease to US -->
-
-<!-- - Review of historical herbarium samples revealed Nuclear type Leprosis, **CiLV-N** -->
-
-<!-- ```{r citrus_label, fig.height=9, fig.width=10.5, echo=FALSE} -->
-<!-- knitr::include_graphics('../images/orange_label.png') -->
-<!-- ``` -->
-
-<!-- # Map of Citrus Leprosis in World -->
-<!-- - CiLV serious problem for Americas: Moving northward: Mexico, Central America, Panama, Paraguay, Peru, Uruguay, Venezuela, Argentina and Brazil -->
-
-<!-- ```{r cilv_map, fig.height=9, fig.width=10.5, echo=FALSE} -->
-<!-- knitr::include_graphics('../images/leprosis-Fig1.jpg') -->
-<!-- ``` -->
-
-<!-- # Overview of What is Known About Citrus Leprosis Disease -->
-<!-- - Citrus Leprosis is a complex of similar diseases transmitted by mites in the genus *Brevipalpus* -->
-<!-- - Multiple mite species are involved, and are present in Florida -->
-<!-- - *Brevipalpus* mites are known to have cryptic species complexes and unresolved questions about host specificity -->
-<!-- - There is some variability in susceptibility of CiLV for different orange cultivars -->
-<!-- - Citrus leprosis has been reported from non-citrus plants in citrus groves (both Cytoplasmic and Nuclear types) -->
-<!-- - The unusual Nuclear-type Dichorhavirus species of Citrus Leprosis (CiLV-N) was likely the virus devastating Florida oranges in the past, and yet we know very little about CiLV-N and the related Dichorhavirus-disease complexes -->
-<!-- - **Some reports of Citrus Leprosis have been found to be caused by another Dichorhavirus closely related to CiLV-N: Orchid Fleck Virus** -->
-
-<!-- # Statement of Research Frontiers -->
-<!-- - The dispersal of mites and virus through the landscape still needs more work -->
-<!-- - It is not clear how mite populations are correlated with disease symptoms severity over time -->
-<!-- - The percentage of viruliferous mites in a population is either unknown or is not being reported -->
-<!-- - Very little research has been done on the nuclear CiLV or related Dichorhaviruses -->
-
-<!-- ```{r front_img, fig.height=9, fig.width=10.5, echo=FALSE} -->
-<!-- knitr::include_graphics('../images/brevi_scope.jpg') -->
-<!-- ``` -->
-
-<!-- # Overview of What is Known About Citrus Leprosis Disease -->
-<!-- - Citrus Leprosis is a complex of similar diseases transmitted by mites in the genus *Brevipalpus* -->
-<!-- - Multiple mite species are involved, and are present in Florida -->
-<!-- - *Brevipalpus* mites are known to have cryptic species complexes and unresolved questions about host specificity -->
-<!-- - There is some variability in susceptibility of CiLV for different orange cultivars -->
-<!-- - Citrus leprosis has been reported from non-citrus plants in citrus groves (both Cytoplasmic and Nuclear types) -->
-<!-- - The unusual Nuclear-type Dichorhavirus species of Citrus Leprosis (CiLV-N) was likely the virus devastating Florida oranges in the past, and yet we know very little about CiLV-N and the related Dichorhavirus-disease complexes -->
-<!-- - **Some reports of Citrus Leprosis have been found to be caused by another Dichorhavirus closely related to CiLV-N: Orchid Fleck Virus** -->
-
-<!-- # Symptoms of Orchid Fleck Virus (OFV) on *Liriope gigantea* -->
-
-<!-- ```{r ofv_1, fig.height=9, fig.width=10.5, echo=FALSE} -->
-<!-- knitr::include_graphics('../images/ofv.jpg') -->
-<!-- ``` -->
-
-<!-- # OFV Symptoms on *Ophiopogon intermedius* -->
-
-<!-- ```{r ofv_2, fig.height=9, fig.width=10.5, echo=FALSE} -->
-<!-- knitr::include_graphics('../images/ofv_2.jpg') -->
-<!-- ``` -->
-
-<!-- # OFV causes chlorosis on *Aspidistra elatior* -->
-
-<!-- ```{r ofv_asp, fig.height=9, fig.width=10.5, echo=FALSE} -->
-<!-- knitr::include_graphics('../images/ofv_asp.jpg') -->
-<!-- ``` -->
-
-<!-- # Suspected Vector: *Brevipalpus californicus*, *sensu lato* -->
-
-<!-- ```{r brevi_cali, fig.height=9, fig.width=10.5, echo=FALSE} -->
-<!-- knitr::include_graphics('../images/brevi_mite.jpg') -->
-<!-- ``` -->
-
-<!-- # Distribution of Orchid Fleck Virus in Florida -->
-
-<!-- ```{r ofv_city_map, echo=FALSE, fig.height=8, fig.width=10.5} -->
-<!-- ##LOADING REQUIRED FILES# -->
-<!-- knitr::include_graphics('../images/map_combo_city_ofv.png') -->
-<!-- ``` -->
-
-<!-- # Distribution of OFV-Infected Plants -->
-
-<!-- ```{r ofv_muse_map, echo=FALSE, fig.height=8, fig.width=10.5} -->
-<!-- knitr::include_graphics('../images/horseycorn_1.png') -->
-<!-- ``` -->
-
-<!-- # Results & Discussion -->
-<!-- - Citrus currently uninfected, in spite of close proximity and high levels of OFV present in the landscape -->
-<!-- - Monitoring these trees may give us further insight into -->
-
-<!-- # Figures -->
-<!-- ```{r, fig_3, warning=FALSE} -->
-<!-- grid::grid.raster(tiff::readTIFF( "images/b_cali.tif")) -->
-<!-- ``` -->
-<!-- `r fig_nums(name = "fig_3", caption = "LT-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.")` -->
-
-<!-- ```{r, fig_4, warning=FALSE} -->
-<!-- grid::grid.raster(tiff::readTIFF( "images/other_mites.tif")) -->
-<!-- ``` -->
-<!-- `r fig_nums(name = "fig_4", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
-yothersi*, dorsal (b) *B.
-yothersi*, lateral (c) *B.
-obovatus*, dorsal.")` -->
-
-<!-- ```{r, fig_5, warning=FALSE} -->
-<!-- grid::grid.raster(tiff::readTIFF("images/fungus_mite.tif")) -->
-<!-- ``` -->
-<!-- `r fig_nums(name = "fig_5", caption = "LT-SEM images of unidentified fungus infecting *Brevipalpus californicus* sensu lato: (a) Infested *B.
-californicus* adult, dorsal (b) Detail of fungal sporangia.
-LT-SEM images provided by Dr.
-Gary Bauchan, USDA-ARS 2021")` -->

### 2021-03-29 ofv_fife_2021.Rmd
Added images and updated files

@@
 During June 2020, chlorotic ringspot symptoms on Giant Lilyturf (*Liriope* spp., cv.
-‘Gigantea’) were observed in a landscape in Leon County, Florida.
-Later in the year, the presence of OFV was confirmed using OFV specific conventional reverse transcription polymerase chain assay (RT-PCR) assay and Sanger sequencing.
+‘Gigantea’, Asparagaceae: Nolinoidaea) were observed in a landscape in Leon County, Florida.
+Similar symptoms were observed on Giant Lilyturf (*Liriope* spp., cv.
+‘Gigantea’) and Aztec Grass (*Ophiopogon intermedius* cv.
+'Argenteomarginatus' D.
+Don, Asparagaceae: Nolinoidaea) in Alachua county, Florida.
+In both cases, the presence of OFV was confirmed using OFV specific conventional reverse transcription polymerase chain assay (RT-PCR) assay and Sanger sequencing.
 RT-PCR amplicons had a 98\% identity with the known OFV sequences available in the Genbank.
 The identification was also confirmed with the quantitative RT-PCR (RT-qPCR).
-Additional samples were taken from other Nolinoidaea, including *Liriope muscari*, *Ophiopogon japonicus*, *O.
-intermedius* and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua counties.
+Additional samples were taken from other Nolinoidaea, including *L.
+muscari*, *O.
+japonicus*, *O.
+intermedius* and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua counties (`r citet("tab_1")`).
 Identification of partial genome sequence confirmed the presence of both the orchid strains (OFV-Orc1 and OFV-Orc2) in Florida.
@@
 We suggest that OFV already has a wide distribution in Florida which will continue to spread if unchecked, representing a potential threat for *Liriope* spp., *Ophiopogon* spp.
-and *Aspidistra elatior* which are commonly used in landscaping in Florida .
+and *Aspidistra elatior* which are commonly used in landscaping in the southeastern US.
 In this study we are reporting three new hosts from the family Asperagaceae.
@@
 \pagebreak
-*Orchid fleck virus* (OFV) is the type member for the genus *Dichorhavirus*, family Rhabdoviridae; a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
+*Orchid fleck dichorhavirus* (OFV) is the type member for the genus *Dichorhavirus*, family Rhabdoviridae; a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
 Other members of this genus are: *Citrus chlorotic spot virus*, *Citrus leprosis virus* N, *Clerodendrum chlorotic spot virus* and *Coffee ringspot virus* [@Dietzgen2018a].
@@
 'Gigantea' in a landscape of Leon County, Florida (`r citef("fig_1")`).
-*Liriope* belong to a group of plants in the family Asparagaceae, subfamily Nolinoidaea, which includes a diverse array of various monocotyledonous lilliod plants which are native to southeastern Asia [@Chase2009; @Meng2021].
+*Liriope* belong to a group of plants in the family Asparagaceae, subfamily Nolinoidaea, which includes a diverse array of various monocotyledonous liliod plants which are native to southeastern Asia [@Chase2009; @Meng2021].
 *Liriope* and the closely related *Ophiopogon* Ker Gawler (Asparagaceae: Nolinoidaea) are considered the most important ground cover sold by the nursery industry in southeastern US [@Mcharo2003].
@@
 elatior*).
-The flat mites were originally identified as *Brevipalpus californicus* (Banks) sensu lato by the FDACS via Differential Interference Contrast (DIC) microscopy.
+The flat mites were originally identified as *Brevipalpus californicus* (Banks) sensu lato by the first author and later confirmed by the FDACS via Differential Interference Contrast (DIC) microscopy.
 The *Brevipalpus* mite species complex is known to contain cryptic species [@Childers2011] that require advanced microscopy techniques, such as cryo scanning electron microscopy (Cryo-SEM) for species identification [@Skoracka2015; @Leon2010; @Beard2015].
@@
 Unfortunately, @Ko1985 made no mention of mites or further investigations of this virus.
-The first certain report of OFV in the US was made by @Bratsch2015, confirming the presence of OFV in *Phalaenopsis* hybrids in the US, using TEM of ultrathin sections of plant tissue as well as molecular sequence analysis and its association with *Brevipalpus* mites.
+The first certain report of OFV was from Hawaii in 2001 [@citation], while the first report from the continental US was by @Bratsch2015.
+In that publication, the authors confirmed the presence of OFV in *Phalaenopsis* hybrids in the US, using TEM of ultrathin sections of plant tissue as well as molecular sequence analysis and its association with *Brevipalpus* mites [@Bratsch2015].
 The authors did not make a conclusive species identification but suggested the mite vector was within the *B.
@@
 reticulata* (mandarin) and *C.
-jambhiri* (rough lemon) highlights the threat of different strains of OFV; which will be a definite concern to the multi-billion dollar citrus industry.
-Lastly, some OFV isolates are known to be involved with citrus leprosis disease in Mexico [@Roy2015], which is a cause for concern for the citrus industry.
+jambhiri* (rough lemon) associated with leprosis-like symptoms highlights the threat of different strains of OFV on citrus; which will be a definite concern to the multi-billion dollar citrus industry.
+Another unsettling association between *citrus* and OFV is the similarity of Mexican CiLV-N to OFV, with a genome organization identical to OFV and high phylogenetic similarity as well [@Roy2015].
 *B.
@@
 
-<!-- ### Table -->
+### Table
 
-<!-- |Scientific Name|Common Names|Symptoms Observed| -->
-<!-- |:-----------|:--------------|:----------------| -->
-<!-- |*Liriope muscari* Bailey| Lilyturf, Orchardgrass, Monkeygrass| Ringspots, Chlorotic Flecking, Necrotic Lesions| -->
-<!-- |*Liriope gigantea*\* Hume| Giant Lilyturf| Ringspots, Chlorotic Flecking, Necrotic Lesions| -->
-<!-- |*Ophiopogon japonicus* Ker Gawl.| Dwarf Lilyturf, Mondo Grass, Snake's beard| Ringspots, Chlorotic Flecking, Necrotic Lesions| -->
-<!-- |*Ophiopogon intermedius*\*\* Don| Aztec Grass, 'Argenteomarginatus' | Ringspots, Chlorotic Flecking, Necrotic Lesions| -->
-<!-- |*Aspidistra elatior* Blume| Cast Iron Plant, Bar-room Plant | Chlorosis, Necrotic Lesions| -->
-<!-- `r tab_nums(name = "tab_1", caption = "List of plants with symptoms of Orchid fleck dichorhavirus found in northern Florida.
+|Scientific Name|Common Names|Symptoms Observed|
+|:-----------|:--------------|:----------------|
+|*Liriope muscari* Bailey| Lilyturf, Orchardgrass, Monkeygrass| Ringspots, Chlorotic Flecking, Necrotic Lesions|
+|*Liriope gigantea*\* Hume| Giant Lilyturf| Ringspots, Chlorotic Flecking, Necrotic Lesions|
+|*Ophiopogon japonicus* Ker Gawl.| Dwarf Lilyturf, Mondo Grass, Snake's beard| Ringspots, Chlorotic Flecking, Necrotic Lesions|
+|*Ophiopogon intermedius*\*\* Don| Aztec Grass, 'Argenteomarginatus' | Ringspots, Chlorotic Flecking, Necrotic Lesions|
+|*Aspidistra elatior* Blume| Cast Iron Plant, Bar-room Plant | Chlorosis, Chlorotic Flecking, Necrotic Lesions|
+`r tab_nums(name = "tab_1", caption = "List of plants with symptoms of Orchid fleck dichorhavirus found in northern Florida.
 * *L.
@@
 * * *O.
-intermedius* is sometimes misclassified as *Liriope muscari* ‘Variegated Evergreen Giant’ [@Fantz2008b, @Fantz2009] or ‘Grandiflora White’ [@Fantz2009].")` -->
+intermedius* is sometimes misclassified as *Liriope muscari* ‘Variegated Evergreen Giant’ [@Fantz2008b, @Fantz2009] or ‘Grandiflora White’ [@Fantz2009].")`
 

### 2021-03-29 ofv_presentation_2021.Rmd
updated

@@
 csl: 'j_med_entomol.csl'
-#always_allow_html: true
+always_allow_html: true
 ---
@@
 #a list of packages used for scripts
-pkgs <- c('captioner', 'pryr', 'tiff')
+pkgs <-
+  c(
+    'captioner',
+    'pryr',
+    'tiff',
+    'sf',
+    'rgeos',
+    'ggspatial',
+    'rnaturalearth',
+    'rnaturalearthdata',
+    'tidyverse',
+    'ggmap',
+    'ggplot2',
+    'ggthemes',
+    'extrafont',
+    'showtext',
+    'leaflet',
+    'dplyr',
+    'readxl',
+    'maps',
+    'mapview',
+    'htmlwidgets',
+    'viridis',
+    'RColorBrewer'
+  )
 
@@
 ::: {.column}
- - Tested negative for begomovirus, potyvirus, tospovirus as well as for Impatiens necrotic spot virus, Tobacco mosaic virus and Tomato spotted wilt virus
+ - Tested negative for begomovirus, potyvirus, tospovirus as well as for *Impatiens necrotic spot virus*, *Tobacco mosaic virus* and *Tomato spotted wilt virus*
  - Sent to the Florida Department of Agriculture and Consumer Services (FDACS) $\rightarrow$ sent to USDA
@@
 
-# Distribution of OFV
-:::::::::::::: {.columns}
-::: {.column}
-content
-:::
-::: {.column}
+# Worldwide Distribution of OFV
  - First described infecting *Cymbidium* orchids in Japan [@Doi1977]
@@
  - Prevalence of OFV and its mite vector is thought to be associated with the movement of infected orchids [@Dietzgen2018a]
-:::
-::::::::::::::
 
-# Maps
+# World Map of OFV Distribution
+```{r, warning=FALSE, echo=FALSE, comment=FALSE}
+#https://slcladal.github.io/maps.html
+library(maptools)
+data(wrld_simpl)
+myCountries = wrld_simpl@data$NAME %in% c("China", "Korea, Republic of", "Korea, Democratic People's Republic of", "South Africa", "United States", "Mexico", "Brazil", "Colombia", "Costa Rica", "Paraguay", "Denmark", "France", "Germany", "Australia", "Fiji", "Vanuatu", "Japan")
+plot(wrld_simpl, col = c(gray(.90), "orange")[myCountries+1])
+```
+
+# Map of OFV distribution in Tallahassee 
+```{r}
+#####LOADING REQUIRED FILES####
+df <- read_xlsx('data/ofv_clean_datasheet.xlsx')
+
+#making sure R knows what variables are factors
+df$symptoms <- as_factor(df$symptoms)
+df$plant_cv <- as_factor(df$plant_cv)
+df$family <- as_factor(df$family)
+df$order <- as_factor(df$order)
+
+####REMOVING NAS####
+#removing columns of NA
+df <- drop_na(df)
+
+#makes the dataframe into a spatial dataframe
+df <-
+  st_as_sf(df,
+           coords = c("lon", "lat"),
+           crs = 4326)
+
+####GRAPHING SAMPLING LOCATIONS####
+#creating a subset of the data containing only asparagales
+asp <- df %>%
+  filter(order == 'asparagales')
+
+#making color pallet for the map
+#the order goes (ringspot, stippling, none, chlorosis)
+pal <- c('#092C48', '#A3B7F9', '#EDE6DE', '#C59434')
+
+#mapping locations
+mapview(
+  asp,
+  zcol = 'symptoms',
+  col.regions = pal,
+  legend = TRUE,
+  alpha.regions = 1,
+  layer.name = 'Ringspot Symptoms on Asparagales',
+  map.types = 'Stamen.TonerLite'
+)
+```
+
+# Mites Recovered During Our Survey
 :::::::::::::: {.columns}
 ::: {.column}
- - Additional samples were taken from other Nolinoidaea, including *Liriope muscari*, *Ophiopogon japonicus*, *O.
-intermedius* and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua counties.
-:::
-::: {.column}
-content
-:::
-::::::::::::::
-
-# Mites Recovered
-:::::::::::::: {.columns}
-::: {.column}
+- Unidentified eriophyid mite
 - Three *Brevipalpus* mite species were recovered from OFV-infected plants: 
@@
 - One of these species is presumably responsible for OFV transmission
-  - *Brevipalpus californicus* (Banks) group are the only known to transmit OFV in a persistent propagative manner
-  - *Brevipalpus* mite species complex contains cryptic species [@Childers2011]
+- **Cryo-SEM to help determine *Brevipalpus* species identity**
 :::
 ::: {.column}
-content
+![Various *Brevipalpus* spp. live in Florida](images/other_mites.tif)
 :::
 ::::::::::::::
+
+# The Main Suspect: *B. californicus* sensu lato
+![*Brevipalpus californicus* s.l](images/b_cali_detail.tif)
+- *Brevipalpus californicus* (Banks) group are the only known to transmit OFV in a persistent propagative manner
+  - *Brevipalpus* mite species complex contains cryptic species $\rightarrow$ develop molecular methods?
 
@@
 ::: {.column}
-content
+```{r}
+grid::grid.raster(tiff::readTIFF("images/NPA-20-02-Orchid-fleck-virus_Page_1.tiff"))
+```
 :::
 ::::::::::::::
-
-# Further considerations
- - Florida is also home to a plethora of native and naturalized orchid species
-  - Cultivating *Vanilla* in southern Florida [@Chambers2019] 
-  - Famous Ghost Orchid, [*Dendrophylax lindenii* (Lindl.) Benth. ex Rolfe].
- - Citrus leprosis was present in Florida during the 1860’s and eradicated in the mid-1960s
- - @Kitajima2011 found that the Citrus Leprosis virus (CiLV) which previously affected Florida citrus was a nuclear type of citrus leprosis closely related to OFV strains [@Roy2013]
-  - Association of a distant relative of OFV named Citrus leprosis dichorhavirus-N0 (CiLV-N0) was confirmed in relation to the leprosis disease outbreak in Florida [@Hartung2015].
-
-# Threat for the multi-billion dollar citrus industry
-  - Detection of OFV-Orc1 in South Africa [@Cook2019] in *C.
-sinensis* (Navel and Valencia orange) and OFV-Orc2 in Hawaii [@Velarde2021] in *C.
-reticulata* (mandarin) and *C.
-jambhiri* (rough lemon) highlights the threat of different strains of OFV
-  - Lastly, some OFV isolates are known to be involved with citrus leprosis disease in Mexico [@Roy2015]
-
-# Mites: a large part of the problem
-:::::::::::::: {.columns}
-::: {.column}
-- Florida has various mite species of *Brevipalpus*:
-- *B. californicus* and *B. yothersi* are both known vectors of Dichorhaviruses (OFV) and Cileviruses (Citrus Leprosis) [@Knorr1968; @Kondo2003; @Beltran-Beltran2020]
-- *B. obovatus* is a suspected vector as well [@Childers2003]
-- *Brevipalpus* mites are known to have cryptic species complexes and unresolved questions about host specificity
-- Critical to identify the vector of OFVs in Florida and monitor its spread to determine the risk this virus represents for the native plants, agriculture and the ornamental/landscaping industries of Florida and the surrounding regions.
-:::
-::: {.column}
-content
-:::
-::::::::::::::
-
-# Conclusions
- - Three new hosts from the family Asperagaceae
- - Need to know the extended host range of OFVs
-  - Survey of Florida's citrus growing regions, esp. plants within the families Rutaceae and Asparagaceae
- - Mite species determination: PCR methods?
- - Mite transmission assays
 

### 2021-03-30 ofv_fife_2021.Rmd
Changed images used in report to show more symptoms of OFV on both plant species involved. Changed captions and in text references

@@
 
-OFV-infected plants exhibit various symptoms depending on the infected plant species as well as the strain of the OFV [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns (`r citef("fig_1")`).
+OFV-infected plants exhibit various symptoms depending on the infected plant species as well as the strain of the OFV [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns (`r citef("fig_1")`, `r citef("fig_2")`).
 <!-- These lesions are thought to be associated with the feeding sites of the mite vector [@cite?]. Also, is it possibly a sign of RNAi plant defenses? See Hull Plant Virology -->
@@
 *A.
-elatior* infected with OFV have chlorotic leaves or chlorotic flecks (`r citef("fig_1")`).
+elatior* infected with OFV have chlorotic leaves or chlorotic flecks (`r citef("fig_2")`).
 No ringspots have been observed on *A.
 elatior* to date.
-All plant samples were tested via RT-PCR at the NFREC<!-- (`r citet("tab_1")`) --> to confirm the presence of OFV.
+All plant samples were tested via RT-PCR at the NFREC to confirm the presence of OFV.
 
@@
 The *Brevipalpus* mite species complex is known to contain cryptic species [@Childers2011] that require advanced microscopy techniques, such as cryo scanning electron microscopy (Cryo-SEM) for species identification [@Skoracka2015; @Leon2010; @Beard2015].
-Additional mite samples from the original OFV detection site were observed with Cryo-SEM (`r citef("fig_2")`).
+Additional mite samples from the original OFV detection site were observed with Cryo-SEM (`r citef("fig_3")`).
 The determinations agreed with both prior identifications of *B.
@@
 obovatus* and *B.
-confusus* (`r citef("fig_3")`).
+confusus* (`r citef("fig_4")`).
 
@@
 
-<!-- ### Control methods for *Brevipalpus* mites -->
-
-<!-- <!-- Reducing the populations of the *Brevipalpus* mite vector may be able to reduce the spread of OFV by infective mites, but infected plants are not able to recover from the virus and must be rouged or removed.
-Rouging plants is a direct and efficient option to remove mite and virus populations quickly but increases in difficultly with the number of plants involved.
-Once infected plants have been removed, the objective will be to prevent re-infestation of the *Brevipalpus* vector via conventional pest management methods.
--->
-
-<!-- <!-- Most research on the integrated management of mites has been catered towards controlling various species of spider mites (Acari: Tetranychidae) [@Leeuwen2015], but many of those methods can be applied to *Brevipalpus* spp.
-as well: -->
-<!-- Chemical control via synthetic acaricides is commonly used to manage *Brevipalpus* spp.
-[@Leeuwen2015], but acaricides have some drawbacks.
-Many products control a broad class of arthropods, but often they do so indiscriminately, killing beneficial insects as well as pests [@Suckling2013].
-Control strategies which rely heavily on chemical control have the potential to encourage pesticide resistance in mite populations and pesticide resistance has been reported in various *Brevipalpus* populations [@Alves2000; @Campos2002; @Omoto2000; @Rocha2021].
-In addition, it is important to consider the interactions which may occur between different chemical applications or tank mixes [@Vechia2018].
-Lastly, application costs of chemical controls can be large and increase the cost of production [@Rodrigues2000a], nevertheless chemical applications are valuable tools used to consider against *Brevipalpus*.
--->
-
-<!-- Various biological control methods have also been studied, but their use has not been widely adopted [@Messing2017].
-Even so, some studies have found biological control methods which could be used specifically for *Brevipalpus* mites: The predatory mite *Galendromus helveolus* (Chant) (Acari: Phytoseiidae) has been reported to feed on eggs, larvae and nymphs of *B.
-californicus* [@Chen2006] and studies of *Amblyseius largoensis* (Muma) (Acari: Phytoseiidae) demonstrated its ability to suppress populations of *B.
-yothersi* on citrus plants [@Argolo2020].
-In addition, the entomopathogenic fungus *Metarhizium anisopliae* var.
-*acridum* was found to be pathogenic to *B.
-phoenicis* [@Magalhaes2005].
-In our own surveys, we have found mites which succumbed to fungal infections (`r citef("fig_3")`); however the fungal species was not determined.
--->
-
 ### Conclusion
@@
 obovatus* is a suspected vector as well [@Childers2003].
-All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017] (`r citef("fig_3")`).
+All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017] (`r citef("fig_4")`).
 Therefore, it is critical to identify the vector of OFVs in Florida and monitor its spread to determine the risk this virus represents for the native plants, agriculture and the ornamental/landscaping industries of Florida and the surrounding regions.
@@
 ### Figure captions
-`r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by plants infected with Orchid fleck dichorhavirus: (a) ringspot symptoms on *Liriope gigantea* (b) chlorotic flecking on *Aspidistra elatior*.")`
+`r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by *Liriope* spp.
+infected with Orchid fleck dichorhavirus (OFV): (a) ringspot symptoms on *Liriope gigantea* (b-c) Details of ringspot symptoms on *Liriope gigantea* (d) chlorotic ringspots *Liriope muscari* cv.
+'Silvery Sunproof'")`
 
-`r fig_nums(name = "fig_2", caption = "LT-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.")`
+`r fig_nums(name = "fig_2", caption = "Symptoms expressed by *Aspidistra elatior* infected with Orchid fleck dichorhavirus (OFV): (a) Detail of leaf chlorosis (b) Chlorosis caused by OFV appears similar to sunburn damage (c-d) Chlorotic ringspots may indicate early symptoms of OFV")`
 
-`r fig_nums(name = "fig_3", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
+`r fig_nums(name = "fig_3", caption = "LT-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.")`
+
+`r fig_nums(name = "fig_4", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
 yothersi*, dorsal (b) *B.
@@
 ```{r, fig_1, warning=FALSE}
-grid::grid.raster(tiff::readTIFF( "images/fig_1.tif"))
+grid::grid.raster(tiff::readTIFF("images/symp-ofv-lir.tif"))
 ```
@@
 ```{r, fig_2, warning=FALSE}
-grid::grid.raster(tiff::readTIFF( "images/b_cali.tif"))
+grid::grid.raster(tiff::readTIFF("images/symp-ofv-asp.tif"))
 ```
@@
 ```{r, fig_3, warning=FALSE}
-grid::grid.raster(tiff::readTIFF( "images/other_mites.tif"))
+grid::grid.raster(tiff::readTIFF("images/b_cali.tif"))
+```
+
+```{r, fig_4, warning=FALSE}
+grid::grid.raster(tiff::readTIFF("images/other_mites.tif"))
 ```

### 2021-03-30 ofv_fife_2021.Rmd
changed name of image folder to 'figure' for easy copypasta into dissertation

@@
 ```{r, fig_1, warning=FALSE}
-grid::grid.raster(tiff::readTIFF("images/symp-ofv-lir.tif"))
+grid::grid.raster(tiff::readTIFF("figure/symp-ofv-lir.tif"))
 ```
@@
 ```{r, fig_2, warning=FALSE}
-grid::grid.raster(tiff::readTIFF("images/symp-ofv-asp.tif"))
+grid::grid.raster(tiff::readTIFF("figure/symp-ofv-asp.tif"))
 ```
@@
 ```{r, fig_3, warning=FALSE}
-grid::grid.raster(tiff::readTIFF("images/b_cali.tif"))
+grid::grid.raster(tiff::readTIFF("figure/b_cali.tif"))
 ```
@@
 ```{r, fig_4, warning=FALSE}
-grid::grid.raster(tiff::readTIFF("images/other_mites.tif"))
+grid::grid.raster(tiff::readTIFF("figure/other_mites.tif"))
 ```
@@
 <!-- ```{r, fig_4, warning=FALSE} -->
-<!-- grid::grid.raster(tiff::readTIFF("images/fungus_mite.tif")) -->
+<!-- grid::grid.raster(tiff::readTIFF("figure/fungus_mite.tif")) -->
 <!-- ``` -->

### 2021-04-02 ofv_fife_2021.Rmd
Made some final minor tweaks, should be ready for submission soon

@@
 # - html_document
-bibliography: 'thesis.bib'
+bibliography: 'bib/thesis.bib'
 csl: 'j_med_entomol.csl'
@@
 Unfortunately, @Ko1985 made no mention of mites or further investigations of this virus.
-The first certain report of OFV was from Hawaii in 2001 [@citation], while the first report from the continental US was by @Bratsch2015.
+The first certain report of OFV was from Hawaii in 2001 [@Blanchfield2001], while the first report from the continental US was by @Bratsch2015.
 In that publication, the authors confirmed the presence of OFV in *Phalaenopsis* hybrids in the US, using TEM of ultrathin sections of plant tissue as well as molecular sequence analysis and its association with *Brevipalpus* mites [@Bratsch2015].

### 2021-04-05 ofv_fife_2021.Rmd
Integrated Dr. Roy's edits. Maybe I should include a map?

@@
 
-### First report of the *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) virus, *Orchid fleck virus* (Mononegavirales: Rhabdoviridae) infecting three ornamentals in Florida
+### First report of the *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) *Orchid fleck dichorhavirus* infecting three ornamentals in the United States
 
@@
 OFV is the type species for the genus *Dichorhavirus* and infects more than fifty plant species belonging to the family Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (*Citrus*).
-During June 2020, chlorotic ringspot symptoms on Giant Lilyturf (*Liriope* spp., cv.
-‘Gigantea’, Asparagaceae: Nolinoidaea) were observed in a landscape in Leon County, Florida.
-Similar symptoms were observed on Giant Lilyturf (*Liriope* spp., cv.
-‘Gigantea’) and Aztec Grass (*Ophiopogon intermedius* cv.
-'Argenteomarginatus' D.
-Don, Asparagaceae: Nolinoidaea) in Alachua county, Florida.
+During the summer of 2020, chlorotic ringspot symptoms were seen on Giant Lilyturf (*Liriope* spp., cv.
+‘Gigantea’, Asparagaceae: Nolinoidaea) and leaf chlorosis was observed on leaves of *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in a landscape in Leon County, Florida.
 In both cases, the presence of OFV was confirmed using OFV specific conventional reverse transcription polymerase chain assay (RT-PCR) assay and Sanger sequencing.
@@
 The identification was also confirmed with the quantitative RT-PCR (RT-qPCR).
-Additional samples were taken from other Nolinoidaea, including *L.
-muscari*, *O.
-japonicus*, *O.
-intermedius* and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua counties (`r citet("tab_1")`).
+Additional samples were taken from other Nolinoidaea, including Aztec Grass (*Ophiopogon intermedius* cv.
+'Argenteomarginatus' D.
+Don, Asparagaceae: Nolinoidaea), Mondo Grass *O.
+japonicus* and Lilyturf *L.
+muscari*, with ringspot symptoms were observed in Leon and Alachua counties.
 Identification of partial genome sequence confirmed the presence of both the orchid strains (OFV-Orc1 and OFV-Orc2) in Florida.
@@
 One of these species is presumably responsible for OFV transmission.
-Florida has various mite species of *Brevipalpus* and a diverse array of susceptible native and introduced plant species in the landscape.
-We suggest that OFV already has a wide distribution in Florida which will continue to spread if unchecked, representing a potential threat for *Liriope* spp., *Ophiopogon* spp.
-and *Aspidistra elatior* which are commonly used in landscaping in the southeastern US.
-In this study we are reporting three new hosts from the family Asperagaceae.
-To know the extended host range of OFVs, a survey in Florida's citrus growing regions is essential, emphasizing plants within the families Rutaceae and Asparagaceae.
+Florida has various *Brevipalpus*susceptible native and introduced plant species in the landscape.
+In this study we are reporting three new hosts from the family Asperagaceae from multiple locations.
+We suggest that the OFV is widely distributed in Florida and might be a potential threat for *Liriope* spp., *Ophiopogon* spp.
+and *Aspidistra elatior* which are commonly used in landscaping in the southeastern US, if not controlled.
+As both the orchid strains of OFV are known to infect citrus and cause citrus leprosis disease, a survey in citrus growing regions of Florida is essential, emphasizing plants within the families Orchidaceae, Rutaceae and Asparagaceae.
 
@@
 *Orchid fleck dichorhavirus* (OFV) is the type member for the genus *Dichorhavirus*, family Rhabdoviridae; a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
-Other members of this genus are: *Citrus chlorotic spot virus*, *Citrus leprosis virus* N, *Clerodendrum chlorotic spot virus* and *Coffee ringspot virus* [@Dietzgen2018a].
-Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the only known vector for dichorhaviruses [@Maeda1998], and mites in the *Brevipalpus californicus* (Banks) group are the only known to transmit OFV in a persistent propagative manner [@Kondo2003].
+Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the only known vectors for cileviruses and dichorhaviruses [@Maeda1998], and *B.
+californicus* (Banks) group of mites are the only known to transmit OFV in a persistent propagative manner [@Kondo2003].
 
@@
 OFV was first described infecting *Cymbidium* orchids in Japan [@Doi1977].
-OFV and OFV-like rhabdoviruses have been reported infecting orchids in Asia: [China [@Peng2017], Korea [@Chang1991, @Zheng2013]], Africa: [South Africa [@Cook2019]], North America: [The United States [@Blanchfield2001; @Bratsch2015], Mexico [@OteroColina2021]], South America: [Brazil [@Kitajima1974; @Kitajima2001], Colombia [@Kubo2009b], Costa Rica [@FreitasAstua2002], Paraguay [@RamosGonzalez2015]], Europe: [Denmark [@Begtrup1972], France [@Sauvetre2018], Germany [@Lesemann1975; @Petzold1971]] and Oceania: [Australia [@Lesemann1971; @Lesemann1975; @Gibbs2000], Fiji [@Pearson1993], Vanuatu [@Pearson1993]].
+OFV and OFV-like rhabdoviruses have been reported infecting orchids in Asia, Africa, North America, South America, Europe, and Oceania.
 The prevalence of OFV and its mite vector is thought to be associated with the movement of infected orchids [@Dietzgen2018a].
 
-OFV naturally infects more than fifty species of Orchidaceae [@Kitajima2010; @Peng2013], some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], as well as Rutaceae: (*Citrus*), where it causes citrus leprosis-like symptoms [@Cook2019; @OlmedoVelarde2019; @Roy2015; @Roy2020].
-Mechanical transmission of OFV is possible under lab conditions to various Chenopodiaceae, Aizoaceae, Fabaceae, and Solanaceae [@Chang1976; @Kondo2003; @Peng2013].
+OFV naturally infects more than fifty species of Orchidaceae [@Kitajima2010; @Peng2013], some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], and Rutaceae: (*Citrus*), where it causes citrus leprosis-like symptoms [@Cook2019; @OlmedoVelarde2019; @Roy2015; @Roy2020].
+Mechanical transmission of OFV is possible to some plants belonging to the plant families Chenopodiaceae, Aizoaceae, Fabaceae, and Solanaceae [@Chang1976; @Kondo2003; @Peng2013], under labe conditions.
 
@@
 
-Viral infections of suspected plant leaf samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL.
-All the samples tested negative for begomovirus, potyvirus, tospovirus as well as for Impatiens necrotic spot virus, Tobacco mosaic virus and Tomato spotted wilt virus.
-The infected materials were subsequently sent to the Florida Department of Agriculture and Consumer Services (FDACS).
+Viral infections of suspected leaf samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL.
+All the samples were tested with RT-PCR and were found negative for begomovirus, carlavirus, potyvirus, tospovirus as well as for Cucumber mosaic virus, Impatiens necrotic spot virus, Tobacco mosaic virus and Tomato spotted wilt virus.
+
+The initial site of collection was visited two more times during 2020 to gather plants for identification of the unidentified plant pathogen.
+These surveys were conducted on July 28th and August 19th, to collect more putatively-infected *Liriope* spp.
+and a new member of the family Asparagaceae; *Aspidistra elatior* Blume with chlorotic leaves (`r citef("fig_2")`), respectively.
+Upon collection, these new samples were sent to the Florida Department of Agriculture and Consumer Services (FDACS) for identification.
+
 The presence of OFV was confirmed using OFV generic R2-Dicho-GF and R2-Dicho-GR primers [@Roy2020] by one step conventional RT-PCR, amplifying ~800 nt of L-gene (RNA2) amplicon from an infected *Liriope* leaf sample.
 Sanger sequencing of RT-PCR amplicons shared 98\% nucleotide identity with orchid strains of OFV: OFV-Orc1 and OFV-Orc2 (GenBank Accession numbers: AB244418 and LC222630) [@Kondo2006; @Kondo2017].
-Further surveys of putatively OFV-infected plants were taken during subsequent visits to the initial site of collection.
-Plant samples included various cultivars of Nolinoid plants, including *Liriope* spp., *Ophiopogon* spp., and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea).
-*A.
-elatior* infected with OFV have chlorotic leaves or chlorotic flecks (`r citef("fig_2")`).
-No ringspots have been observed on *A.
-elatior* to date.
-All plant samples were tested via RT-PCR at the NFREC to confirm the presence of OFV.
 
-Further surveys of plants belonging to the subfamily Nolinoidaea in Florida have revealed more sites with symptomatic plants in Leon and Alachua counties.
+Subsequent surveys of plants belonging to the subfamily Nolinoidaea in Florida have revealed more sites with Asparagaceae putatively infected with OFV in Leon and Alachua counties (`r citet("tab_1")`).
 Mites were collected from symptomatic plants in Leon county and observed with phase contrast microscopy.
-We encountered both an unidentified eriophyoid mite species on the *Liriope* spp., along with flat mites on all the plant species tested (*Liriope* spp., *Ophiopogon* spp., and *A.
-elatior*).
-The flat mites were originally identified as *Brevipalpus californicus* (Banks) sensu lato by the first author and later confirmed by the FDACS via Differential Interference Contrast (DIC) microscopy.
+Tenuipalpid mites (aka flat mites or false spider mites) were commonly found in abundance on the Asparagaceae which tested positive for OFV.
+These flat mites were originally identified as *Brevipalpus californicus* (Banks) sensu lato and later confirmed by the FDACS via Differential Interference Contrast (DIC) microscopy.
 The *Brevipalpus* mite species complex is known to contain cryptic species [@Childers2011] that require advanced microscopy techniques, such as cryo scanning electron microscopy (Cryo-SEM) for species identification [@Skoracka2015; @Leon2010; @Beard2015].
-Additional mite samples from the original OFV detection site were observed with Cryo-SEM (`r citef("fig_3")`).
-The determinations agreed with both prior identifications of *B.
+Additional mite samples were collected from the original OFV detection site, and examined under Cryo-SEM (`r citef("fig_3")`).
+The determinations approved prior identifications of *B.
 californicus* s.l.
@@
 OFV has been reported in other Nolinoidaea in Australia [@Dietzgen2018b; @Mei2016], including *Liriope spicata* (Thunb.) Lour.
-[@Mei2016].
+[@Mei2016] but not in the United States.
 The Florida collected plants of *Liriope* spp., cv 'Gigantea' are thought to belong to either *Liriope muscari* or *Liriope gigantea*.
 We are not aware of any previous report of OFV infection in *Ophiopogon* plants.
-Unfortunately, the Ophiopogonae group includes species of *Liriope* and *Ophiopogon* which are very similar in appearance and growth habit, with few useful morphological characters available for their classification [@Fantz2008a].
-Furthermore, the horticultural industry has created a diverse array of cultivars of these plants, which are often mislabeled [@Fantz2008a].
-Aside from the taxonomic confusion created by humans, natural hybrids between *Ophiopogon* and *Liriope* have created a natural source of error for reconstructing phylogenies [@Zhou2009].
-Together, these factors make it difficult to differentiate and identify plants in the landscape by visual inspection alone.
-These obfuscations of species identity may be accounted for in the future via sequence comparisons of the OFV-infected plants [@Rudall2000; @Wang2014], but these comparisons are beyond the scope of our current report.
-Nonetheless, we are confident that ours is the first report of OFV infecting *A.
-elatior*; although [@Zheng2013] mentions the association of *B.
+Although @Zheng2013 mentions the association of *B.
 californicus* with *A.
-elatior* they make no mention of OFV symptoms in this plant.
+elatior* but they did not mention the presence of OFV symptoms in this plant.
+However, our finding will be notified as the first report of OFV in the United States on ornamentals and among them *A.
+elatior* is a new natural host of OFV.
 
@@
 Citrus leprosis was present in Florida during the 1860’s and eradicated in the mid-1960s.
-In fact, @Kitajima2011 found that the Citrus Leprosis virus (CiLV) which previously affected Florida citrus was a nuclear type of citrus leprosis closely related to OFV strains [@Roy2013].
+In fact, @Kitajima2011 found that the Citrus Leprosis virus (CiLV) which previously affected Florida citrus was a nuclear type of citrus leprosis closely related to OFV strains [@Roy2020; @Hartung2015].
 Association of a distant relative of OFV named Citrus leprosis dichorhavirus-N0 (CiLV-N0) was confirmed in relation to the leprosis disease outbreak in Florida [@Hartung2015].
@@
 jambhiri* (rough lemon) associated with leprosis-like symptoms highlights the threat of different strains of OFV on citrus; which will be a definite concern to the multi-billion dollar citrus industry.
-Another unsettling association between *citrus* and OFV is the similarity of Mexican CiLV-N to OFV, with a genome organization identical to OFV and high phylogenetic similarity as well [@Roy2015].
 *B.
@@
 of Sao Paulo, Brazil for checking the mites we have sent for species validation.
+Furthermore we are grateful for Dr.
+Marc S.
+Frank's identification of the Liriopogons collected.
 We are especially indebted to the late Dr.
@@
 
-`r fig_nums(name = "fig_3", caption = "LT-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.")`
+`r fig_nums(name = "fig_3", caption = "Cryo-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.")`
 

### 2021-04-08 ofv_fife_2021.Rmd
Added Dr. Roy's newest draft, fixed image references, added a placeholder caption and image for the OFV maps

@@
 ### Abstract
-Several flat mite species, all from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae), are the only known vectors of dichorhaviruses.
+
+<!-- Several flat mite species, all from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae), are the only known vectors for the plant viruses known as cileviruses and dichorhaviruses.
 The *B.
 californicus* species group exclusively can transmit Orchid fleck dichorhavirus (OFV) in a persistent propagative manner.
+-->
 OFV is the type species for the genus *Dichorhavirus* and infects more than fifty plant species belonging to the family Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (*Citrus*).
@@
 In both cases, the presence of OFV was confirmed using OFV specific conventional reverse transcription polymerase chain assay (RT-PCR) assay and Sanger sequencing.
-RT-PCR amplicons had a 98\% identity with the known OFV sequences available in the Genbank.
+RT-PCR amplicons had a 98\% identity with the known OFV sequences available in the GenBank (Accession numbers: AB244418 and LC222630).
 The identification was also confirmed with the quantitative RT-PCR (RT-qPCR).
-Additional samples were taken from other Nolinoidaea, including Aztec Grass (*Ophiopogon intermedius* cv.
+Additional leaf samples were collected from other Nolinoidaea, including Aztec Grass (*Ophiopogon intermedius* cv.
 'Argenteomarginatus' D.
@@
 Identification of partial genome sequence confirmed the presence of both the orchid strains (OFV-Orc1 and OFV-Orc2) in Florida.
-Three mite species were recovered from OFV-infected plants: *Brevipalpus californicus* sensu lato, *B.
+Three mite species were identified from OFV-infected plants: *Brevipalpus californicus* sensu lato, *B.
 obovatus* Donnadieu and *B.
 confusus* Banks.
-One of these species is presumably responsible for OFV transmission.
+At least one of these species is presumably responsible for OFV transmission.
 Florida has various *Brevipalpus*susceptible native and introduced plant species in the landscape.
 In this study we are reporting three new hosts from the family Asperagaceae from multiple locations.
-We suggest that the OFV is widely distributed in Florida and might be a potential threat for *Liriope* spp., *Ophiopogon* spp.
-and *Aspidistra elatior* which are commonly used in landscaping in the southeastern US, if not controlled.
+Our data suggested that the OFV is widely distributed in Florida and might be a potential threat for *Liriope* spp., *Ophiopogon* spp.
+and *Aspidistra elatior* which are commonly used in landscaping in the southeastern United States, if not controlled.
 As both the orchid strains of OFV are known to infect citrus and cause citrus leprosis disease, a survey in citrus growing regions of Florida is essential, emphasizing plants within the families Orchidaceae, Rutaceae and Asparagaceae.
@@
 *Orchid fleck dichorhavirus* (OFV) is the type member for the genus *Dichorhavirus*, family Rhabdoviridae; a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
-Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the only known vectors for cileviruses and dichorhaviruses [@Maeda1998], and *B.
+Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the sole vectors for cileviruses and dichorhaviruses [@Maeda1998], and *B.
 californicus* (Banks) group of mites are the only known to transmit OFV in a persistent propagative manner [@Kondo2003].
 
-OFV-infected plants exhibit various symptoms depending on the infected plant species as well as the strain of the OFV [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns (`r citef("fig_1")`, `r citef("fig_2")`).
+OFV-infected plants exhibit various symptoms depending on the infected plant species as well as the strain of the OFV associated with the infection [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns (`r citef("fig_1")`, `r citef("fig_2")`).
 <!-- These lesions are thought to be associated with the feeding sites of the mite vector [@cite?]. Also, is it possibly a sign of RNAi plant defenses? See Hull Plant Virology -->
@@
 OFV naturally infects more than fifty species of Orchidaceae [@Kitajima2010; @Peng2013], some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], and Rutaceae: (*Citrus*), where it causes citrus leprosis-like symptoms [@Cook2019; @OlmedoVelarde2019; @Roy2015; @Roy2020].
-Mechanical transmission of OFV is possible to some plants belonging to the plant families Chenopodiaceae, Aizoaceae, Fabaceae, and Solanaceae [@Chang1976; @Kondo2003; @Peng2013], under labe conditions.
+Mechanical transmission of OFV is possible to some plants belonging to the plant families Chenopodiaceae, Aizoaceae, Fabaceae, and Solanaceae [@Chang1976; @Kondo2003; @Peng2013], under laboratory conditions.
 
@@
 'Gigantea' in a landscape of Leon County, Florida (`r citef("fig_1")`).
-*Liriope* belong to a group of plants in the family Asparagaceae, subfamily Nolinoidaea, which includes a diverse array of various monocotyledonous liliod plants which are native to southeastern Asia [@Chase2009; @Meng2021].
-*Liriope* and the closely related *Ophiopogon* Ker Gawler (Asparagaceae: Nolinoidaea) are considered the most important ground cover sold by the nursery industry in southeastern US [@Mcharo2003].
+*Liriope* belong to a group of plants in the family Asparagaceae, subfamily Nolinoidaea, which includes a diverse array of various monocotyledonous southeastern Asia native liliod plants [@Chase2009; @Meng2021].
+*Liriope* and the closely related *Ophiopogon* Ker Gawler (Asparagaceae: Nolinoidaea) are considered the most important ground cover nursery plants in the southeastern United States [@Mcharo2003].
 
@@
 The initial site of collection was visited two more times during 2020 to gather plants for identification of the unidentified plant pathogen.
-These surveys were conducted on July 28th and August 19th, to collect more putatively-infected *Liriope* spp.
-and a new member of the family Asparagaceae; *Aspidistra elatior* Blume with chlorotic leaves (`r citef("fig_2")`), respectively.
+These surveys were conducted during July and August to collect more putatively infected plants, including more *Liriope* spp.
+as well as a new species which also belongs to the family Asparagaceae; *Aspidistra elatior* Blume, which was suspected to be infected due to unusually chlorotic leaves (`r citef("fig_2")`).
 Upon collection, these new samples were sent to the Florida Department of Agriculture and Consumer Services (FDACS) for identification.
 
-The presence of OFV was confirmed using OFV generic R2-Dicho-GF and R2-Dicho-GR primers [@Roy2020] by one step conventional RT-PCR, amplifying ~800 nt of L-gene (RNA2) amplicon from an infected *Liriope* leaf sample.
+The presence of OFV was confirmed using OFV generic R2-Dicho-GF and R2-Dicho-GR primers by one step conventional RT-PCR [@Roy2020], amplifying ~800 nt of L-gene (RNA2) amplicon from an infected *Liriope* leaf sample.
 Sanger sequencing of RT-PCR amplicons shared 98\% nucleotide identity with orchid strains of OFV: OFV-Orc1 and OFV-Orc2 (GenBank Accession numbers: AB244418 and LC222630) [@Kondo2006; @Kondo2017].
 
-Subsequent surveys of plants belonging to the subfamily Nolinoidaea in Florida have revealed more sites with Asparagaceae putatively infected with OFV in Leon and Alachua counties (`r citet("tab_1")`).
+Subsequent surveys of plants belonging to the subfamily Nolinoidaea in Florida have revealed more sites with Asparagaceae putatively infected with OFV in Leon and Alachua counties (`r citet("tab_1")`, `r citef("fig_3")`).
 Mites were collected from symptomatic plants in Leon county and observed with phase contrast microscopy.
-Tenuipalpid mites (aka flat mites or false spider mites) were commonly found in abundance on the Asparagaceae which tested positive for OFV.
+Tenuipalpid mites (flat mites or false spider mites) were commonly found in abundance on the Asparagaceae which tested positive for OFV.
 These flat mites were originally identified as *Brevipalpus californicus* (Banks) sensu lato and later confirmed by the FDACS via Differential Interference Contrast (DIC) microscopy.
 The *Brevipalpus* mite species complex is known to contain cryptic species [@Childers2011] that require advanced microscopy techniques, such as cryo scanning electron microscopy (Cryo-SEM) for species identification [@Skoracka2015; @Leon2010; @Beard2015].
-Additional mite samples were collected from the original OFV detection site, and examined under Cryo-SEM (`r citef("fig_3")`).
+Additional mite samples were collected from the original OFV detection site, and examined under Cryo-SEM (`r citef("fig_4")`).
 The determinations approved prior identifications of *B.
@@
 obovatus* and *B.
-confusus* (`r citef("fig_4")`).
+confusus* (`r citef("fig_5")`).
 
-The first report of OFV in the United States is thought to be @Ko1985, who describes nuclear inclusions caused by an undescribed bacilliform rhabdovirus in *Brassia* orchids.
+The first report of OFV in the US is thought to be @Ko1985, who describes nuclear inclusions caused by an undescribed bacilliform rhabdovirus in *Brassia* orchids.
 The significance of this report is their reference to spoke-wheel configurations of the viral particles [@Ko1985], a sign typically associated with OFV infection [@Chang1976].
@@
 OFV has been reported in other Nolinoidaea in Australia [@Dietzgen2018b; @Mei2016], including *Liriope spicata* (Thunb.) Lour.
-[@Mei2016] but not in the United States.
+[@Mei2016] but not in the US.
 The Florida collected plants of *Liriope* spp., cv 'Gigantea' are thought to belong to either *Liriope muscari* or *Liriope gigantea*.
@@
 elatior* but they did not mention the presence of OFV symptoms in this plant.
-However, our finding will be notified as the first report of OFV in the United States on ornamentals and among them *A.
+However, our finding will be notified as the first report of OFV in the US on ornamentals and among them *A.
 elatior* is a new natural host of OFV.
@@
 obovatus* is a suspected vector as well [@Childers2003].
-All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017] (`r citef("fig_4")`).
+All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017] (`r citef("fig_5")`).
 Therefore, it is critical to identify the vector of OFVs in Florida and monitor its spread to determine the risk this virus represents for the native plants, agriculture and the ornamental/landscaping industries of Florida and the surrounding regions.
@@
 
-`r fig_nums(name = "fig_3", caption = "Cryo-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.")`
+`r fig_nums(name = "fig_3", caption = "Map of OFV cases in Florida")`
 
-`r fig_nums(name = "fig_4", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
+`r fig_nums(name = "fig_4", caption = "Cryo-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.")`
+
+`r fig_nums(name = "fig_5", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
 yothersi*, dorsal (b) *B.
@@
 obovatus*, dorsal.")`
-
-<!-- `r fig_nums(name = "fig_4", caption = "LT-SEM images of unidentified fungus infecting *Brevipalpus californicus* sensu lato: (a) Infested *B.
-californicus* adult, dorsal (b) Detail of fungal sporangia.
-LT-SEM images provided by Dr.
-Gary Bauchan, USDA-ARS 2021")` -->
 
@@
 ```{r, fig_3, warning=FALSE}
+grid::grid.raster(tiff::readTIFF("figure/map_ofv_fl.tif"))
+```
+
+```{r, fig_4, warning=FALSE}
 grid::grid.raster(tiff::readTIFF("figure/b_cali.tif"))
@@
 
-```{r, fig_4, warning=FALSE}
+```{r, fig_5, warning=FALSE}
 grid::grid.raster(tiff::readTIFF("figure/other_mites.tif"))
 ```
-
-<!-- ```{r, fig_4, warning=FALSE} -->
-<!-- grid::grid.raster(tiff::readTIFF("figure/fungus_mite.tif")) -->
-<!-- ``` -->

### 2021-04-08 ofv_fife_2021.Rmd
Gave up on the map concept, added a column in the table to indicate location where OFV was found

@@
 
-<!-- Several flat mite species, all from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae), are the only known vectors for the plant viruses known as cileviruses and dichorhaviruses.
+Several flat mite species, all from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae), are the only known vectors for the plant viruses known as cileviruses and dichorhaviruses.
 The *B.
 californicus* species group exclusively can transmit Orchid fleck dichorhavirus (OFV) in a persistent propagative manner.
--->
 OFV is the type species for the genus *Dichorhavirus* and infects more than fifty plant species belonging to the family Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (*Citrus*).
@@
 OFV-infected plants exhibit various symptoms depending on the infected plant species as well as the strain of the OFV associated with the infection [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns (`r citef("fig_1")`, `r citef("fig_2")`).
-<!-- These lesions are thought to be associated with the feeding sites of the mite vector [@cite?]. Also, is it possibly a sign of RNAi plant defenses? See Hull Plant Virology -->
 
@@
 
-Subsequent surveys of plants belonging to the subfamily Nolinoidaea in Florida have revealed more sites with Asparagaceae putatively infected with OFV in Leon and Alachua counties (`r citet("tab_1")`, `r citef("fig_3")`).
+Subsequent surveys of plants belonging to the subfamily Nolinoidaea in Florida have revealed more sites with Asparagaceae putatively infected with OFV in Leon and Alachua counties (`r citet("tab_1")`).
 Mites were collected from symptomatic plants in Leon county and observed with phase contrast microscopy.
@@
 The *Brevipalpus* mite species complex is known to contain cryptic species [@Childers2011] that require advanced microscopy techniques, such as cryo scanning electron microscopy (Cryo-SEM) for species identification [@Skoracka2015; @Leon2010; @Beard2015].
-Additional mite samples were collected from the original OFV detection site, and examined under Cryo-SEM (`r citef("fig_4")`).
+Additional mite samples were collected from the original OFV detection site, and examined under Cryo-SEM (`r citef("fig_3")`).
 The determinations approved prior identifications of *B.
@@
 obovatus* and *B.
-confusus* (`r citef("fig_5")`).
+confusus* (`r citef("fig_4")`).
 
@@
 obovatus* is a suspected vector as well [@Childers2003].
-All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017] (`r citef("fig_5")`).
+All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017] (`r citef("fig_4")`).
 Therefore, it is critical to identify the vector of OFVs in Florida and monitor its spread to determine the risk this virus represents for the native plants, agriculture and the ornamental/landscaping industries of Florida and the surrounding regions.
@@
 
-|Scientific Name|Common Names|Symptoms Observed|
-|:-----------|:--------------|:----------------|
-|*Liriope muscari* Bailey| Lilyturf, Orchardgrass, Monkeygrass| Ringspots, Chlorotic Flecking, Necrotic Lesions|
-|*Liriope gigantea*\* Hume| Giant Lilyturf| Ringspots, Chlorotic Flecking, Necrotic Lesions|
-|*Ophiopogon japonicus* Ker Gawl.| Dwarf Lilyturf, Mondo Grass, Snake's beard| Ringspots, Chlorotic Flecking, Necrotic Lesions|
-|*Ophiopogon intermedius*\*\* Don| Aztec Grass, 'Argenteomarginatus' | Ringspots, Chlorotic Flecking, Necrotic Lesions|
-|*Aspidistra elatior* Blume| Cast Iron Plant, Bar-room Plant | Chlorosis, Chlorotic Flecking, Necrotic Lesions|
+|Scientific Name|Common Names|Symptoms Observed|County|
+|:-----------|:--------------|:----------------|:-----|
+|*Liriope muscari* Bailey| Lilyturf, Orchardgrass, Monkeygrass| Ringspots, Chlorotic Flecking, Necrotic Lesions|Alachua & Leon|
+|*Liriope gigantea*\* Hume| Giant Lilyturf| Ringspots, Chlorotic Flecking, Necrotic Lesions|Alachua & Leon|
+|*Ophiopogon japonicus* Ker Gawl.| Dwarf Lilyturf, Mondo Grass, Snake's beard| Ringspots, Chlorotic Flecking, Necrotic Lesions|Leon|
+|*Ophiopogon intermedius*\*\* Don| Aztec Grass, 'Argenteomarginatus' | Ringspots, Chlorotic Flecking, Necrotic Lesions|Alachua & Leon|
+|*Aspidistra elatior* Blume| Cast Iron Plant, Bar-room Plant | Chlorosis, Chlorotic Flecking, Necrotic Lesions|Leon|
 `r tab_nums(name = "tab_1", caption = "List of plants with symptoms of Orchid fleck dichorhavirus found in northern Florida.
@@
 
-`r fig_nums(name = "fig_3", caption = "Map of OFV cases in Florida")`
+`r fig_nums(name = "fig_3", caption = "Cryo-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.")`
 
-`r fig_nums(name = "fig_4", caption = "Cryo-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.")`
-
-`r fig_nums(name = "fig_5", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
+`r fig_nums(name = "fig_4", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
 yothersi*, dorsal (b) *B.
@@
 ```{r, fig_3, warning=FALSE}
-grid::grid.raster(tiff::readTIFF("figure/map_ofv_fl.tif"))
+grid::grid.raster(tiff::readTIFF("figure/b_cali.tif"))
 ```
@@
 ```{r, fig_4, warning=FALSE}
-grid::grid.raster(tiff::readTIFF("figure/b_cali.tif"))
-```
-
-```{r, fig_5, warning=FALSE}
 grid::grid.raster(tiff::readTIFF("figure/other_mites.tif"))

### 2021-04-09 ofv_fife_2021.Rmd
fixed error, added html
Hacked down the abstract to fit under 250 word limit. Probably will need to be edited again, sent it to other authors

@@
 
-Several flat mite species, all from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae), are the only known vectors for the plant viruses known as cileviruses and dichorhaviruses.
-The *B.
-californicus* species group exclusively can transmit Orchid fleck dichorhavirus (OFV) in a persistent propagative manner.
-OFV is the type species for the genus *Dichorhavirus* and infects more than fifty plant species belonging to the family Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (*Citrus*).
-During the summer of 2020, chlorotic ringspot symptoms were seen on Giant Lilyturf (*Liriope* spp., cv.
-‘Gigantea’, Asparagaceae: Nolinoidaea) and leaf chlorosis was observed on leaves of *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in a landscape in Leon County, Florida.
-In both cases, the presence of OFV was confirmed using OFV specific conventional reverse transcription polymerase chain assay (RT-PCR) assay and Sanger sequencing.
+Orchid Fleck Virus (OFV) is the type species for the genus *Dichorhavirus*, a plant pathogen which infects more than fifty plant species belonging to the family Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (*Citrus*).
+The sole vectors for dichorhaviruses are mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae), which are also known to spread cileviruses.
+OFV was found infecting liriopogons *Liriope* spp.
+& *Ophiopogon* spp.
+(Asparagaceae: Nolinoidaea) and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea), during the summer of 2020 in a landscape in Leon County, Florida.
+OFV specific conventional reverse transcription polymerase chain assay (RT-PCR) assay and Sanger sequencing.
 RT-PCR amplicons had a 98\% identity with the known OFV sequences available in the GenBank (Accession numbers: AB244418 and LC222630).
-The identification was also confirmed with the quantitative RT-PCR (RT-qPCR).
-Additional leaf samples were collected from other Nolinoidaea, including Aztec Grass (*Ophiopogon intermedius* cv.
-'Argenteomarginatus' D.
-Don, Asparagaceae: Nolinoidaea), Mondo Grass *O.
-japonicus* and Lilyturf *L.
-muscari*, with ringspot symptoms were observed in Leon and Alachua counties.
-Identification of partial genome sequence confirmed the presence of both the orchid strains (OFV-Orc1 and OFV-Orc2) in Florida.
-Three mite species were identified from OFV-infected plants: *Brevipalpus californicus* sensu lato, *B.
+Virus identity was also confirmed via quantitative RT-PCR (RT-qPCR).
+Additional leaf samples were collected from other putatively infected Asparagaceae from Leon and Alachua counties.
+Identification of partial genome sequence confirmed the presence of both OFV orchid strains (OFV-Orc1 and OFV-Orc2) in Florida.
+These strains of OFV are known to infect citrus and cause citrus leprosis disease.
+Three potential vector species were identified from OFV-infected plants: *Brevipalpus californicus* sensu lato, *B.
 obovatus* Donnadieu and *B.
 confusus* Banks.
-At least one of these species is presumably responsible for OFV transmission.
-Florida has various *Brevipalpus*susceptible native and introduced plant species in the landscape.
-In this study we are reporting three new hosts from the family Asperagaceae from multiple locations.
-Our data suggested that the OFV is widely distributed in Florida and might be a potential threat for *Liriope* spp., *Ophiopogon* spp.
-and *Aspidistra elatior* which are commonly used in landscaping in the southeastern United States, if not controlled.
-As both the orchid strains of OFV are known to infect citrus and cause citrus leprosis disease, a survey in citrus growing regions of Florida is essential, emphasizing plants within the families Orchidaceae, Rutaceae and Asparagaceae.
+Florida has various *Brevipalpus* susceptible native and introduced plant species in the landscape.
+In this study we report three new hosts from the family Asperagaceae from multiple locations.
+Our data suggested that the OFV widely distributed in Florida and might be a threat for various plant species and possibly citrus growing in the southeastern US.
 

### 2021-05-13 ofv_fife_2021.Rmd
Working in the revisions received from the editors

@@
 
-Orchid Fleck Virus (OFV) is the type species for the genus *Dichorhavirus*, a plant pathogen which infects more than fifty plant species belonging to the family Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (*Citrus*).
-The sole vectors for dichorhaviruses are mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae), which are also known to spread cileviruses.
+*Orchid fleck dichorhavirus* (OFV) infects over fifty plant species belonging to the family Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (Citrus).
+The sole vectors for dichorhaviruses are flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae), which are also known to spread cileviruses.
 OFV was found infecting liriopogons *Liriope* spp.
-& *Ophiopogon* spp.
-(Asparagaceae: Nolinoidaea) and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea), during the summer of 2020 in a landscape in Leon County, Florida.
-OFV specific conventional reverse transcription polymerase chain assay (RT-PCR) assay and Sanger sequencing.
-RT-PCR amplicons had a 98\% identity with the known OFV sequences available in the GenBank (Accession numbers: AB244418 and LC222630).
+and *Ophiopogon* spp.,  as well as *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in the landscape in Leon County, Florida, during the summer of 2020.
+The presence of OFV was confirmed using OFV-specific conventional reverse transcription polymerase chain assay (RT-PCR) assay and Sanger sequencing.
+RT-PCR amplicons had a 98% identity with the known OFV sequences available in the NCBI GenBank.
 Virus identity was also confirmed via quantitative RT-PCR (RT-qPCR).
-Additional leaf samples were collected from other putatively infected Asparagaceae from Leon and Alachua counties.
+Additional leaf samples were collected from other possibly infected Asparagaceae from Leon and Alachua counties.
 Identification of partial genome sequence confirmed the presence of both OFV orchid strains (OFV-Orc1 and OFV-Orc2) in Florida.
 These strains of OFV are known to infect citrus and cause citrus leprosis disease.
-Three potential vector species were identified from OFV-infected plants: *Brevipalpus californicus* sensu lato, *B.
-obovatus* Donnadieu and *B.
-confusus* Banks.
-Florida has various *Brevipalpus* susceptible native and introduced plant species in the landscape.
-In this study we report three new hosts from the family Asperagaceae from multiple locations.
-Our data suggested that the OFV widely distributed in Florida and might be a threat for various plant species and possibly citrus growing in the southeastern US.
+Three potential mite vectors were identified from OFV-infected plants using cryo-scanning electron microscopy (Cryo-SEM): *Brevipalpus californicus* s.l., *B.
+obovatus*, and *B.
+confusus*.
+Florida has various native and introduced plants in the landscape that Brevipalpus spp.
+feed on, which are potentially susceptible to OFV.
+In this study, we report three new hosts from the family Asparagaceae from multiple locations.
+Our data suggested that OFV is widely distributed in Florida and might be a threat for various plant species growing in the southeastern US.
 
@@
 *Orchid fleck dichorhavirus* (OFV) is the type member for the genus *Dichorhavirus*, family Rhabdoviridae; a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
-Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the sole vectors for cileviruses and dichorhaviruses [@Maeda1998], and *B.
-californicus* (Banks) group of mites are the only known to transmit OFV in a persistent propagative manner [@Kondo2003].
+Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the sole vectors for cileviruses and dichorhaviruses [@Maeda1998].
+*Brevipalpus californicus* (Banks) sensu lato mites are the only group known to transmit OFV in a persistent propagative manner [@Kondo2003].
 
@@
 
-OFV was first described infecting *Cymbidium* orchids in Japan [@Doi1977].
+OFV was first described as infecting *Cymbidium* orchids in Japan [@Doi1977].
 OFV and OFV-like rhabdoviruses have been reported infecting orchids in Asia, Africa, North America, South America, Europe, and Oceania.
@@
 Viral infections of suspected leaf samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL.
-All the samples were tested with RT-PCR and were found negative for begomovirus, carlavirus, potyvirus, tospovirus as well as for Cucumber mosaic virus, Impatiens necrotic spot virus, Tobacco mosaic virus and Tomato spotted wilt virus.
+All the samples were tested with RT-PCR and were found negative for begomovirus, carlavirus, potyvirus, tospovirus, and *Cucumber mosaic virus*, *Impatiens necrotic spot virus*, *Tobacco mosaic virus*, and *Tomato spotted wilt virus*.
 
@@
 Mites were collected from symptomatic plants in Leon county and observed with phase contrast microscopy.
-Tenuipalpid mites (flat mites or false spider mites) were commonly found in abundance on the Asparagaceae which tested positive for OFV.
-These flat mites were originally identified as *Brevipalpus californicus* (Banks) sensu lato and later confirmed by the FDACS via Differential Interference Contrast (DIC) microscopy.
+Tenuipalpid mites (flat mites or false spider mites) were commonly found in abundance on the Asparagaceae, which tested positive for OFV.
+These flat mites were initially identified as *B.
+californicus* s.
+l.
+and later confirmed by the FDACS via Differential Interference Contrast (DIC) microscopy.
 The *Brevipalpus* mite species complex is known to contain cryptic species [@Childers2011] that require advanced microscopy techniques, such as cryo scanning electron microscopy (Cryo-SEM) for species identification [@Skoracka2015; @Leon2010; @Beard2015].
@@
 We are not aware of any previous report of OFV infection in *Ophiopogon* plants.
-Although @Zheng2013 mentions the association of *B.
+Although @Zheng2013 mention the association of *B.
 californicus* with *A.
-elatior* but they did not mention the presence of OFV symptoms in this plant.
-However, our finding will be notified as the first report of OFV in the US on ornamentals and among them *A.
+elatior*, but never reported OFV symptoms in this plant.
+However, our finding will be notified as the first report of OFV in Florida, in the US on ornamentals and among them, *A.
 elatior* is a new natural host of OFV.
@@
 The dichorhavirus that infects citrus in Hawaii, Mexico, Colombia, and South Africa are identical to the OFV in gene order, content, and the genome sequence.
-According to the International committee on Taxonomy of Viruses (ICTV) classification, OFV consist of two orchid strains (OFV-Orc1 and OFV-Orc2) and two citrus strains (OFV-Cit1 and OFV-Cit2).
+According to the International Committee on Taxonomy of Viruses (ICTV) classification, OFV consist of two orchid strains (OFV-Orc1 and OFV-Orc2) and two citrus strains (OFV-Cit1 and OFV-Cit2).
 Both the orchid strains of OFV infects citrus [@Roy2020], but none of the citrus strains have been reported from any orchid species.
@@
 Citrus leprosis was present in Florida during the 1860’s and eradicated in the mid-1960s.
-In fact, @Kitajima2011 found that the Citrus Leprosis virus (CiLV) which previously affected Florida citrus was a nuclear type of citrus leprosis closely related to OFV strains [@Roy2020; @Hartung2015].
+In fact, @Kitajima2011a found that the Citrus Leprosis virus (CiLV) which previously affected Florida citrus was a nuclear type of citrus leprosis closely related to OFV strains [@Roy2020; @Hartung2015].
 Association of a distant relative of OFV named Citrus leprosis dichorhavirus-N0 (CiLV-N0) was confirmed in relation to the leprosis disease outbreak in Florida [@Hartung2015].
@@
 reticulata* (mandarin) and *C.
-jambhiri* (rough lemon) associated with leprosis-like symptoms highlights the threat of different strains of OFV on citrus; which will be a definite concern to the multi-billion dollar citrus industry.
+jambhiri* (rough lemon) associated with leprosis-like symptoms highlights the threat of different strains of OFV on citrus; which will be a definite concern to the US multi-billion dollar citrus industry.
 *B.
-californicus* and *B.
-yothersi* are both known vectors of Dichorhaviruses (OFV) and Cileviruses (Citrus Leprosis) [@Knorr1968; @Kondo2003; @Beltran-Beltran2020] and *B.
+californicus*, as well as *B.
+yothersi* (Baker), are both known vectors of Dichorhaviruses (OFV) and Cileviruses (Citrus Leprosis) [@Knorr1968; @Kondo2003; @Beltran-Beltran2020] and *B.
 obovatus* is a suspected vector as well [@Childers2003].
@@
 ### Acknowledgements
-We would like to give a special thanks to the Tallahassee Museum for their patience, cooperation, and support with collecting plant samples.
+We would like to give special thanks to the Tallahassee Museum for their patience, cooperation, and support with collecting plant samples.
 We also want to thank Drs.
@@
 of Sao Paulo, Brazil for checking the mites we have sent for species validation.
-Furthermore we are grateful for Dr.
+Furthermore, we are grateful for Dr.
 Marc S.
@@
 
-### Table
+### Table 1: List of plants with symptoms of *Orchid fleck dichorhavirus* found in northern Florida
 
@@
 |*Aspidistra elatior* Blume| Cast Iron Plant, Bar-room Plant | Chlorosis, Chlorotic Flecking, Necrotic Lesions|Leon|
-`r tab_nums(name = "tab_1", caption = "List of plants with symptoms of Orchid fleck dichorhavirus found in northern Florida.
-* *L.
-gigantea* have been traditionally classified as seperate from *L.
+`r tab_nums(name = "tab_1", caption = "* *L.
+gigantea* has been traditionally classified as seperate from *L.
 muscari* by @Broussard2007 and @Fantz2015, although this distinction has been challenged by @Wang2014 and @Masiero2020.
@@
 `r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by *Liriope* spp.
-infected with Orchid fleck dichorhavirus (OFV): (a) ringspot symptoms on *Liriope gigantea* (b-c) Details of ringspot symptoms on *Liriope gigantea* (d) chlorotic ringspots *Liriope muscari* cv.
+infected with Orchid fleck dichorhavirus (OFV): (a) ringspot symptoms on *Liriope gigantea* (b-c) Details of ringspot symptoms on *Liriope gigantea* (d) chlorotic ringspot *Liriope muscari* cv.
 'Silvery Sunproof'")`
 
-`r fig_nums(name = "fig_2", caption = "Symptoms expressed by *Aspidistra elatior* infected with Orchid fleck dichorhavirus (OFV): (a) Detail of leaf chlorosis (b) Chlorosis caused by OFV appears similar to sunburn damage (c-d) Chlorotic ringspots may indicate early symptoms of OFV")`
+`r fig_nums(name = "fig_2", caption = "Symptoms expressed by *Aspidistra elatior* infected with Orchid fleck dichorhavirus (OFV): (a) Detail of leaf chlorosis (b) Chlorosis caused by OFV appears similar to sunburn damage (c-d) Chlorotic ringspot may indicate early symptoms of OFV")`
 
@@
 
-`r fig_nums(name = "fig_4", caption = "Florida is home to other common pest species of *Brevipalpus* which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
+`r fig_nums(name = "fig_4", caption = "Florida is home to other common pest species of *Brevipalpus*, which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
 yothersi*, dorsal (b) *B.

### 2021-05-14 editorial_reviews/response_editors_ofv_fife_2021.Rmd
Added response to editors

---
title: "response_editors_ofv_fife_2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

04-May-2021

Dear Mr. Fife,

Manuscript ID JIPM-2021-0034 entitled "First report of the <i>Brevipalpus</i>-transmitted (Trombidiformes: Tenuipalpidae) <i>Orchid fleck dichorhavirus</i> infecting three ornamentals in the United States" which you submitted to the Journal of Integrated Pest Management, has been reviewed and will be reconsidered for publication after the completion of the major revisions as noted. The comments of the reviewer(s) are included at the bottom of this letter.

Your revised manuscript should be uploaded within 45 days. Please let us know if you will require an extension. The due date is 18-Jun-2021.

To revise your manuscript, log into [hyperlink removed]  and enter your Author Centre, where you will find your manuscript title listed under "Manuscripts with Decisions."  Under "Actions," click on "Create a Revision."  Your manuscript number has been appended to denote a revision.

You may also click the below link to start the revision process.

*** PLEASE NOTE: This is a two-step process. After clicking on the link, you will be directed to a webpage to confirm. ***

[hyperlink removed]

Manuscript revision instructions
•       Please ensure your paper follows journal style and requirements as listed in the instructions to authors: [hyperlink removed]
•       Please highlight the changes to your manuscript within the document by using the track changes mode in MS Word or by using bold or colored text. Please also include a point-by-point response to reviews as well as a clean version (non-track changes version) of the paper.
•       If your paper was created in LaTeX, please upload the PDF along with the tex files.
•       Please delete any outdated files (e.g., the original manuscript, any outdated figures, etc.) before uploading the revised files.
•       Figures should be submitted as separate files and not inserted into the main document. Figures should be submitted as at least 300 dpi (600 dpi for line graphs) and in one of the following file types: tif, eps, rtf, ppt/pptx, xls/xlsx, editable PDF, ps, psd, ai, gif, or png.

Once again, thank you for submitting your manuscript to the Journal of Integrated Pest Management and I look forward to receiving your revision.

Sincerely,
Dr. Nathan Walker
Subject Editor, Journal of Integrated Pest Management nathan.walker\@okstate.edu ESA Editorial Office: 3 Park Place, Suite 307, Annapolis, MD 21401-3722, USA. Editorial Office Phone: 1-301-731-4535.

Reviewer(s)' Comments to Author:

Reviewer: 1

Comments to the Author
JIPM-2021-0034

This manuscript reports the discovery of orchid fleck virus infecting ornamental ground cover plants in Florida, USA.  The authors observed symptomatic plants of the family Asparagaceae in two northern counties of the state, and also identified brevipalpid mites on these plants, which may serve as the putative vector of the virus.  The discovery of OFV being potentially widespread in ornamental plants in Florida is an issue for those growing these (and other) plants in the family that are a host to these flat mites. There exists a threat to orchid and citrus industries, and I think it is worth discussing in the manuscript any speculation on why OFV has not been reported in orchids or citrus if the pathogen and vectors appear so widespread in the state.  Since the journal selected by the authors does focus on IPM, I think discussion of potential control measures to reduce the impact and spread of this virus is warranted.

A small note: the authors refer to cilevirus(es) in at least three locations in the manuscript.  There is no introduction or indication of why this virus is relevant to the study.  Unless this relevance is addressed, I would recommend removing such text.

For the mite descriptions, there seems to be inconsistency in providing taxonomic authorities.  My understanding is that the authorities should be used upon introduction, but not afterwards.  For example, see how Brevipalpus californicus is mentioned in L48, L64, L113, L164 etc.

The wording, organization, and grammar of the manuscript require significant revision for clarity and accuracy; perhaps more than I can offer below.  More notably, some references are either incorrect, or interpreted incorrectly.

In the abstract it is mentioned that additional leaf samples were collected in Leon and Alachua counties, and in the following sentence it states that partial genome sequence confirmed the presence of OFV.  Are these sentences linked? In the main text it appears only the samples from Leon County were actually found to be positive for OFV; the samples from Alachua were only examined for mites.  I think this is an important clarification; are the authors basing their claim of the virus being widespread in Florida (L51) based on symptoms, or actually detecting OFV in both counties. Infection by different dichorhaviruses can result in similar symptoms; diagnostics are critical.

L33: “Orchid fleck virus (OFV) is a dichorhavirus that infects over 50 plant species belonging to the families Asparagaceae, Orchidaceae, and Rutaceae.  The only known vectors for…”
L37: (Liriope and Ophiopogon spp.)
L40: “…Sanger sequencing.”
L41: remove “the known” and “the NCBI”
L42: I see no mention of a qPCR assay in the main text
L43: “…possibly infected plants of the family Asparagaceae from…”
L44: please elaborate on “Identification of partial genome sequence…” is this sequence from the PCR products or was HTS performed on the samples?
L48: perhaps identify what s.l. means; authorities are provided elsewhere in the manuscript
L49: italicize “Brevipalpus”
L59: Virus species should not be abbreviated; remove “(OFV)”
L60: virus families are italicized (Rhabdoviridae)
L63: replace “sole” with “only known”
L64: “group of mites” vs “sensu lato”?
L69: I don’t think referencing figures 1 and 2 are appropriate here
L73,76: is listing the second author the correct way to distinguish articles for this journal?  Rather than “a” or “b” after publication year?
L77: remove “: (Citrus)
L78: Olmedo-Velarde et al. is not an appropriate reference here
L82: “In June 2020,…”; (Lirope spp.)
L83: belongs
L85: perhaps “monocotyledonous liliod plants native to southeastern Asia (Chase…”
L86: is it appropriate to provide an authority for the genus (Ker Gawler)?
L92: none of these virus names should be italicized; INSV and TSWV are orthotospoviruses – why mentioned separately?
L97: “…as well as Aspidistra elaitor Blume (Asparagaceae), which was suspected…”
L103: “Lirope sp.”
L108: how many sites?
L127: This is incorrect: Blanchfield et al 2001 identified a virion larger than OFV, and the sample was negative for OFV when tested by RT-PCR.
L134: Nolinoideae
L145: The ICTV is not responsible for classification below species level, and as such, does not recognize virus strains; scientists and experts can recognize strains, but the  ICTV does not.
L152: “including Vanilla spp. in southern Florida…”
L154: a reference for this statement is advisable
L155: “…found that the virus which previously affected…”
L165: “…vectors of dichorhaviruses (Knorr 1968,…”
L168: “…identify the vector(s) of OFV in Florida…”

Table 1:
L338: “…with symptoms of orchid fleck virus infection found in…”
I am a little concerned about reporting on plants with symptoms, vs confirmed by diagnostics.  As mentioned earlier, different dichorhaviruses can cause similar symptoms in the same host.  Although remote, there is the possibility another virus could be responsible for the symptoms in a different location

Figure captions:
Please use “orchid fleck virus (OFV)” when describing a physical virus, and "Orchid fleck dichorhavirus" (in italics) when describing the species.

Reviewer: 2

Comments to the Author
The authors presented a well-written and illustrated communication about the co-occurrence of OFV and putative vector species (Brevipalpus spp.) in Florida, US.

My primary suggestion is that they be more specific about referring that the disease was reported in Florida. Other regions of the country were not part of the current work and should not be suggested as having a broad distribution.

I made a few editions, suggesting proper spellings for species “Family” names and the use of correct reference directly on the manuscript file attached.

Kitajima et. al. (2011) - correct reference mentioned is:
Kitajima E W, Chagas CM, Harakava R, Calegario RF, Freitas-Astúa J, Rodrigues JCV, Childers, CC. 2011. Citrus Leprosis in Florida, USA, appears to have been caused by the Nuclear Type of Citrus Leprosis Virus (CiLV-N). Virus Reviews & Research 16:1-5.

### 2021-05-14 editorial_reviews/response_editors_ofv_fife_2021.Rmd
created response to editors

@@
 ---
-title: "response_editors_ofv_fife_2021"
 output: word_document
@@
 
-Manuscript ID JIPM-2021-0034 entitled "First report of the <i>Brevipalpus</i>-transmitted (Trombidiformes: Tenuipalpidae) <i>Orchid fleck dichorhavirus</i> infecting three ornamentals in the United States" which you submitted to the Journal of Integrated Pest Management, has been reviewed and will be reconsidered for publication after the completion of the major revisions as noted.
+Manuscript ID JIPM-2021-0034 entitled "First report of the *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) *Orchid fleck dichorhavirus* infecting three ornamentals in the United States" which you submitted to the Journal of Integrated Pest Management, has been reviewed and will be reconsidered for publication after the completion of the major revisions as noted.
 The comments of the reviewer(s) are included at the bottom of this letter.
@@
 Manuscript revision instructions
-•       Please ensure your paper follows journal style and requirements as listed in the instructions to authors: [hyperlink removed]
-•       Please highlight the changes to your manuscript within the document by using the track changes mode in MS Word or by using bold or colored text.
+- Please ensure your paper follows journal style and requirements as listed in the instructions to authors: [hyperlink removed]
+- Please highlight the changes to your manuscript within the document by using the track changes mode in MS Word or by using bold or colored text.
 Please also include a point-by-point response to reviews as well as a clean version (non-track changes version) of the paper.
-•       If your paper was created in LaTeX, please upload the PDF along with the tex files.
-•       Please delete any outdated files (e.g., the original manuscript, any outdated figures, etc.) before uploading the revised files.
-•       Figures should be submitted as separate files and not inserted into the main document.
+- If your paper was created in LaTeX, please upload the PDF along with the tex files.
+- Please delete any outdated files (e.g., the original manuscript, any outdated figures, etc.) before uploading the revised files.
+- Figures should be submitted as separate files and not inserted into the main document.
 Figures should be submitted as at least 300 dpi (600 dpi for line graphs) and in one of the following file types: tif, eps, rtf, ppt/pptx, xls/xlsx, editable PDF, ps, psd, ai, gif, or png.
@@
 Subject Editor, Journal of Integrated Pest Management nathan.walker\@okstate.edu ESA Editorial Office: 3 Park Place, Suite 307, Annapolis, MD 21401-3722, USA. Editorial Office Phone: 1-301-731-4535.
+
+\newpage
+
+**Response to Decision Letter from the authors:**
+
+**We thank you for dedicating your time to review our manuscript.**
+
+**We believe that our revisions have addressed the errors and concerns mentioned. We are extremely grateful for your patience and thoughtful comments.**
+
+**Thank you for your assistance,**
+
+**-- The Authors**
+
+\newpage
 
@@
 L33: “Orchid fleck virus (OFV) is a dichorhavirus that infects over 50 plant species belonging to the families Asparagaceae, Orchidaceae, and Rutaceae.  The only known vectors for…”
+
 L37: (Liriope and Ophiopogon spp.)
+
 L40: “…Sanger sequencing.”
+
 L41: remove “the known” and “the NCBI”
+
 L42: I see no mention of a qPCR assay in the main text
+
 L43: “…possibly infected plants of the family Asparagaceae from…”
+
 L44: please elaborate on “Identification of partial genome sequence…” is this sequence from the PCR products or was HTS performed on the samples?
+
 L48: perhaps identify what s.l. means; authorities are provided elsewhere in the manuscript
+
 L49: italicize “Brevipalpus”
+
 L59: Virus species should not be abbreviated; remove “(OFV)”
+
 L60: virus families are italicized (Rhabdoviridae)
+
 L63: replace “sole” with “only known”
+
 L64: “group of mites” vs “sensu lato”?
+
 L69: I don’t think referencing figures 1 and 2 are appropriate here
+
 L73,76: is listing the second author the correct way to distinguish articles for this journal?  Rather than “a” or “b” after publication year?
+
 L77: remove “: (Citrus)
+
 L78: Olmedo-Velarde et al. is not an appropriate reference here
+
 L82: “In June 2020,…”; (Lirope spp.)
+
 L83: belongs
+
 L85: perhaps “monocotyledonous liliod plants native to southeastern Asia (Chase…”
+
 L86: is it appropriate to provide an authority for the genus (Ker Gawler)?
+
 L92: none of these virus names should be italicized; INSV and TSWV are orthotospoviruses – why mentioned separately?
+
 L97: “…as well as Aspidistra elaitor Blume (Asparagaceae), which was suspected…”
+
 L103: “Lirope sp.”
+
 L108: how many sites?
+
 L127: This is incorrect: Blanchfield et al 2001 identified a virion larger than OFV, and the sample was negative for OFV when tested by RT-PCR.
+
 L134: Nolinoideae
+
 L145: The ICTV is not responsible for classification below species level, and as such, does not recognize virus strains; scientists and experts can recognize strains, but the  ICTV does not.
+
 L152: “including Vanilla spp. in southern Florida…”
+
 L154: a reference for this statement is advisable
+
 L155: “…found that the virus which previously affected…”
+
 L165: “…vectors of dichorhaviruses (Knorr 1968,…”
+
 L168: “…identify the vector(s) of OFV in Florida…”
@@
 Please use “orchid fleck virus (OFV)” when describing a physical virus, and "Orchid fleck dichorhavirus" (in italics) when describing the species.
+
+**Response to Reviewer 1:**
+**Thank you for reviewing our article. We have made the following changes based on your remarks:**
 
@@
 Virus Reviews & Research 16:1-5.
+
+**Response to Reviewer 2:**
+**Thank you for reviewing our article. We have made the following changes based on your remarks:**

### 2021-05-14 editorial_reviews/response_editors_ofv_fife_2021.Rmd
fixed a lot of citations, tried to address some reviewer comments

@@
 
+Accepted edits:
+
+- L3 - 'the United States' $\rightarrow$ 'Florida'
+
+- L33 - 'Orchid Fleck Virus' $\rightarrow$ '*Orchid fleck dichorhavirus*'
+
+- L155 - reference manager error: citation link '\@Kitajima2011b' $\rightarrow$ citation link '\@Kitajima2011a' (produces correct reference)
+
+- fixed reference manager errors: added brackets {} around capitalized words {} and italic species names '{\\textit{}}' to protect case.
+also: Asparagalean, Amaryllidaceae, Asparagaceae, Xanthorrhoeaceae, *Rhabdoviridae*, Asparagaceae, RNA, *Psilanthus*
+
+Open edits:
+
+- L319 - Is it necessary to italicize Rhabdoviridae in this context?
+
+- L321 - no need to italicize Asparagaceae, it is a plant family
+
 Reviewer: 2

### 2021-05-14 ofv_fife_2021.Rmd
fixed a lot of citations, tried to address some reviewer comments

@@
 
-### First report of the *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) *Orchid fleck dichorhavirus* infecting three ornamentals in the United States
+### First report of the *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) *Orchid fleck dichorhavirus* infecting three ornamentals in Florida
 
-Austin **Fife**^1^, Daniel **Carrillo**^2^, Gary **Knox**^3^, Fanny **Iriarte**^4^, Kishore **Dey**^5^, Avijit **Roy**^6^, Ronald **Ochoa**^7^, Gary **Bauchan**^8^ $\dagger$, Mathews **Paret**^4,9^, Xavier **Martini**^1^\*
+Austin **Fife**^1^, Daniel **Carrillo**^2^, Gary **Knox**^3^, Fanny **Iriarte**^4^, Kishore **Dey**^5^, Avijit **Roy**^6^, Ronald **Ochoa**^7^, Gary **Bauchan**^8^$\dagger$, Mathews **Paret**^4,9^, Xavier **Martini**^1^\*
 

### 2021-05-17 ofv_fife_2021.Rmd
Changed the .csl from 'disambiguate-add-names: true' to 'false' and set 'disambiguate-add-year-suffix' to 'true' to make citations add an 'a' or 'b' to the year in inline citations, instead of showing the second author to disambiguate publications in the same year with the same first author. This is a modification of the ESA's .csl file.

@@
 bibliography: 'bib/thesis.bib'
-csl: 'j_med_entomol.csl'
+citation_package: natbib
+biblio-style: apalike
+csl: 'entsoc.csl'
 #always_allow_html: true
@@
 
-*Orchid fleck dichorhavirus* (OFV) infects over fifty plant species belonging to the family Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (Citrus).
-The sole vectors for dichorhaviruses are flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae), which are also known to spread cileviruses.
-OFV was found infecting liriopogons *Liriope* spp.
-and *Ophiopogon* spp.,  as well as *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in the landscape in Leon County, Florida, during the summer of 2020.
+*Orchid fleck dichorhavirus* (OFV) infects over 50 plant species belonging to the family Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (Citrus).
+The only known vectors of dichorhaviruses are flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae).
+OFV was found infecting liriopogons (*Liriope* spp.
+and *Ophiopogon* spp.),  as well as *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in the landscape in Leon County, Florida, during the summer of 2020.
 The presence of OFV was confirmed using OFV-specific conventional reverse transcription polymerase chain assay (RT-PCR) assay and Sanger sequencing.
-RT-PCR amplicons had a 98% identity with the known OFV sequences available in the NCBI GenBank.
-Virus identity was also confirmed via quantitative RT-PCR (RT-qPCR).
-Additional leaf samples were collected from other possibly infected Asparagaceae from Leon and Alachua counties.
-Identification of partial genome sequence confirmed the presence of both OFV orchid strains (OFV-Orc1 and OFV-Orc2) in Florida.
+RT-PCR amplicons had a 98% identity with known OFV sequences available in NCBI GenBank.
+Other leaf samples of the plant family Asparagaceae with ringspots and chlorosis were collected from Leon and Alachua counties and tested with PCR and Sanger sequencing to detect OFV.
+Identification of partial genome sequence from PCR products confirmed the presence of both OFV orchid strains (OFV-Orc1 and OFV-Orc2) in Florida.
 These strains of OFV are known to infect citrus and cause citrus leprosis disease.
-Three potential mite vectors were identified from OFV-infected plants using cryo-scanning electron microscopy (Cryo-SEM): *Brevipalpus californicus* s.l., *B.
+Three potential mite vectors were identified from OFV-infected plants using cryo-scanning electron microscopy (Cryo-SEM): *Brevipalpus californicus* (sensu lato), *B.
 obovatus*, and *B.
@@
 *Orchid fleck dichorhavirus* (OFV) is the type member for the genus *Dichorhavirus*, family Rhabdoviridae; a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
-Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the sole vectors for cileviruses and dichorhaviruses [@Maeda1998].
+Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the sole vectors of dichorhaviruses [@Maeda1998].
 *Brevipalpus californicus* (Banks) sensu lato mites are the only group known to transmit OFV in a persistent propagative manner [@Kondo2003].
 
-OFV-infected plants exhibit various symptoms depending on the infected plant species as well as the strain of the OFV associated with the infection [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns (`r citef("fig_1")`, `r citef("fig_2")`).
+OFV-infected plants exhibit various symptoms depending on the infected plant species as well as the strain of the OFV associated with the infection [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns<!--(`r citef("fig_1")`, `r citef("fig_2")`)-->.
 
@@
 californicus*, as well as *B.
-yothersi* (Baker), are both known vectors of Dichorhaviruses (OFV) and Cileviruses (Citrus Leprosis) [@Knorr1968; @Kondo2003; @Beltran-Beltran2020] and *B.
+yothersi* (Baker), are both known vectors of Dichorhaviruses (OFV) [@Kondo2003; @Beltran-Beltran2020] and *B.
 obovatus* is a suspected vector as well [@Childers2003].

### 2021-05-17 ofv_fife_2021.Rmd
Making more corrections to MS based on reviewers

@@
 confusus*.
-Florida has various native and introduced plants in the landscape that Brevipalpus spp.
+Florida has various native and introduced plants in the landscape that *Brevipalpus* spp.
 feed on, which are potentially susceptible to OFV.
 In this study, we report three new hosts from the family Asparagaceae from multiple locations.
-Our data suggested that OFV is widely distributed in Florida and might be a threat for various plant species growing in the southeastern US.
+Our data suggested that *Orchid fleck dichorhavirus* is widely distributed in Florida and might be a threat for various plant species growing in the southeastern US.
 
@@
 \pagebreak
-*Orchid fleck dichorhavirus* (OFV) is the type member for the genus *Dichorhavirus*, family Rhabdoviridae; a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
-Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the sole vectors of dichorhaviruses [@Maeda1998].
+*Orchid fleck dichorhavirus* (OFV) is the type member for the genus *Dichorhavirus*, family *Rhabdoviridae*; a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
+Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the only known vectors of dichorhaviruses [@Maeda1998].
 *Brevipalpus californicus* (Banks) sensu lato mites are the only group known to transmit OFV in a persistent propagative manner [@Kondo2003].

### 2021-05-20 editorial_reviews/response_editors_ofv_fife_2021.Rmd
Revised abstract to be less than 250 words and to improve clarity

@@
 
-Reviewer: 1
+#### Reviewer: 1
 
@@
 
-Accepted edits:
+<!-- - Added discussion on why OFV has not been reported in orchids or citrus if the pathogen and vectors appear so widespread in the state. -->
 
-- L3 - 'the United States' $\rightarrow$ 'Florida'
+<!-- - Added discussion of potential control measures to reduce the impact and spread of this virus is warranted. -->
 
-- L33 - 'Orchid Fleck Virus' $\rightarrow$ '*Orchid fleck dichorhavirus*'
+- Removed references to cileviruses
 
-- L155 - reference manager error: citation link '\@Kitajima2011b' $\rightarrow$ citation link '\@Kitajima2011a' (produces correct reference)
+For the mite descriptions, there seems to be inconsistency in providing taxonomic authorities.
+My understanding is that the authorities should be used upon introduction, but not afterwards.
+For example, see how Brevipalpus californicus is mentioned in L48, L64, L113, L164 etc.
 
-- fixed reference manager errors: added brackets {} around capitalized words {} and italic species names '{\\textit{}}' to protect case.
-also: Asparagalean, Amaryllidaceae, Asparagaceae, Xanthorrhoeaceae, *Rhabdoviridae*, Asparagaceae, RNA, *Psilanthus*
+The wording, organization, and grammar of the manuscript require significant revision for clarity and accuracy; perhaps more than I can offer below.
+More notably, some references are either incorrect, or interpreted incorrectly.
 
-Open edits:
+In the abstract it is mentioned that additional leaf samples were collected in Leon and Alachua counties, and in the following sentence it states that partial genome sequence confirmed the presence of OFV.
+Are these sentences linked?
+In the main text it appears only the samples from Leon County were actually found to be positive for OFV; the samples from Alachua were only examined for mites.
+I think this is an important clarification; are the authors basing their claim of the virus being widespread in Florida (L51) based on symptoms, or actually detecting OFV in both counties.
+Infection by different dichorhaviruses can result in similar symptoms; diagnostics are critical.
 
-- L319 - Is it necessary to italicize Rhabdoviridae in this context?
+L33: “Orchid fleck virus (OFV) is a dichorhavirus that infects over 50 plant species belonging to the families Asparagaceae, Orchidaceae, and Rutaceae.  The only known vectors for…”
 
-- L321 - no need to italicize Asparagaceae, it is a plant family
+L37: (Liriope and Ophiopogon spp.)
 
-Reviewer: 2
+L40: “…Sanger sequencing.”
+
+L41: remove “the known” and “the NCBI”
+
+L42: I see no mention of a qPCR assay in the main text
+
+L43: “…possibly infected plants of the family Asparagaceae from…”
+
+L44: please elaborate on “Identification of partial genome sequence…” is this sequence from the PCR products or was HTS performed on the samples?
+
+L48: perhaps identify what s.l. means; authorities are provided elsewhere in the manuscript
+
+L49: italicize “Brevipalpus”
+
+L59: Virus species should not be abbreviated; remove “(OFV)”
+
+L60: virus families are italicized (Rhabdoviridae)
+
+L63: replace “sole” with “only known”
+
+L64: “group of mites” vs “sensu lato”?
+
+L69: I don’t think referencing figures 1 and 2 are appropriate here
+
+L73,76: is listing the second author the correct way to distinguish articles for this journal?  Rather than “a” or “b” after publication year?
+
+L77: remove “: (Citrus)
+
+L78: Olmedo-Velarde et al. is not an appropriate reference here
+
+L82: “In June 2020,…”; (Lirope spp.)
+
+L83: belongs
+
+L85: perhaps “monocotyledonous liliod plants native to southeastern Asia (Chase…”
+
+L86: is it appropriate to provide an authority for the genus (Ker Gawler)?
+
+L92: none of these virus names should be italicized; INSV and TSWV are orthotospoviruses – why mentioned separately?
+
+L97: “…as well as Aspidistra elaitor Blume (Asparagaceae), which was suspected…”
+
+L103: “Lirope sp.”
+
+L108: how many sites?
+
+L127: This is incorrect: Blanchfield et al 2001 identified a virion larger than OFV, and the sample was negative for OFV when tested by RT-PCR.
+
+L134: Nolinoideae
+
+L145: The ICTV is not responsible for classification below species level, and as such, does not recognize virus strains; scientists and experts can recognize strains, but the  ICTV does not.
+
+L152: “including Vanilla spp. in southern Florida…”
+
+L154: a reference for this statement is advisable
+
+L155: “…found that the virus which previously affected…”
+
+L165: “…vectors of dichorhaviruses (Knorr 1968,…”
+
+L168: “…identify the vector(s) of OFV in Florida…”
+
+Table 1:
+L338: “…with symptoms of orchid fleck virus infection found in…”
+I am a little concerned about reporting on plants with symptoms, vs confirmed by diagnostics.
+As mentioned earlier, different dichorhaviruses can cause similar symptoms in the same host.
+Although remote, there is the possibility another virus could be responsible for the symptoms in a different location
+
+Figure captions:
+Please use “orchid fleck virus (OFV)” when describing a physical virus, and "Orchid fleck dichorhavirus" (in italics) when describing the species.
+
+#### Reviewer: 2
 
@@
 **Thank you for reviewing our article. We have made the following changes based on your remarks:**
+
+**Response to PDF edits (Reviewer #?):**
+**Thank you for reviewing our article. We have made the following changes based on your remarks:**
+
+Accepted edits:
+
+- L3 - 'the United States' $\rightarrow$ 'Florida'
+
+- L33 - 'Orchid Fleck Virus' $\rightarrow$ '*Orchid fleck dichorhavirus*'
+
+- L155 - reference manager error: citation link '\@Kitajima2011b' $\rightarrow$ citation link '\@Kitajima2011a' (produces correct reference)
+
+- fixed reference manager errors: added brackets {} around capitalized words {} and italic species names '{\\textit{}}' to protect case.
+also: Asparagalean, Amaryllidaceae, Asparagaceae, Xanthorrhoeaceae, *Rhabdoviridae*, Asparagaceae, RNA, *Psilanthus*
+
+Italicized all instances of *Rhabdoviridae*
+
+- L321 - no need to italicize Asparagaceae, it is a plant family

### 2021-05-20 ofv_fife_2021.Rmd
Revised abstract to be less than 250 words and to improve clarity

@@
 
-*Orchid fleck dichorhavirus* (OFV) infects over 50 plant species belonging to the family Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (Citrus).
-The only known vectors of dichorhaviruses are flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae).
-OFV was found infecting liriopogons (*Liriope* spp.
-and *Ophiopogon* spp.),  as well as *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in the landscape in Leon County, Florida, during the summer of 2020.
-The presence of OFV was confirmed using OFV-specific conventional reverse transcription polymerase chain assay (RT-PCR) assay and Sanger sequencing.
-RT-PCR amplicons had a 98% identity with known OFV sequences available in NCBI GenBank.
-Other leaf samples of the plant family Asparagaceae with ringspots and chlorosis were collected from Leon and Alachua counties and tested with PCR and Sanger sequencing to detect OFV.
-Identification of partial genome sequence from PCR products confirmed the presence of both OFV orchid strains (OFV-Orc1 and OFV-Orc2) in Florida.
-These strains of OFV are known to infect citrus and cause citrus leprosis disease.
-Three potential mite vectors were identified from OFV-infected plants using cryo-scanning electron microscopy (Cryo-SEM): *Brevipalpus californicus* (sensu lato), *B.
-obovatus*, and *B.
-confusus*.
-Florida has various native and introduced plants in the landscape that *Brevipalpus* spp.
-feed on, which are potentially susceptible to OFV.
-In this study, we report three new hosts from the family Asparagaceae from multiple locations.
-Our data suggested that *Orchid fleck dichorhavirus* is widely distributed in Florida and might be a threat for various plant species growing in the southeastern US.
+<!-- 250 words or less. -->
+<!-- Give scientific name and authority at first mention of each organism. -->
+<!-- Do not cite references, figures, tables, probability levels, or results. -->
+<!-- Refer to results only in the general sense. -->
+<!-- A second abstract in a second language is permitted. -->
+
+We report outbreaks of *Orchid fleck dichorhavirus* (OFV-Orc) infecting three new hosts: *Liriope* spp.
+*Ophiopogon* and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua Counties, Florida.
+Strains of OFV-Orc infect over 50 plant species belonging to the plant families Orchidaceae, Asparagaceae (Nolinoidaea), and infects *Citrus* (Rutaceae), as citrus leprosis disease.
+The only known vectors of OFV-Orc are flat mites from the genus *Brevipalpus* (Trombidiformes: Tenuipalpidae).
+Florida has various native and introduced plants in the landscape which *Brevipalpus* spp.
+feed on, which are potentially susceptible to OFV-Orc.
+
+Chlorotic ringspots flecking were seen affecting Liriopogons (*Liriope* spp.
+and *Ophiopogon* spp.) in Leon County, FL.
+Nearby *A.
+elatior* also appeared chlorotic.
+Local diagnostics returned negative for common plant viruses, so samples were sent to the Florida Department of Agriculture and Consumer Services for identification.
+Orchid-infecting *Orchid fleck dichorhavirus* was confirmed via conventional reverse transcription polymerase chain reaction of L-gene (RNA2) and Sanger sequencing of amplicons.
+Amplicons had a 98% identity with known OFV sequences available in NCBI GenBank.
+
+New samples from symptomatic plants were collected in both Leon and Alachua counties.
+High-throughput sequencing (HTS) at the USDA-ARS detected OFV-Orc and OFV-Orc2 in *Aspidistra* and *Liriope*, respectively.
+Three potential mite vectors were identified via cryo-scanning electron microscopy (Cryo-SEM): *Brevipalpus californicus* (Banks) sensu lato, *B.
+obovatus* Donnadieu, and *B.
+confusus* Baker.
+
+Our report suggests that *Orchid fleck dichorhavirus* is present in northern Florida, representing a risk for susceptible plants in the southeastern US.
 
@@
 *Orchid fleck dichorhavirus* (OFV) is the type member for the genus *Dichorhavirus*, family *Rhabdoviridae*; a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
-Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the only known vectors of dichorhaviruses [@Maeda1998].
+Flat mites from the genus *Brevipalpus* (Trombidiformes: Tenuipalpidae) are the only known vectors of dichorhaviruses [@Maeda1998].
 *Brevipalpus californicus* (Banks) sensu lato mites are the only group known to transmit OFV in a persistent propagative manner [@Kondo2003].
@@
 and later confirmed by the FDACS via Differential Interference Contrast (DIC) microscopy.
-The *Brevipalpus* mite species complex is known to contain cryptic species [@Childers2011] that require advanced microscopy techniques, such as cryo scanning electron microscopy (Cryo-SEM) for species identification [@Skoracka2015; @Leon2010; @Beard2015].
-Additional mite samples were collected from the original OFV detection site, and examined under Cryo-SEM (`r citef("fig_3")`).
-The determinations approved prior identifications of *B.
+The *B.
+californicus* s.
+l.
+species group, sensu @Baker1987 is suspected to contain cryptic species [@Childers2011; @Rodrigues2013], as seen in other *Brevipalpus* species, such as *B.
+phoenicis* (Geijskes) [@Beard2015].
+
+<!-- You need to identify mites with special techniques [@Skoracka2015] which require supplemental techniques in addition to light microscopy for accurate identification [@Beard2015].
+A plea for awareness of cryptic species [@Leon2010] -->
+
+New mite samples were collected from the site where OFV was first confirmed and sent to USDA-ARS's Electron and Confocal Microscopy Unit for analysis.
+Three mite species were recovered and examined under cryo scanning electron microscopy (Cryo-SEM): *B.
 californicus* s.l.
-but revealed the presence of two other species *B.
-obovatus* and *B.
-confusus* (`r citef("fig_4")`).
+(`r citef("fig_3")`), *B.
+obovatus* Baker and *B.
+confusus* Donnadieu (`r citef("fig_4")`).
 
@@
 
-### Table 1: List of plants with symptoms of *Orchid fleck dichorhavirus* found in northern Florida
+### Table 1: List of Asparagaceae (Nolinoidaea) species with verified cases of *Orchid fleck dichorhavirus*, along with basic descriptions of foliar symptoms seen in the landscape of northern Florida
 
@@
 `r fig_nums(name = "fig_4", caption = "Florida is home to other common pest species of *Brevipalpus*, which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
-yothersi*, dorsal (b) *B.
+phoenicis*, dorsal (b) *B.
 yothersi*, lateral (c) *B.

### 2021-05-21 ofv_fife_2021.Rmd
Word smithing up the distinctions between virus detection methods to clarify exactly what happened, where and to what plants.

@@
 
-We report outbreaks of *Orchid fleck dichorhavirus* (OFV-Orc) infecting three new hosts: *Liriope* spp.
-*Ophiopogon* and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua Counties, Florida.
+We describe the first outbreaks of *Orchid fleck dichorhavirus*, belonging to the orchid-infecting subgroup (OFV-Orc), from three unreported hosts: *Liriope muscari* (Decaisne) Bailey, *Ophiopogon intermedius* Don and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua Counties, FL.
 Strains of OFV-Orc infect over 50 plant species belonging to the plant families Orchidaceae, Asparagaceae (Nolinoidaea), and infects *Citrus* (Rutaceae), as citrus leprosis disease.
@@
 
-Chlorotic ringspots flecking were seen affecting Liriopogons (*Liriope* spp.
+Chlorotic ringspots and flecking were seen affecting Liriopogons (*Liriope* spp.
 and *Ophiopogon* spp.) in Leon County, FL.
-Nearby *A.
+Adjacent *A.
 elatior* also appeared chlorotic.
-Local diagnostics returned negative for common plant viruses, so samples were sent to the Florida Department of Agriculture and Consumer Services for identification.
-Orchid-infecting *Orchid fleck dichorhavirus* was confirmed via conventional reverse transcription polymerase chain reaction of L-gene (RNA2) and Sanger sequencing of amplicons.
-Amplicons had a 98% identity with known OFV sequences available in NCBI GenBank.
+Local diagnostics returned negative for common plant pathogens, therefore samples were sent to the Florida Department of Agriculture and Consumer Services for identification.
+OFV-Orc was confirmed in *L.
+muscari* and *A.
+elatior* via conventional reverse transcription polymerase chain reaction and Sanger sequencing of amplicons.
+Amplicons had a 98% identity with known sequences of Orchid fleck virus available in NCBI GenBank.
 
-New samples from symptomatic plants were collected in both Leon and Alachua counties.
-High-throughput sequencing (HTS) at the USDA-ARS detected OFV-Orc and OFV-Orc2 in *Aspidistra* and *Liriope*, respectively.
+New samples from symptomatic plants were collected in both Leon and Alachua counties and sent to the USDA-ARS.
+Conventional RT-PCR, RT-qPCR and Sanger sequencing confirmed the presence of Orchid fleck virus, OFV-Orc subgroup.
+High-throughput sequencing detected OFV-Orc and OFV-Orc2 in *A.
+elatior* and *L.
+muscari*, respectively.
 Three potential mite vectors were identified via cryo-scanning electron microscopy (Cryo-SEM): *Brevipalpus californicus* (Banks) sensu lato, *B.
@@
 ### Keywords:
-False spider mite, flat mite, *Brevipalpus*-transmitted viruses, *Liriope*, Nolinoideae, *Ophiopogon*, Ruscaceae, Rutaceae, Asparagaceae, orchid, Orchidaceae, pests, ornamental plants, orchid fleck virus.
+False spider mite, flat mite, *Brevipalpus*-transmitted viruses, *Liriope*, Nolinoideae, *Ophiopogon*, *Aspidistra*, Ruscaceae, Rutaceae, Asparagaceae, orchid, Orchidaceae, pests, ornamental plants, Orchid fleck virus.
 
@@
 
-OFV-infected plants exhibit various symptoms depending on the infected plant species as well as the strain of the OFV associated with the infection [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns<!--(`r citef("fig_1")`, `r citef("fig_2")`)-->.
+OFV-infected plants exhibit various symptoms depending on the infected plant species as well as the strain of the OFV associated with the infection [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns <!--(`r citef("fig_1")`, `r citef("fig_2")`)-->.
 
@@
 Upon collection, these new samples were sent to the Florida Department of Agriculture and Consumer Services (FDACS) for identification.
+The FDACS determined that the virus was *Orchid fleck dichorhavirus* using previously published primers and methods [@Kubo2006a; @Kubo2006b; @Kubo2009a; @Kubo2009b; @RamosGonzalez2015].
+Orchid subgroup OFV-Orc was identified following the methods described in @Kondo2017.
 
-The presence of OFV was confirmed using OFV generic R2-Dicho-GF and R2-Dicho-GR primers by one step conventional RT-PCR [@Roy2020], amplifying ~800 nt of L-gene (RNA2) amplicon from an infected *Liriope* leaf sample.
-Sanger sequencing of RT-PCR amplicons shared 98\% nucleotide identity with orchid strains of OFV: OFV-Orc1 and OFV-Orc2 (GenBank Accession numbers: AB244418 and LC222630) [@Kondo2006; @Kondo2017].
+Samples sent to the USDA confirmed the presence of OFV via one step conventional RT-PCR and RT-qPCR, using generic R2-Dicho-GF and R2-Dicho-GR primers, amplifying ~800 nt of L-gene (RNA2) amplicon [@Roy2020].
+Follow-up Sanger sequencing demonstrated a shared 98\% nucleotide identity with the orchid strain subgroup, OFV-Orc (isolates So and Br with GenBank Accession numbers: AB244418 and MK522807, respectively) [@Kondo2006; @Kondo2017].
+High Throughput sequencing results confirmed the presence of OFV-Orc2 strain in the *Liriope* sample.
 
@@
 [@Mei2016] but not in the US.
-The Florida collected plants of *Liriope* spp., cv 'Gigantea' are thought to belong to either *Liriope muscari* or *Liriope gigantea*.
+The *Liriope* spp., cv 'Gigantea' is considered a synonym of *Liriope muscari* [@Masiero2020; @Wang2014], but some consider it a separate species: *Liriope gigantea* Hume [@Fantz2015].
 We are not aware of any previous report of OFV infection in *Ophiopogon* plants.
@@
 All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017] (`r citef("fig_4")`).
-Therefore, it is critical to identify the vector of OFVs in Florida and monitor its spread to determine the risk this virus represents for the native plants, agriculture and the ornamental/landscaping industries of Florida and the surrounding regions.
+Therefore, it is critical to identify the vector of these strains of OFV in Florida to monitor their spread, and to determine the risk they represent for the native plants, agriculture and the ornamental/landscaping industries of Florida and the surrounding regions.
 
@@
 |:-----------|:--------------|:----------------|:-----|
-|*Liriope muscari* Bailey| Lilyturf, Orchardgrass, Monkeygrass| Ringspots, Chlorotic Flecking, Necrotic Lesions|Alachua & Leon|
+|*Liriope muscari* (Decaisne) Bailey| Lilyturf, Orchardgrass, Monkeygrass| Ringspots, Chlorotic Flecking, Necrotic Lesions|Alachua & Leon|
 |*Liriope gigantea*\* Hume| Giant Lilyturf| Ringspots, Chlorotic Flecking, Necrotic Lesions|Alachua & Leon|

### 2021-05-21 ofv_fife_2021.Rmd
Added information on OFV strain

@@
 
-We describe the first outbreaks of *Orchid fleck dichorhavirus*, belonging to the orchid-infecting subgroup (OFV-Orc), from three unreported hosts: *Liriope muscari* (Decaisne) Bailey, *Ophiopogon intermedius* Don and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua Counties, FL.
-Strains of OFV-Orc infect over 50 plant species belonging to the plant families Orchidaceae, Asparagaceae (Nolinoidaea), and infects *Citrus* (Rutaceae), as citrus leprosis disease.
-The only known vectors of OFV-Orc are flat mites from the genus *Brevipalpus* (Trombidiformes: Tenuipalpidae).
-Florida has various native and introduced plants in the landscape which *Brevipalpus* spp.
+We describe the first outbreaks of *Orchid fleck dichorhavirus*, belonging to the orchid-infecting subgroup (OFV-Orc), from three unreported hosts: *Liriope muscari*, cv.
+'Gigantea (Decaisne) Bailey, *Ophiopogon intermedius* Don and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua Counties, FL.
+Strains of OFV-Orc infect over 50 plant species belonging to the plant families Orchidaceae, Asparagaceae (Nolinoidaea), and infects *Citrus* (Rutaceae) as citrus leprosis disease.
+The only known vectors of OFV-Orc are flat mites, genus *Brevipalpus* (Trombidiformes: Tenuipalpidae).
+Florida has various plants in the landscape which *Brevipalpus* spp.
 feed on, which are potentially susceptible to OFV-Orc.
@@
 elatior* also appeared chlorotic.
-Local diagnostics returned negative for common plant pathogens, therefore samples were sent to the Florida Department of Agriculture and Consumer Services for identification.
+Local diagnostics returned negative for common plant pathogens, therefore samples were sent to the Florida Department of Agriculture and Consumer Services and USDA-ARS for identification.
+
 OFV-Orc was confirmed in *L.
 muscari* and *A.
-elatior* via conventional reverse transcription polymerase chain reaction and Sanger sequencing of amplicons.
-Amplicons had a 98% identity with known sequences of Orchid fleck virus available in NCBI GenBank.
-
-New samples from symptomatic plants were collected in both Leon and Alachua counties and sent to the USDA-ARS.
-Conventional RT-PCR, RT-qPCR and Sanger sequencing confirmed the presence of Orchid fleck virus, OFV-Orc subgroup.
+elatior* via conventional and quantitative reverse transcription polymerase chain reaction.
+Sanger sequencing of amplicons found 98% nucleotide identity with orchid-infecting strains of Orchid fleck virus available in NCBI GenBank.
 High-throughput sequencing detected OFV-Orc and OFV-Orc2 in *A.
@@
 muscari*, respectively.
-Three potential mite vectors were identified via cryo-scanning electron microscopy (Cryo-SEM): *Brevipalpus californicus* (Banks) sensu lato, *B.
-obovatus* Donnadieu, and *B.
-confusus* Baker.
+
+Three potential mite vectors were identified via cryo-scanning electron microscopy (Cryo-SEM): *Brevipalpus californicus* (Banks) sensu lato, *B. obovatus* Donnadieu, and *B. confusus* Baker.
 
@@
 The FDACS determined that the virus was *Orchid fleck dichorhavirus* using previously published primers and methods [@Kubo2006a; @Kubo2006b; @Kubo2009a; @Kubo2009b; @RamosGonzalez2015].
-Orchid subgroup OFV-Orc was identified following the methods described in @Kondo2017.
+Orchid subgroup 1, OFV-Orc was identified following the methods described in @Kondo2017.
 
 Samples sent to the USDA confirmed the presence of OFV via one step conventional RT-PCR and RT-qPCR, using generic R2-Dicho-GF and R2-Dicho-GR primers, amplifying ~800 nt of L-gene (RNA2) amplicon [@Roy2020].
-Follow-up Sanger sequencing demonstrated a shared 98\% nucleotide identity with the orchid strain subgroup, OFV-Orc (isolates So and Br with GenBank Accession numbers: AB244418 and MK522807, respectively) [@Kondo2006; @Kondo2017].
+Sanger sequencing demonstrated a shared 98\% nucleotide identity with the orchid strain subgroup, OFV-Orc (isolates So and Br with GenBank Accession numbers: AB244418 and MK522807, respectively) [@Kondo2006; @Kondo2017].
 High Throughput sequencing results confirmed the presence of OFV-Orc2 strain in the *Liriope* sample.

### 2021-05-25 ofv_fife_2021.Rmd
Added Dr. Roy's clarifications, edited abstract

@@
 Florida has various plants in the landscape which *Brevipalpus* spp.
-feed on, which are potentially susceptible to OFV-Orc.
+feed on, which are susceptible to infection by OFV-Orc.
 
-Chlorotic ringspots and flecking were seen affecting Liriopogons (*Liriope* spp.
+Chlorotic ringspots and flecking was seen affecting Liriopogons (*Liriope* spp.
 and *Ophiopogon* spp.) in Leon County, FL.
-Adjacent *A.
+Nearby *A.
 elatior* also appeared chlorotic.
-Local diagnostics returned negative for common plant pathogens, therefore samples were sent to the Florida Department of Agriculture and Consumer Services and USDA-ARS for identification.
+Local diagnostics returned negative for common plant pathogens, therefore new samples were sent to the Florida Department of Agriculture and Consumer Services (FDACS) and USDA-ARS for identification.
 
-OFV-Orc was confirmed in *L.
-muscari* and *A.
-elatior* via conventional and quantitative reverse transcription polymerase chain reaction.
-Sanger sequencing of amplicons found 98% nucleotide identity with orchid-infecting strains of Orchid fleck virus available in NCBI GenBank.
-High-throughput sequencing detected OFV-Orc and OFV-Orc2 in *A.
-elatior* and *L.
-muscari*, respectively.
+Two orchid-infecting strains of Orchid fleck virus were detected via combinations of conventional RT-PCR, RT-qPCR, Sanger sequencing and High Throughput Sequencing.
+Amplicons shared 98% nucleotide identity with OFV-Orc1 and OFV-Orc2 available in NCBI GenBank.
+Coinfections were seen in each county, but single strains of OFV-Orc were seen in *L.
+muscari* (Alachua, OFV-Orc2) and *A.
+elatior* (Leon, OFV-Orc1).
 
@@
 
-Our report suggests that *Orchid fleck dichorhavirus* is present in northern Florida, representing a risk for susceptible plants in the southeastern US.
+In conclusion, *Orchid fleck dichorhavirus* is present in northern Florida, representing a risk for susceptible plants in the southeastern US.
 

### 2021-05-25 ofv_fife_2021.Rmd
Updated with edits based on Dr. Roy's notes

@@
 We describe the first outbreaks of *Orchid fleck dichorhavirus*, belonging to the orchid-infecting subgroup (OFV-Orc), from three unreported hosts: *Liriope muscari*, cv.
-'Gigantea (Decaisne) Bailey, *Ophiopogon intermedius* Don and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua Counties, FL.
+'Gigantea' (Decaisne) Bailey, *Ophiopogon intermedius* Don and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua Counties, FL.
 Strains of OFV-Orc infect over 50 plant species belonging to the plant families Orchidaceae, Asparagaceae (Nolinoidaea), and infects *Citrus* (Rutaceae) as citrus leprosis disease.
@@
 Sanger sequencing demonstrated a shared 98\% nucleotide identity with the orchid strain subgroup, OFV-Orc (isolates So and Br with GenBank Accession numbers: AB244418 and MK522807, respectively) [@Kondo2006; @Kondo2017].
-High Throughput sequencing results confirmed the presence of OFV-Orc2 strain in the *Liriope* sample.
+These methods detected OFV-Orc1 and OFV-Orc2 in both *O.
+intermedius* and *A.
+elatior* from Leon County.
+High Throughput Sequencing (HTS) reaffirmed the presence of OFV-Orc1 and OFV-Orc2 strains in Leon and Alachua counties (`r citet("tab_1")`).
+HTS results from Leon County revealed that *L.
+muscari* were coinfected with both strains (OFV-Orc1 and OFV-Orc2), while *A.
+elatior* were solely infected with OFV-Orc1.
+HTS of *L.
+muscari* from Alachua County revealed infections with the OFV-Orc2 strain.
 
-Subsequent surveys of plants belonging to the subfamily Nolinoidaea in Florida have revealed more sites with Asparagaceae putatively infected with OFV in Leon and Alachua counties (`r citet("tab_1")`).
+<!-- Subsequent surveys of plants belonging to the subfamily Nolinoidaea in Florida have revealed more sites with Asparagaceae putatively infected with OFV in Leon and Alachua counties (`r citet("tab_1")`).
+-->
+
 Mites were collected from symptomatic plants in Leon county and observed with phase contrast microscopy.
@@
 
-### Table 1: List of Asparagaceae (Nolinoidaea) species with verified cases of *Orchid fleck dichorhavirus*, along with basic descriptions of foliar symptoms seen in the landscape of northern Florida
+### Table 1: List of Asparagaceae (Nolinoidaea) species with verified cases of *Orchid fleck dichorhavirus*, collected from the landscape of northern Florida
 
-|Scientific Name|Common Names|Symptoms Observed|County|
-|:-----------|:--------------|:----------------|:-----|
-|*Liriope muscari* (Decaisne) Bailey| Lilyturf, Orchardgrass, Monkeygrass| Ringspots, Chlorotic Flecking, Necrotic Lesions|Alachua & Leon|
-|*Liriope gigantea*\* Hume| Giant Lilyturf| Ringspots, Chlorotic Flecking, Necrotic Lesions|Alachua & Leon|
-|*Ophiopogon japonicus* Ker Gawl.| Dwarf Lilyturf, Mondo Grass, Snake's beard| Ringspots, Chlorotic Flecking, Necrotic Lesions|Leon|
-|*Ophiopogon intermedius*\*\* Don| Aztec Grass, 'Argenteomarginatus' | Ringspots, Chlorotic Flecking, Necrotic Lesions|Alachua & Leon|
-|*Aspidistra elatior* Blume| Cast Iron Plant, Bar-room Plant | Chlorosis, Chlorotic Flecking, Necrotic Lesions|Leon|
-`r tab_nums(name = "tab_1", caption = "* *L.
-gigantea* has been traditionally classified as seperate from *L.
-muscari* by @Broussard2007 and @Fantz2015, although this distinction has been challenged by @Wang2014 and @Masiero2020.
+|Scientific Name|Common Names|County|Strains|
+|:-----------|:--------------|:-----|:------|
+|*Liriope muscari* cv. 'Gigantea'\* (Decaisne) Bailey | Lilyturf, Orchardgrass, Monkeygrass|Alachua & Leon|OFV-Orc1 & OFV-Orc2|
+|*Ophiopogon intermedius*\*\* Don| Aztec Grass, 'Argenteomarginatus'|Leon|OFV-Orc1 & OFV-Orc2|
+|*Aspidistra elatior* Blume| Cast Iron Plant, Bar-room Plant|Leon|OFV-Orc1 & OFV-Orc2|
+`r tab_nums(name = "tab_1", caption = "* *Liriope muscari* cv.
+'Gigantea' has been traditionally classified as *L.
+gigantea* Hume by @Broussard2007 and @Fantz2015, although this distinction has been challenged by @Wang2014 and @Masiero2020.
 * * *O.

### 2021-05-27 ofv_fife_2021.Rmd
Minor edit

@@
 These surveys were conducted during July and August to collect more putatively infected plants, including more *Liriope* spp.
-as well as a new species which also belongs to the family Asparagaceae; *Aspidistra elatior* Blume, which was suspected to be infected due to unusually chlorotic leaves (`r citef("fig_2")`).
+as well as a new species which also belongs to the family Asparagaceae; *Aspidistra elatior* Blume, which was suspected to be infected, due to both its proximity to infected *Liriope* and its unusually chlorotic leaves (`r citef("fig_2")`).
 Upon collection, these new samples were sent to the Florida Department of Agriculture and Consumer Services (FDACS) for identification.

### 2021-06-03 ofv_fife_2021.Rmd
minor edits

@@
 OFV naturally infects more than fifty species of Orchidaceae [@Kitajima2010; @Peng2013], some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], and Rutaceae: (*Citrus*), where it causes citrus leprosis-like symptoms [@Cook2019; @OlmedoVelarde2019; @Roy2015; @Roy2020].
-Mechanical transmission of OFV is possible to some plants belonging to the plant families Chenopodiaceae, Aizoaceae, Fabaceae, and Solanaceae [@Chang1976; @Kondo2003; @Peng2013], under laboratory conditions.
+Mechanical transmission of OFV is possible under laboratory conditions to some plants belonging to the plant families Chenopodiaceae, Aizoaceae, Fabaceae, and Solanaceae [@Chang1976; @Kondo2003; @Peng2013].
 
@@
 'Gigantea' in a landscape of Leon County, Florida (`r citef("fig_1")`).
-*Liriope* belong to a group of plants in the family Asparagaceae, subfamily Nolinoidaea, which includes a diverse array of various monocotyledonous southeastern Asia native liliod plants [@Chase2009; @Meng2021].
-*Liriope* and the closely related *Ophiopogon* Ker Gawler (Asparagaceae: Nolinoidaea) are considered the most important ground cover nursery plants in the southeastern United States [@Mcharo2003].
+*Liriope* belong to a group of plants in the family Asparagaceae, subfamily Nolinoidaea, comprised of grass-like monocotyledonous liliod plants native to southeastern Asia [@Chase2009; @Meng2021].
+*Liriope* and the closely related *Ophiopogon* Ker Gawler (Asparagaceae: Nolinoidaea) are considered the most important ground cover plant in the southeastern United States [@Mcharo2003].
 

### 2021-06-03 ofv_fife_2021.Rmd
Your response seems appropriate. In our lab we just did RT-PCR and sequencing using Kundo’s paper. I feel you should highlight that USDA reconfirmed the findings of FDACS via RT-PCR, q-PCR and HTS. Because, we sent the same tissues to Beltsville so its double confirmation.

@@
 
-The initial site of collection was visited two more times during 2020 to gather plants for identification of the unidentified plant pathogen.
-These surveys were conducted during July and August to collect more putatively infected plants, including more *Liriope* spp.
-as well as a new species which also belongs to the family Asparagaceae; *Aspidistra elatior* Blume, which was suspected to be infected, due to both its proximity to infected *Liriope* and its unusually chlorotic leaves (`r citef("fig_2")`).
-Upon collection, these new samples were sent to the Florida Department of Agriculture and Consumer Services (FDACS) for identification.
-The FDACS determined that the virus was *Orchid fleck dichorhavirus* using previously published primers and methods [@Kubo2006a; @Kubo2006b; @Kubo2009a; @Kubo2009b; @RamosGonzalez2015].
+As initial diagnostics were inconclusive, new plant samples were collected during July and August of 2020 to collect more of these putatively-infected plants with ringspot symptoms.
+The plants collected included *Liriope* spp.
+and *Ophiopogon* spp., as well as *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea).
+*A.
+elatior* was suspected to be infected, due to both its proximity to infected *Liriope* and the presence of unusually chlorotic leaves (`r citef("fig_2")`).
+Upon collection, the new samples were sent to the Florida Department of Agriculture and Consumer Services (FDACS) for identification.
+
+The FDACS determined that the virus was *Orchid fleck dichorhavirus* using RT-PCR and Sanger sequencing using previously published primers and methods [@Kubo2006a; @Kubo2006b; @Kubo2009a; @Kubo2009b; @RamosGonzalez2015].
 Orchid subgroup 1, OFV-Orc was identified following the methods described in @Kondo2017.
+
+I feel you should highlight that USDA reconfirmed the findings of FDACS via RT-PCR, q-PCR and HTS. Because, we sent the same tissues to Beltsville so its double confirmation.
 

### 2021-06-03 ofv_fife_2021.Rmd
Made some edits for clarity

@@
 Viral infections of suspected leaf samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL.
-All the samples were tested with RT-PCR and were found negative for begomovirus, carlavirus, potyvirus, tospovirus, and *Cucumber mosaic virus*, *Impatiens necrotic spot virus*, *Tobacco mosaic virus*, and *Tomato spotted wilt virus*.
+All the samples were tested with one step conventional RT-PCR, and were found negative for begomovirus, carlavirus, potyvirus, tospovirus, and *Cucumber mosaic virus*, *Impatiens necrotic spot virus*, *Tobacco mosaic virus*, and *Tomato spotted wilt virus*.
 
-As initial diagnostics were inconclusive, new plant samples were collected during July and August of 2020 to collect more of these putatively-infected plants with ringspot symptoms.
+As initial diagnostics were inconclusive, new samples were collected during July and August of 2020 to collect more of these putatively-infected plants with ringspot symptoms.
 The plants collected included *Liriope* spp.
@@
 
-The FDACS determined that the virus was *Orchid fleck dichorhavirus* using RT-PCR and Sanger sequencing using previously published primers and methods [@Kubo2006a; @Kubo2006b; @Kubo2009a; @Kubo2009b; @RamosGonzalez2015].
+The FDACS determined that the pathogen was *Orchid fleck dichorhavirus* using previously published primers and methods to conduct RT-PCR and Sanger sequencing [@Kubo2006a; @Kubo2006b; @Kubo2009a; @Kubo2009b; @RamosGonzalez2015].
 Orchid subgroup 1, OFV-Orc was identified following the methods described in @Kondo2017.
+Sequencing demonstrated a shared 98\% nucleotide identity with the orchid strain subgroup, OFV-Orc (isolates So and Br with GenBank Accession numbers: AB244418 and MK522807, respectively) [@Kondo2006; @Kondo2017].
 
-I feel you should highlight that USDA reconfirmed the findings of FDACS via RT-PCR, q-PCR and HTS. Because, we sent the same tissues to Beltsville so its double confirmation.
-
-Samples sent to the USDA confirmed the presence of OFV via one step conventional RT-PCR and RT-qPCR, using generic R2-Dicho-GF and R2-Dicho-GR primers, amplifying ~800 nt of L-gene (RNA2) amplicon [@Roy2020].
-Sanger sequencing demonstrated a shared 98\% nucleotide identity with the orchid strain subgroup, OFV-Orc (isolates So and Br with GenBank Accession numbers: AB244418 and MK522807, respectively) [@Kondo2006; @Kondo2017].
-These methods detected OFV-Orc1 and OFV-Orc2 in both *O.
+These samples from FDACS were subsequently retested by the USDA-ARS, in conjunction with tests of fresh samples from both Alachua and Leon counties.
+The USDA used RT-PCR, RT-qPCR, and High Throughput Sequencing (HTS) in sequence to reconfirm the presence of *Orchid fleck dichorhavirus*.
+RT-PCR and qPCR with Generic R2-Dicho-GF and R2-Dicho-GR primers amplifed ~800 nt of L-gene (RNA2) amplicon [@Roy2020], and OFV-Orc1 and OFV-Orc2 were detected in both *O.
 intermedius* and *A.
 elatior* from Leon County.
-High Throughput Sequencing (HTS) reaffirmed the presence of OFV-Orc1 and OFV-Orc2 strains in Leon and Alachua counties (`r citet("tab_1")`).
+
+HTS reaffirmed the presence of OFV-Orc1 and OFV-Orc2 strains in Leon and Alachua counties (`r citet("tab_1")`).
 HTS results from Leon County revealed that *L.
@@
 
-<!-- Subsequent surveys of plants belonging to the subfamily Nolinoidaea in Florida have revealed more sites with Asparagaceae putatively infected with OFV in Leon and Alachua counties (`r citet("tab_1")`).
--->
+After the initial identification by FDACS of OFV-Orc, mite samples were collected from symptomatic Asparagaceae in Leon county.
+The majority of mites collected were Tenuipalpid mites (flat mites or false spider mites), a known pest of ornamental plants, some of which are known to act as vectors for plant viruses [@Childers2003; @Childers2011].
 
-Mites were collected from symptomatic plants in Leon county and observed with phase contrast microscopy.
-Tenuipalpid mites (flat mites or false spider mites) were commonly found in abundance on the Asparagaceae, which tested positive for OFV.
-These flat mites were initially identified as *B.
+Mite taxonomy is perturbed by the cryptic species complexes which exist in many plant-feeding species of the Acari [@Arthur2011; @Skoracka2010; @Skoracka2013; @Umina1999], including tenuipalpid mites from the common genus *Brevipalpus* [@Navia2013].
+Notwithstanding, additional techniques in addition to basic light microscopy can help to find characters necessary to separate species groups, including cryptic species [@Beard2015].
+
+The flat mites collected were initially suspected to belong to *B.
 californicus* s.
 l.
-and later confirmed by the FDACS via Differential Interference Contrast (DIC) microscopy.
-The *B.
+after inspection with phase contrast microscopy.
+Subsequent observation via Differential Interference Contrast (DIC) microscopy at FDACS agreed with this tentative identification.
+Unfortunately, the *B.
 californicus* s.
 l.
-species group, sensu @Baker1987 is suspected to contain cryptic species [@Childers2011; @Rodrigues2013], as seen in other *Brevipalpus* species, such as *B.
-phoenicis* (Geijskes) [@Beard2015].
+species group, sensu @Baker1987 is suspected to contain cryptic species [@Childers2011; @Rodrigues2013] as well.
 
-<!-- You need to identify mites with special techniques [@Skoracka2015] which require supplemental techniques in addition to light microscopy for accurate identification [@Beard2015].
-A plea for awareness of cryptic species [@Leon2010] -->
-
-New mite samples were collected from the site where OFV was first confirmed and sent to USDA-ARS's Electron and Confocal Microscopy Unit for analysis.
-Three mite species were recovered and examined under cryo scanning electron microscopy (Cryo-SEM): *B.
+With this information in mind, new mite samples were collected from symptomatic liriopogons and *A.
+elatior* in Leon County and sent to USDA-ARS's Electron and Confocal Microscopy Unit for analysis.
+Three mite species were recovered and examined under cryo-scanning electron microscopy (Cryo-SEM): *B.
 californicus* s.l.
@@
 In that publication, the authors confirmed the presence of OFV in *Phalaenopsis* hybrids in the US, using TEM of ultrathin sections of plant tissue as well as molecular sequence analysis and its association with *Brevipalpus* mites [@Bratsch2015].
-The authors did not make a conclusive species identification but suggested the mite vector was within the *B.
+The authors did not make a conclusive species identification but suggested the mite vector belonged to the *B.
 californicus* group, as referred by @Kondo2003.
@@
 OFV has been reported in other Nolinoidaea in Australia [@Dietzgen2018b; @Mei2016], including *Liriope spicata* (Thunb.) Lour.
-[@Mei2016] but not in the US.
-The *Liriope* spp., cv 'Gigantea' is considered a synonym of *Liriope muscari* [@Masiero2020; @Wang2014], but some consider it a separate species: *Liriope gigantea* Hume [@Fantz2015].
-We are not aware of any previous report of OFV infection in *Ophiopogon* plants.
-Although @Zheng2013 mention the association of *B.
-californicus* with *A.
-elatior*, but never reported OFV symptoms in this plant.
-However, our finding will be notified as the first report of OFV in Florida, in the US on ornamentals and among them, *A.
-elatior* is a new natural host of OFV.
+[@Mei2016] but has not been reported in any of these plants in the US.
+The *Liriope muscari* cv 'Gigantea' is considered a synonym of *Liriope gigantea* Hume [@Masiero2020; @Wang2014], but some consider it a separate species [@Fantz2015].
+We are not aware of any previous report of OFV-Orc infection in *Ophiopogon* plants.
+@Zheng2013 does mention an association between *B.
+californicus* and *A.
+elatior*, but they never reported symptoms of OFV-Orc in this plant.
+However, we believe that our findings indicate the first report of OFV-Orc infecting ornamentals in Florida, and possibly the US.
+This publication also marks the first reports of *A.
+elatior* and *Ophopogon* spp.
+as natural hosts of OFV-Orc.
 
@@
 obovatus* is a suspected vector as well [@Childers2003].
-All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017] (`r citef("fig_4")`).
-Therefore, it is critical to identify the vector of these strains of OFV in Florida to monitor their spread, and to determine the risk they represent for the native plants, agriculture and the ornamental/landscaping industries of Florida and the surrounding regions.
+All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017] (`r citef("fig_4")`), and are difficult to identify by non-experts, or without advanced methodologies.
+DNA barcoding [@Armstrong2005] or a similarly simple and accurate method for identification of these mite complexes is vital to determine which of these species are responsible for transmission of OFV-Orc, and therefore which mite populations need to be monitored or controlled.
+By doing so, we can determine the risk they represent for the native plants, agriculture and the ornamental/landscaping industries of Florida and the surrounding regions.
 

### 2021-06-04 editorial_reviews/response_editors_ofv_fife_2021.Rmd
Your response seems appropriate. In our lab we just did RT-PCR and sequencing using Kundo’s paper. I feel you should highlight that USDA reconfirmed the findings of FDACS via RT-PCR, q-PCR and HTS. Because, we sent the same tissues to Beltsville so its double confirmation.
Made some edits for clarity
Added citations, added discussion about why OFV-Orc hasn't infected citrus yet

@@
 
-<!-- - Added discussion on why OFV has not been reported in orchids or citrus if the pathogen and vectors appear so widespread in the state. -->
-
+- Added discussion on why OFV has not been reported in nearby citrus.
 <!-- - Added discussion of potential control measures to reduce the impact and spread of this virus is warranted. -->
-
-- Removed references to cileviruses
-
-For the mite descriptions, there seems to be inconsistency in providing taxonomic authorities.
-My understanding is that the authorities should be used upon introduction, but not afterwards.
-For example, see how Brevipalpus californicus is mentioned in L48, L64, L113, L164 etc.
+- We have removed all references to cileviruses
+- We have corrected inconsistencies with taxonomic authorities
 

### 2021-06-04 ofv_fife_2021.Rmd
Added citations, added discussion about why OFV-Orc hasn't infected citrus yet

@@
 title: "For submission to the Journal of Integrated Pest Management"
-subtitle: "Category: 'Issues'"
+subtitle: "Category: 'Brief Communications'"
 output: 
@@
 
-After the initial identification by FDACS of OFV-Orc, mite samples were collected from symptomatic Asparagaceae in Leon county.
+After the initial identification by FDACS of OFV-Orc strains, mite samples were collected from symptomatic Asparagaceae in Leon county.
 The majority of mites collected were Tenuipalpid mites (flat mites or false spider mites), a known pest of ornamental plants, some of which are known to act as vectors for plant viruses [@Childers2003; @Childers2011].
 
-Mite taxonomy is perturbed by the cryptic species complexes which exist in many plant-feeding species of the Acari [@Arthur2011; @Skoracka2010; @Skoracka2013; @Umina1999], including tenuipalpid mites from the common genus *Brevipalpus* [@Navia2013].
-Notwithstanding, additional techniques in addition to basic light microscopy can help to find characters necessary to separate species groups, including cryptic species [@Beard2015].
+Mite taxonomy is complicated by cryptic species complexes which occur in many plant-feeding groups of the Acari [@Arthur2011; @Skoracka2010; @Skoracka2013; @Umina1999], including tenuipalpid mites from the genus *Brevipalpus* [@Navia2013].
+The commonly used phase-contrast microscopy is insufficient to detect some diagnostic characters for seperation of cryptic species, instead best practices recommend the combination of Differential Interference Contrast (DIC) Microscopy and Scanning Electron Microscopy along with molecular methods to separate cryptic species [@Beard2015].
 
@@
 after inspection with phase contrast microscopy.
-Subsequent observation via Differential Interference Contrast (DIC) microscopy at FDACS agreed with this tentative identification.
+Subsequent observation via DIC microscopy at FDACS agreed with this tentative identification.
 Unfortunately, the *B.
@@
 l.
-species group, sensu @Baker1987 is suspected to contain cryptic species [@Childers2011; @Rodrigues2013] as well.
-
-With this information in mind, new mite samples were collected from symptomatic liriopogons and *A.
+species group, sensu @Baker1987 is suspected to contain cryptic species [@Childers2011; @Rodrigues2013].
+With this in mind, new mite samples were collected from symptomatic liriopogons and *A.
 elatior* in Leon County and sent to USDA-ARS's Electron and Confocal Microscopy Unit for analysis.
@@
 The first report of OFV in the US is thought to be @Ko1985, who describes nuclear inclusions caused by an undescribed bacilliform rhabdovirus in *Brassia* orchids.
-The significance of this report is their reference to spoke-wheel configurations of the viral particles [@Ko1985], a sign typically associated with OFV infection [@Chang1976].
-Unfortunately, @Ko1985 made no mention of mites or further investigations of this virus.
-The first certain report of OFV was from Hawaii in 2001 [@Blanchfield2001], while the first report from the continental US was by @Bratsch2015.
-In that publication, the authors confirmed the presence of OFV in *Phalaenopsis* hybrids in the US, using TEM of ultrathin sections of plant tissue as well as molecular sequence analysis and its association with *Brevipalpus* mites [@Bratsch2015].
-The authors did not make a conclusive species identification but suggested the mite vector belonged to the *B.
-californicus* group, as referred by @Kondo2003.
+The significance of this report is their description of the spoke-wheel configurations of the viral particles [@Ko1985], a sign typically associated with OFV infection [@Chang1976].
+Unfortunately, this article made no mention of mites or further investigations of the virus.
+In 2001, @Blanchfield2001 published the first certain report of OFV from Hawaii.
+The first report of OFV in the continental US was @Bratsch2015, who confirmed the presence of OFV in *Phalaenopsis* hybrids using Transmission Electron Microscopy of ultrathin sections of plant tissue as well as molecular sequence analysis.
+They also discuss the association of OFV with *Brevipalpus* mites, but the authors did not make a conclusive species identification beyond suggesting that the mite vector belonged to the *B.
+californicus* group, referring to @Kondo2003's publication [@Bratsch2015].
 
-OFV has been reported in other Nolinoidaea in Australia [@Dietzgen2018b; @Mei2016], including *Liriope spicata* (Thunb.) Lour.
-[@Mei2016] but has not been reported in any of these plants in the US.
-The *Liriope muscari* cv 'Gigantea' is considered a synonym of *Liriope gigantea* Hume [@Masiero2020; @Wang2014], but some consider it a separate species [@Fantz2015].
-We are not aware of any previous report of OFV-Orc infection in *Ophiopogon* plants.
-@Zheng2013 does mention an association between *B.
+Later reports of OFV described OFV infecting a previously undescribed Nolinoidaea hosts in Australia [@Dietzgen2018b; @Mei2016], including *Liriope spicata* (Thunb.) Lour, a different species of liriopogon than those identified from the Florida sites.
+We are not aware of any reports of OFV infecting liriopogons, *A.
+elatior* nor other Nolinoidaea in the US.
+Although @Zheng2013 had mentioned an association between *B.
 californicus* and *A.
-elatior*, but they never reported symptoms of OFV-Orc in this plant.
-However, we believe that our findings indicate the first report of OFV-Orc infecting ornamentals in Florida, and possibly the US.
+elatior*, they never reported symptoms of OFV-Orc in this plant.
+Taking this information into consideration, we believe that our findings indicate the first report of OFV-Orc infecting ornamental Nolinoidaea in Florida, and possibly the US.
 This publication also marks the first reports of *A.
-elatior* and *Ophopogon* spp.
+elatior* and *Ophiopogon* spp.
 as natural hosts of OFV-Orc.
 
-### Conclusion
-The dichorhavirus that infects citrus in Hawaii, Mexico, Colombia, and South Africa are identical to the OFV in gene order, content, and the genome sequence.
-According to the International Committee on Taxonomy of Viruses (ICTV) classification, OFV consist of two orchid strains (OFV-Orc1 and OFV-Orc2) and two citrus strains (OFV-Cit1 and OFV-Cit2).
-Both the orchid strains of OFV infects citrus [@Roy2020], but none of the citrus strains have been reported from any orchid species.
+OFV consists of two orchid strains (OFV-Orc1 and OFV-Orc2) and two citrus strains (OFV-Cit1 and OFV-Cit2) [@Roy2020; @Beltran-Beltran2020].
+The OFV strains detected in Florida are identical in gene order, content, and genome sequence to the orchid strains of OFV infecting citrus in Hawaii, Mexico, Colombia, and South Africa [@Roy2020; @Beltran-Beltran2020].
+Both OFV-Orc1 and OFV-Orc2 infect citrus [@Roy2020], but none of the citrus strains have been reported from any orchid species.
+The *Brevipalpus* mites collected from liriopogons and *A.
+elatior* in Leon county were abundant on OFV-infected plants very near to citrus trees, some plants even surrounding the trunk.
+*B.
+californicus* s.
+l.
+have been reported as a pest of citrus [@Childers2003] and are often collected from citrus rinds [@Baker1949; @Baker1987], so the proximity of these mite vectors to citrus raises the question: why these trees are not currently infected with OFV-Orc?
+Each possibility suggest further research, but there are a few possible explanations.
+It is important to note thge uncertaintly surrounding the vector for OFV-Orc.
+There are three mite species which have been recovered from OFV-Orc infected plants: *B.
+californicus* (the most likely culprit), *B.
+obovatus*, and *B.
+confusus*.
+Each species has its own unique biology and all have been implicated with a variety of different hosts.
+This suggests that the spread of OFV-Orc would be a function of various combinations of a number of potential factors, possibly including: host preferences, vectorial capacity, viral propagation/circulation in the vector, viral acquisition times, and feeding times required for transmission.
+Another possiblity is that the *B.
+californicus* which we find on liriopogons and *A.
+elatior* are not actually the same species as those found on citrus, and instead represent 2-3 different cryptic species.
+
 Detecting OFV in Florida represents a concern for horticulturists who grow orchids, *Liriope*, *Ophiopogon*, or other susceptible Asparagaceae species which are commonly used in landscaping.
@@
 
-`r fig_nums(name = "fig_3", caption = "Cryo-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2012] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.")`
+`r fig_nums(name = "fig_3", caption = "Cryo-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2015] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.")`
 

### 2021-06-07 editorial_reviews/response_editors_ofv_fife_2021.Rmd
Made final edits to MS, ready to forward to rest of the authors

--- 2021-05-14 editorial_reviews/response_editors_ofv_fife_2021.Rmd
@@
 
-Accepted edits:
+**We have adjusted some wording, organization, and grammar of the manuscript in an attempt to aid clarity and accuracy. We also reviewed and corrected some citations.**
 
-- L3 - 'the United States' $\rightarrow$ 'Florida'
+**We rewrote the sections describing sampling methods and diagnostics in the abstract and main text.
+Both samples from Leon County and Alachua were found to be positive for OFV; only samples from Leon were examined for mites.
+We have removed the claim that the virus is widespread.**
 
-- L33 - 'Orchid Fleck Virus' $\rightarrow$ '*Orchid fleck dichorhavirus*'
+Specific Edits:
 
-- L155 - reference manager error: citation link '\@Kitajima2011b' $\rightarrow$ citation link '\@Kitajima2011a' (produces correct reference)
+- Added discussion on why OFV has not been reported in nearby citrus.
+- We have removed all references to cileviruses
+- We have corrected inconsistencies with taxonomic authorities
+- We have not added a discussion of potential control measures due to word limits, and lack of specific documentation regarding control methods/chemical applications for these specific ornamental plants.
 
-- fixed reference manager errors: added brackets {} around capitalized words {} and italic species names '{\\textit{}}' to protect case.
-also: Asparagalean, Amaryllidaceae, Asparagaceae, Xanthorrhoeaceae, *Rhabdoviridae*, Asparagaceae, RNA, *Psilanthus*
+Also: 
+L33: “Orchid fleck virus (OFV) is a dichorhavirus that infects over 50 plant species belonging to the families Asparagaceae, Orchidaceae, and Rutaceae.
+The only known vectors for…” $\rightarrow$ **rewritten**
 
-Open edits:
+L37: (Liriope and Ophiopogon spp.) $\rightarrow$ **fixed**
 
-- L319 - Is it necessary to italicize Rhabdoviridae in this context?
+L40: “…Sanger sequencing.” $\rightarrow$ **fixed**
 
-- L321 - no need to italicize Asparagaceae, it is a plant family
+L41: remove “the known” and “the NCBI” $\rightarrow$ **fixed**
 
-Reviewer: 2
+L42: I see no mention of a qPCR assay in the main text $\rightarrow$ **fixed**
+
+L43: “…possibly infected plants of the family Asparagaceae from…” $\rightarrow$ **rewritten**
+
+L44: please elaborate on “Identification of partial genome sequence…” is this sequence from the PCR products or was HTS performed on the samples? $\rightarrow$ **rewritten**
+
+L48: perhaps identify what s.l.
+means; authorities are provided elsewhere in the manuscript $\rightarrow$ **sensu lato in this case refers to the fact that it not the specific mite referred to by Baker as *B.
+californicus*, which has been split into 3 subgroups, but have not been adequately described yet**
+
+L49: italicize “Brevipalpus” $\rightarrow$ **fixed**
+
+L59: Virus species should not be abbreviated; remove “(OFV)” $\rightarrow$ **Is this an acceptable alternative?**
+
+L60: virus families are italicized (Rhabdoviridae) $\rightarrow$ **fixed**
+
+L63: replace “sole” with “only known” $\rightarrow$ **fixed**
+
+L64: “group of mites” vs “sensu lato”? $\rightarrow$ **fixed**
+
+L69: I don’t think referencing figures 1 and 2 are appropriate here $\rightarrow$ **fixed**
+
+L73,76: is listing the second author the correct way to distinguish articles for this journal?  Rather than “a” or “b” after publication year? $\rightarrow$ **citation manager error, fixed**
+
+L77: remove “: (Citrus) $\rightarrow$ **fixed**
+
+L78: Olmedo-Velarde et al. is not an appropriate reference here $\rightarrow$ **citation should have been @Velarde2021, fixed**
+
+L82: “In June 2020,…”; (Lirope spp.) $\rightarrow$ **fixed**
+
+L83: belongs $\rightarrow$ **fixed**
+
+L85: perhaps “monocotyledonous liliod plants native to southeastern Asia (Chase…” $\rightarrow$ **fixed**
+
+L86: is it appropriate to provide an authority for the genus (Ker Gawler)? $\rightarrow$ **fixed**
+
+L92: none of these virus names should be italicized; INSV and TSWV are orthotospoviruses – why mentioned separately? $\rightarrow$ **I believe that these were specific tests, fixed**
+
+L97: “…as well as Aspidistra elaitor Blume (Asparagaceae), which was suspected…” $\rightarrow$ **fixed, *A. elatior***
+
+L103: “Lirope sp.” $\rightarrow$ **fixed**
+
+L108: how many sites?
+$\rightarrow$ **There are multiple sites with OFV-infected plants in Leon County, and one site identified in Alachua County.
+The plant samples tested from Leon Co.
+were taken from the first site where the pathogen was found.**
+
+L127: This is incorrect: Blanchfield et al 2001 identified a virion larger than OFV, and the sample was negative for OFV when tested by RT-PCR.
+$\rightarrow$ **Thank you for correcting this mistake, fixed**
+
+L134: Nolinoideae $\rightarrow$ **fixed**
+
+L145: The ICTV is not responsible for classification below species level, and as such, does not recognize virus strains; scientists and experts can recognize strains, but the  ICTV does not.
+$\rightarrow$ **fixed**
+
+L152: “including Vanilla spp. in southern Florida…” $\rightarrow$ **clarified**
+
+L154: a reference for this statement is advisable  $\rightarrow$ **clarified**
+
+L155: “…found that the virus which previously affected…”  $\rightarrow$ **clarified**
+
+L165: “…vectors of dichorhaviruses (Knorr 1968,…” $\rightarrow$ **clarified**
+
+L168: “…identify the vector(s) of OFV in Florida…” $\rightarrow$ **clarified**
+
+Table 1:
+L338: “…with symptoms of orchid fleck virus infection found in…”
+I am a little concerned about reporting on plants with symptoms, vs confirmed by diagnostics.
+As mentioned earlier, different dichorhaviruses can cause similar symptoms in the same host.
+Although remote, there is the possibility another virus could be responsible for the symptoms in a different location $\rightarrow$ **clarified in text**
+
+Figure captions:
+Please use “orchid fleck virus (OFV)” when describing a physical virus, and "Orchid fleck dichorhavirus" (in italics) when describing the species. $\rightarrow$ **fixed**
+
+#### Reviewer: 2
 
@@
 
-**Response to Reviewer 2:**
+**Reply to Reviewer 2:**
 **Thank you for reviewing our article. We have made the following changes based on your remarks:**
+
+**We have removed references to a 'wide distribution' in Florida, corrected species names and inconsistencies with citations. We are grateful for your assistance.**
+
+Specific Edits:
+
+- L3 - 'the United States' $\rightarrow$ 'Florida'
+
+- L33 - 'Orchid Fleck Virus' $\rightarrow$ '*Orchid fleck dichorhavirus*'
+
+- L155 - reference manager error: citation link '\@Kitajima2011b' $\rightarrow$ citation link '\@Kitajima2011a' (produces correct reference)
+
+- fixed reference manager errors: added brackets {} around capitalized words {} and italic species names '{\\textit{}}' to protect case.
+Also: Asparagalean, Amaryllidaceae, Asparagaceae, Xanthorrhoeaceae, *Rhabdoviridae*, Asparagaceae, RNA, *Psilanthus*
+
+Italicized all instances of *Rhabdoviridae*
+
+- L321 - We do not believe it is necessary to italicize the plant family 'Asparagaceae'

### 2021-06-07 ofv_fife_2021.Rmd
Made final edits to MS, ready to forward to rest of the authors

@@
 
-Chlorotic ringspots and flecking was seen affecting Liriopogons (*Liriope* spp.
-and *Ophiopogon* spp.) in Leon County, FL.
+Chlorotic ringspots and flecking was seen affecting Liriopogons (*Liriope* and *Ophiopogon* spp.) in Leon County, FL.
 Nearby *A.
@@
 ### Keywords:
-False spider mite, flat mite, *Brevipalpus*-transmitted viruses, *Liriope*, Nolinoideae, *Ophiopogon*, *Aspidistra*, Ruscaceae, Rutaceae, Asparagaceae, orchid, Orchidaceae, pests, ornamental plants, Orchid fleck virus.
+False spider mite, flat mite, *Brevipalpus*-transmitted viruses, *Liriope*, Nolinoidaea, *Ophiopogon*, *Aspidistra*, Ruscaceae, Rutaceae, Asparagaceae, orchid, Orchidaceae, pests, ornamental plants, Orchid fleck virus.
 
 \pagebreak
-*Orchid fleck dichorhavirus* (OFV) is the type member for the genus *Dichorhavirus*, family *Rhabdoviridae*; a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
-Flat mites from the genus *Brevipalpus* (Trombidiformes: Tenuipalpidae) are the only known vectors of dichorhaviruses [@Maeda1998].
-*Brevipalpus californicus* (Banks) sensu lato mites are the only group known to transmit OFV in a persistent propagative manner [@Kondo2003].
+*Orchid fleck dichorhavirus*, commonly referred to as Orchid Fleck Virus (OFV), is the type member for the genus *Dichorhavirus*, family *Rhabdoviridae*.
+OFV is a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
+Flat mites from the genus *Brevipalpus* (Trombidiformes: Tenuipalpidae) are the only group known to transmit dichorhaviruses [@Maeda1998], and *Brevipalpus californicus* (Banks) sensu lato are the only mites which do so in a persistent propagative manner [@Kondo2003].
 
@@
 
-OFV naturally infects more than fifty species of Orchidaceae [@Kitajima2010; @Peng2013], some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], and Rutaceae: (*Citrus*), where it causes citrus leprosis-like symptoms [@Cook2019; @OlmedoVelarde2019; @Roy2015; @Roy2020].
+OFV naturally infects more than fifty species of Orchidaceae [@Kitajima2010; @Peng2013], some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], and Rutaceae, where it causes citrus leprosis-like symptoms [@Cook2019; @Velarde2021; @Roy2015; @Roy2020].
 Mechanical transmission of OFV is possible under laboratory conditions to some plants belonging to the plant families Chenopodiaceae, Aizoaceae, Fabaceae, and Solanaceae [@Chang1976; @Kondo2003; @Peng2013].
@@
 *Liriope* belong to a group of plants in the family Asparagaceae, subfamily Nolinoidaea, comprised of grass-like monocotyledonous liliod plants native to southeastern Asia [@Chase2009; @Meng2021].
-*Liriope* and the closely related *Ophiopogon* Ker Gawler (Asparagaceae: Nolinoidaea) are considered the most important ground cover plant in the southeastern United States [@Mcharo2003].
+*Liriope* and the closely related *Ophiopogon* (Asparagaceae: Nolinoidaea) are considered the most important ground cover plant in the southeastern United States [@Mcharo2003].
 
 Viral infections of suspected leaf samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL.
-All the samples were tested with one step conventional RT-PCR, and were found negative for begomovirus, carlavirus, potyvirus, tospovirus, and *Cucumber mosaic virus*, *Impatiens necrotic spot virus*, *Tobacco mosaic virus*, and *Tomato spotted wilt virus*.
+All the samples were tested with one step conventional RT-PCR, and were found negative for begomovirus, carlavirus, potyvirus, tospovirus, Cucumber mosaic virus and Tobacco mosaic virus.
 
@@
 The flat mites collected were initially suspected to belong to *B.
-californicus* s.
-l.
-after inspection with phase contrast microscopy.
+californicus* after inspection with phase contrast microscopy.
 Subsequent observation via DIC microscopy at FDACS agreed with this tentative identification.
 Unfortunately, the *B.
-californicus* s.
-l.
+californicus* s.l.
 species group, sensu @Baker1987 is suspected to contain cryptic species [@Childers2011; @Rodrigues2013].
@@
 Unfortunately, this article made no mention of mites or further investigations of the virus.
-In 2001, @Blanchfield2001 published the first certain report of OFV from Hawaii.
 The first report of OFV in the continental US was @Bratsch2015, who confirmed the presence of OFV in *Phalaenopsis* hybrids using Transmission Electron Microscopy of ultrathin sections of plant tissue as well as molecular sequence analysis.
@@
 Each possibility suggest further research, but there are a few possible explanations.
-It is important to note thge uncertaintly surrounding the vector for OFV-Orc.
+It is important to note the uncertainty surrounding the vector for OFV-Orc.
 There are three mite species which have been recovered from OFV-Orc infected plants: *B.
@@
 Detecting OFV in Florida represents a concern for horticulturists who grow orchids, *Liriope*, *Ophiopogon*, or other susceptible Asparagaceae species which are commonly used in landscaping.
-Florida is also home to a plethora of native and naturalized orchid species, many of which are threatened, including cultivating *Vanilla* in southern Florida [@Chambers2019] and the famous Ghost Orchid, [*Dendrophylax lindenii* (Lindl.) Benth.
+Florida is also home to a plethora of native and naturalized orchid species, many of which are threatened, including cultivated *Vanilla* in southern Florida [@Chambers2019] and the famous Ghost Orchid, [*Dendrophylax lindenii* (Lindl.) Benth.
 ex Rolfe].
-Citrus leprosis was present in Florida during the 1860’s and eradicated in the mid-1960s.
-In fact, @Kitajima2011a found that the Citrus Leprosis virus (CiLV) which previously affected Florida citrus was a nuclear type of citrus leprosis closely related to OFV strains [@Roy2020; @Hartung2015].
-Association of a distant relative of OFV named Citrus leprosis dichorhavirus-N0 (CiLV-N0) was confirmed in relation to the leprosis disease outbreak in Florida [@Hartung2015].
+Citrus leprosis was present in Florida during the 1860’s and almost eradicated by the mid-1960s [@Childers2003; @Knorr1968a; @Knorr1968b].
+An examination of herbarium specimens of Florida citrus found that this historical virus, Citrus leprosis dichorhavirus-N0, is distantly related to the modern strains of OFV [@Hartung2015; @Kitajima2011a; @Roy2020].
 The recent detection of OFV-Orc1 in South Africa [@Cook2019] in *C.
@@
 californicus*, as well as *B.
-yothersi* (Baker), are both known vectors of Dichorhaviruses (OFV) [@Kondo2003; @Beltran-Beltran2020] and *B.
+yothersi* (Baker), are both known vectors of dichorhaviruses (OFV) [@Kondo2003; @Beltran-Beltran2020] and *B.
 obovatus* is a suspected vector as well [@Childers2003].
@@
 DNA barcoding [@Armstrong2005] or a similarly simple and accurate method for identification of these mite complexes is vital to determine which of these species are responsible for transmission of OFV-Orc, and therefore which mite populations need to be monitored or controlled.
-By doing so, we can determine the risk they represent for the native plants, agriculture and the ornamental/landscaping industries of Florida and the surrounding regions.
+By doing so, we can determine the risk OFV-Orc represents for the native plants, agriculture and the ornamental/landscaping industries of Florida and the surrounding regions.
 
@@
 `r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by *Liriope* spp.
-infected with Orchid fleck dichorhavirus (OFV): (a) ringspot symptoms on *Liriope gigantea* (b-c) Details of ringspot symptoms on *Liriope gigantea* (d) chlorotic ringspot *Liriope muscari* cv.
+infected with *Orchid fleck dichorhavirus*: (a) ringspot symptoms on *Liriope gigantea* (b-c) Details of ringspot symptoms on *Liriope gigantea* (d) chlorotic ringspot *Liriope muscari* cv.
 'Silvery Sunproof'")`
 
-`r fig_nums(name = "fig_2", caption = "Symptoms expressed by *Aspidistra elatior* infected with Orchid fleck dichorhavirus (OFV): (a) Detail of leaf chlorosis (b) Chlorosis caused by OFV appears similar to sunburn damage (c-d) Chlorotic ringspot may indicate early symptoms of OFV")`
+`r fig_nums(name = "fig_2", caption = "Symptoms expressed by *Aspidistra elatior* infected with *Orchid fleck dichorhavirus*: (a) Detail of leaf chlorosis (b) Chlorosis appears similar to sun damage (c-d) Chlorotic ringspot may indicate early symptoms of OFV")`
 

### 2021-06-08 ofv_fife_2021.Rmd
Authorities mixed up on B. confusus and B. obovatus in main text. Fixed minor grammatical errors as suggested by Word.

@@
 
-Chlorotic ringspots and flecking was seen affecting Liriopogons (*Liriope* and *Ophiopogon* spp.) in Leon County, FL.
+Chlorotic ringspots and flecking were seen affecting Liriopogons (*Liriope* and *Ophiopogon* spp.) in Leon County, FL.
 Nearby *A.
@@
 
-OFV-infected plants exhibit various symptoms depending on the infected plant species as well as the strain of the OFV associated with the infection [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into larger spots or ringspot patterns <!--(`r citef("fig_1")`, `r citef("fig_2")`)-->.
+OFV-infected plants exhibit various symptoms depending on the infected plant species as well as the strain of the OFV associated with the infection [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into ringspot patterns.
 
@@
 
-As initial diagnostics were inconclusive, new samples were collected during July and August of 2020 to collect more of these putatively-infected plants with ringspot symptoms.
+As initial diagnostics were inconclusive, new samples were collected during July and August of 2020 to collect more of these putatively infected plants with ringspot symptoms.
 The plants collected included *Liriope* spp.
@@
 
-After the initial identification by FDACS of OFV-Orc strains, mite samples were collected from symptomatic Asparagaceae in Leon county.
-The majority of mites collected were Tenuipalpid mites (flat mites or false spider mites), a known pest of ornamental plants, some of which are known to act as vectors for plant viruses [@Childers2003; @Childers2011].
+After the initial identification by FDACS of OFV-Orc strains, mite samples were collected from symptomatic Asparagaceae in Leon County.
+Most mites collected were Tenuipalpid mites (flat mites or false spider mites), a known pest of ornamental plants, some of which are known to act as vectors for plant viruses [@Childers2003; @Childers2011].
 
@@
 species group, sensu @Baker1987 is suspected to contain cryptic species [@Childers2011; @Rodrigues2013].
-With this in mind, new mite samples were collected from symptomatic liriopogons and *A.
+New mite samples were collected from symptomatic liriopogons and *A.
 elatior* in Leon County and sent to USDA-ARS's Electron and Confocal Microscopy Unit for analysis.
@@
 (`r citef("fig_3")`), *B.
-obovatus* Baker and *B.
-confusus* Donnadieu (`r citef("fig_4")`).
+obovatus* Donnadieu and *B.
+confusus* Baker (`r citef("fig_4")`).
 
@@
 The *Brevipalpus* mites collected from liriopogons and *A.
-elatior* in Leon county were abundant on OFV-infected plants very near to citrus trees, some plants even surrounding the trunk.
+elatior* in Leon County were abundant on OFV-infected plants very near to citrus trees, some plants even surrounding the trunk.
 *B.
@@
 l.
-have been reported as a pest of citrus [@Childers2003] and are often collected from citrus rinds [@Baker1949; @Baker1987], so the proximity of these mite vectors to citrus raises the question: why these trees are not currently infected with OFV-Orc?
-Each possibility suggest further research, but there are a few possible explanations.
+has been reported as a pest of citrus [@Childers2003] and are often collected from citrus rinds [@Baker1949; @Baker1987], so the proximity of these mite vectors to citrus raises the question: why these trees are not currently infected with OFV-Orc?
+Each possibility suggests further research, but there are a few possible explanations.
 It is important to note the uncertainty surrounding the vector for OFV-Orc.
@@
 confusus*.
-Each species has its own unique biology and all have been implicated with a variety of different hosts.
-This suggests that the spread of OFV-Orc would be a function of various combinations of a number of potential factors, possibly including: host preferences, vectorial capacity, viral propagation/circulation in the vector, viral acquisition times, and feeding times required for transmission.
-Another possiblity is that the *B.
+Each species has its own unique biology, and all have been implicated with a variety of different hosts.
+This suggests that the spread of OFV-Orc would be a function of various combinations of several potential factors, possibly including host preferences, vectorial capacity, viral propagation/circulation in the vector, viral acquisition times, and feeding times required for transmission.
+Another possibility is that the *B.
 californicus* which we find on liriopogons and *A.
@@
 reticulata* (mandarin) and *C.
-jambhiri* (rough lemon) associated with leprosis-like symptoms highlights the threat of different strains of OFV on citrus; which will be a definite concern to the US multi-billion dollar citrus industry.
+jambhiri* (rough lemon) associated with leprosis-like symptoms highlights the threat of different strains of OFV on citrus, which will be a definite concern to the US multi-billion-dollar citrus industry.
 *B.

### 2021-06-10 ofv_fife_2021.Rmd
Added reference
New citations

@@
 This suggests that the spread of OFV-Orc would be a function of various combinations of several potential factors, possibly including host preferences, vectorial capacity, viral propagation/circulation in the vector, viral acquisition times, and feeding times required for transmission.
-Another possibility is that the *B.
+@Ferreira2020 notes  Another possibility is that the *B.
 californicus* which we find on liriopogons and *A.
@@
 
-Detecting OFV in Florida represents a concern for horticulturists who grow orchids, *Liriope*, *Ophiopogon*, or other susceptible Asparagaceae species which are commonly used in landscaping.
+Best practices for integrated pest management have not been created for controlling *Brevipalpus* mites on these ornamentals, but methods designed to control other mite species may be applicable.
+The most common method used to control mites are synthetic acaricides and horticultural oils [@Leeuwen2015; @Gill2002].
+Unfortunately, some acaricides and their residues can harm beneficial predatory mites as well [@Fernandez2017], even at low doses [@Havasi2021], and mixing different chemistries can be detrimental for mite control [@Vechia2018].
+In addition, pesticide resistance has been reported in various *Brevipalpus* populations [@Alves2000; @Campos2002; @Omoto2000], possibly as the result of exposure to chemistry meant to control other arthropod pests [@Vechia2021].
+Various biological control methods have been studied as well, but their use has not been widely adopted for various reasons [@Messing2017], but predatory mites [@Chen2006], entomopathogenic fungi [@Reddy2001; @Midthassel2016], host plant resistance [@Leeuwen2009], and even ultraviolet radiation [@Osakabe2021] have shown some promise for controlling other plant-feeding mites.
+It is often possible to integrate different biological control techniques for improved control, such as combining predatory mites with entopathogenic fungi [@Reddy2001; @Midthassel2016].
+However, it is still necessary to consider the biology of biological agents to avoid incompatibilities, such as cannibalism [@Cakmak2009], requiring refuges [@Smith1991], or reapplying after conventional pesticides are used [@Smith1991].
+The predatory mite *Galendromus helveolus* (Chant) (Acari: Phytoseiidae) have been reported to feed on eggs, larvae and nymphs of *B.
+californicus* [@Chen2006] and studies of *Amblyseius largoensis* (Muma) (Acari: Phytoseiidae) demonstrated its ability to suppress populations of *B.
+yothersi* on citrus plants [@Argolo2020].
+In addition, the entomopathogenic fungus *Metarhizium anisopliae* var.
+*acridum* was found to be pathogenic to *B.
+phoenicis* [@Magalhaes2005].
+
+In conclusion, detecting OFV in Florida represents a concern for horticulturists who grow orchids, *Liriope*, *Ophiopogon*, or other susceptible Asparagaceae species which are commonly used in landscaping.
 Florida is also home to a plethora of native and naturalized orchid species, many of which are threatened, including cultivated *Vanilla* in southern Florida [@Chambers2019] and the famous Ghost Orchid, [*Dendrophylax lindenii* (Lindl.) Benth.
@@
 californicus*, as well as *B.
-yothersi* (Baker), are both known vectors of dichorhaviruses (OFV) [@Kondo2003; @Beltran-Beltran2020] and *B.
+yothersi* (Baker), are both known vectors of dichorhaviruses (OFV) [@GarciaEscamilla2018; @Kondo2003; @Beltran-Beltran2020] and *B.
 obovatus* is a suspected vector as well [@Childers2003].

### 2021-06-10 ofv_fife_2021.Rmd
I added the IPM section and integrated the other suggestions made

@@
 OFV is a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
-Flat mites from the genus *Brevipalpus* (Trombidiformes: Tenuipalpidae) are the only group known to transmit dichorhaviruses [@Maeda1998], and *Brevipalpus californicus* (Banks) sensu lato are the only mites which do so in a persistent propagative manner [@Kondo2003].
+Flat mites from the genus *Brevipalpus* (Trombidiformes: Tenuipalpidae) are the only group known to transmit dichorhaviruses [@Maeda1998], and *Brevipalpus californicus* (Banks) *sensu lato* are the only mites which do so in a persistent propagative manner [@Kondo2003].
 
@@
 
+#### Virus Detection
+
 During June 2020, chlorotic ringspot symptoms were observed on Giant Lilyturf *Liriope* spp., cv.
@@
 Viral infections of suspected leaf samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL.
-All the samples were tested with one step conventional RT-PCR, and were found negative for begomovirus, carlavirus, potyvirus, tospovirus, Cucumber mosaic virus and Tobacco mosaic virus.
+All the samples were tested with one step conventional RT-PCR, and were found negative for begomovirus, carlavirus, potyvirus, tospovirus, *Cucumber mosaic virus* and *Tobacco mosaic virus*.
 
@@
 
-The FDACS determined that the pathogen was *Orchid fleck dichorhavirus* using previously published primers and methods to conduct RT-PCR and Sanger sequencing [@Kubo2006a; @Kubo2006b; @Kubo2009a; @Kubo2009b; @RamosGonzalez2015].
+The FDACS determined eventually that the pathogen was *Orchid fleck dichorhavirus* using previously published primers and methods to conduct RT-PCR and Sanger sequencing [@Kubo2006a; @Kubo2006b; @Kubo2009a; @Kubo2009b; @RamosGonzalez2015].
 Orchid subgroup 1, OFV-Orc was identified following the methods described in @Kondo2017.
@@
 
+#### Mite Description
+
 Mite taxonomy is complicated by cryptic species complexes which occur in many plant-feeding groups of the Acari [@Arthur2011; @Skoracka2010; @Skoracka2013; @Umina1999], including tenuipalpid mites from the genus *Brevipalpus* [@Navia2013].
-The commonly used phase-contrast microscopy is insufficient to detect some diagnostic characters for seperation of cryptic species, instead best practices recommend the combination of Differential Interference Contrast (DIC) Microscopy and Scanning Electron Microscopy along with molecular methods to separate cryptic species [@Beard2015].
+The commonly used phase-contrast microscopy is insufficient to detect some diagnostic characters for separation of cryptic species, instead best practices recommend the combination of Differential Interference Contrast (DIC) Microscopy and Scanning Electron Microscopy along with molecular methods to separate cryptic species [@Beard2015].
 
@@
 californicus* s.l.
-species group, sensu @Baker1987 is suspected to contain cryptic species [@Childers2011; @Rodrigues2013].
+species group, *sensu* @Baker1987 is suspected to contain cryptic species [@Childers2011; @Rodrigues2013].
 New mite samples were collected from symptomatic liriopogons and *A.
@@
 has been reported as a pest of citrus [@Childers2003] and are often collected from citrus rinds [@Baker1949; @Baker1987], so the proximity of these mite vectors to citrus raises the question: why these trees are not currently infected with OFV-Orc?
-Each possibility suggests further research, but there are a few possible explanations.
 It is important to note the uncertainty surrounding the vector for OFV-Orc.
 There are three mite species which have been recovered from OFV-Orc infected plants: *B.
-californicus* (the most likely culprit), *B.
+californicus* s.l.
+(the most likely culprit), *B.
 obovatus*, and *B.
@@
 @Ferreira2020 notes  Another possibility is that the *B.
-californicus* which we find on liriopogons and *A.
-elatior* are not actually the same species as those found on citrus, and instead represent 2-3 different cryptic species.
+californicus* that we find on liriopogons and *A.
+elatior* are not actually the same species as those found on citrus, and instead represent 2 to 3 different cryptic species.
 
@@
 reticulata* (mandarin) and *C.
-jambhiri* (rough lemon) associated with leprosis-like symptoms highlights the threat of different strains of OFV on citrus, which will be a definite concern to the US multi-billion-dollar citrus industry.
+jambhiri* (rough lemon) associated with leprosis-like symptoms highlights the threat of different strains of OFV on citrus, which will be a definite concern to the US multi-billion-dollar citrus industry already impacted by the Huanglongbing disease.
 *B.
@@
 
-`r fig_nums(name = "fig_3", caption = "Cryo-SEM images of *Brevipalpus californicus* sensu lato displaying various characters used for identification [@Baker1987; @Beard2015] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.")`
+`r fig_nums(name = "fig_3", caption = "Cryo-SEM images of *Brevipalpus californicus* *sensu lato* displaying various characters used for identification [@Baker1987; @Beard2015] (a) Dorsum  (b) Lateral view (c) Venter (d) Close up of distal end of leg 2, with arrows indicating paired solenidia, characteristic of the genus *Brevipalpus* (e) Enlargement of the microplates of the mite cerotegument (f) Dorsal view of the distal portion of mite abdomen (g) Dorsal view of the mite rostrum (h) Ventral view of mite rostrum, observe 3 distal setae.")`
 

### 2021-06-11 ofv_fife_2021.Rmd
integrated new author comments

@@
 elatior*, they never reported symptoms of OFV-Orc in this plant.
-Taking this information into consideration, we believe that our findings indicate the first report of OFV-Orc infecting ornamental Nolinoidaea in Florida, and possibly the US.
+We believe that our findings indicate the first report of OFV-Orc infecting ornamental Nolinoidaea in Florida, and possibly the US.
 This publication also marks the first reports of *A.
@@
 l.
-has been reported as a pest of citrus [@Childers2003] and are often collected from citrus rinds [@Baker1949; @Baker1987], so the proximity of these mite vectors to citrus raises the question: why these trees are not currently infected with OFV-Orc?
+has been reported as a pest of citrus [@Childers2003] and are often collected from citrus rinds [@Baker1949; @Baker1987].
+The proximity of these mite vectors to citrus raises the question: why these trees are not currently infected with OFV-Orc?
 It is important to note the uncertainty surrounding the vector for OFV-Orc.
@@
 Each species has its own unique biology, and all have been implicated with a variety of different hosts.
-This suggests that the spread of OFV-Orc would be a function of various combinations of several potential factors, possibly including host preferences, vectorial capacity, viral propagation/circulation in the vector, viral acquisition times, and feeding times required for transmission.
-@Ferreira2020 notes  Another possibility is that the *B.
-californicus* that we find on liriopogons and *A.
-elatior* are not actually the same species as those found on citrus, and instead represent 2 to 3 different cryptic species.
+This suggests that the spread of OFV-Orc would be a function of various combinations of several potential factors, including host preferences, vectorial capacity, viral propagation/circulation in the vector, viral acquisition times, and feeding times required for transmission.
+Some of these factors have been tested: *Brevipalpus* vectors have demonstrated such virus-vector specificity with another dichorhavirus \em *Citrus leprosis virus N*, which causes citrus leprosis [@Roy2013a] \em in studies done by @Ferreira2020 and @GarciaEscamilla2018.
+In these studies, *Brevipalpus* mites were not able to transmit more than one virus.
+This could mean that the *B.
+californicus* which we find on liriopogons and *A.
+elatior* are not actually the same species as those found on citrus, or at least are not able to transmit OFV to citrus.
 
-Best practices for integrated pest management have not been created for controlling *Brevipalpus* mites on these ornamentals, but methods designed to control other mite species may be applicable.
-The most common method used to control mites are synthetic acaricides and horticultural oils [@Leeuwen2015; @Gill2002].
+Best practices for integrated pest management have not been created for controlling *Brevipalpus* mites on these ornamentals, but methods designed to control *Brevipalpus* in other systems may be applicable.
+The most common method used to control *Bervipalpus* are synthetic acaricides [@Andrade2010; @Andrade2019]].
 Unfortunately, some acaricides and their residues can harm beneficial predatory mites as well [@Fernandez2017], even at low doses [@Havasi2021], and mixing different chemistries can be detrimental for mite control [@Vechia2018].
-In addition, pesticide resistance has been reported in various *Brevipalpus* populations [@Alves2000; @Campos2002; @Omoto2000], possibly as the result of exposure to chemistry meant to control other arthropod pests [@Vechia2021].
-Various biological control methods have been studied as well, but their use has not been widely adopted for various reasons [@Messing2017], but predatory mites [@Chen2006], entomopathogenic fungi [@Reddy2001; @Midthassel2016], host plant resistance [@Leeuwen2009], and even ultraviolet radiation [@Osakabe2021] have shown some promise for controlling other plant-feeding mites.
-It is often possible to integrate different biological control techniques for improved control, such as combining predatory mites with entopathogenic fungi [@Reddy2001; @Midthassel2016].
-However, it is still necessary to consider the biology of biological agents to avoid incompatibilities, such as cannibalism [@Cakmak2009], requiring refuges [@Smith1991], or reapplying after conventional pesticides are used [@Smith1991].
-The predatory mite *Galendromus helveolus* (Chant) (Acari: Phytoseiidae) have been reported to feed on eggs, larvae and nymphs of *B.
-californicus* [@Chen2006] and studies of *Amblyseius largoensis* (Muma) (Acari: Phytoseiidae) demonstrated its ability to suppress populations of *B.
-yothersi* on citrus plants [@Argolo2020].
-In addition, the entomopathogenic fungus *Metarhizium anisopliae* var.
-*acridum* was found to be pathogenic to *B.
-phoenicis* [@Magalhaes2005].
+In addition, pesticide resistance has been reported in various *Brevipalpus* populations [@Rocha2021; @Alves2000; @Campos2002; @Omoto2000], due to exposure to pesticides used to control other arthropod pests [@Vechia2021].
+In addition, predatory mites [@Argolo2020; @Chen2006], entomopathogenic fungi [@RossiZalaf2008; @Magalhaes2005; @Pena2015; @Revynthi2019] have shown promise for controlling other *Brevipalpus* mites.
+Moreover, it is often possible to integrate different control techniques for improved management, such as combining predatory mites with compatible acaricides and entomopathogenic fungi [@Reddy2001; @Midthassel2016; @Andrade2019].
 
@@
 californicus*, as well as *B.
-yothersi* (Baker), are both known vectors of dichorhaviruses (OFV) [@GarciaEscamilla2018; @Kondo2003; @Beltran-Beltran2020] and *B.
+yothersi*, are both known vectors of dichorhaviruses (OFV) [@GarciaEscamilla2018; @Kondo2003; @Beltran-Beltran2020] and *B.
 obovatus* is a suspected vector as well [@Childers2003].

### 2021-06-11 ofv_fife_2021.Rmd
submitted to other authors

@@
 This suggests that the spread of OFV-Orc would be a function of various combinations of several potential factors, including host preferences, vectorial capacity, viral propagation/circulation in the vector, viral acquisition times, and feeding times required for transmission.
-Some of these factors have been tested: *Brevipalpus* vectors have demonstrated such virus-vector specificity with another dichorhavirus \em *Citrus leprosis virus N*, which causes citrus leprosis [@Roy2013a] \em in studies done by @Ferreira2020 and @GarciaEscamilla2018.
+Some of these factors have been tested: *Brevipalpus* vectors have demonstrated such virus-vector specificity with *Citrus leprosis virus N*--another dichorhavirus which causes citrus leprosis [@Roy2013a]--in studies done by @Ferreira2020 and @GarciaEscamilla2018.
 In these studies, *Brevipalpus* mites were not able to transmit more than one virus.
@@
 Best practices for integrated pest management have not been created for controlling *Brevipalpus* mites on these ornamentals, but methods designed to control *Brevipalpus* in other systems may be applicable.
-The most common method used to control *Bervipalpus* are synthetic acaricides [@Andrade2010; @Andrade2019]].
+The most common method used to control *Bervipalpus* are synthetic acaricides [@Andrade2010; @Andrade2019].
 Unfortunately, some acaricides and their residues can harm beneficial predatory mites as well [@Fernandez2017], even at low doses [@Havasi2021], and mixing different chemistries can be detrimental for mite control [@Vechia2018].

### 2021-06-16 ofv_fife_2021.Rmd
finishing touches, ready to submit!

@@
 title: "For submission to the Journal of Integrated Pest Management"
-subtitle: "Category: 'Brief Communications'"
+subtitle: "Category: 'Issues'"
 output: 

### 2021-06-16 ofv_fife_2021.Rmd
forgot to update the figure captions with the correct plant IDs, as verified by Dr. Hale

@@
 `r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by *Liriope* spp.
-infected with *Orchid fleck dichorhavirus*: (a) ringspot symptoms on *Liriope gigantea* (b-c) Details of ringspot symptoms on *Liriope gigantea* (d) chlorotic ringspot *Liriope muscari* cv.
-'Silvery Sunproof'")`
+infected with *Orchid fleck dichorhavirus*: (a) ringspot symptoms on *Liriope muscari* cv.
+'Gigantea' (b-c) Details of ringspot symptoms on *L.
+muscari* cv.
+'Gigantea' (d) rust colored spots on *Ophiopogon intermedius*")`
 

### 2021-08-12 ofv_fife_2021.Rmd
making adjustments based on reviewer's suggestions

@@
 
-### First report of the *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) *Orchid fleck dichorhavirus* infecting three ornamentals in Florida
+### **Request from Reviewer 4: Revise title to better reflect content of publiction** First report of the *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) orchid fleck virus infecting three ornamentals in Florida
 
@@
 
-We describe the first outbreaks of *Orchid fleck dichorhavirus*, belonging to the orchid-infecting subgroup (OFV-Orc), from three unreported hosts: *Liriope muscari*, cv.
+We describe the first detection of orchid fleck virus (OFV), belonging to the orchid-infecting subgroup (OFV-Orc), infecting three unreported hosts: *Liriope muscari*, cv.
 'Gigantea' (Decaisne) Bailey, *Ophiopogon intermedius* Don and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua Counties, FL.
 Strains of OFV-Orc infect over 50 plant species belonging to the plant families Orchidaceae, Asparagaceae (Nolinoidaea), and infects *Citrus* (Rutaceae) as citrus leprosis disease.
-The only known vectors of OFV-Orc are flat mites, genus *Brevipalpus* (Trombidiformes: Tenuipalpidae).
+The only known vectors of OFV-Orc are the flat mites  *Brevipalpus californicus* (Banks) *sensu lato* (Trombidiformes: Tenuipalpidae).
 Florida has various plants in the landscape which *Brevipalpus* spp.
@@
 
-Two orchid-infecting strains of Orchid fleck virus were detected via combinations of conventional RT-PCR, RT-qPCR, Sanger sequencing and High Throughput Sequencing.
+Two orchid-infecting strains of OFV were detected via combinations of conventional RT-PCR, RT-qPCR, Sanger sequencing and High Throughput Sequencing.
 Amplicons shared 98% nucleotide identity with OFV-Orc1 and OFV-Orc2 available in NCBI GenBank.
@@
 
-In conclusion, *Orchid fleck dichorhavirus* is present in northern Florida, representing a risk for susceptible plants in the southeastern US.
+In conclusion, OFV is present in northern Florida, representing a risk for susceptible plants in the southeastern US.
 
 ### Keywords:
-False spider mite, flat mite, *Brevipalpus*-transmitted viruses, *Liriope*, Nolinoidaea, *Ophiopogon*, *Aspidistra*, Ruscaceae, Rutaceae, Asparagaceae, orchid, Orchidaceae, pests, ornamental plants, Orchid fleck virus.
+False spider mite, flat mite, *Brevipalpus*-transmitted viruses, *Liriope*, Nolinoidaea, *Ophiopogon*, *Aspidistra*, Ruscaceae, Rutaceae, Asparagaceae, orchid, Orchidaceae, pests, ornamental plants, orchid fleck virus.
 
 \pagebreak
-*Orchid fleck dichorhavirus*, commonly referred to as Orchid Fleck Virus (OFV), is the type member for the genus *Dichorhavirus*, family *Rhabdoviridae*.
+Orchid fleck virus (OFV), is the type member for the genus *Dichorhavirus*, family *Rhabdoviridae*.
 OFV is a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
-Flat mites from the genus *Brevipalpus* (Trombidiformes: Tenuipalpidae) are the only group known to transmit dichorhaviruses [@Maeda1998], and *Brevipalpus californicus* (Banks) *sensu lato* are the only mites which do so in a persistent propagative manner [@Kondo2003].
+Flat mites from the genus *Brevipalpus* (Trombidiformes: Tenuipalpidae) are the only which have been experimentally shown to transmit dichorhaviruses [@Maeda1998].
 
@@
 Viral infections of suspected leaf samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL.
-All the samples were tested with one step conventional RT-PCR, and were found negative for begomovirus, carlavirus, potyvirus, tospovirus, *Cucumber mosaic virus* and *Tobacco mosaic virus*.
+All the samples were tested with one step conventional RT-PCR, and were found negative for begomovirus, carlavirus, potyvirus, tospovirus, cucumber mosaic virus and tobacco mosaic virus.
 
-As initial diagnostics were inconclusive, new samples were collected during July and August of 2020 to collect more of these putatively infected plants with ringspot symptoms.
-The plants collected included *Liriope* spp.
-and *Ophiopogon* spp., as well as *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea).
-*A.
-elatior* was suspected to be infected, due to both its proximity to infected *Liriope* and the presence of unusually chlorotic leaves (`r citef("fig_2")`).
-Upon collection, the new samples were sent to the Florida Department of Agriculture and Consumer Services (FDACS) for identification.
+As initial diagnostics were inconclusive, samples were taken of putatively infected plants with ringspot symptoms during July and August of 2020.
+Leaves were taken from *Liriope* spp.
+and *Ophiopogon* spp., as well as *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea), which were suspected to be infected, due to both its proximity to infected *Liriope* and the presence of unusually chlorotic leaves (`r citef("fig_2")`).
+Plant materials were sent to the Florida Department of Agriculture and Consumer Services (FDACS) for identification.
 
-The FDACS determined eventually that the pathogen was *Orchid fleck dichorhavirus* using previously published primers and methods to conduct RT-PCR and Sanger sequencing [@Kubo2006a; @Kubo2006b; @Kubo2009a; @Kubo2009b; @RamosGonzalez2015].
-Orchid subgroup 1, OFV-Orc was identified following the methods described in @Kondo2017.
+The FDACS determined that the pathogen was OFV using previously published primers and methods to conduct RT-PCR and Sanger sequencing [@Kubo2009a; @Kubo2009b; @RamosGonzalez2015].
+Orchid subgroup 1, OFV-Orc, was identified following the methods described in @Kondo2017.
 Sequencing demonstrated a shared 98\% nucleotide identity with the orchid strain subgroup, OFV-Orc (isolates So and Br with GenBank Accession numbers: AB244418 and MK522807, respectively) [@Kondo2006; @Kondo2017].
@@
 These samples from FDACS were subsequently retested by the USDA-ARS, in conjunction with tests of fresh samples from both Alachua and Leon counties.
-The USDA used RT-PCR, RT-qPCR, and High Throughput Sequencing (HTS) in sequence to reconfirm the presence of *Orchid fleck dichorhavirus*.
+The USDA used RT-PCR, RT-qPCR, and High Throughput Sequencing (HTS) to reconfirm the presence of OFV.
 RT-PCR and qPCR with Generic R2-Dicho-GF and R2-Dicho-GR primers amplifed ~800 nt of L-gene (RNA2) amplicon [@Roy2020], and OFV-Orc1 and OFV-Orc2 were detected in both *O.
@@
 elatior* from Leon County.
+**(insert statement of how much OFV-Orc1 and OFV-Orc2 differ at the nucleotide level)** ***Request from Reviewer 2: deposit and include GenBank accession numbers for the identified virus isolates in Florida?
+Re:New reports of viruses required that or two other alternative methods for viral detection** **Question from Reviewer 4: Does each isolate reflect a strain?**
 
@@
 After the initial identification by FDACS of OFV-Orc strains, mite samples were collected from symptomatic Asparagaceae in Leon County.
-Most mites collected were Tenuipalpid mites (flat mites or false spider mites), a known pest of ornamental plants, some of which are known to act as vectors for plant viruses [@Childers2003; @Childers2011].
+Most mites collected were Tenuipalpid mites (flat mites or false spider mites), a pest of ornamental plants, some of which are known to act as vectors for plant viruses [@Childers2003; @Childers2011].
 
@@
 obovatus* Donnadieu and *B.
-confusus* Baker (`r citef("fig_4")`).
+confusus* Baker<!--  (`r citef("fig_4")`) -->.
 
@@
 l.
-has been reported as a pest of citrus [@Childers2003] and are often collected from citrus rinds [@Baker1949; @Baker1987].
+has been reported as a pest of citrus [@Childers2003] and are often collected from citrus fruits [@Vacante2016; @Vacante2010; @Baker1987; @Baker1949].
 The proximity of these mite vectors to citrus raises the question: why these trees are not currently infected with OFV-Orc?
@@
 There are three mite species which have been recovered from OFV-Orc infected plants: *B.
-californicus* s.l.
-(the most likely culprit), *B.
 obovatus*, and *B.
-confusus*.
-Each species has its own unique biology, and all have been implicated with a variety of different hosts.
-This suggests that the spread of OFV-Orc would be a function of various combinations of several potential factors, including host preferences, vectorial capacity, viral propagation/circulation in the vector, viral acquisition times, and feeding times required for transmission.
-Some of these factors have been tested: *Brevipalpus* vectors have demonstrated such virus-vector specificity with *Citrus leprosis virus N*--another dichorhavirus which causes citrus leprosis [@Roy2013a]--in studies done by @Ferreira2020 and @GarciaEscamilla2018.
-In these studies, *Brevipalpus* mites were not able to transmit more than one virus.
-This could mean that the *B.
+confusus* and *B.
+californicus* s.l., but only *B.
+californicus* has been described as a vector of OFV.
+Even so, the *B.
 californicus* which we find on liriopogons and *A.
-elatior* are not actually the same species as those found on citrus, or at least are not able to transmit OFV to citrus.
+elatior* may not be the same species as those found on citrus.
+Transmission of OFV from populations of *B.
+californicus* liriopogon/*A.
+elatior* to citrus may be limited by host preferences, vectorial capacity, viral propagation/circulation in the vector, viral acquisition times, or feeding times required for transmission to citrus.
+Even so, these types of questions require future study to determine the potential of nolinoidaea to citrus transmission.
 
@@
 reticulata* (mandarin) and *C.
-jambhiri* (rough lemon) associated with leprosis-like symptoms highlights the threat of different strains of OFV on citrus, which will be a definite concern to the US multi-billion-dollar citrus industry already impacted by the Huanglongbing disease.
+jambhiri* (rough lemon) associated with leprosis-like symptoms highlights the potential threat of different strains of OFV on citrus, which will be a definite concern to the US multi-billion-dollar citrus industry already impacted by the Huanglongbing disease.
 *B.
-californicus*, as well as *B.
-yothersi*, are both known vectors of dichorhaviruses (OFV) [@GarciaEscamilla2018; @Kondo2003; @Beltran-Beltran2020] and *B.
-obovatus* is a suspected vector as well [@Childers2003].
-All three mite species/complexes are present in Florida [@Childers2003; @Akyazi2017] (`r citef("fig_4")`), and are difficult to identify by non-experts, or without advanced methodologies.
-DNA barcoding [@Armstrong2005] or a similarly simple and accurate method for identification of these mite complexes is vital to determine which of these species are responsible for transmission of OFV-Orc, and therefore which mite populations need to be monitored or controlled.
+californicus*, *B.
+yothersi*, and *B.
+obovatus* are all present in Florida [@Childers2003; @Akyazi2017] (`r citef("fig_4")`), and are difficult to identify by non-experts, or without advanced methodologies.
+DNA barcoding [@Armstrong2005] or a similarly simple and accurate method for identification of these mite complexes is vital to identify mite populations which need to be monitored or controlled.
 By doing so, we can determine the risk OFV-Orc represents for the native plants, agriculture and the ornamental/landscaping industries of Florida and the surrounding regions.
@@
 
-### Table 1: List of Asparagaceae (Nolinoidaea) species with verified cases of *Orchid fleck dichorhavirus*, collected from the landscape of northern Florida
+### Table 1: List of Asparagaceae (Nolinoidaea) species with verified cases of orchid fleck virus, collected from the landscape of northern Florida
 
@@
 * * *O.
-intermedius* is sometimes misclassified as *Liriope muscari* ‘Variegated Evergreen Giant’ [@Fantz2008b, @Fantz2009] or ‘Grandiflora White’ [@Fantz2009].")`
+intermedius* is sometimes misclassified as *Liriope muscari* ‘Variegated Evergreen Giant’ [@Fantz2008b, @Fantz2009] or ‘Grandiflora White’ [@Fantz2009].
+Both OFV-Orc1 and OFV-Orc2 were detected in all host species.")`
 
@@
 `r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by *Liriope* spp.
-infected with *Orchid fleck dichorhavirus*: (a) ringspot symptoms on *Liriope muscari* cv.
+infected with orchid fleck virus: (a) ringspot symptoms on *Liriope muscari* cv.
 'Gigantea' (b-c) Details of ringspot symptoms on *L.
@@
 
-`r fig_nums(name = "fig_2", caption = "Symptoms expressed by *Aspidistra elatior* infected with *Orchid fleck dichorhavirus*: (a) Detail of leaf chlorosis (b) Chlorosis appears similar to sun damage (c-d) Chlorotic ringspot may indicate early symptoms of OFV")`
+`r fig_nums(name = "fig_2", caption = "Symptoms expressed by *Aspidistra elatior* infected with orchid fleck virus: (a) Detail of leaf chlorosis (b) Chlorosis appears similar to sun damage (c-d) Chlorotic ringspot may indicate early symptoms of OFV")`
 
@@
 
-`r fig_nums(name = "fig_4", caption = "Florida is home to other common pest species of *Brevipalpus*, which are potential vectors of *Orchid fleck dichorhavirus*: (a) *B.
+<!-- `r fig_nums(name = "fig_4", caption = "Florida is home to other common pest species of *Brevipalpus*, which could be confused with *B.
+californicus*: (a) *B.
 phoenicis*, dorsal (b) *B.
 yothersi*, lateral (c) *B.
-obovatus*, dorsal.")`
+obovatus*, dorsal.")` -->
 
@@
 
-```{r, fig_4, warning=FALSE}
-grid::grid.raster(tiff::readTIFF("figure/other_mites.tif"))
-```
+<!-- ```{r, fig_4, warning=FALSE} -->
+<!-- grid::grid.raster(tiff::readTIFF("figure/other_mites.tif")) -->
+<!-- ``` -->

### 2021-08-13 ofv_fife_2021.Rmd
Chaged title, added information about sequence identity

@@
 
-### **Request from Reviewer 4: Revise title to better reflect content of publiction** First report of the *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) orchid fleck virus infecting three ornamentals in Florida
+### Identification of three new ornamental hosts of *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) orchid fleck virus from Florida
 
@@
 Two orchid-infecting strains of OFV were detected via combinations of conventional RT-PCR, RT-qPCR, Sanger sequencing and High Throughput Sequencing.
-Amplicons shared 98% nucleotide identity with OFV-Orc1 and OFV-Orc2 available in NCBI GenBank.
+Amplicons shared 98% nucleotide identity with OFV-Orc1 and OFV-Orc2 RNA2 genome sequences available in NCBI GenBank.
 Coinfections were seen in each county, but single strains of OFV-Orc were seen in *L.
@@
 
-These samples from FDACS were subsequently retested by the USDA-ARS, in conjunction with tests of fresh samples from both Alachua and Leon counties.
+These samples from FDACS were subsequently retested by the USDA-APHIS-PPQ S&T Beltsville laboratory, in conjunction with tests of fresh samples from both Alachua and Leon counties.
 The USDA used RT-PCR, RT-qPCR, and High Throughput Sequencing (HTS) to reconfirm the presence of OFV.
@@
 elatior* from Leon County.
-**(insert statement of how much OFV-Orc1 and OFV-Orc2 differ at the nucleotide level)** ***Request from Reviewer 2: deposit and include GenBank accession numbers for the identified virus isolates in Florida?
-Re:New reports of viruses required that or two other alternative methods for viral detection** **Question from Reviewer 4: Does each isolate reflect a strain?**
+OFV-Orc1 and OFV-Orc2 strains share >90% nt sequence identity, and differ >25% in the L gene nucleotide sequence, indicating two separate species of *Dichoravirus* [@Dietzgen2014].
 
@@
 obovatus* Donnadieu and *B.
-confusus* Baker<!--  (`r citef("fig_4")`) -->.
+confusus* Baker.
 
-The first report of OFV in the US is thought to be @Ko1985, who describes nuclear inclusions caused by an undescribed bacilliform rhabdovirus in *Brassia* orchids.
+The recent report of OFV in the US is thought to be @Ko1985, who describes nuclear inclusions caused by an undescribed bacilliform rhabdovirus in *Brassia* orchids.
 The significance of this report is their description of the spoke-wheel configurations of the viral particles [@Ko1985], a sign typically associated with OFV infection [@Chang1976].
@@
 yothersi*, and *B.
-obovatus* are all present in Florida [@Childers2003; @Akyazi2017] (`r citef("fig_4")`), and are difficult to identify by non-experts, or without advanced methodologies.
+obovatus* are all present in Florida [@Childers2003; @Akyazi2017], and are difficult to identify by non-experts, or without advanced methodologies.
 DNA barcoding [@Armstrong2005] or a similarly simple and accurate method for identification of these mite complexes is vital to identify mite populations which need to be monitored or controlled.
@@
 ### Acknowledgements
-We would like to give special thanks to the Tallahassee Museum for their patience, cooperation, and support with collecting plant samples.
+We would like to give special thanks for the Tallahassee Museum and their patience, cooperation, and support with collecting plant samples.
+We are grateful for the USDA-APHIS PPQ Beltsville laboratory for their support in the identification and confirmation OFV strains, as well as *Brevipalpus* mite identification.
 We also want to thank Drs.
@@
 
-<!-- `r fig_nums(name = "fig_4", caption = "Florida is home to other common pest species of *Brevipalpus*, which could be confused with *B.
-californicus*: (a) *B.
-phoenicis*, dorsal (b) *B.
-yothersi*, lateral (c) *B.
-obovatus*, dorsal.")` -->
-
 ### Figures
@@
 ```
-
-<!-- ```{r, fig_4, warning=FALSE} -->
-<!-- grid::grid.raster(tiff::readTIFF("figure/other_mites.tif")) -->
-<!-- ``` -->

### 2021-08-13 ofv_fife_2021.Rmd
added placeholder for GenBank Accession numbers

@@
 elatior* from Leon County.
-OFV-Orc1 and OFV-Orc2 strains share >90% nt sequence identity, and differ >25% in the L gene nucleotide sequence, indicating two separate species of *Dichoravirus* [@Dietzgen2014].
+OFV-Orc1 and OFV-Orc2 strains share >90% nt sequence identity, and differ >25% in the L gene nucleotide sequence, indicating two separate species of *Dichoravirus* [@Dietzgen2014]<!-- GenBank Accession No# and No #, respectively-->.
 

### 2021-08-13 ofv_fife_2021.Rmd
Updated with DOIs

--- 2021-08-13 ofv_fife_2021.Rmd
@@
 
-### Identification of three new ornamental hosts of *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) orchid fleck virus from Florida
+### *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) orchid fleck virus infecting three new ornamental hosts in Florida
 
@@
 elatior* from Leon County.
-OFV-Orc1 and OFV-Orc2 strains share >90% nt sequence identity, and differ >25% in the L gene nucleotide sequence, indicating two separate species of *Dichoravirus* [@Dietzgen2014].
+OFV-Orc1 and OFV-Orc2 strains share >90% nt sequence identity and differ >25% in the L gene nucleotide sequence, indicating two separate species of *Dichoravirus* [@Dietzgen2014]<!-- GenBank Accession No# and No #, respectively-->.
 

### 2021-08-13 ofv_fife_2021.Rmd
Added my attempt at a Spanish abstract, greatly aided by Google translate: It has been a while since I have had to write in Spanish!

@@
 
-### *Brevipalpus*-transmitted (Trombidiformes: Tenuipalpidae) orchid fleck virus infecting three new ornamental hosts in Florida
+### *Brevipalpus*-transmitted orchid fleck virus infecting three new ornamental hosts in Florida
 
@@
 In conclusion, OFV is present in northern Florida, representing a risk for susceptible plants in the southeastern US.
+
+<!-- Spanish Abstract -->
+### Resumen
+
+Se describe la primera detección del virus de orchid fleck virus, lo cual pertenece al subgrupo que infecta a las orquídeas (OFV-Orc), infectando a tres huéspedes no reportados: *Liriope muscari*, cv.
+'Gigantea' (Decaisne) Bailey, *Ophiopogon intermedius* Don and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) por los condados de Leon y Alachua, FL.
+Las cepas del OFV-Orc se puedan infectar más que 50 especies de plantas pertenecientes a las familias Orchidaceae, Asparagaceae (Nolinoidaea), y infecta *Citrus* (Rutaceae) cómo la enfermedad leprosis de los cítricos.
+Los únicos vectores de OFV-Orc son los falsos ácaros tetraníquidos *Brevipalpus californicus* (Banks) *sensu lato* (Trombidiformes: Tenuipalpidae).
+La Florida tiene varias plantas en el paisaje, por lo cúales las especias de *Brevipalpus* se puedan alimentarse, y esas plantas son susceptibles a las infecciones de OFV-Orc.
+Se observaron manchas anulares cloróticas y salpicaduras por las hojas de las Serpentinas (*Liriope* y *Ophiopogon* spp.) y también se vieron hojas cloróticas del *A.
+elatior* adyacente, situado en el condando de Leon, FL.
+Los diagnósticos del laboratorio local fueron negativos para los patógenos comunes, por lo tanto, se enviaron nuevos ejemplares del tejido de las plantas al Florida Department of Agriculture and Consumer Services (FDACS) y al USDA-ARS para su identificación.
+
+Se detectaron dos cepas del OFV mediante la combinación de RT-PCR convencional, RT-qPCR, secuenciación de Sanger y secuenciación de alto rendimiento.
+Los amplicones compartían una identidad de nucleótidos del 98% con las secuencias del genoma de ARN2 de OFV-Orc1 y OFV-Orc2 disponibles en el NCBI GenBank.
+Se observaron coinfecciones del virus en cada condado, pero se observaron cepas únicas de OFV-Orc en *L.
+muscari* (Alachua , OFV-Orc2) y *A.
+elatior* (Leon , OFV-Orc1).
+
+Se identificaron tres ácaros mediante microscopía electrónica de barrido criogénico (Cryo-SEM) con potencial de ser vectores: *Brevipalpus californicus* (Banks) *sensu lato*, *B.
+obovatus* Donnadieu y *B.
+confusus* Baker.
+En conclusión, OFV está presente en el norte de Florida, lo que representa un riesgo para las plantas susceptibles en el sureste de Estados Unidos.
 

### 2021-08-17 ofv_fife_2021.Rmd
added Dr. Martini's minor edits and the Spanish abstract with Dr. Ochoa's minor edits included

--- 2021-08-13 ofv_fife_2021.Rmd
@@
 In conclusion, OFV is present in northern Florida, representing a risk for susceptible plants in the southeastern US.
+
+<!-- Spanish Abstract -->
+### Resumen
+
+Se describe la primera detección del virus de orchid fleck virus, lo cual pertenece al subgrupo que infecta a las orquídeas (OFV-Orc), infectando a tres huéspedes no reportados: *Liriope muscari*, cv.
+‘Gigantea’ (Decaisne) Bailey, *Ophiopogon intermedius* Don and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) para los condados de Leon y Alachua, FL.
+Las cepas del OFV-Orc puedan infectar más de 50 especies de plantas pertenecientes a las familias Orchidaceae, Asparagaceae (Nolinoidaea), e infecta *Citrus* (Rutaceae) cómo la enfermedad de la leprosis de los cítricos.
+Los únicos vectores de OFV-Orc son los ácaros planos *Brevipalpus californicus* (Banks) *sensu lato* (Trombidiformes: Tenuipalpidae).
+La Florida tiene varias plantas en el campo ornamental, por lo cúales las especias de *Brevipalpus* se puedan alimentarse, y esas plantas son susceptibles a las infecciones de OFV-Orc.
+Se observaron manchas anulares cloróticas y salpicaduras en las hojas de las Serpentinas (*Liriope* y *Ophiopogon* spp.) y también se vieron hojas cloróticas en el *A.
+elatior* adyacente, situado en el condando de Leon, FL.
+Los diagnósticos del laboratorio local fueron negativos para los patógenos comunes, por lo tanto, se enviaron nuevos ejemplares del tejido de las plantas al Florida Department of Agriculture and Consumer Services (FDACS) y el USDA-ARS para su identificación.
+Se detectaron dos cepas del OFV mediante la combinación de RT-PCR convencional, RT-qPCR, secuenciación de Sanger y secuenciación de alto rendimiento.
+Las ampliaciones compartían una identidad de nucleótidos del 98% con las secuencias del genoma de ARN2 de OFV-Orc1 y OFV-Orc2 disponibles en el NCBI GenBank.
+Se observaron coinfecciones del virus en cada condado, pero se observaron cepas únicas de OFV-Orc en *L.
+muscari* (Alachua , OFV-Orc2) y *A.
+elatior* (Leon , OFV-Orc1).
+Se identificaron tres ácaros mediante microscopía electrónica de barrido criogénico (Cryo-SEM) con potencial de ser vectores: *Brevipalpus californicus* (Banks) *sensu lato*, *B.
+obovatus* Donnadieu y *B.
+confusus* Baker.
+En conclusión, OFV está presente en el norte de Florida, lo que representa un riesgo para las plantas susceptibles en el sureste de Estados Unidos.
 
@@
 
-The recent report of OFV in the US is thought to be @Ko1985, who describes nuclear inclusions caused by an undescribed bacilliform rhabdovirus in *Brassia* orchids.
+The recent report of OFV in the US is thought to be @Ko1985 which describes nuclear inclusions caused by an undescribed bacilliform rhabdovirus in *Brassia* orchids.
 The significance of this report is their description of the spoke-wheel configurations of the viral particles [@Ko1985], a sign typically associated with OFV infection [@Chang1976].
@@
 californicus* which we find on liriopogons and *A.
-elatior* may not be the same species as those found on citrus.
+elatior* may not be the same cryptic species as those found on citrus.
 Transmission of OFV from populations of *B.
@@
 
-`r fig_nums(name = "fig_2", caption = "Symptoms expressed by *Aspidistra elatior* infected with orchid fleck virus: (a) Detail of leaf chlorosis (b) Chlorosis appears similar to sun damage (c-d) Chlorotic ringspot may indicate early symptoms of OFV")`
+`r fig_nums(name = "fig_2", caption = "Symptoms expressed by *Aspidistra elatior* infected with OFV: (a) Detail of leaf chlorosis (b) Chlorosis appears similar to sun damage (c-d) Chlorotic ringspot may indicate early symptoms of OFV")`
 

### 2021-08-23 ofv_fife_2021.Rmd
Added accession numbers, changed mentions of 'strain' to 'isolate' and added a link to the 'Virus Detection' section in the table, updated the table title and footnote

@@
 'Gigantea' (Decaisne) Bailey, *Ophiopogon intermedius* Don and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua Counties, FL.
-Strains of OFV-Orc infect over 50 plant species belonging to the plant families Orchidaceae, Asparagaceae (Nolinoidaea), and infects *Citrus* (Rutaceae) as citrus leprosis disease.
+OFV-Orc infects over 50 plant species belonging to the plant families Orchidaceae, Asparagaceae (Nolinoidaea), and infects *Citrus* (Rutaceae) as citrus leprosis disease.
 The only known vectors of OFV-Orc are the flat mites *Brevipalpus californicus* (Banks) *sensu lato* (Trombidiformes: Tenuipalpidae).
@@
 
-Two orchid-infecting strains of OFV were detected via combinations of conventional RT-PCR, RT-qPCR, Sanger sequencing and High Throughput Sequencing.
+Two orchid-infecting isolates of OFV were detected via combinations of conventional RT-PCR, RT-qPCR, Sanger sequencing and High Throughput Sequencing.
 Amplicons shared 98% nucleotide identity with OFV-Orc1 and OFV-Orc2 RNA2 genome sequences available in NCBI GenBank.
-Coinfections were seen in each county, but single strains of OFV-Orc were seen in *L.
+Coinfections were seen in each county, but single isolates of OFV-Orc were seen in *L.
 muscari* (Alachua, OFV-Orc2) and *A.
@@
 
-OFV-infected plants exhibit various symptoms depending on the infected plant species as well as the strain of the OFV associated with the infection [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into ringspot patterns.
+OFV-infected plants exhibit various symptoms depending on the infected plant species as well as the isolate of the OFV associated with the infection [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into ringspot patterns.
 
@@
 Orchid subgroup 1, OFV-Orc, was identified following the methods described in @Kondo2017.
-Sequencing demonstrated a shared 98\% nucleotide identity with the orchid strain subgroup, OFV-Orc (isolates So and Br with GenBank Accession numbers: AB244418 and MK522807, respectively) [@Kondo2006; @Kondo2017].
+Sequencing demonstrated a shared 98\% nucleotide identity with the orchid isolate subgroup, OFV-Orc (isolates So and Br with GenBank Accession numbers: AB244418 and MK522807, respectively) [@Kondo2006; @Kondo2017].
 
@@
 intermedius* and *A.
-elatior* from Leon County.
-OFV-Orc1 and OFV-Orc2 strains share >90% nt sequence identity and differ >25% in the L gene nucleotide sequence, indicating two separate species of *Dichoravirus* [@Dietzgen2014]<!-- GenBank Accession No# and No #, respectively-->.
+elatior* from Leon County (GenBank Accession Numbers: MZ852004, MZ852005 MZ852006, and MZ852007).
+OFV-Orc1 and OFV-Orc2 share >90% nt sequence identity and differ >25% in the L gene nucleotide sequence, indicating two separate species of *Dichoravirus* [@Dietzgen2014].
 
-HTS reaffirmed the presence of OFV-Orc1 and OFV-Orc2 strains in Leon and Alachua counties (`r citet("tab_1")`).
+HTS reaffirmed the presence of OFV-Orc1 and OFV-Orc2 in Leon and Alachua counties (`r citet("tab_1")`).
 HTS results from Leon County revealed that *L.
-muscari* were coinfected with both strains (OFV-Orc1 and OFV-Orc2), while *A.
+muscari* were coinfected with both OFV-Orc1 and OFV-Orc2, while *A.
 elatior* were solely infected with OFV-Orc1.
 HTS of *L.
-muscari* from Alachua County revealed infections with the OFV-Orc2 strain.
+muscari* from Alachua County revealed infections with OFV-Orc2 (GenBank Accession MZ852006).
 
-After the initial identification by FDACS of OFV-Orc strains, mite samples were collected from symptomatic Asparagaceae in Leon County.
+After the initial identification by FDACS of OFV-Orc, mite samples were collected from symptomatic Asparagaceae in Leon County.
 Most mites collected were Tenuipalpid mites (flat mites or false spider mites), a pest of ornamental plants, some of which are known to act as vectors for plant viruses [@Childers2003; @Childers2011].
@@
 
-OFV consists of two orchid strains (OFV-Orc1 and OFV-Orc2) and two citrus strains (OFV-Cit1 and OFV-Cit2) [@Roy2020; @Beltran-Beltran2020].
-The OFV strains detected in Florida are identical in gene order, content, and genome sequence to the orchid strains of OFV infecting citrus in Hawaii, Mexico, Colombia, and South Africa [@Roy2020; @Beltran-Beltran2020].
-Both OFV-Orc1 and OFV-Orc2 infect citrus [@Roy2020], but none of the citrus strains have been reported from any orchid species.
+OFV consists of two orchid isolates (OFV-Orc1 and OFV-Orc2) and two citrus isolates (OFV-Cit1 and OFV-Cit2) [@Roy2020; @Beltran-Beltran2020].
+The OFV isolates detected in Florida are identical in gene order, content, and genome sequence to the orchid isolates of OFV infecting citrus in Hawaii, Mexico, Colombia, and South Africa [@Roy2020; @Beltran-Beltran2020].
+Both OFV-Orc1 and OFV-Orc2 infect citrus [@Roy2020], but none of the citrus  isolates have been reported from any orchid species.
 The *Brevipalpus* mites collected from liriopogons and *A.
@@
 Citrus leprosis was present in Florida during the 1860’s and almost eradicated by the mid-1960s [@Childers2003; @Knorr1968a; @Knorr1968b].
-An examination of herbarium specimens of Florida citrus found that this historical virus, Citrus leprosis dichorhavirus-N0, is distantly related to the modern strains of OFV [@Hartung2015; @Kitajima2011a; @Roy2020].
+An examination of herbarium specimens of Florida citrus found that this historical virus, Citrus leprosis dichorhavirus-N0, is distantly related to the modern isolates of OFV [@Hartung2015; @Kitajima2011a; @Roy2020].
 The recent detection of OFV-Orc1 in South Africa [@Cook2019] in *C.
@@
 reticulata* (mandarin) and *C.
-jambhiri* (rough lemon) associated with leprosis-like symptoms highlights the potential threat of different strains of OFV on citrus, which will be a definite concern to the US multi-billion-dollar citrus industry already impacted by the Huanglongbing disease.
+jambhiri* (rough lemon) associated with leprosis-like symptoms highlights the potential threat of different isolates of OFV on citrus, which will be a definite concern to the US multi-billion-dollar citrus industry already impacted by the Huanglongbing disease.
 *B.
@@
 We would like to give special thanks for the Tallahassee Museum and their patience, cooperation, and support with collecting plant samples.
-We are grateful for the USDA-APHIS PPQ Beltsville laboratory for their support in the identification and confirmation OFV strains, as well as *Brevipalpus* mite identification.
+We are grateful for the USDA-APHIS PPQ Beltsville laboratory for their support in the identification and confirmation OFV isolates, as well as *Brevipalpus* mite identification.
 We also want to thank Drs.
@@
 
-### Table 1: List of Asparagaceae (Nolinoidaea) species with verified cases of orchid fleck virus, collected from the landscape of northern Florida
+### Table 1: List of Asparagaceae (Nolinoidaea) species infected with orchid fleck virus, collected from the landscape of northern Florida
 
-|Scientific Name|Common Names|County|Strains|
+|Scientific Name|Common Names|County|Isolates Detected|
 |:-----------|:--------------|:-----|:------|
@@
 intermedius* is sometimes misclassified as *Liriope muscari* ‘Variegated Evergreen Giant’ [@Fantz2008b, @Fantz2009] or ‘Grandiflora White’ [@Fantz2009].
-Both OFV-Orc1 and OFV-Orc2 were detected in all host species.")`
+Both OFV-Orc1 and OFV-Orc2 were detected in each species tested, many plants were coinfected with both isolates, see '[Virus Detection]'.")`
 

### 2021-08-25 ofv_fife_2021.Rmd
integrated Dr. Roy's edits

@@
 
-We describe the first detection of orchid fleck virus (OFV), belonging to the orchid-infecting subgroup (OFV-Orc), infecting three unreported hosts: *Liriope muscari*, cv.
+We describe the first detection of orchid fleck virus (OFV) infecting three unreported hosts: *Liriope muscari*, cv.
 'Gigantea' (Decaisne) Bailey, *Ophiopogon intermedius* Don and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua Counties, FL.
-OFV-Orc infects over 50 plant species belonging to the plant families Orchidaceae, Asparagaceae (Nolinoidaea), and infects *Citrus* (Rutaceae) as citrus leprosis disease.
-The only known vectors of OFV-Orc are the flat mites *Brevipalpus californicus* (Banks) *sensu lato* (Trombidiformes: Tenuipalpidae).
+Orchid-infecting subgroup (Orc) of OFV infects over 50 plant species belonging to the plant families Orchidaceae, Asparagaceae (Nolinoidaea), and causes citrus leprosis disease in *Citrus* (Rutaceae).
+The only known vectors of OFV-Orc are the flat mites, *Brevipalpus californicus* (Banks) *sensu lato* (Trombidiformes: Tenuipalpidae).
 Florida has various plants in the landscape which *Brevipalpus* spp.
@@
 
-Two orchid-infecting isolates of OFV were detected via combinations of conventional RT-PCR, RT-qPCR, Sanger sequencing and High Throughput Sequencing.
+Two orchid-infecting strains of OFV were detected via combinations of conventional RT-PCR, RT-qPCR, Sanger sequencing and High Throughput Sequencing (HTS).
 Amplicons shared 98% nucleotide identity with OFV-Orc1 and OFV-Orc2 RNA2 genome sequences available in NCBI GenBank.
-Coinfections were seen in each county, but single isolates of OFV-Orc were seen in *L.
+Coinfections were seen in each county, but single strains of OFV-Orc were seen in *L.
 muscari* (Alachua, OFV-Orc2) and *A.
@@
 
-In conclusion, OFV is present in northern Florida, representing a risk for susceptible plants in the southeastern US.
+In conclusion, OFV orchid strains are present in northern Florida, representing a risk for susceptible plants in the southeastern US.
 
@@
 
-OFV-infected plants exhibit various symptoms depending on the infected plant species as well as the isolate of the OFV associated with the infection [@Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into ringspot patterns.
+OFV-infected plants exhibit various symptoms depending on the infected plant species as well as the strain of the OFV associated with the infection [@Kubo2009a; @Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into ringspot patterns.
 
@@
 Leaves were taken from *Liriope* spp.
-and *Ophiopogon* spp., as well as *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea), which were suspected to be infected, due to both its proximity to infected *Liriope* and the presence of unusually chlorotic leaves (`r citef("fig_2")`).
+and *Ophiopogon* spp., as well as the *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea), nearby, which appeared sickly and chlorotic (`r citef("fig_2")`).
 Plant materials were sent to the Florida Department of Agriculture and Consumer Services (FDACS) for identification.
@@
 The FDACS determined that the pathogen was OFV using previously published primers and methods to conduct RT-PCR and Sanger sequencing [@Kubo2009a; @Kubo2009b; @RamosGonzalez2015].
-Orchid subgroup 1, OFV-Orc, was identified following the methods described in @Kondo2017.
-Sequencing demonstrated a shared 98\% nucleotide identity with the orchid isolate subgroup, OFV-Orc (isolates So and Br with GenBank Accession numbers: AB244418 and MK522807, respectively) [@Kondo2006; @Kondo2017].
+OFV Orchid strain 1, (OFV-Orc1), was identified following the methods described in @Kondo2017.
+Nucleotide sequencing shared 98\% nucleotide identity with the OFV-isolates So (Accession No.
+AB244418) and Br (Accession No.
+MK522807), which belong to orchid subgroup I [@Kondo2006; @Kondo2017].
 
 These samples from FDACS were subsequently retested by the USDA-APHIS-PPQ S&T Beltsville laboratory, in conjunction with tests of fresh samples from both Alachua and Leon counties.
-The USDA used RT-PCR, RT-qPCR, and High Throughput Sequencing (HTS) to reconfirm the presence of OFV.
-RT-PCR and qPCR with Generic R2-Dicho-GF and R2-Dicho-GR primers amplifed ~800 nt of L-gene (RNA2) amplicon [@Roy2020], and OFV-Orc1 and OFV-Orc2 were detected in both *O.
+The USDA used RT-PCR, RT-qPCR, and HTS to reconfirm the presence of OFV.
+Conventional RT-PCR with Generic R2-Dicho-GF and R2-Dicho-GR primers amplifed ~800 nt of L-gene (RNA2) amplicon [@Roy2020], and OFV-Orc1 and OFV-Orc2 were detected in both *O.
 intermedius* and *A.
-elatior* from Leon County (GenBank Accession Numbers: MZ852004, MZ852005 MZ852006, and MZ852007).
-OFV-Orc1 and OFV-Orc2 share >90% nt sequence identity and differ >25% in the L gene nucleotide sequence, indicating two separate species of *Dichoravirus* [@Dietzgen2014].
+elatior* from Leon County [@Kondo2017] (GenBank Accession Numbers: MZ852004, MZ852005 MZ852006, and MZ852007).
+OFV-Orc1 and OFV-Orc2 share 99% nucleotide sequence identity with their RNA2 genome wheras 90\% nt sequence identity was found between these two reassortment strains.
 
@@
 
-OFV consists of two orchid isolates (OFV-Orc1 and OFV-Orc2) and two citrus isolates (OFV-Cit1 and OFV-Cit2) [@Roy2020; @Beltran-Beltran2020].
-The OFV isolates detected in Florida are identical in gene order, content, and genome sequence to the orchid isolates of OFV infecting citrus in Hawaii, Mexico, Colombia, and South Africa [@Roy2020; @Beltran-Beltran2020].
-Both OFV-Orc1 and OFV-Orc2 infect citrus [@Roy2020], but none of the citrus  isolates have been reported from any orchid species.
+OFV consists of two orchid strains (OFV-Orc1 and OFV-Orc2) and two citrus strains (OFV-Cit1 and OFV-Cit2) [@Roy2020; @Beltran-Beltran2020].
+The OFV strains detected in Florida are identical in gene order, content, and genome sequence to the orchid strains of OFV infecting citrus in Hawaii, Mexico, Colombia, and South Africa [@Roy2020; @Beltran-Beltran2020].
+Both OFV-Orc1 and OFV-Orc2 infect citrus [@Roy2020], but none of the citrus  strains have been reported from any orchid species.
 The *Brevipalpus* mites collected from liriopogons and *A.
@@
 We would like to give special thanks for the Tallahassee Museum and their patience, cooperation, and support with collecting plant samples.
-We are grateful for the USDA-APHIS PPQ Beltsville laboratory for their support in the identification and confirmation OFV isolates, as well as *Brevipalpus* mite identification.
+We are grateful for the USDA-APHIS PPQ Beltsville laboratory for their support in the identification and confirmation OFV isolates, as well as *Brevipalpus* mite identification at the USDA-ARS.
 We also want to thank Drs.
@@
 
-|Scientific Name|Common Names|County|Isolates Detected|
+|Scientific Name|Common Names|County|Strains Detected|
 |:-----------|:--------------|:-----|:------|
@@
 intermedius* is sometimes misclassified as *Liriope muscari* ‘Variegated Evergreen Giant’ [@Fantz2008b, @Fantz2009] or ‘Grandiflora White’ [@Fantz2009].
-Both OFV-Orc1 and OFV-Orc2 were detected in each species tested, many plants were coinfected with both isolates, see '[Virus Detection]'.")`
+Both OFV-Orc1 and OFV-Orc2 were detected in each species tested, many plants were coinfected with both strains, see '[Virus Detection]'.")`
 

### 2021-08-25 editorial_reviews/response_editors_ofv_fife_2021_R1.Rmd
added files

--- 2021-06-07 editorial_reviews/response_editors_ofv_fife_2021.Rmd
@@
 Both samples from Leon County and Alachua were found to be positive for OFV; only samples from Leon were examined for mites.
-We have removed the claim that the virus is widespread.**
+We have removed the claim that the virus is widespread, and added a section on control as requested.**
 
@@
 - We have corrected inconsistencies with taxonomic authorities
-- We have not added a discussion of potential control measures due to word limits, and lack of specific documentation regarding control methods/chemical applications for these specific ornamental plants.
+- We have added a discussion of potential control measures for these mites
 

### 2021-08-25 editorial_reviews/response_editors_ofv_fife_2021_R2.Rmd
added files

---
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

28-Jul-2021

Dear Mr. Fife,

Manuscript ID JIPM-2021-0034.R1 entitled "First report of the <i>Brevipalpus</i>-transmitted (Trombidiformes: Tenuipalpidae) <i>Orchid fleck dichorhavirus</i> infecting three ornamentals in Florida" which you submitted to the Journal of Integrated Pest Management, has been reviewed.  The comments of the reviewer(s) are included at the bottom of this letter.

The reviewer(s) have recommended publication, but also suggest some minor revisions to your manuscript.  Therefore, I invite you to respond to the reviewer(s)' comments and submit a revised version of your manuscript.

Your revised manuscript should be uploaded within 30 days. Please let us know if you will require an extension. The due date is 27-Aug-2021.

To revise your manuscript, log into [hyperlink removed] and enter your Author Centre, where you will find your manuscript title listed under "Manuscripts with Decisions."  Under "Actions," click on "Create a Revision."  Your manuscript number has been appended to denote a revision.

You may also click the below link to start the revision process.

*** PLEASE NOTE: This is a two-step process. After clicking on the link, you will be directed to a webpage to confirm. ***

[hyperlink removed]

Manuscript revision instructions
- Please ensure your paper follows journal style and requirements as listed in the instructions to authors: [hyperlink removed]

- Please highlight the changes to your manuscript within the document by using the track changes mode in MS Word or by using bold or colored text. Please also include a point-by-point response to reviews as well as a clean version (non-track changes version) of the paper.
- If your paper was created in LaTeX, please upload the PDF along with the tex files.
- Please delete any outdated files (e.g., the original manuscript, any outdated figures, etc.) before uploading the revised files.
- Figures should be submitted as separate files and not inserted into the main document. Figures should be submitted as at least 300 dpi (600 dpi for line graphs) and in one of the following file types: tif, eps, rtf, ppt/pptx, xls/xlsx, editable PDF, ps, psd, ai, gif, or png.

Once again, thank you for submitting your manuscript to the Journal of Integrated Pest Management and I look forward to receiving your revision.

Sincerely,
Dr. Nathan Walker
Subject Editor, Journal of Integrated Pest Management
nathan.walker\@okstate.edu
ESA Editorial Office: 3 Park Place, Suite 307, Annapolis, MD 21401-3722, USA. Editorial Office Phone: 1-301-731-4535.

\newpage

**Response to Decision Letter from the authors:**

**We are grateful for your willingness to review the manuscript a second time.**

**This second revision attempts to add missing technical information regarding virus isolates and accession numbers.**

**Thank you for your assistance,**

**-- The Authors**

\newpage

Reviewer(s)' Comments to Author:

**Reviewer: 3**

Comments to the Author
TThe manuscript reports new hosts for a known virus in a limited geographic region – northern Florida. In my opinion, it should be published as a disease note instead of a short communication in an IPM-related journal. The discussion on management is not in depth and, in fact, is often speculative.
Several methods are used to identify the OFV strains, but there is no discussion on them at all. The discussion on the mite vector is highly inaccurate and misleading. There is no transmission tests, and the authors state in lines 226-228 that *B. californicus* and *B. yothersi* are known vectors of OFV, while only the first one transmits the virus. The two references cited in the text to support the authors´ statement (García-Escamilla et al., 2018 and Beltran-Beltran et al. 2020) clearly show that both mite species acquire OFV, but no transmission was obtained.

Other minor edits or comments are:

- Title, lines 33, 106, 116 etc. – The common name of the virus (as pathogen) should not be written in italics. It should be used orchid fleck virus. For more detailed information, access the ICTV homepage on “how to write a virus name”

- Line 39 – Brevipalpus californicus

- 47 – orchid (lowercase)

- Lines – 53 and 54 – other species are not reported as vectors of OFV

- Line 62 – Orchid fleck dichorhavirus (in italics) is the scientific name of the virus, whereas orchid fleck virus (with lowercase) is the common name of the virus. This confusion has been made in several places of the manuscript. They are not the same thing.

- Lines 67 -69 – This sentence is not accurate. There are reports of Dr. Kitajima´s group and Dr. Freitas-Astúa´s group suggesting replication of other dichorhaviruses in their *B. yothersi* and *B. phoenicis* vectors due to the identification of viroplasmas in mite cells.

- Lines 97-98 – cucumber mosaic virus and tobacco mosaic virus (lowercase and not italics)
The paragraph that starts in line 99 has 4 times the words collect, collected, or collection. Please rephrase it.

- Line 108 – The citation of references Kubo et al. 2006a and 2006b (mistakenly mentioned as Kubo 2006a and 2006b) are not necessary, as they refer to abstracts published in scientific meetings. The complete article bringing the information presented in the abstracts were published, and correctly cited in the manuscript, in 2009a and 2009b.

- Line 109 – Add comma to “subgroup 1, OFV-Orc, was… “

- Line 115 – eliminate “in sequence”

- Lines 178-179: the authors mention that “*B. californicus* are often collected from citrus rinds” and cite two supporting references from 1949 and from 1987. Are there newer references to support this statement?

- Line 189 – substitute citrus leprosis virus N by OFV, unless the authors mean the CiLV-N reported in Brazil by Ramos-González et al. (2017). This sentence is confusing and needs to be re-written. There seems to have, indeed, virus-vector specificity among BTV, but there are reports of one vector species transmitting more than one virus (examples are B. yothersi transmitting the dichorhaviruses clerodendrum chlorotic spot virus and coffee ringspot virus, and the cileviruses citrus leprosis virus C, CiLV-C2 and passion fruit green spot virus). On the other hand, so far OFV has been reported exclusively with *B. californicus* – and that should be very clear in the manuscript, which suggests that *B. obovatus* and *B. confusus* could transmit OFV.

- Line 227 – *B. yothersi* is a vector of other dichorhaviruses, but not of OFV.
- Fig. 4: Why do the authors suggest that *B. phoenicis*, *B. yothersi* and *B. obovatus* are potencial vectors of OFV? They can transmit other dichorhaviruses (not cited in the manuscript), but neither the authors have addressed that in this manuscript, nor it is suggested elsewhere.

**Response to Reviewer 3:**
**Thank you for reviewing our article. We have made the following changes based on your remarks:**

**The authors respectfully disagree with publishing the current MS as a 'Disease Note': Disease Notes do not have provisions for identification of arthropods, nor does it allow inclusion of figures, or acknowledgments. The work presented is multidisciplinary and collaborative in nature, which requires acknowledgment of assistance given by state and governmental agencies. Furthermore, the authors consider the figures to be a vital part of this MS, due to their unique characteristics which differ from OFV symptoms in other plants. Instead, we believe that our MS would be of benefit to JIPM's audience by raising awareness and highlighting the 'known unknowns' surrounding this understudied mite-plant-pathosystem.**

**Our cursory treatment of methodology is primarily due to their more complete treatment in the cited references. We revised portions of the MS which implied that *B. phoenicis*, *B. yothersi* and *B. obovatus* may be vectors of OFV.**

Specific Edits:

 - Corrected improper usage of the common name of viruses $\rightarrow$ **fixed italics**

 - Line 39 – *Brevipalpus californicus* $\rightarrow$ **fixed**

 - 47 – orchid (lowercase) $\rightarrow$ **fixed case**

 - Lines – 53 and 54 – other species are not reported as vectors of OFV $\rightarrow$ **corrected**

 - Lines 67 -69 – This sentence is not accurate. There are reports of Dr. Kitajima´s group and Dr. Freitas-Astúa´s group suggesting replication of other dichorhaviruses in their *B. yothersi* and *B. phoenicis* vectors due to the identification of viroplasmas in mite cells. $\rightarrow$ **fixed**

 - Lines 97-98 – cucumber mosaic virus and tobacco mosaic virus (lowercase and not italics) $\rightarrow$ **fixed**

 - The paragraph that starts in line 99 has 4 times the words collect, collected, or collection. Please rephrase it. $\rightarrow$ **rewrote**

 - Line 108 – The citation of references Kubo et al. 2006a and 2006b (mistakenly mentioned as Kubo 2006a and 2006b) are not necessary, as they refer to abstracts published in scientific meetings. The complete article bringing the information presented in the abstracts were published, and correctly cited in the manuscript, in 2009a and 2009b. $\rightarrow$ **removed unnecessary citations**

 - Line 109 – Add comma to “subgroup 1, OFV-Orc, was… “ $\rightarrow$ **fixed**

 - Line 115 – eliminate “in sequence” $\rightarrow$ **fixed**

 - Lines 178-179: the authors mention that “*B. californicus* are often collected from citrus rinds” and cite two supporting references from 1949 and from 1987. Are there newer references to support this statement? $\rightarrow$ **added modern references**

 -  Line 189 – substitute citrus leprosis virus N by OFV, unless the authors mean the CiLV-N reported in Brazil by Ramos-González et al. (2017). This sentence is confusing and needs to be re-written. There seems to have, indeed, virus-vector specificity among BTV, but there are reports of one vector species transmitting more than one virus (examples are B. yothersi transmitting the dichorhaviruses clerodendrum chlorotic spot virus and coffee ringspot virus, and the cileviruses citrus leprosis virus C, CiLV-C2 and passion fruit green spot virus). On the other hand, so far OFV has been reported exclusively with *B. californicus* – and that should be very clear in the manuscript, which suggests that *B. obovatus* and *B. confusus* could transmit OFV. $\rightarrow$ **removed sentences implying other mite spp. could transmit OFV**

 - Line 227 – *B. yothersi* is a vector of other dichorhaviruses, but not of OFV. $\rightarrow$ **fixed**

 - Fig. 4: Why do the authors suggest that *B. phoenicis*, *B. yothersi* and *B. obovatus* are potencial vectors of OFV? They can transmit other dichorhaviruses (not cited in the manuscript), but neither the authors have addressed that in this manuscript, nor it is suggested elsewhere. $\rightarrow$ **fixed in text, removed figure**

**Reviewer: 2**

Comments to the Author
The authors improved the manuscript, and it is providing important original information.
My only suggestion at this point would be that the authors deposit and include GenBank accession number(s) for the identified virus isolates in Florida. New reports of viruses required that or two other alternative methods for viral detection.

**Response to Reviewer 2:**
**Thank you for reviewing our article. We have made the following changes based on your remarks:**

**Thank you for your time, we added GenBank accession numbers for the virus isolates**

**Reviewer: 4**

Comments to the Author
This article represents a somewhat odd mix of limited original data (symptom and mite observations on ornamental hosts, and some diagnostic assays) and perspectives & review on orchid fleck virus and its potential threats to ornamental and citrus industries. The responses to reviewers 1 and 2 have significantly improved the manuscript, but some important issues remain to be addressed by the authors.

1. Considering the above, the title of the article does not reflect its contents and should be revised, ie. it goes beyond the first report of OFV in previously unknown hosts in Florida.
2. The authors should refer to “orchid fleck virus” or OFV throughout the manuscript. Orchid fleck dichorhavirus is a taxonomic entity that does not exist in nature. Unlike the virus OFV, it does not have strains, does not cause symptoms, does not have a genome and cannot be transmitted. L62 sentence should be revised since the taxonomic classification and the virus are not the same thing.
3. Finding OFV in some symptomatic plant samples does not constitute an “outbreak” (L33) and overstates the data.
4. The authors should more clearly differentiate between strains and isolates; the way the article is written, it appears that each of their isolates is/represents a strain which is likely incorrect.
5. L68: …only mites which have been experimentally shown to do so …
6. L97-98: by convention, virus names must be written in lower case and without italics
7. L118: mention how much OPFV-Orc1 and -Orc2 differ at the nucleotide level
8. L224: highlights the potential threat …
9. L473: add the Doi number for this publication
10. Table 1: title: “verified cases of orchid fleck virus collected …”. Were isolates of both strains identified in all hosts? Please clarify in the last column.
11. Fig. 4: this reads like the heading for a review figure. How is this data related to the research reported here? What are the sources of the micrographs? Mention this in the legend.

**Response to Reviewer 4:**
**Thank you for reviewing our article. We have made the following changes based on your remarks:**

**We have revised the title as advised to the following: '*Brevipalpus*-transmitted orchid fleck virus infecting three new ornamental hosts in Florida.'**

1. Considering the above, the title of the article does not reflect its contents and should be revised, ie. it goes beyond the first report of OFV in previously unknown hosts in Florida. $\rightarrow$ **renamed**
2. The authors should refer to “orchid fleck virus” or OFV throughout the manuscript. Orchid fleck dichorhavirus is a taxonomic entity that does not exist in nature. Unlike the virus OFV, it does not have strains, does not cause symptoms, does not have a genome and cannot be transmitted. L62 sentence should be revised since the taxonomic classification and the virus are not the same thing. $\rightarrow$ **corrected improper italicization of virus names**
3. Finding OFV in some symptomatic plant samples does not constitute an “outbreak” (L33) and overstates the data. $\rightarrow$ **removed statement**
4. The authors should more clearly differentiate between strains and isolates; the way the article is written, it appears that each of their isolates is/represents a strain which is likely incorrect. $\rightarrow$ **corrected to 'isolates'**
5. L68: …only mites which have been experimentally shown to do so … $\rightarrow$ **fixed**
6. L97-98: by convention, virus names must be written in lower case and without italics $\rightarrow$ **fixed**
7. L118: mention how much OPFV-Orc1 and -Orc2 differ at the nucleotide level $\rightarrow$ **added description of differences**
8. L224: highlights the potential threat … $\rightarrow$ **fixed**
9. L473: add the Doi number for this publication $\rightarrow$ **added DOIs**
10. Table 1: title: “verified cases of orchid fleck virus collected …”. Were isolates of both strains identified in all hosts? Please clarify in the last column. $\rightarrow$ **Isolates of both strains were found in the majority of plants sampled, but there were a few plants without coinfection. Reworded**
11. Fig. 4: this reads like the heading for a review figure. How is this data related to the research reported here? What are the sources of the micrographs? Mention this in the legend. $\rightarrow$ **removed**

### 2021-08-27 ofv_fife_2021.Rmd
updated

--- 2021-08-23 ofv_fife_2021.Rmd
@@
 
-Se describe la primera detección del virus de orchid fleck virus, lo cual pertenece al subgrupo que infecta a las orquídeas (OFV-Orc), infectando a tres huéspedes no reportados: *Liriope muscari*, cv.
+Se describe la primera detección del virus de orchid fleck virus (OFV), infectando a tres huéspedes no reportados: *Liriope muscari*, cv.
 ‘Gigantea’ (Decaisne) Bailey, *Ophiopogon intermedius* Don and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) para los condados de Leon y Alachua, FL.
-Las cepas del OFV-Orc puedan infectar más de 50 especies de plantas pertenecientes a las familias Orchidaceae, Asparagaceae (Nolinoidaea), e infecta *Citrus* (Rutaceae) cómo la enfermedad de la leprosis de los cítricos.
+Los subgrupos de OFV que infectan a las orquídeas (Orc) puedan infectar más de 50 especies de plantas pertenecientes a las familias Orchidaceae, Asparagaceae (Nolinoidaea), e infecta *Citrus* (Rutaceae) cómo la enfermedad de la leprosis de los cítricos.
 Los únicos vectores de OFV-Orc son los ácaros planos *Brevipalpus californicus* (Banks) *sensu lato* (Trombidiformes: Tenuipalpidae).
@@
 elatior* adyacente, situado en el condando de Leon, FL.
-Los diagnósticos del laboratorio local fueron negativos para los patógenos comunes, por lo tanto, se enviaron nuevos ejemplares del tejido de las plantas al Florida Department of Agriculture and Consumer Services (FDACS) y el USDA-ARS para su identificación.
+Los diagnósticos del laboratorio local fueron negativos para los patógenos comunes, por lo tanto, se enviaron nuevos ejemplares al Florida Department of Agriculture and Consumer Services (FDACS) y el USDA-ARS para su identificación.
 Se detectaron dos cepas del OFV mediante la combinación de RT-PCR convencional, RT-qPCR, secuenciación de Sanger y secuenciación de alto rendimiento.

### 2021-08-27 ofv_fife_2021.Rmd
added track revisions version
added abbreviation OFV to caption in Fig 1

@@
 Two orchid-infecting strains of OFV were detected via combinations of conventional RT-PCR, RT-qPCR, Sanger sequencing and High Throughput Sequencing (HTS).
-Amplicons shared 98% nucleotide identity with OFV-Orc1 and OFV-Orc2 RNA2 genome sequences available in NCBI GenBank.
+Amplicons shared 98\% nucleotide identity with OFV-Orc1 and OFV-Orc2 RNA2 genome sequences available in NCBI GenBank.
 Coinfections were seen in each county, but single strains of OFV-Orc were seen in *L.
@@
 `r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by *Liriope* spp.
-infected with orchid fleck virus: (a) ringspot symptoms on *Liriope muscari* cv.
+infected with orchid fleck virus (OFV): (a) ringspot symptoms on *Liriope muscari* cv.
 'Gigantea' (b-c) Details of ringspot symptoms on *L.

### 2021-09-07 ofv_fife_2021.Rmd
Addressing comments to authors: Dr. Nathan Walker: My Comments to Authors: Line 40 and throughout the manuscript, not needed hard returns are present and need to be removed. Lines 49-50 Coinfections were seen in each county, but single strains of OFV-Orc were seen in L. muscari – Can coinfections be seen? Can single strains be seen?  No, symptoms can be and coinfections are determined by analysis. The Spanish abstract addition is not warranted and I am confused why you added this at this late stage? The staff editors have suggested “So, my suggestion would be just to assume the other [English]

@@
 feed on, which are susceptible to infection by OFV-Orc.
-
 Chlorotic ringspots and flecking were seen affecting Liriopogons (*Liriope* and *Ophiopogon* spp.) in Leon County, FL.
@@
 Local diagnostics returned negative for common plant pathogens, therefore new samples were sent to the Florida Department of Agriculture and Consumer Services (FDACS) and USDA-ARS for identification.
-
 Two orchid-infecting strains of OFV were detected via combinations of conventional RT-PCR, RT-qPCR, Sanger sequencing and High Throughput Sequencing (HTS).
 Amplicons shared 98\% nucleotide identity with OFV-Orc1 and OFV-Orc2 RNA2 genome sequences available in NCBI GenBank.
-Coinfections were seen in each county, but single strains of OFV-Orc were seen in *L.
+Coinfections were detected in each county, but single strains of OFV-Orc were detected in *L.
 muscari* (Alachua, OFV-Orc2) and *A.
 elatior* (Leon, OFV-Orc1).
-
-Three potential mite vectors were identified via cryo-scanning electron microscopy (Cryo-SEM): *Brevipalpus californicus* (Banks) sensu lato, *B. obovatus* Donnadieu, and *B. confusus* Baker.
-
+Three potential mite vectors were identified via cryo-scanning electron microscopy (Cryo-SEM): *Brevipalpus californicus* (Banks) sensu lato, *B.
+obovatus* Donnadieu, and *B.
+confusus* Baker.
 In conclusion, OFV orchid strains are present in northern Florida, representing a risk for susceptible plants in the southeastern US.
@@
 Las ampliaciones compartían una identidad de nucleótidos del 98% con las secuencias del genoma de ARN2 de OFV-Orc1 y OFV-Orc2 disponibles en el NCBI GenBank.
-Se observaron coinfecciones del virus en cada condado, pero se observaron cepas únicas de OFV-Orc en *L.
+Se detectaron coinfecciones del virus en cada condado, pero se detectaron cepas únicas de OFV-Orc en *L.
 muscari* (Alachua , OFV-Orc2) y *A.
@@
 Orchid fleck virus (OFV), is the type member for the genus *Dichorhavirus*, family *Rhabdoviridae*.
-OFV is a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
+The virus is a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
 Flat mites from the genus *Brevipalpus* (Trombidiformes: Tenuipalpidae) are the only which have been experimentally shown to transmit dichorhaviruses [@Maeda1998].
-
-OFV-infected plants exhibit various symptoms depending on the infected plant species as well as the strain of the OFV associated with the infection [@Kubo2009a; @Kubo2009b], but symptoms typically appear as chlorotic flecks, which ultimately coalesce into ringspot patterns.
-
-OFV was first described as infecting *Cymbidium* orchids in Japan [@Doi1977].
-OFV and OFV-like rhabdoviruses have been reported infecting orchids in Asia, Africa, North America, South America, Europe, and Oceania.
+Plants infected with OFV exhibit chlorotic and necrotic flecks on their leaves[@Kubo2009a; @Kubo2009b; @Dietzgen2018b].
+The virus was first described as infecting *Cymbidium* orchids in Japan [@Doi1977].
+There have been reports of OFV and OFV-like rhabdoviruses infecting orchids in Asia, Africa, North America, South America, Europe, and Oceania.
 The prevalence of OFV and its mite vector is thought to be associated with the movement of infected orchids [@Dietzgen2018a].
-
-OFV naturally infects more than fifty species of Orchidaceae [@Kitajima2010; @Peng2013], some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], and Rutaceae, where it causes citrus leprosis-like symptoms [@Cook2019; @Velarde2021; @Roy2015; @Roy2020].
-Mechanical transmission of OFV is possible under laboratory conditions to some plants belonging to the plant families Chenopodiaceae, Aizoaceae, Fabaceae, and Solanaceae [@Chang1976; @Kondo2003; @Peng2013].
+More than fifty species of Orchidaceae [@Kitajima2010; @Peng2013] can naturally become infected with OFV, as well as some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], and Rutaceae, where infection causes citrus leprosis-like symptoms [@Cook2019; @Velarde2021; @Roy2015; @Roy2020].
+Mechanical transmission of OFV is possible under laboratory conditions to the plant families Chenopodiaceae, Aizoaceae, Fabaceae, and Solanaceae [@Chang1976; @Kondo2003; @Peng2013].
 
@@
 
-During June 2020, chlorotic ringspot symptoms were observed on Giant Lilyturf *Liriope* spp., cv.
+During June 2020, chlorotic flecks and ringspot patterns of unknown etiology were observed on Giant Lilyturf *Liriope* spp., cv.
 'Gigantea' in a landscape of Leon County, Florida (`r citef("fig_1")`).
@@
 *Liriope* and the closely related *Ophiopogon* (Asparagaceae: Nolinoidaea) are considered the most important ground cover plant in the southeastern United States [@Mcharo2003].
-
 Viral infections of suspected leaf samples were initially tested at the Plant Disease Diagnostic Clinic at the North Florida Research and Education Center (NFREC) in Quincy, FL.
 All the samples were tested with one step conventional RT-PCR, and were found negative for begomovirus, carlavirus, potyvirus, tospovirus, cucumber mosaic virus and tobacco mosaic virus.
-
 As initial diagnostics were inconclusive, samples were taken of putatively infected plants with ringspot symptoms during July and August of 2020.
@@
 Plant materials were sent to the Florida Department of Agriculture and Consumer Services (FDACS) for identification.
-
 The FDACS determined that the pathogen was OFV using previously published primers and methods to conduct RT-PCR and Sanger sequencing [@Kubo2009a; @Kubo2009b; @RamosGonzalez2015].
-OFV Orchid strain 1, (OFV-Orc1), was identified following the methods described in @Kondo2017.
+The identity of the virus was verified as OFV Orchid strain 1, (OFV-Orc1), following the methods described in @Kondo2017.
 Nucleotide sequencing shared 98\% nucleotide identity with the OFV-isolates So (Accession No.
@@
 MK522807), which belong to orchid subgroup I [@Kondo2006; @Kondo2017].
-
 These samples from FDACS were subsequently retested by the USDA-APHIS-PPQ S&T Beltsville laboratory, in conjunction with tests of fresh samples from both Alachua and Leon counties.
-The USDA used RT-PCR, RT-qPCR, and HTS to reconfirm the presence of OFV.
+The USDA used RT-PCR, RT-qPCR, and High Throughput Sequencing (HTS) to reconfirm the presence of OFV.
 Conventional RT-PCR with Generic R2-Dicho-GF and R2-Dicho-GR primers amplifed ~800 nt of L-gene (RNA2) amplicon [@Roy2020], and OFV-Orc1 and OFV-Orc2 were detected in both *O.
@@
 elatior* from Leon County [@Kondo2017] (GenBank Accession Numbers: MZ852004, MZ852005 MZ852006, and MZ852007).
-OFV-Orc1 and OFV-Orc2 share 99% nucleotide sequence identity with their RNA2 genome wheras 90\% nt sequence identity was found between these two reassortment strains.
-
-HTS reaffirmed the presence of OFV-Orc1 and OFV-Orc2 in Leon and Alachua counties (`r citet("tab_1")`).
-HTS results from Leon County revealed that *L.
-muscari* were coinfected with both OFV-Orc1 and OFV-Orc2, while *A.
+99% nucleotide sequence identity is shared between OFV-Orc1 and OFV-Orc2 for the RNA2 genome, whereas 90\% nt sequence identity was found between these two reassortment strains.
+The presence of OFV-Orc1 and OFV-Orc2 in Leon and Alachua counties was reaffirmed with HTS data (`r citet("tab_1")`): Analysis of HTS data from Leon County found that the symptomatic *L.
+muscari* were coinfected with both OFV-Orc1 and OFV-Orc2, while the symptomatic *A.
 elatior* were solely infected with OFV-Orc1.
-HTS of *L.
+Sequence data of symptomatic *L.
 muscari* from Alachua County revealed infections with OFV-Orc2 (GenBank Accession MZ852006).
-
 After the initial identification by FDACS of OFV-Orc, mite samples were collected from symptomatic Asparagaceae in Leon County.
@@
 The commonly used phase-contrast microscopy is insufficient to detect some diagnostic characters for separation of cryptic species, instead best practices recommend the combination of Differential Interference Contrast (DIC) Microscopy and Scanning Electron Microscopy along with molecular methods to separate cryptic species [@Beard2015].
-
 The flat mites collected were initially suspected to belong to *B.
@@
 confusus* Baker.
-
 The recent report of OFV in the US is thought to be @Ko1985 which describes nuclear inclusions caused by an undescribed bacilliform rhabdovirus in *Brassia* orchids.
@@
 californicus* group, referring to @Kondo2003's publication [@Bratsch2015].
-
 Later reports of OFV described OFV infecting a previously undescribed Nolinoidaea hosts in Australia [@Dietzgen2018b; @Mei2016], including *Liriope spicata* (Thunb.) Lour, a different species of liriopogon than those identified from the Florida sites.
@@
 as natural hosts of OFV-Orc.
-
-OFV consists of two orchid strains (OFV-Orc1 and OFV-Orc2) and two citrus strains (OFV-Cit1 and OFV-Cit2) [@Roy2020; @Beltran-Beltran2020].
-The OFV strains detected in Florida are identical in gene order, content, and genome sequence to the orchid strains of OFV infecting citrus in Hawaii, Mexico, Colombia, and South Africa [@Roy2020; @Beltran-Beltran2020].
+There are two orchid strains of OFV (OFV-Orc1 and OFV-Orc2), and two citrus strains (OFV-Cit1 and OFV-Cit2) [@Roy2020; @Beltran-Beltran2020].
+The OFV strains detected in Florida are identical in genome sequence to the orchid strains of OFV infecting citrus in Hawaii, Mexico, Colombia, and South Africa [@Roy2020; @Beltran-Beltran2020].
 Both OFV-Orc1 and OFV-Orc2 infect citrus [@Roy2020], but none of the citrus  strains have been reported from any orchid species.
@@
 Even so, these types of questions require future study to determine the potential of nolinoidaea to citrus transmission.
-
 Best practices for integrated pest management have not been created for controlling *Brevipalpus* mites on these ornamentals, but methods designed to control *Brevipalpus* in other systems may be applicable.
@@
 Moreover, it is often possible to integrate different control techniques for improved management, such as combining predatory mites with compatible acaricides and entomopathogenic fungi [@Reddy2001; @Midthassel2016; @Andrade2019].
-
 In conclusion, detecting OFV in Florida represents a concern for horticulturists who grow orchids, *Liriope*, *Ophiopogon*, or other susceptible Asparagaceae species which are commonly used in landscaping.
@@
 ### Figure captions
-`r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by *Liriope* spp.
-infected with orchid fleck virus (OFV): (a) ringspot symptoms on *Liriope muscari* cv.
-'Gigantea' (b-c) Details of ringspot symptoms on *L.
+`r fig_nums(name = "fig_1", caption = "Variety of symptoms seen on *Liriope* spp.
+infected with orchid fleck virus (OFV): (a) symptoms on *Liriope muscari* cv.
+'Gigantea' (b-c) Details of symptoms on *L.
 muscari* cv.
@@
 
-`r fig_nums(name = "fig_2", caption = "Symptoms expressed by *Aspidistra elatior* infected with OFV: (a) Detail of leaf chlorosis (b) Chlorosis appears similar to sun damage (c-d) Chlorotic ringspot may indicate early symptoms of OFV")`
+`r fig_nums(name = "fig_2", caption = "Symptoms seen on *Aspidistra elatior* infected with OFV: (a) Detail of leaf chlorosis (b) Chlorosis appears similar to sun damage (c-d) Chlorotic flecks may indicate early symptoms of OFV")`
 

### 2021-09-07 ofv_fife_2021.Rmd
fixes from a second proofread

@@
 The USDA used RT-PCR, RT-qPCR, and High Throughput Sequencing (HTS) to reconfirm the presence of OFV.
-Conventional RT-PCR with Generic R2-Dicho-GF and R2-Dicho-GR primers amplifed ~800 nt of L-gene (RNA2) amplicon [@Roy2020], and OFV-Orc1 and OFV-Orc2 were detected in both *O.
+Conventional RT-PCR with Generic R2-Dicho-GF and R2-Dicho-GR primers amplified ~800 nt amplicons of the L-gene (RNA2) [@Roy2020], to detect both OFV-Orc1 and OFV-Orc2 in *O.
 intermedius* and *A.
 elatior* from Leon County [@Kondo2017] (GenBank Accession Numbers: MZ852004, MZ852005 MZ852006, and MZ852007).
-99% nucleotide sequence identity is shared between OFV-Orc1 and OFV-Orc2 for the RNA2 genome, whereas 90\% nt sequence identity was found between these two reassortment strains.
+99% nucleotide sequence identity is shared between OFV-Orc1 and OFV-Orc2 for the RNA2 genome, whereas 90\% sequence identity was found between these two reassortment strains.
 The presence of OFV-Orc1 and OFV-Orc2 in Leon and Alachua counties was reaffirmed with HTS data (`r citet("tab_1")`): Analysis of HTS data from Leon County found that the symptomatic *L.

### 2021-09-07 ofv_fife_2021.Rmd
'The'

@@
 'Gigantea' (Decaisne) Bailey, *Ophiopogon intermedius* Don and *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in Leon and Alachua Counties, FL.
-Orchid-infecting subgroup (Orc) of OFV infects over 50 plant species belonging to the plant families Orchidaceae, Asparagaceae (Nolinoidaea), and causes citrus leprosis disease in *Citrus* (Rutaceae).
+The orchid-infecting subgroup (Orc) of OFV infects over 50 plant species belonging to the plant families Orchidaceae, Asparagaceae (Nolinoidaea), and causes citrus leprosis disease in *Citrus* (Rutaceae).
 The only known vectors of OFV-Orc are the flat mites, *Brevipalpus californicus* (Banks) *sensu lato* (Trombidiformes: Tenuipalpidae).

### 2021-09-07 editorial_reviews/response_editors_ofv_fife_2021_R3.Rmd
addresses concerns from the subject editor

07-Sep-2021

Dear Mr. Fife,

I have reviewed manuscript ID JIPM-2021-0034.R2 entitled "<i>Brevipalpus</i>-transmitted orchid fleck virus infecting three new ornamentals in Florida" which you submitted to the Journal of Integrated Pest Management.  My comments are included at the bottom of this letter.

I suggest some minor revisions to your manuscript, I cannot accept it in it's current state and this will require you to submit a revised version of your manuscript.

Your revised manuscript should be uploaded within 30 days. Please let us know if you will require an extension. The due date is 07-Oct-2021.

To revise your manuscript, log into https://mc.manuscriptcentral.com/jipm and enter your Author Centre, where you will find your manuscript title listed under "Manuscripts with Decisions."  Under "Actions," click on "Create a Revision."  Your manuscript number has been appended to denote a revision.

You may also click the below link to start the revision process.

*** PLEASE NOTE: This is a two-step process. After clicking on the link, you will be directed to a webpage to confirm. ***

[hyperlink removed]

Manuscript revision instructions
• Please ensure your paper follows journal style and requirements as listed in the instructions to authors: https://academic.oup.com/jipm/pages/Manuscript_Preparation
• Please highlight the changes to your manuscript within the document by using the track changes mode in MS Word or by using bold or colored text. Please also include a point-by-point response to reviews as well as a clean version (non-track changes version) of the paper.
• If your paper was created in LaTeX, please upload the PDF along with the tex files.
• Please delete any outdated files (e.g., the original manuscript, any outdated figures, etc.) before uploading the revised files.
• Figures should be submitted as separate files and not inserted into the main document. Figures should be submitted as at least 300 dpi (600 dpi for line graphs) and in one of the following file types: tif, eps, rtf, ppt/pptx, xls/xlsx, editable PDF, ps, psd, ai, gif, or png.

Once again, thank you for submitting your manuscript to the Journal of Integrated Pest Management and I look forward to receiving your revision.

Sincerely,
Dr. Nathan Walker
Subject Editor, Journal of Integrated Pest Management
nathan.walker\@okstate.edu
ESA Editorial Office: 3 Park Place, Suite 307, Annapolis, MD 21401-3722, USA. Editorial Office Phone: 1-301-731-4535.

My Comments to Authors:

Line 40 and throughout the manuscript, not needed hard returns are present and need to be removed.
Lines 49-50 Coinfections were seen in each county, but single strains of OFV-Orc were seen in L. muscari – Can coinfections be seen? Can single strains be seen?  No, symptoms can be and coinfections are determined by analysis.
The Spanish abstract addition is not warranted and I am confused why you added this at this late stage? The staff editors have suggested “So, my suggestion would be just to assume the other [English] abstract is ok.”.
Line 91: ‘OFV is a bacilliform’, here and throughout, while not a big issue generally it is preferred that a sentence is not started with and acronym. Consider ‘The virus is a bacilliform’
Line 94: are the only which have been- consider improving the wording
Line 96: on the infected plant, remove infected
Line 109: conditions to some plants belonging to the [plant] families, I think it is given these are plant families
Lines 135 and 146 you use ‘nucleotide identity’ then you use ‘nt’, which is not defined and there is a typo in ‘wheras’
Line 140: define “HTS”, just because I know what that is in English does not mean someone else will know what that is.
Line 149: HTS results ‘for samples obtained’ from Leon County revealed that L. muscari
Line 199: identical in gene order, content, and genome sequence – I think you mean genome sequence? I am not sure what is meant by gene order and content, it is an identical genome, correct?

Please ensure all authors have reviewed the document.

\newpage

**Response to Decision Letter:**
**This third revision addresses the minor errors described in the decision letter:**

- Line 40 and throughout the manuscript, not needed hard returns are present and need to be removed. $\rightarrow$ removed hard returns

- Lines 49-50 Coinfections were seen in each county, but single strains of OFV-Orc were seen in L. muscari – Can coinfections be seen? Can single strains be seen?  No, symptoms can be and coinfections are determined by analysis. $\rightarrow$ changed to 'detected'

- The Spanish abstract addition is not warranted and I am confused why you added this at this late stage? The staff editors have suggested “So, my suggestion would be just to assume the other [English] abstract is ok.”.

- Line 91: ‘OFV is a bacilliform’, here and throughout, while not a big issue generally it is preferred that a sentence is not started with and acronym. Consider ‘The virus is a bacilliform’ $\rightarrow$ moved acronyms from beginnings of sentences

- Line 94: are the only which have been- consider improving the wording $\rightarrow$ changed to "Only Flat mites (Trombidiformes: Tenuipalpidae) from the genus *Brevipalpus* are known to transmit dichorhaviruses..."

- Line 96: on the infected plant, remove infected $\rightarrow$ removed

- Line 109: conditions to some plants belonging to the [plant] families, I think it is given these are plant families $\rightarrow$ removed redundancy

- Lines 135 and 146 you use ‘nucleotide identity’ then you use ‘nt’, which is not defined and there is a typo in ‘wheras’ $\rightarrow$ clarified, 'nt' is a measurement of the amplicon $\rightarrow$ corrected to 'whereas'

- Line 140: define “HTS”, just because I know what that is in English does not mean someone else will know what that is. $\rightarrow$ changed to "High Throughput Sequencing (HTS)"

- Line 149: HTS results ‘for samples obtained’ from Leon County revealed that L. muscari $\rightarrow$ reworded

- Line 199: identical in gene order, content, and genome sequence – I think you mean genome sequence? I am not sure what is meant by gene order and content, it is an identical genome, correct? $\rightarrow$ removed repeated content

Please ensure all authors have reviewed the document.

**Thank you for your time and patience,**

**-- The Authors**

### 2021-09-07 editorial_reviews/response_editors_ofv_fife_2021_R3.Rmd
added the edits I made, explained our reasonsing for adding the Spanish abstract

@@
 
-- Line 40 and throughout the manuscript, not needed hard returns are present and need to be removed. $\rightarrow$ removed hard returns
+- Line 40 and throughout the manuscript, not needed hard returns are present and need to be removed. $\rightarrow$ **removed hard returns**
 
@@
 No, symptoms can be and coinfections are determined by analysis.
-$\rightarrow$ changed to 'detected'
+$\rightarrow$ **changed to 'detected'**
 
@@
 The staff editors have suggested “So, my suggestion would be just to assume the other [English] abstract is ok.”.
+$\rightarrow$ **the authors added the Spanish abstract in order to be more inclusive of the Latin American researchers who study Orchid fleck virus and similar pathogens in the citrus-growing regions Mexico and South America.
+We believe that the abstract is in compliance with the directions described in the 'Language' section under 'Manuscript Preparation' for the Journal of Integrated Pest Management: https://academic.oup.com/jipm/pages/Manuscript_Preparation, which indicates that a "...A second abstract in a second language is permitted." The authors did not intend to cause concern by adding the abstract at a later stage of editing, because JIPM's Manuscript Preparation page says "Authors are responsible for the accuracy of non-English abstracts".
+The authors believe that our abstract will be found to be an accurate translation, faithful to the English version.**
 
 - Line 91: ‘OFV is a bacilliform’, here and throughout, while not a big issue generally it is preferred that a sentence is not started with and acronym.
-Consider ‘The virus is a bacilliform’ $\rightarrow$ moved acronyms from beginnings of sentences
+Consider ‘The virus is a bacilliform’ $\rightarrow$ **moved acronyms from beginnings of sentences**
 
-- Line 94: are the only which have been- consider improving the wording $\rightarrow$ changed to "Only Flat mites (Trombidiformes: Tenuipalpidae) from the genus *Brevipalpus* are known to transmit dichorhaviruses..."
+- Line 94: are the only which have been- consider improving the wording $\rightarrow$ **changed to "Only Flat mites (Trombidiformes: Tenuipalpidae) from the genus *Brevipalpus* are known to transmit dichorhaviruses..."**
 
@@
 
-- Line 109: conditions to some plants belonging to the [plant] families, I think it is given these are plant families $\rightarrow$ removed redundancy
+- Line 109: conditions to some plants belonging to the [plant] families, I think it is given these are plant families $\rightarrow$ **removed redundancy**
 
-- Lines 135 and 146 you use ‘nucleotide identity’ then you use ‘nt’, which is not defined and there is a typo in ‘wheras’ $\rightarrow$ clarified, 'nt' is a measurement of the amplicon $\rightarrow$ corrected to 'whereas'
+- Lines 135 and 146 you use ‘nucleotide identity’ then you use ‘nt’, which is not defined and there is a typo in ‘wheras’ $\rightarrow$ **clarified, 'nt' is a measurement of the amplicon $\rightarrow$ corrected to 'whereas'**
 
-- Line 140: define “HTS”, just because I know what that is in English does not mean someone else will know what that is. $\rightarrow$ changed to "High Throughput Sequencing (HTS)"
+- Line 140: define “HTS”, just because I know what that is in English does not mean someone else will know what that is. $\rightarrow$ **changed to "High Throughput Sequencing (HTS)"**
 
-- Line 149: HTS results ‘for samples obtained’ from Leon County revealed that L. muscari $\rightarrow$ reworded
+- Line 149: HTS results ‘for samples obtained’ from Leon County revealed that L. muscari $\rightarrow$ **reworded**
 
@@
 I am not sure what is meant by gene order and content, it is an identical genome, correct?
-$\rightarrow$ removed repeated content
+$\rightarrow$ **removed repeated content**
 

### 2021-09-07 editorial_reviews/response_editors_ofv_fife_2021_R3.Rmd
working on formatting

@@
+---
+output: word_document
+---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+```
+
 07-Sep-2021
@@
 Manuscript revision instructions
-• Please ensure your paper follows journal style and requirements as listed in the instructions to authors: https://academic.oup.com/jipm/pages/Manuscript_Preparation
-• Please highlight the changes to your manuscript within the document by using the track changes mode in MS Word or by using bold or colored text.
+
+- Please ensure your paper follows journal style and requirements as listed in the instructions to authors: https://academic.oup.com/jipm/pages/Manuscript_Preparation
+- Please highlight the changes to your manuscript within the document by using the track changes mode in MS Word or by using bold or colored text.
 Please also include a point-by-point response to reviews as well as a clean version (non-track changes version) of the paper.
-• If your paper was created in LaTeX, please upload the PDF along with the tex files.
-• Please delete any outdated files (e.g., the original manuscript, any outdated figures, etc.) before uploading the revised files.
-• Figures should be submitted as separate files and not inserted into the main document.
+- If your paper was created in LaTeX, please upload the PDF along with the tex files.
+- Please delete any outdated files (e.g., the original manuscript, any outdated figures, etc.) before uploading the revised files.
+- Figures should be submitted as separate files and not inserted into the main document.
 Figures should be submitted as at least 300 dpi (600 dpi for line graphs) and in one of the following file types: tif, eps, rtf, ppt/pptx, xls/xlsx, editable PDF, ps, psd, ai, gif, or png.
@@
 
-Line 40 and throughout the manuscript, not needed hard returns are present and need to be removed.
-Lines 49-50 Coinfections were seen in each county, but single strains of OFV-Orc were seen in L.
-muscari – Can coinfections be seen?
+- Line 40 and throughout the manuscript, not needed hard returns are present and need to be removed.
+- Lines 49-50 Coinfections were seen in each county, but single strains of OFV-Orc were seen in *L.
+muscari* – Can coinfections be seen?
 Can single strains be seen?
 No, symptoms can be and coinfections are determined by analysis.
-The Spanish abstract addition is not warranted and I am confused why you added this at this late stage?
+- The Spanish abstract addition is not warranted and I am confused why you added this at this late stage?
 The staff editors have suggested “So, my suggestion would be just to assume the other [English] abstract is ok.”.
-Line 91: ‘OFV is a bacilliform’, here and throughout, while not a big issue generally it is preferred that a sentence is not started with and acronym. Consider ‘The virus is a bacilliform’
-Line 94: are the only which have been- consider improving the wording
-Line 96: on the infected plant, remove infected
-Line 109: conditions to some plants belonging to the [plant] families, I think it is given these are plant families
-Lines 135 and 146 you use ‘nucleotide identity’ then you use ‘nt’, which is not defined and there is a typo in ‘wheras’
-Line 140: define “HTS”, just because I know what that is in English does not mean someone else will know what that is.
-Line 149: HTS results ‘for samples obtained’ from Leon County revealed that L. muscari
-Line 199: identical in gene order, content, and genome sequence – I think you mean genome sequence? I am not sure what is meant by gene order and content, it is an identical genome, correct?
+- Line 91: ‘OFV is a bacilliform’, here and throughout, while not a big issue generally it is preferred that a sentence is not started with and acronym. Consider ‘The virus is a bacilliform’
+- Line 94: are the only which have been- consider improving the wording
+- Line 96: on the infected plant, remove infected
+- Line 109: conditions to some plants belonging to the [plant] families, I think it is given these are plant families
+- Lines 135 and 146 you use ‘nucleotide identity’ then you use ‘nt’, which is not defined and there is a typo in ‘wheras’
+- Line 140: define “HTS”, just because I know what that is in English does not mean someone else will know what that is.
+- Line 149: HTS results ‘for samples obtained’ from Leon County revealed that *L. muscari*
+- Line 199: identical in gene order, content, and genome sequence – I think you mean genome sequence? I am not sure what is meant by gene order and content, it is an identical genome, correct?
 
@@
 
-- Lines 49-50 Coinfections were seen in each county, but single strains of OFV-Orc were seen in L.
-muscari – Can coinfections be seen?
+- Lines 49-50 Coinfections were seen in each county, but single strains of OFV-Orc were seen in *L.
+muscari* – Can coinfections be seen?
 Can single strains be seen?
@@
 
-- Line 149: HTS results ‘for samples obtained’ from Leon County revealed that L. muscari $\rightarrow$ **reworded**
+- Line 149: HTS results ‘for samples obtained’ from Leon County revealed that *L. muscari* $\rightarrow$ **reworded**
 

### 2021-09-09 ofv_fife_2021.Rmd
reworded the sentence on Brevipalpus being the sole vector for OFV
Caught citation error, first author was Peng

@@
 The virus is a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018].
-Flat mites from the genus *Brevipalpus* (Trombidiformes: Tenuipalpidae) are the only which have been experimentally shown to transmit dichorhaviruses [@Maeda1998].
+Only Flat mites (Trombidiformes: Tenuipalpidae) from the genus *Brevipalpus* are known to transmit dichorhaviruses [@Maeda1998].
 Plants infected with OFV exhibit chlorotic and necrotic flecks on their leaves[@Kubo2009a; @Kubo2009b; @Dietzgen2018b].
@@
 elatior* nor other Nolinoidaea in the US.
-Although @Zheng2013 had mentioned an association between *B.
+Although @Peng2013 had mentioned an association between *B.
 californicus* and *A.

### 2021-09-21 ofv_fife_2021.Rmd
updated section title, it doesn't reflect a description of the mite, just describes relationships
Updated to reflect editorial comments

@@
   word_document:
-    reference_docx: ../r-word-templates/word-template-jis.docx
+    reference_docx: word-template-jis.docx
 # - html_document
@@
 
-#### Mite Description
+#### A comment on the the status of *Brevipalpus* in Florida
 
@@
 Both OFV-Orc1 and OFV-Orc2 infect citrus [@Roy2020], but none of the citrus  strains have been reported from any orchid species.
-The *Brevipalpus* mites collected from liriopogons and *A.
-elatior* in Leon County were abundant on OFV-infected plants very near to citrus trees, some plants even surrounding the trunk.
-*B.
-californicus* s.
-l.
-has been reported as a pest of citrus [@Childers2003] and are often collected from citrus fruits [@Vacante2016; @Vacante2010; @Baker1987; @Baker1949].
-The proximity of these mite vectors to citrus raises the question: why these trees are not currently infected with OFV-Orc?
 It is important to note the uncertainty surrounding the vector for OFV-Orc.
@@
 californicus* has been described as a vector of OFV.
-Even so, the *B.
-californicus* which we find on liriopogons and *A.
-elatior* may not be the same cryptic species as those found on citrus.
-Transmission of OFV from populations of *B.
-californicus* liriopogon/*A.
-elatior* to citrus may be limited by host preferences, vectorial capacity, viral propagation/circulation in the vector, viral acquisition times, or feeding times required for transmission to citrus.
 Even so, these types of questions require future study to determine the potential of nolinoidaea to citrus transmission.
@@
 reticulata* (mandarin) and *C.
-jambhiri* (rough lemon) associated with leprosis-like symptoms highlights the potential threat of different isolates of OFV on citrus, which will be a definite concern to the US multi-billion-dollar citrus industry already impacted by the Huanglongbing disease.
+jambhiri* (rough lemon) associated with leprosis-like symptoms highlights the potential threat of different isolates of OFV on citrus.
 *B.

### 2021-10-04 ofv_fife_2021.Rmd
minor tweaks to fix bibliography citation links

@@
 Only Flat mites (Trombidiformes: Tenuipalpidae) from the genus *Brevipalpus* are known to transmit dichorhaviruses [@Maeda1998].
-Plants infected with OFV exhibit chlorotic and necrotic flecks on their leaves[@Kubo2009a; @Kubo2009b; @Dietzgen2018b].
+Plants infected with OFV exhibit chlorotic and necrotic flecks on their leaves[@Kubo2009; @Kubo2009a; @Dietzgen2018].
 The virus was first described as infecting *Cymbidium* orchids in Japan [@Doi1977].
 There have been reports of OFV and OFV-like rhabdoviruses infecting orchids in Asia, Africa, North America, South America, Europe, and Oceania.
-The prevalence of OFV and its mite vector is thought to be associated with the movement of infected orchids [@Dietzgen2018a].
-More than fifty species of Orchidaceae [@Kitajima2010; @Peng2013] can naturally become infected with OFV, as well as some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], and Rutaceae, where infection causes citrus leprosis-like symptoms [@Cook2019; @Velarde2021; @Roy2015; @Roy2020].
+The prevalence of OFV and its mite vector is thought to be associated with the movement of infected orchids [@Dietzgen2018].
+More than fifty species of Orchidaceae [@Kitajima2010; @Peng2013] can naturally become infected with OFV, as well as some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018a], and Rutaceae, where infection causes citrus leprosis-like symptoms [@Cook2019; @Velarde2021; @Roy2015; @Roy2020].
 Mechanical transmission of OFV is possible under laboratory conditions to the plant families Chenopodiaceae, Aizoaceae, Fabaceae, and Solanaceae [@Chang1976; @Kondo2003; @Peng2013].
@@
 Plant materials were sent to the Florida Department of Agriculture and Consumer Services (FDACS) for identification.
-The FDACS determined that the pathogen was OFV using previously published primers and methods to conduct RT-PCR and Sanger sequencing [@Kubo2009a; @Kubo2009b; @RamosGonzalez2015].
+The FDACS determined that the pathogen was OFV using previously published primers and methods to conduct RT-PCR and Sanger sequencing [@Kubo2009; @Kubo2009a; @RamosGonzalez2015].
 The identity of the virus was verified as OFV Orchid strain 1, (OFV-Orc1), following the methods described in @Kondo2017.
@@
 californicus* group, referring to @Kondo2003's publication [@Bratsch2015].
-Later reports of OFV described OFV infecting a previously undescribed Nolinoidaea hosts in Australia [@Dietzgen2018b; @Mei2016], including *Liriope spicata* (Thunb.) Lour, a different species of liriopogon than those identified from the Florida sites.
+Later reports of OFV described OFV infecting a previously undescribed Nolinoidaea hosts in Australia [@Dietzgen2018a; @Mei2016], including *Liriope spicata* (Thunb.) Lour, a different species of liriopogon than those identified from the Florida sites.
 We are not aware of any reports of OFV infecting liriopogons, *A.

### 2021-10-04 editorial_reviews/response_editors_ofv_fife_2021_R3.Rmd
added bold to a line
added an explanation for deleting some stuff, and added new line at the end of the file

@@
 
-- Line 96: on the infected plant, remove infected $\rightarrow$ removed
+- Line 96: on the infected plant, remove infected $\rightarrow$ **removed**
 
@@
 Please ensure all authors have reviewed the document.
+$\rightarrow$ **All authors have reviewed the document, some sections which implied that OFV may pose a risk to citrus were removed and/or reworded to avoid speculation, as per the request of the review board of one of the authors.**
 

### 2021-10-07 ofv_fife_2021.Rmd
complying with review boards and editor comments
added recommended edits

@@
 They also discuss the association of OFV with *Brevipalpus* mites, but the authors did not make a conclusive species identification beyond suggesting that the mite vector belonged to the *B.
-californicus* group, referring to @Kondo2003's publication [@Bratsch2015].
+californicus* group, referring to @Kondo2003.
 Later reports of OFV described OFV infecting a previously undescribed Nolinoidaea hosts in Australia [@Dietzgen2018a; @Mei2016], including *Liriope spicata* (Thunb.) Lour, a different species of liriopogon than those identified from the Florida sites.
@@
 Best practices for integrated pest management have not been created for controlling *Brevipalpus* mites on these ornamentals, but methods designed to control *Brevipalpus* in other systems may be applicable.
-The most common method used to control *Bervipalpus* are synthetic acaricides [@Andrade2010; @Andrade2019].
+The most common method used to control *Bervipalpus* are synthetic acaricides, such as spirodiclofen and cyflumetofen [@Vechia2018; @Andrade2010; @Andrade2019].
 Unfortunately, some acaricides and their residues can harm beneficial predatory mites as well [@Fernandez2017], even at low doses [@Havasi2021], and mixing different chemistries can be detrimental for mite control [@Vechia2018].
-In addition, pesticide resistance has been reported in various *Brevipalpus* populations [@Rocha2021; @Alves2000; @Campos2002; @Omoto2000], due to exposure to pesticides used to control other arthropod pests [@Vechia2021].
-In addition, predatory mites [@Argolo2020; @Chen2006], entomopathogenic fungi [@RossiZalaf2008; @Magalhaes2005; @Pena2015; @Revynthi2019] have shown promise for controlling other *Brevipalpus* mites.
+Furthermore, pesticide resistance has been reported in various *Brevipalpus* populations [@Rocha2021; @Alves2000; @Campos2002; @Omoto2000], due to exposure to pesticides used to control other arthropod pests [@Vechia2021].
+In addition, phytoseiid predatory mites such as *Amblyseius largoensis* (Muma) and *Galendromus helveolus* (Chant) [@Argolo2020; @Chen2006], entomopathogenic fungi [@RossiZalaf2008; @Magalhaes2005; @Pena2015; @Revynthi2019] have shown promise for controlling other *Brevipalpus* mites.
 Moreover, it is often possible to integrate different control techniques for improved management, such as combining predatory mites with compatible acaricides and entomopathogenic fungi [@Reddy2001; @Midthassel2016; @Andrade2019].
@@
 Citrus leprosis was present in Florida during the 1860’s and almost eradicated by the mid-1960s [@Childers2003; @Knorr1968a; @Knorr1968b].
-An examination of herbarium specimens of Florida citrus found that this historical virus, Citrus leprosis dichorhavirus-N0, is distantly related to the modern isolates of OFV [@Hartung2015; @Kitajima2011a; @Roy2020].
+An examination of herbarium specimens of Florida citrus found that one strain of this historical virus, Citrus leprosis dichorhavirus-N0, is distantly related to the modern isolates of OFV [@Hartung2015; @Kitajima2011a; @Roy2020].
 The recent detection of OFV-Orc1 in South Africa [@Cook2019] in *C.

### 2021-10-07 ofv_fife_2021.Rmd
most recent version

@@
 Best practices for integrated pest management have not been created for controlling *Brevipalpus* mites on these ornamentals, but methods designed to control *Brevipalpus* in other systems may be applicable.
-The most common method used to control *Bervipalpus* are synthetic acaricides, such as spirodiclofen and cyflumetofen [@Vechia2018; @Andrade2010; @Andrade2019].
+The most common method used to control *Bervipalpus* are synthetic acaricides, such as spirodiclofen and cyflumetofen [@Vechia2018; @Andrade2010; @Andrade2019; @Leeuwen2015].
 Unfortunately, some acaricides and their residues can harm beneficial predatory mites as well [@Fernandez2017], even at low doses [@Havasi2021], and mixing different chemistries can be detrimental for mite control [@Vechia2018].
@@
 ex Rolfe].
-Citrus leprosis was present in Florida during the 1860’s and almost eradicated by the mid-1960s [@Childers2003; @Knorr1968a; @Knorr1968b].
+Furthermore, Citrus Leprosis was present in Florida during the 1860’s and almost eradicated by the mid-1960s [@Childers2003; @Knorr1968a; @Knorr1968b].
 An examination of herbarium specimens of Florida citrus found that one strain of this historical virus, Citrus leprosis dichorhavirus-N0, is distantly related to the modern isolates of OFV [@Hartung2015; @Kitajima2011a; @Roy2020].
